### 2016-11-16 src/abstract.tex
abstract

The \textsc{maximum carpool matching} problem is a star packing problem in
directed graphs.
Formally, given a directed graph $G = (V, E)$,
a capacity function $ c: V \rightarrow \N $,
and a weight function $w : E \rightarrow \R $,
a feasible \emph{carpool matching} is a triple 
$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
and $M$ is a subset of $E \cap (P \times D)$,
under the constraints that for every vertex $d \in D$, 
$\din(d) \leq c(d)$, 
and for every vertex $p \in P$, $\dout(p) \leq 1$.
In the \textsc{maximum carpool matching} 
problem we seek for a matching $(P, D, M)$ that maximizes the total weight of $M$.

The problem arises when designing an online carpool service, 
such as Zimride~\cite{zimride}, 
that tries to connect between passengers and drivers based on (arbitrary) similarity function.
The problem is known to be NP-hard, 
even for undirected graphs, uniform weights and without capacity constraints.

We present a $2$-approximation algorithm for the problem,
the currnet best known approximation ratio.
Also, when the maximum capacity, $C$, is constant we give a
$\frac{C + 1}{2C}$-approximation algorithms for the 
unweighted variant of the problem, 
improving over the bset known approximation ratio for the special case where $C = 2$.

### 2016-11-16 src/abstract.tex
intro

@@
-The \textsc{maximum carpool matching} problem is a star packing problem in
+The \textsc{\CARPOOL{}} problem is a star packing problem in
 directed graphs.
@@
 and for every vertex $p \in P$, $\dout(p) \leq 1$.
-In the \textsc{maximum carpool matching} 
+In the \textsc{\CARPOOL{}} 
 problem we seek for a matching $(P, D, M)$ that maximizes the total weight of $M$.

### 2016-11-16 src/intro.tex
intro

Carpooling, is the sharing of car journeys so that more than one person travels
in a car.
Knapen et al.~\cite{knapen2013estimating} describe an automatic service
to match commuting trips.
Users of the services register their personal profile and a set of periodically
recurring trips, 
and the service advises registered candidates on how to combine their commuting
trips by carpooling.
The services acts in two phases.

On the first phase, the service estimate the probability that a person $a$
traveling in person's $b$ car will be satisfied from the trip.
This is done based on personal information and feedback from users on past
rides.
The second phase is about finding a carpool matching
that maximizes the global (total expected) satisfaction.

The second phase can be modeled in terms of graph theory.
Given a directed graph $G = (V, E)$.
Each vertex $v \in V$ corresponds to a user of the service and an arc
$(u, v)$ exists if the user corresponded to vertex $u$ is willing to
commute with the user corresponded to vertex $v$.
A capacity function $ c: V \rightarrow \N $ is defined
according to the number of passengers each user can drive if she was
selected as a driver.
A weight function $w : E \rightarrow \R $ defines the amount of
satisfaction $w(u, v)$,
that user $u$ gains when riding with user $v$.

A feasible \emph{carpool matching} (matching) is a triple 
$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
and $M$ is a subset of $E \cap (P \times D)$,
under the constraints that for every driver $d \in D$, 
$\din(d) \leq c(d)$, 
and for every passenger $p \in P$, ${\dout(p) \leq 1}$.
In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
total weight of $M$.
In other words, the \textsc{\CARPOOL{}} problem is about finding a set of 
(directed toward the center) vertex disjoint stars 
that maximizes the total weights on the edges.
Figure~\ref{fig:carpool} is an example of the \textsc{\CARPOOL{}} problem.
\begin{figure}
\centering
\input{fig-carpool}
\caption[]{
\label{fig:carpool}
A carpool matching example: 
\subref{subfloat:input} 
a directed graph with capacities on the vertices and weights on the edges. 
\subref{subfloat:output}
a feasible matching with total weight of 26.
$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
}
\end{figure}

Hartman et al.~\cite{hartman2013optimal} proved that the
\emph{\CARPOOL{}} problem considered in this paper is NP-hard,
and that the problem remains NP-hard even for a binary weight function when
the capacity function $c(v) \leq 2$ for every vertex in $V$.
It is also worth mentioning, that in the undirected, uncapacitated, unweighted
variant of the problem, the set of drivers, in an optimal solution,
form a minimum dominating set.
When the set of drivers is known in advanced, however, the problem becomes
tractable and can be solved using a reduction to a flow network.

Agatz et al. outlined the optimization challenges that arise 
when developing technology to support ride-sharing and survey the
related operations research models in the academic literature~\cite{agatz2012optimization}.  
Hartman et al. designed several heuristics algorithms for the 
\CARPOOL{} problem and compared 
their performance on real data~\cite{hartman2014theory}.
Other heuristics algorithms were developed as well~\cite{knapen2014exploiting}.
Arkin et al, considered other variants of capacitated star packing where
a capacity vector is given as part of the input and 
capacities are needed to be assigned to vertices~\cite{arkin2004approximations}.

Nguyen et al.~\cite{nguyen2008approximating} considered the \textsc{spanning star forest} problem
(the undirected, uncapacitated, unweighted variant of the problem).
They proved the following results:
\begin{inparaenum}
\item
there is a polynomial-time approximation scheme for planner graphs;
\item 
there is a polynomial-time $\frac{3}{5}$-approximation algorithm for graphs;
\item 
there is a polynomial-time $\frac{1}{2}$-approximation algorithm for weighted graphs.
\end{inparaenum}
They also showed how to apply the spanning star forest model to aligning multiple
genomic sequences over a tandem duplication region.
Chen et al.~\cite{chen2007improved} improved the approximation ratio to 0.71,
and also gave showed the the problem can not be approximated to within a factor of
$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ under the assumption 
that $\text{P} \neq \text{NP}$.
None of the technique used to address the \textsc{spanning star forest} problem
can be generalized to the directed capacitated variant.

In Section~\ref{sec:fixed} we discuss how the problem can be solved efficiently,
when $P$ and $D$ are given.
In Section~\ref{sec:uwcm} we describe a 2-approximation algorithm for the
unweighted variant of the problem.
In Section~\ref{sec:ucudcm} we describe a 2-approximation algorithm
for the uncapacitated variant of the problem. 
In Section~\ref{sec:cm} we present a 3-approximation
algorithm for the general problem. 
These are the first known approximation algorithms for any variant of the problem.
Finlay, in Section~\ref{sec:hardness}, we show that the problem is APX-hard.

### 2016-11-16 src/intro.tex
writing local

@@
 
-In Section~\ref{sec:fixed} we discuss how the problem can be solved efficiently,
-when $P$ and $D$ are given.
-In Section~\ref{sec:uwcm} we describe a 2-approximation algorithm for the
-unweighted variant of the problem.
-In Section~\ref{sec:ucudcm} we describe a 2-approximation algorithm
-for the uncapacitated variant of the problem. 
-In Section~\ref{sec:cm} we present a 3-approximation
-algorithm for the general problem. 
-These are the first known approximation algorithms for any variant of the problem.
-Finlay, in Section~\ref{sec:hardness}, we show that the problem is APX-hard.
+\todo{outline}

### 2016-11-16 src/local.tex
writing local

In this section we consider the unweighted variants of the problem.
We describe and analyze a local search algorithm, 
and show that when the maximum possible capacity, $C$, is fixed, the algorithm achieves 
a $\frac{C + 1}{2C}$ approximation ratio.
Throughout this section we consider $C$ to be fixed, and $k$ to be a fixed parameter.

The local search algorithm maintains a feasible matching throughout its execution
and operates in 
iterative manner where in each iteration it tries to find a better solution by
replacing a subset of the edges in the current solution with 
another (larger) subset of edges not in the solution.
The local search algorithm halts when no improvement can be done.
The algorithm is described in Algorithm~\ref{alg:local}

\begin{algorithm}
\SetKw{True}{true}
\SetKw{False}{false}
\KwIn{$G = (V, E)$, $c : V \rightarrow \N$, $k$}
\KwOut{$M$}
$M \leftarrow \emptyset$								\\
\Repeat{done}{
\label{line:outerloop}
 	$done \leftarrow{}$ \True							\\
 	\For{$M' \in M : |M'| \leq Ck$}{
 		\For{$V' \in V \setminus M : |V'| = |M'| + 1$}{
			\If{$M \setminus M' \cup V'$ is feasible}{
				$M \leftarrow{} M \setminus M' \cup V'$	\\
				$done \leftarrow{}$ \False				\\
			}
		}
 	}
}
\Return{$M$}

\caption{
\label{alg:local}
Local Search}
\end{algorithm}

We claim that the local search algorithm halts in polynomial time.
Observed that in every iteration the algorithm either improves the value of the solution
by one or otherwise it terminates. 
Thus, after a maximum of $n$ iterations the algorithm stops.
In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
both these operations can be done in polynomial time.

### 2016-11-16 src/local.tex
going home

@@
 both these operations can be done in polynomial time.
+
+To analyze the approximation ratio achieved by the local search algorithm consider an 
+arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
+where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
+Given the solution outputted by the local search algorithm, 
+define the following graph $L = (\{v_i : s_i \in M^* \}, E)$ 
+where $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
+That is, each vertex in $L$ corresponds to a star in $M^*$ and there is an edge 
+between two vertices if and only if there is an edge $(u,v)$ in $M$ connecting the two 
+corresponded stars.
+Denote by $d^*_i$ the sum of the degrees in $s_i$, and by $d_i$ the sum of the degrees of 
+edges from $M$ intersected with $s_i$. \todo{better define this last line}
+\todo{add an illustration}

### 2016-11-16 src/local.tex
fig-conflict

--- 2016-11-16 src/local.tex
@@
 In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
-both these operations can be done in polynomial time.
+both these operations can be done in polynomial time - $O(n^{Ck + 1})$.
+
+To analyze the approximation ratio achieved by the local search algorithm consider an 
+arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
+where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
+Given the solution outputted by the local search algorithm,
+we build the \emph{conflict graph} of the two solutions in which each node
+represents a star from the optimal solution and edges exits between two nodes if
+the local search solution has at least one edge that connects two stars, formally 
+$G_\text{conflict} = (V, E)$ 
+where $\{v_i : s_i \in M^* \}$ 
+and $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
+Denote by $d^*_i$ the sum of the vertex degree of the optimal solution in $s_i$, 
+and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.
+
+\begin{figure}[h]
+\centering
+\input{fig-conflict}
+\caption[]{
+\label{fig:carpool}
+A carpool matching example: 
+\subref{subfloat:input} 
+a directed graph with capacities on the vertices and weights on the edges. 
+\subref{subfloat:output}
+a feasible matching with total weight of 26.
+$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
+}
+\end{figure}

### 2016-11-16 src/local.tex
going to sleep

@@
 and $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
+Figure~\ref{fig:conflict} depicts this concept.
 Denote by $d^*_i$ the sum of the vertex degree of the optimal solution in $s_i$, 
@@
 \caption[]{
-\label{fig:carpool}
-A carpool matching example: 
+\label{fig:conflict}
 \subref{subfloat:input} 
-a directed graph with capacities on the vertices and weights on the edges. 
+An optimal matching depicted by the dashed red edges,
+and another solution depicted by the solid green edges.  
 \subref{subfloat:output}
-a feasible matching with total weight of 26.
-$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
+The conflict graph, the upper left vertex corresponds 
+to the star that contains the vertices a,b,c.
+The numbers inside the vertices corresponds to $d_i$.   
 }

### 2016-11-18 src/abstract.tex
foo

@@
-The \textsc{\CARPOOL{}} problem is a star packing problem in
-directed graphs.
-Formally, given a directed graph $G = (V, E)$,
+The \textsc{\CARPOOL{}} problem is a star packing problem in directed graphs.
+Formally, given a directed graph $G = (V, A)$,
 a capacity function $ c: V \rightarrow \N $,
-and a weight function $w : E \rightarrow \R $,
+and a weight function $w : A \rightarrow \R $,
 a feasible \emph{carpool matching} is a triple 
-$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
-and $M$ is a subset of $E \cap (P \times D)$,
+$(P, D, M)$, where $P$ (passengers) and $D$ (drivers) form a partition of $V$, 
+and $M$ is a subset of $A \cap (P \times D)$,
 under the constraints that for every vertex $d \in D$, 
@@
 and for every vertex $p \in P$, $\dout(p) \leq 1$.
-In the \textsc{\CARPOOL{}} 
-problem we seek for a matching $(P, D, M)$ that maximizes the total weight of $M$.
+In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
+total weight of $M$.
 
@@
 The problem is known to be NP-hard, 
-even for undirected graphs, uniform weights and without capacity constraints.
+even for uniform weights and without capacity constraints.
 
-We present a $2$-approximation algorithm for the problem,
-the currnet best known approximation ratio.
-Also, when the maximum capacity, $C$, is constant we give a
-$\frac{C + 1}{2C}$-approximation algorithms for the 
-unweighted variant of the problem, 
-improving over the bset known approximation ratio for the special case where $C = 2$.
+we show that the problem can be formulated as
+unconstarints submodular maximization problem, 
+thus it has a 2-approximation algorithm.
+For the unweighted variant of the problem when the maximum possible capacity, $C$, is
+fixed, we give a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm
+for the any $\varepsilon > 0$.

### 2016-11-18 src/in/title.tex
going to think

\title{Improved Approximation Algorithms for the Maximum Carpool Matching
Problme}

\date{}

### 2016-11-18 src/local.tex
going to think

@@
 and show that when the maximum possible capacity, $C$, is fixed, the algorithm achieves 
-a $\frac{C + 1}{2C}$ approximation ratio.
+a $\frac{C + 1}{2C} - \varepsilon$ 
+approximation ratio for any $\varepsilon > 0$.
 Throughout this section we consider $C$ to be fixed, and $k$ to be a fixed parameter.
@@
 \SetKw{False}{false}
-\KwIn{$G = (V, E)$, $c : V \rightarrow \N$, $k$}
+\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
 \KwOut{$M$}
@@
  	$done \leftarrow{}$ \True							\\
- 	\For{$M' \in M : |M'| \leq Ck$}{
- 		\For{$V' \in V \setminus M : |V'| = |M'| + 1$}{
-			\If{$M \setminus M' \cup V'$ is feasible}{
-				$M \leftarrow{} M \setminus M' \cup V'$	\\
+ 	\For{$M' \in M : |M'| \leq k$}{
+ 		\For{$A' \in A \setminus M : |A'| = |M'| + 1$}{
+			\If{$M \setminus M' \cup A'$ is feasible}{
+				$M \leftarrow{} M \setminus M' \cup A'$	\\
 				$done \leftarrow{}$ \False				\\
@@
 In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
-both these operations can be done in polynomial time - $O(n^{Ck + 1})$.
+both these operations can be done in polynomial time - $O(n^{k + 1})$.
 
@@
 and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.
+\todo{define this well}
 
@@
 \end{figure}
+
+\todo{can I state the observation for any component of size at most (least)
+$s$ ?? or does it have to be exavtly of size $s$ ?}
+\begin{observation}
+Let $U = \{v_1 \ldots v_s\}$ be the vertices of any connected component in
+$G^{M^*}_M$ then $\frac{w(U)}{w^*(U)}$
+\end{observation}

### 2016-11-20 src/local.tex
trying to merge

--- 2016-11-16 src/local.tex
@@
 The local search algorithm halts when no improvement can be done.
-The algorithm is described in Algorithm~\ref{alg:local}
+The algorithm is described in Algorithm~\ref{alg:local}.
 
@@
 
-We claim that the local search algorithm halts in polynomial time.
+We claim that the local search algorithm terminates in polynomial time.
 Observed that in every iteration the algorithm either improves the value of the solution
-by one or otherwise it terminates. 
-Thus, after a maximum of $n$ iterations the algorithm stops.
-In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
-both these operations can be done in polynomial time - $O(n^{Ck + 1})$.
+by one or otherwise it stops. 
+Thus the algorithm stops after $n$ iterations at most.
+Finally, 
+in every iteration we examine all the subsets of edges of a fixed size 
+and test for feasibility.
+Both these operations can be done in polynomial time - $O(n^{Ck + 1})$.
 
-To analyze the approximation ratio achieved by the local search algorithm consider an 
-arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
-where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
-Given the solution outputted by the local search algorithm,
-we build the \emph{conflict graph} of the two solutions in which each node
-represents a star from the optimal solution and edges exits between two nodes if
-the local search solution has at least one edge that connects two stars, formally 
-$G_\text{conflict} = (V, E)$ 
-where $\{v_i : s_i \in M^* \}$ 
-and $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
-Denote by $d^*_i$ the sum of the vertex degree of the optimal solution in $s_i$, 
-and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.
+For two sets of stars $S^*, S$ on a common ground set of vertices $V(G)$,
+define the conflict graph $G^{S^*}_{S} = (V, E)$
+where $V = \{v_i : s_i \in S^*\}$, 
+and $E = \{(v_i, v_j) : 
+\exists s \in S : 
+\{v_i, v_j\} \subseteq V(s) 
+\}$.
+Let $w^*(v_i) = 2|E(s_i|$, 
+and let $w(v_i)$ be the sum of degrees (in and out) induced by $S$ on vertices in $s_i$. 
+That is, the stars in $S^*$ define the vertices in the conflict graph,
+and two vertices in the conflict graph are adjacent if there is a star in 
+$S$ that intersect the two corresponded stars in $G$.
+Figure~\ref{fig:conflict} depicts these concepts.
 
@@
 \centering
-\input{fig-conflict}
+\subfloat[]{
+\label{subfloat:graph}
+\input{fig-sub-graph}
+}
+\subfloat[]{
+\label{subfloat:conflict}
+\input{fig-sub-conflict}
+}
 \caption[]{
-\label{fig:carpool}
-A carpool matching example: 
-\subref{subfloat:input} 
-a directed graph with capacities on the vertices and weights on the edges. 
-\subref{subfloat:output}
-a feasible matching with total weight of 26.
-$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
+\label{fig:conflict}
+\subref{subfloat:graph}
+Two sets of stars, 
+$S^* = \{\{a,b,c\}, \{d,e,f\}, \{h,i,j\}, \{k,l\}\}$, 
+$S = \{\{a,h\}, \{c,j\}, \{b,e\}\}$ 
+\subref{subfloat:conflict}
+The conflict graph $G^{S^*}_{S}$, the upper left vertex corresponds 
+to the star \{a,b,c\}.
+The numbers on each vertex $v$ represent the value of $w(v)$.
 }
 \end{figure}
+
+It is easy to verify the following observation regarding the conflict graph.
+
+\begin{observation}  
+The degree of every vertex $v \in V$ is at most $w(v)$.
+\end{observation}
+
+For a subset $U \subset V$ let $S^*(U)$ be the set of stars corresponds to 
+the vertices in $U$,
+$V_U = V(S^*(U))$,
+$\overline{V_U} = V(G) \setminus V_U$,
+$E^{S^*}_U = E(S^*) \cap V_U \times V_U$,
+and 
+$E^{S}_U = E(S) \cap V_U \times V_U$.
+When $U$ is the set of vertices of a maximal connected component of a conflict graph,
+then it is easy to verify that the following observations hold.
+
+\begin{observation}  
+$|E^{S}_U| = \frac{1}{2} \sum_{u \in U} w(u)$.
+\end{observation}
+
+\begin{observation}  
+$|E^{S^*}_U| = \frac{1}{2} \sum_{u \in U} w^*(u) \leq |U| \cdot C$.
+\end{observation}
+
+Let $M^*$ be an arbitrary but fixed optimal star family in $G$, 
+and let $M$ be the output of the local search algorithm,  
+and consider the conflict graph $G^{M^*}_M = (V,E)$,
+and let $U$ denote the vertices of a maximal connected component in $G^{M^*}_M$
+of size at most $|U| \leq k$ then the following holds:
+
+\begin{observation}
+$w^*(U) = w(U)$.
+\end{observation}
+
+\begin{proof}
+Clearly, $E(S) \cap  V_U \times \overline{V_U} = \emptyset$,
+or else this is not a maximal connected component in $G^{M^*}_M$.
+If $w^*(U) \neq w(U)$ 
+the local search algorithm can improve the solution by
+replacing the edges $E^{S}_U$ with the edges $E^{S^*}_U$. 
+\end{proof}
+
+Let $U$, now, represent the vertices of any connected subgraph of $G^{M^*}_M$
+of size $k$, then:
+
+\begin{observation}
+$w^*(U) = w(U)$.
+\end{observation}
+
+\begin{theorem}
+The local search is a $\frac{C + 1}{2C}$-approximation algorithm.
+\end{theorem}
+
+\begin{proof}
+Let $M^*$ be an arbitrary but fixed optimal matching and let $M$ be the matching from the 
+local search algorithm.
+Consider the conflict graph.
+\end{proof}

### 2016-11-20 src/intro.tex
fig-conflict

@@
 to match commuting trips.
-Users of the services register their personal profile and a set of periodically
+Users of the service register their personal profile and a set of periodically
 recurring trips, 
@@
 trips by carpooling.
-The services acts in two phases.
+The service acts in two phases.
 
-On the first phase, the service estimate the probability that a person $a$
-traveling in person's $b$ car will be satisfied from the trip.
+In the first phase, the service estimates the probability that a person $a$
+traveling in person's $b$ car will be satisfied by the trip.
 This is done based on personal information and feedback from users on past
@@
 The second phase can be modeled in terms of graph theory.
-Given a directed graph $G = (V, E)$.
+Given a directed graph $G = (V, A)$.
 Each vertex $v \in V$ corresponds to a user of the service and an arc
-$(u, v)$ exists if the user corresponded to vertex $u$ is willing to
-commute with the user corresponded to vertex $v$.
+$(u, v)$ exists if the user corresponding to vertex $u$ is willing to
+commute with the user corresponding to vertex $v$.
 A capacity function $ c: V \rightarrow \N $ is defined
@@
 selected as a driver.
-A weight function $w : E \rightarrow \R $ defines the amount of
+A weight function $w : A \rightarrow \R $ defines the amount of
 satisfaction $w(u, v)$,
@@
 $(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
-and $M$ is a subset of $E \cap (P \times D)$,
+and $M$ is a subset of $A \cap (P \times D)$,
 under the constraints that for every driver $d \in D$, 
@@
 (directed toward the center) vertex disjoint stars 
-that maximizes the total weights on the edges.
+that maximizes the total weights on the arcs.
 Figure~\ref{fig:carpool} is an example of the \textsc{\CARPOOL{}} problem.
+
 \begin{figure}
@@
 \subref{subfloat:input} 
-a directed graph with capacities on the vertices and weights on the edges. 
+a directed graph with capacities on the vertices and weights on the arcs. 
 \subref{subfloat:output}
@@
 It is also worth mentioning, that in the undirected, uncapacitated, unweighted
-variant of the problem, the set of drivers, in an optimal solution,
+variant of the problem, the set of drivers in an optimal solution
 form a minimum dominating set.
 When the set of drivers is known in advanced, however, the problem becomes
-tractable and can be solved using a reduction to a flow network.
+tractable and can be solved using a reduction to a flow network problem.
 
-Agatz et al. outlined the optimization challenges that arise 
-when developing technology to support ride-sharing and survey the
-related operations research models in the academic literature~\cite{agatz2012optimization}.  
-Hartman et al. designed several heuristics algorithms for the 
-\CARPOOL{} problem and compared 
-their performance on real data~\cite{hartman2014theory}.
-Other heuristics algorithms were developed as well~\cite{knapen2014exploiting}.
-Arkin et al, considered other variants of capacitated star packing where
-a capacity vector is given as part of the input and 
-capacities are needed to be assigned to vertices~\cite{arkin2004approximations}.
+Agatz et al.~\cite{agatz2012optimization} outlined the optimization challenges
+that arise when developing technology to support ride-sharing and survey the
+related operations research models in the academic literature.  
+Hartman et al.~\cite{hartman2014theory} designed several heuristic algorithms
+for the \CARPOOL{} problem and compared 
+their performance on real data.
+Other heuristic algorithms were developed as well~\cite{knapen2014exploiting}.
+Arkin et al.~\cite{arkin2004approximations}, considered other variants of
+capacitated star packing where a capacity vector is given as part of the input and 
+capacities need to be assigned to vertices.
 
@@
 They proved the following results:
-\begin{inparaenum}
+\begin{enumerate*}
 \item
@@
 there is a polynomial-time $\frac{1}{2}$-approximation algorithm for weighted graphs.
-\end{inparaenum}
+\end{enumerate*}
 They also showed how to apply the spanning star forest model to aligning multiple
@@
 Chen et al.~\cite{chen2007improved} improved the approximation ratio to 0.71,
-and also gave showed the the problem can not be approximated to within a factor of
+and also showed that the problem can not be approximated to within a factor of
 $\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ under the assumption 
 that $\text{P} \neq \text{NP}$.
-None of the technique used to address the \textsc{spanning star forest} problem
-can be generalized to the directed capacitated variant.
+It is not clear, however, if any of the technique used to address the
+\textsc{spanning star forest} problem can be generalized to approximate the
+directed capacitated variant.
 
-\todo{outline}
+In section~\ref{sec:sub} we show that the problem can be formulated as
+unconstarints submodular maximization problem, thus it has a 2-approximation
+algorithm.
+In section~\ref{sec:local} we consider the unweighted variant of the problem.
+We show that when the maximum possible capacity, $C$, is fixed, there is a 
+$(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm for the any $\varepsilon > 0$.

### 2016-11-20 src/local.tex

--- 2016-11-18 src/local.tex
@@
 In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
-both these operations can be done in polynomial time - $O(n^{k + 1})$.
+both these operations can be done in polynomial time - $O(n^{Ck + 1})$.
 
@@
 and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.
-\todo{define this well}
 
@@
 \centering
-\input{fig-conflict}
+\subfloat[]{
+\label{subfloat:graph}
+\input{fig-sub-graph}
+}
+\subfloat[]{
+\label{subfloat:conflict}
+\input{fig-sub-conflict}
+}
 \caption[]{
@@
 \end{figure}
-
-\todo{can I state the observation for any component of size at most (least)
-$s$ ?? or does it have to be exavtly of size $s$ ?}
-\begin{observation}
-Let $U = \{v_1 \ldots v_s\}$ be the vertices of any connected component in
-$G^{M^*}_M$ then $\frac{w(U)}{w^*(U)}$
-\end{observation}

### 2016-11-20 src/local.tex
foo

@@
 To analyze the approximation ratio achieved by the local search algorithm consider an 
-arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
-where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
+arbitrary but fixed optimal matching $M^*$.
 Given the solution outputted by the local search algorithm, 
-we build the \emph{conflict graph} of the two solutions in which each node
-represents a star from the optimal solution and edges exits between two nodes if
-the local search solution has at least one edge that connects two stars, formally 
-$G_\text{conflict} = (V, E)$ 
-where $\{v_i : s_i \in M^* \}$ 
-and $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
-Figure~\ref{fig:conflict} depicts this concept.
-Denote by $d^*_i$ the sum of the vertex degree of the optimal solution in $s_i$, 
-and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.
+$M$, 
+we build the \emph{star graph} of the two solutions
+in which each node represents a star from the optimal solution 
+and edges exits between two nodes if
+there is a star in $S(M)$ that intersect the two
+corresponding stars of the optimal solution, 
+formally $G^{M^*}_M = (S, E)$ where $\{v_i : S^*_i \in S(M^*) \}$ 
+and 
+$E = \{(v_i, v_j) : 
+\exists S \in M,
+S \cap S^*_i \neq \emptyset \land S \cap S^*_j \neq \emptyset,
+\}$.
+Figure~\ref{fig:conflict} depicts a star graph.
 
@@
 \end{figure}
+
+For a group of vertices, $U$, denote by $w^*(U)$ the sum of the degrees 
+induced by the underlying graph of the optimal solution on this set, i.e.
+$\sum_{u \in U} \dinout[M^*](u)$, 
+and let $w(S)$ be the sum of the degrees 
+induced by the underlying graph of the local search solution on this set, i.e.
+$\sum_{u \in U} \dinout(u)$.
+
+\begin{lemma}
+If $k \geq something$ then in any connected induced graph of $G^{M^*}_M$, 
+$G'= G^{M^*}_M[U]$, 
+$
+\frac{w(U)}{w^*(U)} 
+\geq \frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
+$.
+\end{lemma}
+
+\begin{proof}
+Consider the solution obtained from the $M$ by removing all the edges from $M$
+that intersect the induced subgraph, and adding all the edges from $M^*$ that
+intersect the induced subgraph.
+It is easy to verify that this is a feasible solution.
+We now bound from below the difference in the value of the solution.
+The value decrease due to the removal of the edges by at most $w(U) - |U| + 1$,
+and increase by exactly $\frac{w^*(U)}{2} \leq C |U|$.
+We know that this difference can not be positive, or else, the local search
+algorithm would not have been terminated.
+Thus 
+$\frac{w^*(U)}{2} \leq w(U) - |U| + 1$ 
+and so
+$
+\frac{w(U)}{w^*(U)} 
+\geq 
+\frac{1}{2} + \frac{|U|}{w^*(U))} - \frac{1}{w^*(U))}  
+\geq
+\frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
+$
+\end{proof}

### 2016-11-20 src/local.tex
foo

@@
 \begin{lemma}
+\label{lemma:r}
 If $k \geq something$ then in any connected induced graph of $G^{M^*}_M$, 
@@
 \end{proof}
+
+\begin{lemma}
+\label{lemma:dec}
+Given a parameter $k$, a bounded degree connected graph $G$, with a maximum
+degree $d$ can be decomposed into connected components of size at least $k$, and at most
+$d(k-1) + 1$.
+\end{lemma}
+
+\begin{proof}
+We give a constructive proof.
+Start constructing a connected component by adding adjacent vertices
+one by one to the component and removing them from the graph.
+If at some point, removing a vertex disconnect the graph, add all the small
+components (of size less than $k$) to the constructed component and decompose
+the large components (of size at least $k$) recursively.
+Note that removing a vertex can break the graph to at most $d - 1$ additional
+components.
+\end{proof}
+
+\begin{theorem}
+The local search is ($\frac{1}{2} + \frac{1}{2c} - \varepsilon$)-approximation
+algorithm.
+\end{theorem}
+
+\begin{proof}
+Combine lemma~\ref{lemma:dec}, and lemma~\ref{lemma:r}, 
+and observe that the maximum degree in $G^{M^*}_M$ is $(C + 1)^C$ to
+get the desire result.
+\end{proof}

### 2016-11-20 src/group.tex
foo

In this section we introduce the group carpool and show that it does not fit the
submodular maximization formulation while the local search algorithm handle it
without any modification.

### 2016-11-20 src/sub.tex
foo

In this section we show that the problem can be formulated as unconstrained
submodular maximization problem, and thus, it has a 2-approximation algorithm.

### 2016-11-21 src/group-2-approximation.tex
outline

In this subsection we give a 2-approximation algorithm for general capacities.

### 2016-12-05 src/hardness.tex
working...

Formally, the (unweighted) minimum dominating set problem is defined as
$\min_{D}(|D|)$,
where $D$ is any feasible dominating set.
It is also easy to see that the (unweighted, undirected, uncapacitated) 
maximum carpool matching problem can be defined as $max_{D}(|V \setminus D|)$, 
where $D$ is any feasible dominating set.
The \textsc{Dominating Set-B} is the problem of finding minimum dominating set on 
graphs with degree bounded by $B$,
and it was shown to be APX-hard (for $B \geq 3$) by 
Papadimitriou et al.~\cite{papadimitriou1988optimization}.

Let $G$ be a b-bounded degree graph,
let $D^*(G)$ be a minimum dominating set in $G$,
and let $C^*(G)$ be a maximum carpool matching in $G$, 
then the following lemmas hold:

\begin{lemma}
$|C^*| = |V| - |D^*|$
\end{lemma}

\begin{proof}
The proof follows immediately from the definitions of the two problems. 
\end{proof}

\begin{lemma}
\label{lm:optc_leq_boptd}
$|C^*| \leq b \cdot |D^*|$
\end{lemma}

\begin{proof}
The proof follows directly from the observation that $|D^*| \geq \frac{|V|}{b}$.
\end{proof}

Let $C(G)$ be any feasible carpool matching on $G$, then the following lemma holds:

\begin{lemma}
\label{lm:erreq}
$|C^*| - |C| = (|V| - |C|) - |D^*|$
\end{lemma}

\begin{proof}
$$
|C^*| - |C| 				= 
|V| - |D^*| - |C| 	= 
(|V| - |C|) - |D^*|
$$
\end{proof}

Let $D(G)$ be any feasible dominating set in $G$, 
we argue that $f(G) = G$, and $g(C(G)) = V \setminus C(G)$ 
define a linear reduction (L-reduction) from the \textsc{Dominating Set-B} problem to the 
\textsc{\CARPOOL{}} problem.
\begin{proof}
By lemma~\ref{lm:optc_leq_boptd} we get that $C^*(f(G)) = C^*(G) \leq b \cdot D^*(G)$,
and by lemma~\ref{lm:erreq} we get that 
\begin{equation}
\begin{split}
|C^*(f(G))| - |C(G)|		& = |C^*(G)| - |C(G)| 			\\
							& = (|V| - |C(G)|) - |D^*(G)|	\\
							& = |g(C(G))| - |D^*(G)|
\end{split}
\end{equation}
\end{proof}

\begin{theorem}
The \textsc{\CARPOOL{}} problem is APX-hard.
\end{theorem}

\begin{proof}
The proof follows directly from the above linear reduction and the fact that 
\textsc{Dominating Set-B} is APX-hard. 
\end{proof}

### 2016-12-05 src/local.tex
working...

@@
-In this section we consider the unweighted variants of the problem.
-We describe and analyze a local search algorithm, 
-and show that when the maximum possible capacity, $C$, is fixed, the algorithm achieves 
-a $\frac{C + 1}{2C} - \varepsilon$ 
-approximation ratio for any $\varepsilon > 0$.
-Throughout this section we consider $C$ to be fixed, and $k$ to be a fixed parameter.
-
 The local search algorithm maintains a feasible matching throughout its execution

### 2016-12-05 src/main.tex
working...

\documentclass[draft]{article}

\input{in/libs}
\input{in/def}
\input{in/tikz}

\input{in/title}
\input{in/authors}

\begin{document}
\maketitle

\input{outline}

\bibliographystyle{plain}
\bibliography{main}
% \resizebox{.9\textwidth}{!}{\input{tmp}}

\end{document}

### 2016-12-05 src/sub.tex
working...

@@
 submodular maximization problem, and thus, it has a 2-approximation algorithm.
+
+Consider the function $w : 2^V \to \R$ where $w(D)$ is the value of the optimal
+carpool matching when the set of drivers is $D$.
+As we mention in the introduction, $w$ can be computed efficiently.
+
+\begin{theorem}
+$w$ is submodular.
+\end{theorem}
+
+\begin{proof}
+Consider two subsets $A,B \subseteq V$, 
+we need to show that $w(A) + w(B) \geq w(A \cup B) + w(A \cap B)$.
+Let $E_{A \setminus B} = (V \setminus A) \times (A \setminus B)$, 
+$E_{B \setminus A} = (V \setminus A) \times (B \setminus A)$,
+and $E_{B \cap A} = (V \setminus (A \cap B)) \times (B \cap A)$.
+
+Let $M_{A \cup B}$ and $M_{A \cap B}$ be the set of edges in an optimal
+matching when the set of drivers are $A \cup B$ and $A \cap B$ respectively.
+We argue that we can construct two (feasible) matchings $M_A$ and $M_B$ using
+the sets of drivers $A$ and $B$ respectively and 
+$w(M_A) + w(M_B) = w(M_{A \cup B}) + w(M_{A \cap B})$.
+First, take all the edges from $M_{A \cup B} \cap E_{A \setminus B}$ and 
+add them to $M_A$, 
+add $M_{A \cup B} \cap E_{B \setminus A}$ to $M_B$.
+Clearly this can be done.
+Now, split the edges from $M_{A \cap B} \cup (M_{A \cup B} \cap E_{A \cap B})$
+between $M_A$ and $M_B$ in a way that does not violate the capacity constraints.
+One can verify that this can be done.
+\end{proof}

### 2016-12-05 src/group-2-approximation.tex
fix warnings

@@
 In this subsection we give a 2-approximation algorithm for general capacities.
+First, let us introduce a $(\frac{1}{2} - \varepsilon)$-approximation algorithm
+for the original problem.
+We then show how to generalize the algorithm to work also for the group carpool
+matching.
+
+\tikzset{m/.style={
+	blue, 
+	dashed,	
+}}
+
+Let $M$ be a feasible carpool matching,
+the \emph{value} of a vertex $v$, denoted $val(v)$, 
+is the sum of the weights of the arcs in $M$ that incident $v$. 
+That is: 
+%
+\begin{definition}[$val$]
+$val_M(v) = \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u)$
+\end{definition}
+%
+If $V$ is a set of vertices, then $val_M(V) \triangleq \sum_{v \in V} val_M(v)$.
+%
+Denote by $\delta(e)$ the difference between the weight of the arc and the value
+of its source vertex,
+that is:
+%
+\begin{definition}[$\delta$]
+$\delta_M(u, v) = w(u, v) - val_M(u)$
+\end{definition}
+%
+If $S$ is a set of arcs, then $\delta(S) \triangleq \sum_{e \in S}\delta(v)$.
+
+An \emph{improvement} to vertex $v$ 
+is a set of arcs entering $v$ of size not greater than the capacity of $v$, 
+for which the sum of the $\delta$s is greater than the value of $v$,
+formally:
+
+\begin{definition}[improvement]
+$S_v \subseteq V \times \{v\} \cap A$ is an \emph{improvement} (w.r.t $M$)
+if the following conditions hold:
+\begin{itemize}
+\item
+$|S_v| \leq c(v)$
+\item
+$\delta_M(S_v) > val_M(v)$
+\end{itemize}  
+\end{definition}
+%
+If, for vertex $v$, an improvement exists, we say that vertex $v$ can be \emph{improved}.
+%
+Given an arc $(u,v)$, 
+let $inc(u,v)$ be the set of arcs that incident $(u, v)$,
+formally:
+%
+\begin{definition}[inc]
+$inc(u,v) = (V \times \{u, v\} \cup \{u, v\} \times V) \cap A$
+\end{definition}
+%
+If $S$ is a set of arcs, then $inc(S) \triangleq \bigcup_{e \in S} inc(e)$.
+%
+The \emph{passengers} of $v$ (w.r.t some set of arcs) are all the vertices that have
+outgoing arc to $v$, formally: 
+%
+\begin{definition}[passengers]
+$\text{pass}_M(v) = \{u : (u, v) \in M\}$
+\end{definition}
+%
+Figure~\ref{fig:defs} depicts all the above definitions.
+
+\begin{figure}
+\centering
+\input{fig-val-delta}
+\caption[]{
+\label{fig:defs}
+In this example, $M$ is the set of the blue, dashed arcs, then:
+$val_M(2) = 7$,
+$val_M(3) = 2$,
+$val_M(6) = 0$,
+$\delta_M(2, 3) = 1$,
+$\delta_M(6, 3) = 2$,
+the set $\{(2,3), (6,3)\}$ is an \emph{improvement} to vertex 3,
+$inc(2,3) = \{(1,2),(4,2),(3,5),(6,3)\}$,
+$\text{pass}_M(2) = \{1, 4\}$.
+}
+\end{figure}
+
+We are now ready to describe our algorithm.
+The algorithm starts with an empty matching,
+in every iteration it seeks for a vertex that can be improved,
+it then improve the matching by adding
+the arcs that improve the vertex, 
+just after removing the arcs that incident them.
+The algorithm halts when no vertex can be improved.
+Figure~\ref{fig:improvement} depicts an improvement step,
+and the full algorithm is listed in Algorithm~\ref{alg:grd}.
+
+\begin{figure}
+\centering
+\input{fig-improvement}
+\caption[]{
+\label{fig:improvement}
+\subref{sub:can improved}
+A matching that can be improved
+\subref{sub:improved}
+The matching after improving vertex 3
+}
+\end{figure}
+
+\begin{algorithm}
+\caption{
+\label{alg:grd}
+GRD
+}
+$M \leftarrow \emptyset$									\\
+\While{done}{
+	done $\leftarrow$ True									\\
+	\For{$v \in V$}{
+		\If{$\exists$~improvment~$S_v$}{
+			$M \leftarrow M \setminus inc(S_v) \cup S_v$	\\
+			done $\leftarrow$ False							\\
+		}
+	}
+}
+\end{algorithm}
+
+\textbf{Remarks:}
+We argue that determining if a vertex $v$ can be improved can be done efficiently,
+by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
+and only ones with positive value.
+Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
+sum up to more than $val_M(v)$.
+
+\todo[inline]{argue that the number of iteration is bounded}
+
+We now argue that, with respect to any matching, 
+the total value of all the vertices equals twice the value of the matching, 
+formally: 
+\begin{lemma}
+\label{lm:val-twice}
+$\sum_{v \in V} val_M(v) = 2 \sum_{e \in M} w(e)$
+\end{lemma}
+
+\begin{proof}
+\begin{equation}
+\begin{split}
+\sum_{v \in V} val_M(v)	& = 
+\sum_{v \in V} \left( \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u) \right)	\\
+						& = \sum_{v \in V}\sum_{(u, v) \in M} w(u, v) + 
+							\sum_{v \in V}\sum_{(v, u) \in M} w(v, u)					\\
+						& = 2 \sum_{e \in M} w(e)
+\end{split}
+\end{equation}
+\end{proof}
+
+Let $M$ be a matching, and let $v$ be a vertex with no improvement,
+let $S \subseteq V \times \{v\} \cap A$ of size not greater than $c(v)$,
+then the following lemma holds:
+
+\begin{lemma}
+\label{lm:no improve}
+$w(S) \leq val_M(v) + val_M(\text{pass}_S(v))$
+\end{lemma}
+
+\begin{proof}
+If no improvement exists then
+$$
+w(S) - val_M(\text{pass}_S(v))=
+\sum_{(u,v) \in S}(w(u,v) - val_M(u)) =
+\delta_M(S) 
+\leq val_M(v)
+$$
+\end{proof}
+
+To bound the approximation ratio of the GRD algorithm, 
+we use a charging scheme argument.
+Given the matching produced by the algorithm, 
+we load every vertex with amount of money equal to its value,
+we then show that this is enough to pay for every arc in an optimal matching.
+
+\begin{theorem}
+Algorithm~\ref{alg:grd} is 2-approximation.
+\end{theorem}
+
+\begin{proof}
+Let $M$ be the matching produced by algorithm~\ref{alg:grd}, 
+and let $M^*$ be an optimal matching.
+Load every vertex with $val_M(v)$ money, 
+by lemma~\ref{lm:val-twice} this is exactly twice the value of $M$.
+Consider a driver $v$ in $M^*$, and let $S = V \times \{v\} \cap M^*$.
+By lemma~\ref{lm:no improve} we know that $w(S) \leq val_M(v) + val_M(\text{pass}_S(v))$,
+thus we can pay for $S$, using the money on $v$ and $\text{pass}_S(v)$.
+Clearly, these vertices will not be charged again.
+\end{proof}
+
+To conclude this section we show that our analysis is tight, 
+as depicts in Figure~\ref{fig:grd worst}.
+\todo[inline]{what happen if we apply the rule on both directions ?}
+\begin{figure}
+\centering
+\input{fig-2-tight}
+\caption[]{
+\label{fig:grd worst}
+GRD algorithm, worst case example: \\
+Consider a path with $2n + 1$ arcs,
+and alternating arc weights (2 and 1),
+if the GRD algorithm selects all the 1 weighted arcs,
+then no further improvement can be done and the value of the matching is $n + 1$,
+while the optimal matching has value of $2n$.
+}
+\end{figure}

### 2016-12-05 src/hardness.tex
fix warnings

@@
-Formally, the (unweighted) minimum dominating set problem is defined as
-$\min_{D}(|D|)$,
+As we mentioned in the introduction, the maximum spanning star forest can not 
+be approximated within a factor of 
+$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ unless P = NP.
+The proof, however, does not hold for the case when the maximum capacity is
+constant. 
+In this subsection we show that the problem remains APX-hard even in this case.
+
+Formally, the (unweighted)
+minimum dominating set problem is defined as $\min_{D}(|D|)$,
 where $D$ is any feasible dominating set.

### 2016-12-05 src/group-2-approximation.tex
foo

@@
 
-\textbf{Remarks:}
-We argue that determining if a vertex $v$ can be improved can be done efficiently,
+\begin{remark}
+Clearly, if the weights on the edges are integral and polynomial bounded the
+algorithm runs in polynomial time, this is because in each iteration the
+algorithm improves the value of the matching by at least one or otherwise it
+terminates.
+\end{remark}
+
+\begin{remark}
+When the weights are not integral nor polynomial bounded one can use scaling and
+rounding first to ensure polynomial runtime in the cost of $\varepsilon$ in the
+approximation ratio.
+\end{remark}
+
+\begin{remark}
+Determining if a vertex $v$ can be improved can be done efficiently
 by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
@@
 sum up to more than $val_M(v)$.
-
-\todo[inline]{argue that the number of iteration is bounded}
+\end{remark}
 

### 2016-12-05 src/group-2-approximation.tex
first draft

@@
 \begin{remark}
-Clearly, if the weights on the edges are integral and polynomial bounded the
-algorithm runs in polynomial time, this is because in each iteration the
+\label{rem:improve}
+Determining if a vertex $v$ can be improved can be done efficiently
+by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
+and only ones with positive value.
+Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
+sum up to more than $val_M(v)$.
+\end{remark}
+
+\begin{remark}
+It is easy to see, if the weights on the edges are integral and polynomial
+bounded the algorithm runs in polynomial time, this is because in each iteration the
 algorithm improves the value of the matching by at least one or otherwise it
@@
 approximation ratio.
-\end{remark}
-
-\begin{remark}
-Determining if a vertex $v$ can be improved can be done efficiently
-by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
-and only ones with positive value.
-Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
-sum up to more than $val_M(v)$.
 \end{remark}
@@
 \begin{theorem}
-Algorithm~\ref{alg:grd} is 2-approximation.
+Algorithm~\ref{alg:grd} is $\frac{1}{2}$-approximation.
 \end{theorem}
@@
 \end{proof}
+
+We now argue that this algorithm can be generalized to solve the group carpool
+matching problem.
+The main concern when trying to adopt the algorithm to the group carpool
+matching is how to determine if a vertex can be improved.
+Observe that Remark~\ref{rem:improve} does not hold anymore.
+If the maximum possible capacity is bounded, one can test for improvement of
+$v$ by considering all the subsets of edges intersecting $v$. 
+When the capacity is unbounded, however, it is easy to see that efficient
+way to test improvement implies a solution to the Knapsack problem.
+Indeed, if this is the case, one can test for improvement by using a known FPTAS
+for Knapsack, this is in the cost of additional $\varepsilon$ reduction in the
+approximation ratio of the algorithm.
 

### 2016-12-05 src/merge.tex
adding merge.tex to git so Dror can edit

\documentclass[draft]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[linesnumbered, ruled]{algorithm2e}
\usepackage[]{subfig}
\usepackage{paralist}
\usepackage{hyperref}
\hypersetup{final}
\usepackage[inline]{enumitem}

% DEBUG
\usepackage{fullpage}
\usepackage{todonotes}
\usepackage{lineno}
\linenumbers

% EXTRA
\usepackage{authblk}
\def\CARPOOL{maximum carpool matching}

\newcommand{\din}[1][M]{deg^{#1}_{in}}
\newcommand{\dout}[1][M]{deg^{#1}_{out}}
\newcommand{\dinout}[1][M]{deg^{#1}}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\def\R{\mathbb{R}}
\def\N{\mathbb{N}}

\newtheorem{observation}{Observation}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\usepackage{tikz}
\usetikzlibrary{
	arrows,
	arrows.meta,
	calc,
	graphs,
	patterns,
	positioning,
	shapes,
	decorations.pathmorphing,
}

%DEFAULT STYLE
\tikzset{default style/.style={
	>=Stealth, 
	on grid, 
	auto, 
	thick,
}}

% NODE
\tikzset{default node/.style={
	draw, 
	circle,
	inner sep=0mm,
	minimum size=5mm,
	very thick,
	font=\small,
	black!70,
}}

% LABELS
\tikzset{label/.style={
	draw=none,
	sloped,
}}

\tikzset{label above/.style={
	label,
	midway,
	above=-1mm,
}}

\tikzset{label below/.style={
	label,
	midway,
	below=-1mm,
}}

\title{Improved Approximation Algorithms for the Maximum Carpool Matching
Problme}

\date{}
\author[1]{Reuven Bar-Yehuda	\thanks{\texttt{reuven@cs.technion.ac.il}}}
\author[1]{Gilad Kutiel			\thanks{\texttt{gkutiel@cs.technion.ac.il}}}
\author[2]{Dror Rawitz			\thanks{\texttt{dror.rawitz@biu.ac.il}}}

\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}

\begin{document}
\maketitle

\begin{abstract}
The \textsc{\CARPOOL{}} problem is a star packing problem in directed graphs.
Formally, given a directed graph $G = (V, A)$,
a capacity function $ c: V \rightarrow \N $,
and a weight function $w : A \rightarrow \R $,
a feasible \emph{carpool matching} is a triple 
$(P, D, M)$, where $P$ (passengers) and $D$ (drivers) form a partition of $V$, 
and $M$ is a subset of $A \cap (P \times D)$,
under the constraints that for every vertex $d \in D$, 
$\din(d) \leq c(d)$, 
and for every vertex $p \in P$, $\dout(p) \leq 1$.
In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
total weight of $M$.

The problem arises when designing an online carpool service, 
such as Zimride~\cite{zimride}, 
that tries to connect between passengers and drivers based on (arbitrary) similarity function.
The problem is known to be NP-hard, 
even for uniform weights and without capacity constraints.

we show that the problem can be formulated as
unconstarints submodular maximization problem, 
thus it has a $\frac{1}{2}$-approximation algorithm.
For the unweighted variant of the problem when the maximum possible capacity, $C$, is
fixed, we give a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm
for the any $\varepsilon > 0$.
\end{abstract}

\section{Introduction}
Carpooling, is the sharing of car journeys so that more than one person travels
in a car.
Knapen et al.~\cite{knapen2013estimating} describe an automatic service
to match commuting trips.
Users of the service register their personal profile and a set of periodically
recurring trips, 
and the service advises registered candidates on how to combine their commuting
trips by carpooling.
The service acts in two phases.

In the first phase, the service estimates the probability that a person $a$
traveling in person's $b$ car will be satisfied by the trip.
This is done based on personal information and feedback from users on past
rides.
The second phase is about finding a carpool matching
that maximizes the global (total expected) satisfaction.

The second phase can be modeled in terms of graph theory.
Given a directed graph $G = (V, A)$.
Each vertex $v \in V$ corresponds to a user of the service and an arc
$(u, v)$ exists if the user corresponding to vertex $u$ is willing to
commute with the user corresponding to vertex $v$.
A capacity function $ c: V \rightarrow \N $ is defined
according to the number of passengers each user can drive if she was
selected as a driver.
A weight function $w : A \rightarrow \R $ defines the amount of
satisfaction $w(u, v)$,
that user $u$ gains when riding with user $v$.

A feasible \emph{carpool matching} (matching) is a triple 
$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
and $M$ is a subset of $A \cap (P \times D)$,
under the constraints that for every driver $d \in D$, 
$\din(d) \leq c(d)$, 
and for every passenger $p \in P$, ${\dout(p) \leq 1}$.
In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
total weight of $M$.
In other words, the \textsc{\CARPOOL{}} problem is about finding a set of 
(directed toward the center) vertex disjoint stars 
that maximizes the total weights on the arcs.
Figure~\ref{fig:carpool} is an example of the \textsc{\CARPOOL{}} problem.

\begin{figure}
\centering
\newcommand{\edge}[3]{
	\draw (#1) -- (#2) node[label above] {#3};
}
\subfloat[]{
\label{subfloat:input}
\begin{tikzpicture}[every node/.style={default node}, ->, very thick]

\node(1) at(-1,3) {2};
\node(2) at(.5,.5) {3};
\node(3) at(-1,0) {1};
\node(4) at(-1,1) {3};
\node(5) at(-2,2) {0};
\node(6) at(-2,-1) {4};
\node(7) at(-3,0) {3};
\node(8) at(.5,-1) {2};
\node(9) at(0,2) {1};
\node(10) at(2,1) {4};

\edge{1}{4}{3}
\edge{2}{4}{4}
\edge{3}{4}{5}

\edge{5}{7}{2}
\edge{6}{7}{4}

\edge{8}{10}{6}
\edge{9}{10}{2}

\edge{1}{5}{4}
\edge{4}{5}{4}

\edge{2}{3}{2}
\edge{6}{3}{2}
\edge{7}{3}{2}

\edge{8}{2}{1}
\edge{10}{2}{1}

\edge{3}{8}{3}
\edge{8}{3}{3}

\edge{1}{9}{1}
\edge{4}{9}{1}

\end{tikzpicture}}
\hfill\subfloat[]{
\label{subfloat:output}
\begin{tikzpicture}[every node/.style={default node}, ->, very thick]

\begin{scope}[every node/.style={default node, draw=blue}]
\node(5) at(-2,2) {0};
\node(6) at(-2,-1) {4};

\node(2) at(.5,.5) {3};
\node(3) at(-1,0) {1};
\node(1) at(-1,3) {2};

\node(8) at(.5,-1) {2};
\node(9) at(0,2) {1};
\end{scope}

\begin{scope}[every node/.style={default node, draw=red, dashed}]
\node(7) at(-3,0) {3};

\node(4) at(-1,1) {3};

\node(10) at(2,1) {4};
\end{scope}

\edge{1}{4}{3}
\edge{2}{4}{4}
\edge{3}{4}{5}

\edge{5}{7}{2}
\edge{6}{7}{4}

\edge{8}{10}{6}
\edge{9}{10}{2}

\end{tikzpicture}}
\caption[]{
\label{fig:carpool}
A carpool matching example: 
\subref{subfloat:input} 
a directed graph with capacities on the vertices and weights on the arcs. 
\subref{subfloat:output}
a feasible matching with total weight of 26.
$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
}
\end{figure}

Hartman et al.~\cite{hartman2013optimal} proved that the
\emph{\CARPOOL{}} problem considered in this paper is NP-hard,
and that the problem remains NP-hard even for a binary weight function when
the capacity function $c(v) \leq 2$ for every vertex in $V$.
It is also worth mentioning, that in the undirected, uncapacitated, unweighted
variant of the problem, the set of drivers in an optimal solution
form a minimum dominating set.
When the set of drivers is known in advanced, however, the problem becomes
tractable and can be solved using a reduction to a flow network problem.

Agatz et al.~\cite{agatz2012optimization} outlined the optimization challenges
that arise when developing technology to support ride-sharing and survey the
related operations research models in the academic literature.  
Hartman et al.~\cite{hartman2014theory} designed several heuristic algorithms
for the \CARPOOL{} problem and compared 
their performance on real data.
Other heuristic algorithms were developed as well~\cite{knapen2014exploiting}.
Arkin et al.~\cite{arkin2004approximations}, considered other variants of
capacitated star packing where a capacity vector is given as part of the input and 
capacities need to be assigned to vertices.

Nguyen et al.~\cite{nguyen2008approximating} considered the \textsc{spanning star forest} problem
(the undirected, uncapacitated, unweighted variant of the problem).
They proved the following results:
\begin{enumerate*}
\item
there is a polynomial-time approximation scheme for planner graphs;
\item 
there is a polynomial-time $\frac{3}{5}$-approximation algorithm for graphs;
\item 
there is a polynomial-time $\frac{1}{2}$-approximation algorithm for weighted graphs.
\end{enumerate*}
They also showed how to apply the spanning star forest model to aligning multiple
genomic sequences over a tandem duplication region.
Chen et al.~\cite{chen2007improved} improved the approximation ratio to 0.71,
and also showed that the problem can not be approximated to within a factor of
$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ under the assumption 
that $\text{P} \neq \text{NP}$.
It is not clear, however, if any of the technique used to address the
\textsc{spanning star forest} problem can be generalized to approximate the
directed capacitated variant.

In section~\ref{sec:sub} we show that the problem can be formulated as
unconstarints submodular maximization problem, thus it has a 2-approximation
algorithm.
In section~\ref{sec:local} we consider the unweighted variant of the problem.
We show that when the maximum possible capacity, $C$, is fixed, there is a 
$(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm for the any $\varepsilon > 0$.

\section{Submodularity}
\label{sec:sub}
In this section we show that the problem can be formulated as unconstrained
submodular maximization problem, and thus, it has a 2-approximation algorithm.

Consider the function $w : 2^V \to \R$ where $w(D)$ is the value of the optimal
carpool matching when the set of drivers is $D$.
As we mention in the introduction, $w$ can be computed efficiently.

\begin{theorem}
$w$ is submodular.
\end{theorem}

\begin{proof}
Consider two subsets $A,B \subseteq V$, 
we need to show that $w(A) + w(B) \geq w(A \cup B) + w(A \cap B)$.
Let $E_{A \setminus B} = (V \setminus A) \times (A \setminus B)$, 
$E_{B \setminus A} = (V \setminus A) \times (B \setminus A)$,
and $E_{B \cap A} = (V \setminus (A \cap B)) \times (B \cap A)$.

Let $M_{A \cup B}$ and $M_{A \cap B}$ be the set of edges in an optimal
matching when the set of drivers are $A \cup B$ and $A \cap B$ respectively.
We argue that we can construct two (feasible) matchings $M_A$ and $M_B$ using
the sets of drivers $A$ and $B$ respectively and 
$w(M_A) + w(M_B) = w(M_{A \cup B}) + w(M_{A \cap B})$.
First, take all the edges from $M_{A \cup B} \cap E_{A \setminus B}$ and 
add them to $M_A$, 
add $M_{A \cup B} \cap E_{B \setminus A}$ to $M_B$.
Clearly this can be done.
Now, split the edges from $M_{A \cap B} \cup (M_{A \cup B} \cap E_{A \cap B})$
between $M_A$ and $M_B$ in a way that does not violate the capacity constraints.
One can verify that this can be done.
\end{proof}

\section{Constant Max Capacity}
In this section we study the carpool problem when the maximum possible capacity
is constant.
We show that this variant of the problem is APX-hard as well.
We also describe and analyze a local search algorithm for the unweighted
variant of the problem, 
and show that the algorithm achieves a 
$\frac{C + 1}{2C} - \varepsilon$ approximation ratio for any $\varepsilon > 0$.
Throughout this section we consider $C$ to be fixed, and $k$ to be a fixed parameter.

	\subsection{Hardness}
	\label{sec:hardness}
As we mentioned in the introduction, the maximum spanning star forest can not 
be approximated within a factor of 
$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ unless P = NP.
The proof, however, does not hold for the case when the maximum capacity is
constant. 
In this subsection we show that the problem remains APX-hard even in this case.

Formally, the (unweighted)
minimum dominating set problem is defined as $\min_{D}(|D|)$,
where $D$ is any feasible dominating set.
It is also easy to see that the (unweighted, undirected, uncapacitated) 
maximum carpool matching problem can be defined as $max_{D}(|V \setminus D|)$, 
where $D$ is any feasible dominating set.
The \textsc{Dominating Set-B} is the problem of finding minimum dominating set on 
graphs with degree bounded by $B$,
and it was shown to be APX-hard (for $B \geq 3$) by 
Papadimitriou et al.~\cite{papadimitriou1988optimization}.

Let $G$ be a b-bounded degree graph,
let $D^*(G)$ be a minimum dominating set in $G$,
and let $C^*(G)$ be a maximum carpool matching in $G$, 
then the following lemmas hold:

\begin{lemma}
$|C^*| = |V| - |D^*|$
\end{lemma}

\begin{proof}
The proof follows immediately from the definitions of the two problems. 
\end{proof}

\begin{lemma}
\label{lm:optc_leq_boptd}
$|C^*| \leq b \cdot |D^*|$
\end{lemma}

\begin{proof}
The proof follows directly from the observation that $|D^*| \geq \frac{|V|}{b}$.
\end{proof}

Let $C(G)$ be any feasible carpool matching on $G$, then the following lemma holds:

\begin{lemma}
\label{lm:erreq}
$|C^*| - |C| = (|V| - |C|) - |D^*|$
\end{lemma}

\begin{proof}
$$
|C^*| - |C| 				= 
|V| - |D^*| - |C| 	= 
(|V| - |C|) - |D^*|
$$
\end{proof}

Let $D(G)$ be any feasible dominating set in $G$, 
we argue that $f(G) = G$, and $g(C(G)) = V \setminus C(G)$ 
define a linear reduction (L-reduction) from the \textsc{Dominating Set-B} problem to the 
\textsc{\CARPOOL{}} problem.
\begin{proof}
By lemma~\ref{lm:optc_leq_boptd} we get that $C^*(f(G)) = C^*(G) \leq b \cdot D^*(G)$,
and by lemma~\ref{lm:erreq} we get that 
\begin{equation}
\begin{split}
|C^*(f(G))| - |C(G)|		& = |C^*(G)| - |C(G)| 			\\
							& = (|V| - |C(G)|) - |D^*(G)|	\\
							& = |g(C(G))| - |D^*(G)|
\end{split}
\end{equation}
\end{proof}

\begin{theorem}
The \textsc{\CARPOOL{}} problem is APX-hard.
\end{theorem}

\begin{proof}
The proof follows directly from the above linear reduction and the fact that 
\textsc{Dominating Set-B} is APX-hard. 
\end{proof}

	\subsection{Local Search}
	\label{sec:local}
The local search algorithm maintains a feasible matching throughout its execution
and operates in 
iterative manner where in each iteration it tries to find a better solution by
replacing a subset of the edges in the current solution with 
another (larger) subset of edges not in the solution.
The local search algorithm halts when no improvement can be done.
The algorithm is described in Algorithm~\ref{alg:local}.

\begin{algorithm}
\SetKw{True}{true}
\SetKw{False}{false}
\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
\KwOut{$M$}
$M \leftarrow \emptyset$								\\
\Repeat{done}{
\label{line:outerloop}
 	$done \leftarrow{}$ \True							\\
 	\For{$M' \in M : |M'| \leq k$}{
 		\For{$A' \in A \setminus M : |A'| = |M'| + 1$}{
			\If{$M \setminus M' \cup A'$ is feasible}{
				$M \leftarrow{} M \setminus M' \cup A'$	\\
				$done \leftarrow{}$ \False				\\
			}
		}
 	}
}
\Return{$M$}

\caption{
\label{alg:local}
Local Search}
\end{algorithm}

We claim that the local search algorithm halts in polynomial time.
Observed that in every iteration the algorithm either improves the value of the solution
by one or otherwise it terminates. 
Thus, after a maximum of $n$ iterations the algorithm stops.
In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
both these operations can be done in polynomial time - $O(n^{Ck + 1})$.

To analyze the approximation ratio achieved by the local search algorithm consider an 
arbitrary but fixed optimal matching $M^*$.
Given the solution outputted by the local search algorithm, 
$M$, 
we build the \emph{star graph} of the two solutions
in which each node represents a star from the optimal solution 
and edges exits between two nodes if
there is a star in $S(M)$ that intersect the two
corresponding stars of the optimal solution, 
formally $G^{M^*}_M = (S, E)$ where $\{v_i : S^*_i \in S(M^*) \}$ 
and 
$E = \{(v_i, v_j) : 
\exists S \in M,
S \cap S^*_i \neq \emptyset \land S \cap S^*_j \neq \emptyset,
\}$.
Figure~\ref{fig:conflict} depicts a star graph.

\begin{figure}[ht]
\centering
\subfloat[]{
\label{subfloat:graph}
\newcommand{\edge}[2]{
	\draw (#1) -- (#2);
}

\begin{tikzpicture}[every node/.style={default node}, ->, very thick]

\node(1) at(0,0) {a};
\node(2) at(0,1.5) {b};
\node(3) at(1.5,0) {c};

\node(4) at(4,0) {d};
\node(5) at(4,1.5) {e};
\node(6) at(2.5,0) {f};

\node(7) at(0,-1.5) {h};
\node(8) at(0,-3) {i};
\node(9) at(1.5,-1.5) {j};

\node(10) at(4,-1.5) {k};
\node(11) at(4,-3) {l};

\begin{scope}[dashed, red]
\edge{2}{1}
\edge{3}{1}

\edge{5}{4}
\edge{6}{4}

\edge{8}{7}
\edge{9}{7}

\edge{11}{10}
\end{scope}

\begin{scope}[green]
\edge{2}{5}

\edge{7}{1}
\edge{3}{9}
\end{scope}

\end{tikzpicture}
}
\subfloat[]{
\label{subfloat:conflict}
\newcommand{\edge}[2]{
	\draw (#1) -- (#2);
}

\begin{tikzpicture}[every node/.style={default node, red}, -, very thick, green]

\node(1) at(0,1.5) {3};
\node(2) at(4,1.5) {1};
\node(3) at(0,-3) {2};
\node(4) at(4,-3) {0};

\edge{1}{2}
\edge{1}{3}

\end{tikzpicture}
}
\caption[]{
\label{fig:conflict}
\subref{subfloat:input} 
An optimal matching depicted by the dashed red edges,
and another solution depicted by the solid green edges.  
\subref{subfloat:output}
The conflict graph, the upper left vertex corresponds 
to the star that contains the vertices a,b,c.
The numbers inside the vertices corresponds to $d_i$.   
}
\end{figure}

For a group of vertices, $U$, denote by $w^*(U)$ the sum of the degrees 
induced by the underlying graph of the optimal solution on this set, i.e.
$\sum_{u \in U} \dinout[M^*](u)$, 
and let $w(S)$ be the sum of the degrees 
induced by the underlying graph of the local search solution on this set, i.e.
$\sum_{u \in U} \dinout(u)$.

\begin{lemma}
\label{lemma:r}
If $k \geq \text{TODO}$ then in any connected induced graph of $G^{M^*}_M$, 
$G'= G^{M^*}_M[U]$, 
$
\frac{w(U)}{w^*(U)} 
\geq \frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
$.
\end{lemma}

\begin{proof}
Consider the solution obtained from the $M$ by removing all the edges from $M$
that intersect the induced subgraph, and adding all the edges from $M^*$ that
intersect the induced subgraph.
It is easy to verify that this is a feasible solution.
We now bound from below the difference in the value of the solution.
The value decrease due to the removal of the edges by at most $w(U) - |U| + 1$,
and increase by exactly $\frac{w^*(U)}{2} \leq C |U|$.
We know that this difference can not be positive, or else, the local search
algorithm would not have been terminated.
Thus 
$\frac{w^*(U)}{2} \leq w(U) - |U| + 1$ 
and so
$
\frac{w(U)}{w^*(U)} 
\geq 
\frac{1}{2} + \frac{|U|}{w^*(U))} - \frac{1}{w^*(U))}  
\geq
\frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
$
\end{proof}

\begin{lemma}
\label{lemma:dec}
Given a parameter $k$, a bounded degree connected graph $G$, with a maximum
degree $d$ can be decomposed into connected components of size at least $k$, and at most
$d(k-1) + 1$.
\end{lemma}

\begin{proof}
We give a constructive proof.
Start constructing a connected component by adding adjacent vertices
one by one to the component and removing them from the graph.
If at some point, removing a vertex disconnect the graph, add all the small
components (of size less than $k$) to the constructed component and decompose
the large components (of size at least $k$) recursively.
Note that removing a vertex can break the graph to at most $d - 1$ additional
components.
\end{proof}

\begin{theorem}
The local search is ($\frac{1}{2} + \frac{1}{2c} - \varepsilon$)-approximation
algorithm.
\end{theorem}

\begin{proof}
Combine lemma~\ref{lemma:dec}, and lemma~\ref{lemma:r}, 
and observe that the maximum degree in $G^{M^*}_M$ is $(C + 1)^C$ to
get the desire result.
\end{proof}

\todo{show that the analysis is tight}

\section{Group Carpool}
\label{sec:group}
In this section we introduce the group carpool and show that it does not fit the
submodular maximization formulation while the local search algorithm handle it
without any modification.

\subsection{2-approximation}
In this subsection we give a 2-approximation algorithm for general capacities.
First, let us introduce a $(\frac{1}{2} - \varepsilon)$-approximation algorithm
for the original problem.
We then show how to generalize the algorithm to work also for the group carpool
matching.

\tikzset{m/.style={
	blue, 
	dashed,	
}}

Let $M$ be a feasible carpool matching,
the \emph{value} of a vertex $v$, denoted $val(v)$, 
is the sum of the weights of the arcs in $M$ that incident $v$. 
That is: 
%
\begin{definition}[$val$]
$val_M(v) = \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u)$
\end{definition}
%
If $V$ is a set of vertices, then $val_M(V) \triangleq \sum_{v \in V} val_M(v)$.
%
Denote by $\delta(e)$ the difference between the weight of the arc and the value
of its source vertex,
that is:
%
\begin{definition}[$\delta$]
$\delta_M(u, v) = w(u, v) - val_M(u)$
\end{definition}
%
If $S$ is a set of arcs, then $\delta(S) \triangleq \sum_{e \in S}\delta(v)$.

An \emph{improvement} to vertex $v$ 
is a set of arcs entering $v$ of size not greater than the capacity of $v$, 
for which the sum of the $\delta$s is greater than the value of $v$,
formally:

\begin{definition}[improvement]
$S_v \subseteq V \times \{v\} \cap A$ is an \emph{improvement} (w.r.t $M$)
if the following conditions hold:
\begin{itemize}
\item
$|S_v| \leq c(v)$
\item
$\delta_M(S_v) > val_M(v)$
\end{itemize}  
\end{definition}
%
If, for vertex $v$, an improvement exists, we say that vertex $v$ can be \emph{improved}.
%
Given an arc $(u,v)$, 
let $inc(u,v)$ be the set of arcs that incident $(u, v)$,
formally:
%
\begin{definition}[inc]
$inc(u,v) = (V \times \{u, v\} \cup \{u, v\} \times V) \cap A$
\end{definition}
%
If $S$ is a set of arcs, then $inc(S) \triangleq \bigcup_{e \in S} inc(e)$.
%
The \emph{passengers} of $v$ (w.r.t some set of arcs) are all the vertices that have
outgoing arc to $v$, formally: 
%
\begin{definition}[passengers]
$\text{pass}_M(v) = \{u : (u, v) \in M\}$
\end{definition}
%
Figure~\ref{fig:defs} depicts all the above definitions.

\begin{figure}
\centering
\begin{tikzpicture}[every node/.style={default node}]

\node(1) at(0,0) {1};
\node(2) at(2,0) {2};
\node(3) at(4,0) {3};

\node(4) at(.4,1.6) {4};
\node(5) at(2.4,1.6) {5};
\node(6) at(6, 0) {6};

\draw[m] (1) -- (2) node[label above]{$5$};
\draw[m] (4) -- (2) node[label above]{$2$};
\draw[m] (3) -- (5) node[label above]{$2$};
\draw[] (6) -- (3) node[label above]{$2$};

\draw (2) -- (3) node[label above]{$8$};

\end{tikzpicture}
\caption[]{
\label{fig:defs}
In this example, $M$ is the set of the blue, dashed arcs, then:
$val_M(2) = 7$,
$val_M(3) = 2$,
$val_M(6) = 0$,
$\delta_M(2, 3) = 1$,
$\delta_M(6, 3) = 2$,
the set $\{(2,3), (6,3)\}$ is an \emph{improvement} to vertex 3,
$inc(2,3) = \{(1,2),(4,2),(3,5),(6,3)\}$,
$\text{pass}_M(2) = \{1, 4\}$.
}
\end{figure}

We are now ready to describe our algorithm.
The algorithm starts with an empty matching,
in every iteration it seeks for a vertex that can be improved,
it then improve the matching by adding
the arcs that improve the vertex, 
just after removing the arcs that incident them.
The algorithm halts when no vertex can be improved.
Figure~\ref{fig:improvement} depicts an improvement step,
and the full algorithm is listed in Algorithm~\ref{alg:grd}.

\begin{figure}
\centering
\subfloat[]{
\label{sub:can improved}
\begin{tikzpicture}[every node/.style={default node}]
\node(1) at(0,0) {1};
\node(2) at(2,0) {2};
\node(3) at(4,0) {3};

\node(4) at(.4,1.6) {4};
\node(5) at(2.4,1.6) {5};
\node(6) at(2.4, -1.6) {6};

\draw[m] (1) -- (2) node[label above]{$5$};
\draw[m] (4) -- (2) node[label above]{$2$};
\draw[m] (3) -- (5) node[label above]{$2$};
\draw[] (6) -- (3) node[label above]{$2$};

\draw (2) -- (3) node[label above]{$8$};

\end{tikzpicture}
}\hspace{1cm}\subfloat[]{
\label{sub:improved}
\begin{tikzpicture}[every node/.style={default node}]
\node(1) at(0,0) {1};
\node(2) at(2,0) {2};
\node(3) at(4,0) {3};

\node(4) at(.4,1.6) {4};
\node(5) at(2.4,1.6) {5};
\node(6) at(2.4, -1.6) {6};

\draw[] (1) -- (2) node[label above]{$5$};
\draw[] (4) -- (2) node[label above]{$2$};
\draw[] (3) -- (5) node[label above]{$2$};
\draw[m] (6) -- (3) node[label above]{$2$};

\draw[m] (2) -- (3) node[label above]{$8$};

\end{tikzpicture}
}
\caption[]{
\label{fig:improvement}
\subref{sub:can improved}
A matching that can be improved
\subref{sub:improved}
The matching after improving vertex 3
}
\end{figure}

\begin{algorithm}
\caption{
\label{alg:grd}
GRD
}
$M \leftarrow \emptyset$									\\
\While{done}{
	done $\leftarrow$ True									\\
	\For{$v \in V$}{
		\If{$\exists$~improvment~$S_v$}{
			$M \leftarrow M \setminus inc(S_v) \cup S_v$	\\
			done $\leftarrow$ False							\\
		}
	}
}
\end{algorithm}

\begin{remark}
\label{rem:improve}
Determining if a vertex $v$ can be improved can be done efficiently
by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
and only ones with positive value.
Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
sum up to more than $val_M(v)$.
\end{remark}

\begin{remark}
It is easy to see, if the weights on the edges are integral and polynomial
bounded the algorithm runs in polynomial time, this is because in each iteration the
algorithm improves the value of the matching by at least one or otherwise it
terminates.
\end{remark}

\begin{remark}
When the weights are not integral nor polynomial bounded one can use scaling and
rounding first to ensure polynomial runtime in the cost of $\varepsilon$ in the
approximation ratio.
\end{remark}

We now argue that, with respect to any matching, 
the total value of all the vertices equals twice the value of the matching, 
formally: 
\begin{lemma}
\label{lm:val-twice}
$\sum_{v \in V} val_M(v) = 2 \sum_{e \in M} w(e)$
\end{lemma}

\begin{proof}
\begin{equation}
\begin{split}
\sum_{v \in V} val_M(v)	& = 
\sum_{v \in V} \left( \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u) \right)	\\
						& = \sum_{v \in V}\sum_{(u, v) \in M} w(u, v) + 
							\sum_{v \in V}\sum_{(v, u) \in M} w(v, u)					\\
						& = 2 \sum_{e \in M} w(e)
\end{split}
\end{equation}
\end{proof}

Let $M$ be a matching, and let $v$ be a vertex with no improvement,
let $S \subseteq V \times \{v\} \cap A$ of size not greater than $c(v)$,
then the following lemma holds:

\begin{lemma}
\label{lm:no improve}
$w(S) \leq val_M(v) + val_M(\text{pass}_S(v))$
\end{lemma}

\begin{proof}
If no improvement exists then
$$
w(S) - val_M(\text{pass}_S(v))=
\sum_{(u,v) \in S}(w(u,v) - val_M(u)) =
\delta_M(S) 
\leq val_M(v)
$$
\end{proof}

To bound the approximation ratio of the GRD algorithm, 
we use a charging scheme argument.
Given the matching produced by the algorithm, 
we load every vertex with amount of money equal to its value,
we then show that this is enough to pay for every arc in an optimal matching.

\begin{theorem}
Algorithm~\ref{alg:grd} is $\frac{1}{2}$-approximation.
\end{theorem}

\begin{proof}
Let $M$ be the matching produced by algorithm~\ref{alg:grd}, 
and let $M^*$ be an optimal matching.
Load every vertex with $val_M(v)$ money, 
by lemma~\ref{lm:val-twice} this is exactly twice the value of $M$.
Consider a driver $v$ in $M^*$, and let $S = V \times \{v\} \cap M^*$.
By lemma~\ref{lm:no improve} we know that $w(S) \leq val_M(v) + val_M(\text{pass}_S(v))$,
thus we can pay for $S$, using the money on $v$ and $\text{pass}_S(v)$.
Clearly, these vertices will not be charged again.
\end{proof}

We now argue that this algorithm can be generalized to solve the group carpool
matching problem.
The main concern when trying to adopt the algorithm to the group carpool
matching is how to determine if a vertex can be improved.
Observe that Remark~\ref{rem:improve} does not hold anymore.
If the maximum possible capacity is bounded, one can test for improvement of
$v$ by considering all the subsets of edges intersecting $v$. 
When the capacity is unbounded, however, it is easy to see that efficient
way to test improvement implies a solution to the Knapsack problem.
Indeed, if this is the case, one can test for improvement by using a known FPTAS
for Knapsack, this is in the cost of additional $\varepsilon$ reduction in the
approximation ratio of the algorithm.

To conclude this section we show that our analysis is tight, 
as depicts in Figure~\ref{fig:grd worst}.
\todo[inline]{what happen if we apply the rule on both directions ?}
\begin{figure}
\centering
\begin{tikzpicture}[every node/.style={default node}]

\def\sep{1.5}

\foreach \n in {0,...,5}{
	\pgfmathsetmacro{\x}{\n * \sep}
	\node(\n) at(\x,0){};
}

\foreach \n/\m in {0/1,2/3,4/5}{
	\draw[m] (\n) -- (\m) node[label above]{1};
}

\foreach \n/\m in {1/2,3/4}{
	\draw[] (\n) -- (\m) node[label above]{2};
}

\pgfmathsetmacro{\x}{6 * \sep}
\node[draw=none] at(\x, 0){$\cdots$};

\foreach \n in {7,...,8}{
	\pgfmathsetmacro{\x}{\n * \sep}
	\node(\n) at(\x,0){};
}

\draw[m] (7) -- (8) node[label above]{1};

\end{tikzpicture}
\caption[]{
\label{fig:grd worst}
GRD algorithm, worst case example: \\
Consider a path with $2n + 1$ arcs,
and alternating arc weights (2 and 1),
if the GRD algorithm selects all the 1 weighted arcs,
then no further improvement can be done and the value of the matching is $n + 1$,
while the optimal matching has value of $2n$.
}
\end{figure}

\bibliographystyle{plain}
\bibliography{main}

\end{document}

### 2016-12-16 src/in/tikz.tex
fig local tight

--- 2016-12-05 src/merge.tex
@@
-\documentclass[draft]{article}
-
-\usepackage{amsmath,amssymb,amsthm,mathtools}
-\usepackage[linesnumbered, ruled]{algorithm2e}
-\usepackage[]{subfig}
-\usepackage{paralist}
-\usepackage{hyperref}
-\hypersetup{final}
-\usepackage[inline]{enumitem}
-
-% DEBUG
-\usepackage{fullpage}
-\usepackage{todonotes}
-\usepackage{lineno}
-\linenumbers
-
-% EXTRA
-\usepackage{authblk}
-\def\CARPOOL{maximum carpool matching}
-
-\newcommand{\din}[1][M]{deg^{#1}_{in}}
-\newcommand{\dout}[1][M]{deg^{#1}_{out}}
-\newcommand{\dinout}[1][M]{deg^{#1}}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\def\R{\mathbb{R}}
-\def\N{\mathbb{N}}
-
-\newtheorem{observation}{Observation}
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{remark}{Remark}
 \usepackage{tikz}
@@
 	decorations.pathmorphing,
+	math,
 }
@@
 }}
-
-\title{Improved Approximation Algorithms for the Maximum Carpool Matching
-Problme}
-
-\date{}
-\author[1]{Reuven Bar-Yehuda	\thanks{\texttt{reuven@cs.technion.ac.il}}}
-\author[1]{Gilad Kutiel			\thanks{\texttt{gkutiel@cs.technion.ac.il}}}
-\author[2]{Dror Rawitz			\thanks{\texttt{dror.rawitz@biu.ac.il}}}
-
-\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
-\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-The \textsc{\CARPOOL{}} problem is a star packing problem in directed graphs.
-Formally, given a directed graph $G = (V, A)$,
-a capacity function $ c: V \rightarrow \N $,
-and a weight function $w : A \rightarrow \R $,
-a feasible \emph{carpool matching} is a triple 
-$(P, D, M)$, where $P$ (passengers) and $D$ (drivers) form a partition of $V$, 
-and $M$ is a subset of $A \cap (P \times D)$,
-under the constraints that for every vertex $d \in D$, 
-$\din(d) \leq c(d)$, 
-and for every vertex $p \in P$, $\dout(p) \leq 1$.
-In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
-total weight of $M$.
-
-The problem arises when designing an online carpool service, 
-such as Zimride~\cite{zimride}, 
-that tries to connect between passengers and drivers based on (arbitrary) similarity function.
-The problem is known to be NP-hard, 
-even for uniform weights and without capacity constraints.
-
-we show that the problem can be formulated as
-unconstarints submodular maximization problem, 
-thus it has a $\frac{1}{2}$-approximation algorithm.
-For the unweighted variant of the problem when the maximum possible capacity, $C$, is
-fixed, we give a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm
-for the any $\varepsilon > 0$.
-\end{abstract}
-
-\section{Introduction}
-Carpooling, is the sharing of car journeys so that more than one person travels
-in a car.
-Knapen et al.~\cite{knapen2013estimating} describe an automatic service
-to match commuting trips.
-Users of the service register their personal profile and a set of periodically
-recurring trips, 
-and the service advises registered candidates on how to combine their commuting
-trips by carpooling.
-The service acts in two phases.
-
-In the first phase, the service estimates the probability that a person $a$
-traveling in person's $b$ car will be satisfied by the trip.
-This is done based on personal information and feedback from users on past
-rides.
-The second phase is about finding a carpool matching
-that maximizes the global (total expected) satisfaction.
-
-The second phase can be modeled in terms of graph theory.
-Given a directed graph $G = (V, A)$.
-Each vertex $v \in V$ corresponds to a user of the service and an arc
-$(u, v)$ exists if the user corresponding to vertex $u$ is willing to
-commute with the user corresponding to vertex $v$.
-A capacity function $ c: V \rightarrow \N $ is defined
-according to the number of passengers each user can drive if she was
-selected as a driver.
-A weight function $w : A \rightarrow \R $ defines the amount of
-satisfaction $w(u, v)$,
-that user $u$ gains when riding with user $v$.
-
-A feasible \emph{carpool matching} (matching) is a triple 
-$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
-and $M$ is a subset of $A \cap (P \times D)$,
-under the constraints that for every driver $d \in D$, 
-$\din(d) \leq c(d)$, 
-and for every passenger $p \in P$, ${\dout(p) \leq 1}$.
-In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
-total weight of $M$.
-In other words, the \textsc{\CARPOOL{}} problem is about finding a set of 
-(directed toward the center) vertex disjoint stars 
-that maximizes the total weights on the arcs.
-Figure~\ref{fig:carpool} is an example of the \textsc{\CARPOOL{}} problem.
-
-\begin{figure}
-\centering
-\newcommand{\edge}[3]{
-	\draw (#1) -- (#2) node[label above] {#3};
-}
-\subfloat[]{
-\label{subfloat:input}
-\begin{tikzpicture}[every node/.style={default node}, ->, very thick]
-
-\node(1) at(-1,3) {2};
-\node(2) at(.5,.5) {3};
-\node(3) at(-1,0) {1};
-\node(4) at(-1,1) {3};
-\node(5) at(-2,2) {0};
-\node(6) at(-2,-1) {4};
-\node(7) at(-3,0) {3};
-\node(8) at(.5,-1) {2};
-\node(9) at(0,2) {1};
-\node(10) at(2,1) {4};
-
-\edge{1}{4}{3}
-\edge{2}{4}{4}
-\edge{3}{4}{5}
-
-\edge{5}{7}{2}
-\edge{6}{7}{4}
-
-\edge{8}{10}{6}
-\edge{9}{10}{2}
-
-\edge{1}{5}{4}
-\edge{4}{5}{4}
-
-\edge{2}{3}{2}
-\edge{6}{3}{2}
-\edge{7}{3}{2}
-
-\edge{8}{2}{1}
-\edge{10}{2}{1}
-
-\edge{3}{8}{3}
-\edge{8}{3}{3}
-
-\edge{1}{9}{1}
-\edge{4}{9}{1}
-
-\end{tikzpicture}}
-\hfill\subfloat[]{
-\label{subfloat:output}
-\begin{tikzpicture}[every node/.style={default node}, ->, very thick]
-
-\begin{scope}[every node/.style={default node, draw=blue}]
-\node(5) at(-2,2) {0};
-\node(6) at(-2,-1) {4};
-
-\node(2) at(.5,.5) {3};
-\node(3) at(-1,0) {1};
-\node(1) at(-1,3) {2};
-
-\node(8) at(.5,-1) {2};
-\node(9) at(0,2) {1};
-\end{scope}
-
-\begin{scope}[every node/.style={default node, draw=red, dashed}]
-\node(7) at(-3,0) {3};
-
-\node(4) at(-1,1) {3};
-
-\node(10) at(2,1) {4};
-\end{scope}
-
-\edge{1}{4}{3}
-\edge{2}{4}{4}
-\edge{3}{4}{5}
-
-\edge{5}{7}{2}
-\edge{6}{7}{4}
-
-\edge{8}{10}{6}
-\edge{9}{10}{2}
-
-\end{tikzpicture}}
-\caption[]{
-\label{fig:carpool}
-A carpool matching example: 
-\subref{subfloat:input} 
-a directed graph with capacities on the vertices and weights on the arcs. 
-\subref{subfloat:output}
-a feasible matching with total weight of 26.
-$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
-}
-\end{figure}
-
-Hartman et al.~\cite{hartman2013optimal} proved that the
-\emph{\CARPOOL{}} problem considered in this paper is NP-hard,
-and that the problem remains NP-hard even for a binary weight function when
-the capacity function $c(v) \leq 2$ for every vertex in $V$.
-It is also worth mentioning, that in the undirected, uncapacitated, unweighted
-variant of the problem, the set of drivers in an optimal solution
-form a minimum dominating set.
-When the set of drivers is known in advanced, however, the problem becomes
-tractable and can be solved using a reduction to a flow network problem.
-
-Agatz et al.~\cite{agatz2012optimization} outlined the optimization challenges
-that arise when developing technology to support ride-sharing and survey the
-related operations research models in the academic literature.  
-Hartman et al.~\cite{hartman2014theory} designed several heuristic algorithms
-for the \CARPOOL{} problem and compared 
-their performance on real data.
-Other heuristic algorithms were developed as well~\cite{knapen2014exploiting}.
-Arkin et al.~\cite{arkin2004approximations}, considered other variants of
-capacitated star packing where a capacity vector is given as part of the input and 
-capacities need to be assigned to vertices.
-
-Nguyen et al.~\cite{nguyen2008approximating} considered the \textsc{spanning star forest} problem
-(the undirected, uncapacitated, unweighted variant of the problem).
-They proved the following results:
-\begin{enumerate*}
-\item
-there is a polynomial-time approximation scheme for planner graphs;
-\item 
-there is a polynomial-time $\frac{3}{5}$-approximation algorithm for graphs;
-\item 
-there is a polynomial-time $\frac{1}{2}$-approximation algorithm for weighted graphs.
-\end{enumerate*}
-They also showed how to apply the spanning star forest model to aligning multiple
-genomic sequences over a tandem duplication region.
-Chen et al.~\cite{chen2007improved} improved the approximation ratio to 0.71,
-and also showed that the problem can not be approximated to within a factor of
-$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ under the assumption 
-that $\text{P} \neq \text{NP}$.
-It is not clear, however, if any of the technique used to address the
-\textsc{spanning star forest} problem can be generalized to approximate the
-directed capacitated variant.
-
-In section~\ref{sec:sub} we show that the problem can be formulated as
-unconstarints submodular maximization problem, thus it has a 2-approximation
-algorithm.
-In section~\ref{sec:local} we consider the unweighted variant of the problem.
-We show that when the maximum possible capacity, $C$, is fixed, there is a 
-$(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm for the any $\varepsilon > 0$.
-
-\section{Submodularity}
-\label{sec:sub}
-In this section we show that the problem can be formulated as unconstrained
-submodular maximization problem, and thus, it has a 2-approximation algorithm.
-
-Consider the function $w : 2^V \to \R$ where $w(D)$ is the value of the optimal
-carpool matching when the set of drivers is $D$.
-As we mention in the introduction, $w$ can be computed efficiently.
-
-\begin{theorem}
-$w$ is submodular.
-\end{theorem}
-
-\begin{proof}
-Consider two subsets $A,B \subseteq V$, 
-we need to show that $w(A) + w(B) \geq w(A \cup B) + w(A \cap B)$.
-Let $E_{A \setminus B} = (V \setminus A) \times (A \setminus B)$, 
-$E_{B \setminus A} = (V \setminus A) \times (B \setminus A)$,
-and $E_{B \cap A} = (V \setminus (A \cap B)) \times (B \cap A)$.
-
-Let $M_{A \cup B}$ and $M_{A \cap B}$ be the set of edges in an optimal
-matching when the set of drivers are $A \cup B$ and $A \cap B$ respectively.
-We argue that we can construct two (feasible) matchings $M_A$ and $M_B$ using
-the sets of drivers $A$ and $B$ respectively and 
-$w(M_A) + w(M_B) = w(M_{A \cup B}) + w(M_{A \cap B})$.
-First, take all the edges from $M_{A \cup B} \cap E_{A \setminus B}$ and 
-add them to $M_A$, 
-add $M_{A \cup B} \cap E_{B \setminus A}$ to $M_B$.
-Clearly this can be done.
-Now, split the edges from $M_{A \cap B} \cup (M_{A \cup B} \cap E_{A \cap B})$
-between $M_A$ and $M_B$ in a way that does not violate the capacity constraints.
-One can verify that this can be done.
-\end{proof}
-
-\section{Constant Max Capacity}
-In this section we study the carpool problem when the maximum possible capacity
-is constant.
-We show that this variant of the problem is APX-hard as well.
-We also describe and analyze a local search algorithm for the unweighted
-variant of the problem, 
-and show that the algorithm achieves a 
-$\frac{C + 1}{2C} - \varepsilon$ approximation ratio for any $\varepsilon > 0$.
-Throughout this section we consider $C$ to be fixed, and $k$ to be a fixed parameter.
-
-	\subsection{Hardness}
-	\label{sec:hardness}
-As we mentioned in the introduction, the maximum spanning star forest can not 
-be approximated within a factor of 
-$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ unless P = NP.
-The proof, however, does not hold for the case when the maximum capacity is
-constant. 
-In this subsection we show that the problem remains APX-hard even in this case.
-
-Formally, the (unweighted)
-minimum dominating set problem is defined as $\min_{D}(|D|)$,
-where $D$ is any feasible dominating set.
-It is also easy to see that the (unweighted, undirected, uncapacitated) 
-maximum carpool matching problem can be defined as $max_{D}(|V \setminus D|)$, 
-where $D$ is any feasible dominating set.
-The \textsc{Dominating Set-B} is the problem of finding minimum dominating set on 
-graphs with degree bounded by $B$,
-and it was shown to be APX-hard (for $B \geq 3$) by 
-Papadimitriou et al.~\cite{papadimitriou1988optimization}.
-
-Let $G$ be a b-bounded degree graph,
-let $D^*(G)$ be a minimum dominating set in $G$,
-and let $C^*(G)$ be a maximum carpool matching in $G$, 
-then the following lemmas hold:
-
-\begin{lemma}
-$|C^*| = |V| - |D^*|$
-\end{lemma}
-
-\begin{proof}
-The proof follows immediately from the definitions of the two problems. 
-\end{proof}
-
-\begin{lemma}
-\label{lm:optc_leq_boptd}
-$|C^*| \leq b \cdot |D^*|$
-\end{lemma}
-
-\begin{proof}
-The proof follows directly from the observation that $|D^*| \geq \frac{|V|}{b}$.
-\end{proof}
-
-Let $C(G)$ be any feasible carpool matching on $G$, then the following lemma holds:
-
-\begin{lemma}
-\label{lm:erreq}
-$|C^*| - |C| = (|V| - |C|) - |D^*|$
-\end{lemma}
-
-\begin{proof}
-$$
-|C^*| - |C| 				= 
-|V| - |D^*| - |C| 	= 
-(|V| - |C|) - |D^*|
-$$
-\end{proof}
-
-Let $D(G)$ be any feasible dominating set in $G$, 
-we argue that $f(G) = G$, and $g(C(G)) = V \setminus C(G)$ 
-define a linear reduction (L-reduction) from the \textsc{Dominating Set-B} problem to the 
-\textsc{\CARPOOL{}} problem.
-\begin{proof}
-By lemma~\ref{lm:optc_leq_boptd} we get that $C^*(f(G)) = C^*(G) \leq b \cdot D^*(G)$,
-and by lemma~\ref{lm:erreq} we get that 
-\begin{equation}
-\begin{split}
-|C^*(f(G))| - |C(G)|		& = |C^*(G)| - |C(G)| 			\\
-							& = (|V| - |C(G)|) - |D^*(G)|	\\
-							& = |g(C(G))| - |D^*(G)|
-\end{split}
-\end{equation}
-\end{proof}
-
-\begin{theorem}
-The \textsc{\CARPOOL{}} problem is APX-hard.
-\end{theorem}
-
-\begin{proof}
-The proof follows directly from the above linear reduction and the fact that 
-\textsc{Dominating Set-B} is APX-hard. 
-\end{proof}
-
-	\subsection{Local Search}
-	\label{sec:local}
-The local search algorithm maintains a feasible matching throughout its execution
-and operates in 
-iterative manner where in each iteration it tries to find a better solution by
-replacing a subset of the edges in the current solution with 
-another (larger) subset of edges not in the solution.
-The local search algorithm halts when no improvement can be done.
-The algorithm is described in Algorithm~\ref{alg:local}.
-
-\begin{algorithm}
-\SetKw{True}{true}
-\SetKw{False}{false}
-\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
-\KwOut{$M$}
-$M \leftarrow \emptyset$								\\
-\Repeat{done}{
-\label{line:outerloop}
- 	$done \leftarrow{}$ \True							\\
- 	\For{$M' \in M : |M'| \leq k$}{
- 		\For{$A' \in A \setminus M : |A'| = |M'| + 1$}{
-			\If{$M \setminus M' \cup A'$ is feasible}{
-				$M \leftarrow{} M \setminus M' \cup A'$	\\
-				$done \leftarrow{}$ \False				\\
-			}
-		}
- 	}
-}
-\Return{$M$}
-
-\caption{
-\label{alg:local}
-Local Search}
-\end{algorithm}
-
-We claim that the local search algorithm halts in polynomial time.
-Observed that in every iteration the algorithm either improves the value of the solution
-by one or otherwise it terminates. 
-Thus, after a maximum of $n$ iterations the algorithm stops.
-In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
-both these operations can be done in polynomial time - $O(n^{Ck + 1})$.
-
-To analyze the approximation ratio achieved by the local search algorithm consider an 
-arbitrary but fixed optimal matching $M^*$.
-Given the solution outputted by the local search algorithm, 
-$M$, 
-we build the \emph{star graph} of the two solutions
-in which each node represents a star from the optimal solution 
-and edges exits between two nodes if
-there is a star in $S(M)$ that intersect the two
-corresponding stars of the optimal solution, 
-formally $G^{M^*}_M = (S, E)$ where $\{v_i : S^*_i \in S(M^*) \}$ 
-and 
-$E = \{(v_i, v_j) : 
-\exists S \in M,
-S \cap S^*_i \neq \emptyset \land S \cap S^*_j \neq \emptyset,
-\}$.
-Figure~\ref{fig:conflict} depicts a star graph.
-
-\begin{figure}[ht]
-\centering
-\subfloat[]{
-\label{subfloat:graph}
-\newcommand{\edge}[2]{
-	\draw (#1) -- (#2);
-}
-
-\begin{tikzpicture}[every node/.style={default node}, ->, very thick]
-
-\node(1) at(0,0) {a};
-\node(2) at(0,1.5) {b};
-\node(3) at(1.5,0) {c};
-
-\node(4) at(4,0) {d};
-\node(5) at(4,1.5) {e};
-\node(6) at(2.5,0) {f};
-
-\node(7) at(0,-1.5) {h};
-\node(8) at(0,-3) {i};
-\node(9) at(1.5,-1.5) {j};
-
-\node(10) at(4,-1.5) {k};
-\node(11) at(4,-3) {l};
-
-\begin{scope}[dashed, red]
-\edge{2}{1}
-\edge{3}{1}
-
-\edge{5}{4}
-\edge{6}{4}
-
-\edge{8}{7}
-\edge{9}{7}
-
-\edge{11}{10}
-\end{scope}
-
-\begin{scope}[green]
-\edge{2}{5}
-
-\edge{7}{1}
-\edge{3}{9}
-\end{scope}
-
-\end{tikzpicture}
-}
-\subfloat[]{
-\label{subfloat:conflict}
-\newcommand{\edge}[2]{
-	\draw (#1) -- (#2);
-}
-
-\begin{tikzpicture}[every node/.style={default node, red}, -, very thick, green]
-
-\node(1) at(0,1.5) {3};
-\node(2) at(4,1.5) {1};
-\node(3) at(0,-3) {2};
-\node(4) at(4,-3) {0};
-
-\edge{1}{2}
-\edge{1}{3}
-
-\end{tikzpicture}
-}
-\caption[]{
-\label{fig:conflict}
-\subref{subfloat:input} 
-An optimal matching depicted by the dashed red edges,
-and another solution depicted by the solid green edges.  
-\subref{subfloat:output}
-The conflict graph, the upper left vertex corresponds 
-to the star that contains the vertices a,b,c.
-The numbers inside the vertices corresponds to $d_i$.   
-}
-\end{figure}
-
-For a group of vertices, $U$, denote by $w^*(U)$ the sum of the degrees 
-induced by the underlying graph of the optimal solution on this set, i.e.
-$\sum_{u \in U} \dinout[M^*](u)$, 
-and let $w(S)$ be the sum of the degrees 
-induced by the underlying graph of the local search solution on this set, i.e.
-$\sum_{u \in U} \dinout(u)$.
-
-\begin{lemma}
-\label{lemma:r}
-If $k \geq \text{TODO}$ then in any connected induced graph of $G^{M^*}_M$, 
-$G'= G^{M^*}_M[U]$, 
-$
-\frac{w(U)}{w^*(U)} 
-\geq \frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
-$.
-\end{lemma}
-
-\begin{proof}
-Consider the solution obtained from the $M$ by removing all the edges from $M$
-that intersect the induced subgraph, and adding all the edges from $M^*$ that
-intersect the induced subgraph.
-It is easy to verify that this is a feasible solution.
-We now bound from below the difference in the value of the solution.
-The value decrease due to the removal of the edges by at most $w(U) - |U| + 1$,
-and increase by exactly $\frac{w^*(U)}{2} \leq C |U|$.
-We know that this difference can not be positive, or else, the local search
-algorithm would not have been terminated.
-Thus 
-$\frac{w^*(U)}{2} \leq w(U) - |U| + 1$ 
-and so
-$
-\frac{w(U)}{w^*(U)} 
-\geq 
-\frac{1}{2} + \frac{|U|}{w^*(U))} - \frac{1}{w^*(U))}  
-\geq
-\frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
-$
-\end{proof}
-
-\begin{lemma}
-\label{lemma:dec}
-Given a parameter $k$, a bounded degree connected graph $G$, with a maximum
-degree $d$ can be decomposed into connected components of size at least $k$, and at most
-$d(k-1) + 1$.
-\end{lemma}
-
-\begin{proof}
-We give a constructive proof.
-Start constructing a connected component by adding adjacent vertices
-one by one to the component and removing them from the graph.
-If at some point, removing a vertex disconnect the graph, add all the small
-components (of size less than $k$) to the constructed component and decompose
-the large components (of size at least $k$) recursively.
-Note that removing a vertex can break the graph to at most $d - 1$ additional
-components.
-\end{proof}
-
-\begin{theorem}
-The local search is ($\frac{1}{2} + \frac{1}{2c} - \varepsilon$)-approximation
-algorithm.
-\end{theorem}
-
-\begin{proof}
-Combine lemma~\ref{lemma:dec}, and lemma~\ref{lemma:r}, 
-and observe that the maximum degree in $G^{M^*}_M$ is $(C + 1)^C$ to
-get the desire result.
-\end{proof}
-
-\todo{show that the analysis is tight}
-
-\section{Group Carpool}
-\label{sec:group}
-In this section we introduce the group carpool and show that it does not fit the
-submodular maximization formulation while the local search algorithm handle it
-without any modification.
-
-\subsection{2-approximation}
-In this subsection we give a 2-approximation algorithm for general capacities.
-First, let us introduce a $(\frac{1}{2} - \varepsilon)$-approximation algorithm
-for the original problem.
-We then show how to generalize the algorithm to work also for the group carpool
-matching.
-
-\tikzset{m/.style={
-	blue, 
-	dashed,	
-}}
-
-Let $M$ be a feasible carpool matching,
-the \emph{value} of a vertex $v$, denoted $val(v)$, 
-is the sum of the weights of the arcs in $M$ that incident $v$. 
-That is: 
-%
-\begin{definition}[$val$]
-$val_M(v) = \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u)$
-\end{definition}
-%
-If $V$ is a set of vertices, then $val_M(V) \triangleq \sum_{v \in V} val_M(v)$.
-%
-Denote by $\delta(e)$ the difference between the weight of the arc and the value
-of its source vertex,
-that is:
-%
-\begin{definition}[$\delta$]
-$\delta_M(u, v) = w(u, v) - val_M(u)$
-\end{definition}
-%
-If $S$ is a set of arcs, then $\delta(S) \triangleq \sum_{e \in S}\delta(v)$.
-
-An \emph{improvement} to vertex $v$ 
-is a set of arcs entering $v$ of size not greater than the capacity of $v$, 
-for which the sum of the $\delta$s is greater than the value of $v$,
-formally:
-
-\begin{definition}[improvement]
-$S_v \subseteq V \times \{v\} \cap A$ is an \emph{improvement} (w.r.t $M$)
-if the following conditions hold:
-\begin{itemize}
-\item
-$|S_v| \leq c(v)$
-\item
-$\delta_M(S_v) > val_M(v)$
-\end{itemize}  
-\end{definition}
-%
-If, for vertex $v$, an improvement exists, we say that vertex $v$ can be \emph{improved}.
-%
-Given an arc $(u,v)$, 
-let $inc(u,v)$ be the set of arcs that incident $(u, v)$,
-formally:
-%
-\begin{definition}[inc]
-$inc(u,v) = (V \times \{u, v\} \cup \{u, v\} \times V) \cap A$
-\end{definition}
-%
-If $S$ is a set of arcs, then $inc(S) \triangleq \bigcup_{e \in S} inc(e)$.
-%
-The \emph{passengers} of $v$ (w.r.t some set of arcs) are all the vertices that have
-outgoing arc to $v$, formally: 
-%
-\begin{definition}[passengers]
-$\text{pass}_M(v) = \{u : (u, v) \in M\}$
-\end{definition}
-%
-Figure~\ref{fig:defs} depicts all the above definitions.
-
-\begin{figure}
-\centering
-\begin{tikzpicture}[every node/.style={default node}]
-
-\node(1) at(0,0) {1};
-\node(2) at(2,0) {2};
-\node(3) at(4,0) {3};
-
-\node(4) at(.4,1.6) {4};
-\node(5) at(2.4,1.6) {5};
-\node(6) at(6, 0) {6};
-
-\draw[m] (1) -- (2) node[label above]{$5$};
-\draw[m] (4) -- (2) node[label above]{$2$};
-\draw[m] (3) -- (5) node[label above]{$2$};
-\draw[] (6) -- (3) node[label above]{$2$};
-
-\draw (2) -- (3) node[label above]{$8$};
-
-\end{tikzpicture}
-\caption[]{
-\label{fig:defs}
-In this example, $M$ is the set of the blue, dashed arcs, then:
-$val_M(2) = 7$,
-$val_M(3) = 2$,
-$val_M(6) = 0$,
-$\delta_M(2, 3) = 1$,
-$\delta_M(6, 3) = 2$,
-the set $\{(2,3), (6,3)\}$ is an \emph{improvement} to vertex 3,
-$inc(2,3) = \{(1,2),(4,2),(3,5),(6,3)\}$,
-$\text{pass}_M(2) = \{1, 4\}$.
-}
-\end{figure}
-
-We are now ready to describe our algorithm.
-The algorithm starts with an empty matching,
-in every iteration it seeks for a vertex that can be improved,
-it then improve the matching by adding
-the arcs that improve the vertex, 
-just after removing the arcs that incident them.
-The algorithm halts when no vertex can be improved.
-Figure~\ref{fig:improvement} depicts an improvement step,
-and the full algorithm is listed in Algorithm~\ref{alg:grd}.
-
-\begin{figure}
-\centering
-\subfloat[]{
-\label{sub:can improved}
-\begin{tikzpicture}[every node/.style={default node}]
-\node(1) at(0,0) {1};
-\node(2) at(2,0) {2};
-\node(3) at(4,0) {3};
-
-\node(4) at(.4,1.6) {4};
-\node(5) at(2.4,1.6) {5};
-\node(6) at(2.4, -1.6) {6};
-
-\draw[m] (1) -- (2) node[label above]{$5$};
-\draw[m] (4) -- (2) node[label above]{$2$};
-\draw[m] (3) -- (5) node[label above]{$2$};
-\draw[] (6) -- (3) node[label above]{$2$};
-
-\draw (2) -- (3) node[label above]{$8$};
-
-\end{tikzpicture}
-}\hspace{1cm}\subfloat[]{
-\label{sub:improved}
-\begin{tikzpicture}[every node/.style={default node}]
-\node(1) at(0,0) {1};
-\node(2) at(2,0) {2};
-\node(3) at(4,0) {3};
-
-\node(4) at(.4,1.6) {4};
-\node(5) at(2.4,1.6) {5};
-\node(6) at(2.4, -1.6) {6};
-
-\draw[] (1) -- (2) node[label above]{$5$};
-\draw[] (4) -- (2) node[label above]{$2$};
-\draw[] (3) -- (5) node[label above]{$2$};
-\draw[m] (6) -- (3) node[label above]{$2$};
-
-\draw[m] (2) -- (3) node[label above]{$8$};
-
-\end{tikzpicture}
-}
-\caption[]{
-\label{fig:improvement}
-\subref{sub:can improved}
-A matching that can be improved
-\subref{sub:improved}
-The matching after improving vertex 3
-}
-\end{figure}
-
-\begin{algorithm}
-\caption{
-\label{alg:grd}
-GRD
-}
-$M \leftarrow \emptyset$									\\
-\While{done}{
-	done $\leftarrow$ True									\\
-	\For{$v \in V$}{
-		\If{$\exists$~improvment~$S_v$}{
-			$M \leftarrow M \setminus inc(S_v) \cup S_v$	\\
-			done $\leftarrow$ False							\\
-		}
-	}
-}
-\end{algorithm}
-
-\begin{remark}
-\label{rem:improve}
-Determining if a vertex $v$ can be improved can be done efficiently
-by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
-and only ones with positive value.
-Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
-sum up to more than $val_M(v)$.
-\end{remark}
-
-\begin{remark}
-It is easy to see, if the weights on the edges are integral and polynomial
-bounded the algorithm runs in polynomial time, this is because in each iteration the
-algorithm improves the value of the matching by at least one or otherwise it
-terminates.
-\end{remark}
-
-\begin{remark}
-When the weights are not integral nor polynomial bounded one can use scaling and
-rounding first to ensure polynomial runtime in the cost of $\varepsilon$ in the
-approximation ratio.
-\end{remark}
-
-We now argue that, with respect to any matching, 
-the total value of all the vertices equals twice the value of the matching, 
-formally: 
-\begin{lemma}
-\label{lm:val-twice}
-$\sum_{v \in V} val_M(v) = 2 \sum_{e \in M} w(e)$
-\end{lemma}
-
-\begin{proof}
-\begin{equation}
-\begin{split}
-\sum_{v \in V} val_M(v)	& = 
-\sum_{v \in V} \left( \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u) \right)	\\
-						& = \sum_{v \in V}\sum_{(u, v) \in M} w(u, v) + 
-							\sum_{v \in V}\sum_{(v, u) \in M} w(v, u)					\\
-						& = 2 \sum_{e \in M} w(e)
-\end{split}
-\end{equation}
-\end{proof}
-
-Let $M$ be a matching, and let $v$ be a vertex with no improvement,
-let $S \subseteq V \times \{v\} \cap A$ of size not greater than $c(v)$,
-then the following lemma holds:
-
-\begin{lemma}
-\label{lm:no improve}
-$w(S) \leq val_M(v) + val_M(\text{pass}_S(v))$
-\end{lemma}
-
-\begin{proof}
-If no improvement exists then
-$$
-w(S) - val_M(\text{pass}_S(v))=
-\sum_{(u,v) \in S}(w(u,v) - val_M(u)) =
-\delta_M(S) 
-\leq val_M(v)
-$$
-\end{proof}
-
-To bound the approximation ratio of the GRD algorithm, 
-we use a charging scheme argument.
-Given the matching produced by the algorithm, 
-we load every vertex with amount of money equal to its value,
-we then show that this is enough to pay for every arc in an optimal matching.
-
-\begin{theorem}
-Algorithm~\ref{alg:grd} is $\frac{1}{2}$-approximation.
-\end{theorem}
-
-\begin{proof}
-Let $M$ be the matching produced by algorithm~\ref{alg:grd}, 
-and let $M^*$ be an optimal matching.
-Load every vertex with $val_M(v)$ money, 
-by lemma~\ref{lm:val-twice} this is exactly twice the value of $M$.
-Consider a driver $v$ in $M^*$, and let $S = V \times \{v\} \cap M^*$.
-By lemma~\ref{lm:no improve} we know that $w(S) \leq val_M(v) + val_M(\text{pass}_S(v))$,
-thus we can pay for $S$, using the money on $v$ and $\text{pass}_S(v)$.
-Clearly, these vertices will not be charged again.
-\end{proof}
-
-We now argue that this algorithm can be generalized to solve the group carpool
-matching problem.
-The main concern when trying to adopt the algorithm to the group carpool
-matching is how to determine if a vertex can be improved.
-Observe that Remark~\ref{rem:improve} does not hold anymore.
-If the maximum possible capacity is bounded, one can test for improvement of
-$v$ by considering all the subsets of edges intersecting $v$. 
-When the capacity is unbounded, however, it is easy to see that efficient
-way to test improvement implies a solution to the Knapsack problem.
-Indeed, if this is the case, one can test for improvement by using a known FPTAS
-for Knapsack, this is in the cost of additional $\varepsilon$ reduction in the
-approximation ratio of the algorithm.
-
-To conclude this section we show that our analysis is tight, 
-as depicts in Figure~\ref{fig:grd worst}.
-\todo[inline]{what happen if we apply the rule on both directions ?}
-\begin{figure}
-\centering
-\begin{tikzpicture}[every node/.style={default node}]
-
-\def\sep{1.5}
-
-\foreach \n in {0,...,5}{
-	\pgfmathsetmacro{\x}{\n * \sep}
-	\node(\n) at(\x,0){};
-}
-
-\foreach \n/\m in {0/1,2/3,4/5}{
-	\draw[m] (\n) -- (\m) node[label above]{1};
-}
-
-\foreach \n/\m in {1/2,3/4}{
-	\draw[] (\n) -- (\m) node[label above]{2};
-}
-
-\pgfmathsetmacro{\x}{6 * \sep}
-\node[draw=none] at(\x, 0){$\cdots$};
-
-\foreach \n in {7,...,8}{
-	\pgfmathsetmacro{\x}{\n * \sep}
-	\node(\n) at(\x,0){};
-}
-
-\draw[m] (7) -- (8) node[label above]{1};
-
-\end{tikzpicture}
-\caption[]{
-\label{fig:grd worst}
-GRD algorithm, worst case example: \\
-Consider a path with $2n + 1$ arcs,
-and alternating arc weights (2 and 1),
-if the GRD algorithm selects all the 1 weighted arcs,
-then no further improvement can be done and the value of the matching is $n + 1$,
-while the optimal matching has value of $2n$.
-}
-\end{figure}
-
-\bibliographystyle{plain}
-\bibliography{main}
-
-\end{document}

### 2016-12-19 src/abstract.tex
going to think
abstract

@@
 Formally, given a directed graph $G = (V, A)$,
-a capacity function $ c: V \rightarrow \N $,
-and a weight function $w : A \rightarrow \R $,
-a feasible \emph{carpool matching} is a triple 
-$(P, D, M)$, where $P$ (passengers) and $D$ (drivers) form a partition of $V$, 
-and $M$ is a subset of $A \cap (P \times D)$,
-under the constraints that for every vertex $d \in D$, 
-$\din(d) \leq c(d)$, 
-and for every vertex $p \in P$, $\dout(p) \leq 1$.
-In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
-total weight of $M$.
+a capacity function $c: V \rightarrow \N$,
+and a profit function $p : A \rightarrow \R $,
+a feasible \emph{carpool matching} is a subset of arcs, 
+$M \subseteq A$, where
+$\forall v \in V, 
+\din[M](v) \cdot \dout[M](v) = 0, 
+\din[M] \leq c(v),
+\dout[M] \leq 1$. 
+In the \textsc{\CARPOOL{}} problem we seek for a matching $M$
+that maximizes the total profit of $M$.
 
@@
 unconstarints submodular maximization problem, 
-thus it has a 2-approximation algorithm.
+thus it has a $\frac{1}{2}$-approximation algorithm.
 For the unweighted variant of the problem when the maximum possible capacity, $C$, is
@@
 for the any $\varepsilon > 0$.
+
+We also consider a variant of the \textsc{\CARPOOL{}} problem where every arc
+has also an integral weight $w:A \to \N$ and the constraint $\din[M] \leq c(v)$
+is replaced with the constraint $\sum_{(u,v)}w(u,v) \leq c(v)$.
+We show that this variant of the problem can not be formulated as an
+unconstarints submodular maximization as before.
+We give, however, a ($2 + \varepsilon$)-approximation algorithm for this
+variant, and argue that the local search algorithm can be generalized to this
+variant of the problem when $C$ is fixed.

### 2016-12-19 src/abstract.tex
intro

@@
 a capacity function $c: V \rightarrow \N$,
-and a profit function $p : A \rightarrow \R $,
+and a weight function $w : A \rightarrow \R $,
 a feasible \emph{carpool matching} is a subset of arcs, 
@@
 In the \textsc{\CARPOOL{}} problem we seek for a matching $M$
-that maximizes the total profit of $M$.
+that maximizes the total weight of $M$.
 
@@
 we show that the problem can be formulated as
-unconstarints submodular maximization problem, 
+unconstrained submodular maximization problem, 
 thus it has a $\frac{1}{2}$-approximation algorithm.
@@
 We also consider a variant of the \textsc{\CARPOOL{}} problem where every arc
-has also an integral weight $w:A \to \N$ and the constraint $\din[M] \leq c(v)$
-is replaced with the constraint $\sum_{(u,v)}w(u,v) \leq c(v)$.
+has also an integral size $s:A \to \N$ and the constraint $\din[M] \leq c(v)$
+is replaced with the constraint $\sum_{(u,v)}s(u,v) \leq c(v)$.
 We show that this variant of the problem can not be formulated as an
-unconstarints submodular maximization as before.
+unconstrained submodular maximization as before.
 We give, however, a ($2 + \varepsilon$)-approximation algorithm for this

### 2016-12-19 src/intro.tex
intro

@@
 
-A feasible \emph{carpool matching} (matching) is a triple 
-$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
-and $M$ is a subset of $A \cap (P \times D)$,
-under the constraints that for every driver $d \in D$, 
-$\din(d) \leq c(d)$, 
-and for every passenger $p \in P$, ${\dout(p) \leq 1}$.
-In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
-total weight of $M$.
+a feasible \emph{carpool matching} is a subset of arcs, 
+$M \subseteq A$, where
+$\forall v \in V, 
+\din[M](v) \cdot \dout[M](v) = 0, 
+\din[M] \leq c(v),
+\dout[M] \leq 1$. 
+In the \textsc{\CARPOOL{}} problem we seek for a matching $M$
+that maximizes the total profit of $M$.
 In other words, the \textsc{\CARPOOL{}} problem is about finding a set of 
@@
 
-In section~\ref{sec:sub} we show that the problem can be formulated as
-unconstarints submodular maximization problem, thus it has a 2-approximation
-algorithm.
-In section~\ref{sec:local} we consider the unweighted variant of the problem.
+In Section~\ref{sec:sub} we show that the problem can be formulated as
+unconstrained submodular maximization problem, thus it has a
+$\frac{1}{2}$-approximation algorithm.
+In Section~\ref{sec:local} we consider the unweighted variant of the problem.
 We show that when the maximum possible capacity, $C$, is fixed, there is a 
 $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm for the any $\varepsilon > 0$.
+We also show that the problem remains APX-hard even if $C \leq 3$.
+In Section~\ref{sec:group} we consider a variant of the problem, the
+\textsc{group \CARPOOL} problem, where each edge has an integral size and 
+the constraint $\din[M] \leq c(v)$ is replaced with the constraint
+$\sum_{(u,v)}s(u,v) \leq c(v)$.
+We show that this variant of the problem can not be formulated as unconstrained
+submodular maximization problem as before.
+We show, however, that this variant of the problem still admits a
+$(\frac{1}{2} - \varepsilon)$-approximation algorithm, and argue that the local
+search algorithm generalized to this variant as well.

### 2016-12-19 src/local.tex
fix warnings
fig local tight
local

@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
@@
 \label{lemma:r}
-If $k \geq something$ then in any connected induced graph of $G^{M^*}_M$, 
+If $k \geq \text{TODO}$ then in any connected induced graph of $G^{M^*}_M$, 
 $G'= G^{M^*}_M[U]$, 
@@
 \begin{theorem}
+\label{theorem:local search}
 The local search is ($\frac{1}{2} + \frac{1}{2c} - \varepsilon$)-approximation
@@
 \end{proof}
+
+We now show that Theorem~\ref{theorem:local search} is tight.
+Consider the example in Figure~\ref{fig:local search tight},
+the example is for the special case when $k=11$ and $C=2$ but this example can
+be generalized in a straightforward manner.
+One can verify that as the graph in the example growth, 
+the ratio between the optimal solution and the local search solution approaches
+$\frac{3}{4}$.
+\begin{figure}
+\begin{center}
+\caption{
+\label{fig:local search tight}
+A tight example for Theorem~\ref{theorem:local search}. 
+The optimal solution is given by the red solid arcs while the local search
+solution is given by the green, dashed arcs.
+The solution can be improved by the local search algorithm only if it removes
+all the edges. 
+}
+\input{fig-local-tight}
+\end{center}
+\end{figure}

### 2016-12-19 src/group.tex
outline
group

@@
 In this section we introduce the group carpool and show that it does not fit the
-submodular maximization formulation while the local search algorithm handle it
-without any modification.
+submodular maximization formulation.
+We show, however, that the problem still has a 
+$\frac{1}{2} - \varepsilon$-approximation algorithm.
+Finally, we argue that the local search algorithm can be trivially generalized
+to handle the new variant of the problem while keeping the same approximation
+guarantees.
+
+We start by giving an example why the maximum \textsc{group carpool} problem can
+not be formalized as an unconstrained submodular maximization problem as
+before.
+Considered the instance given in Figure~\ref{fig:not submodular}
+
+\begin{figure}
+\caption{
+\label{fig:not submodular}
+Consider the following instance where node capacity are written inside nodes, 
+arcs are labeled with their size and all weights are equal to 1.
+It is easy to see that if $f(S)$ is the optimal solution where $S$ is the set of
+drivers, then $f(A) + f(B) = 2 \leq 3 = f(A \cup B) + f(A \cap B)$,
+thus, $f$ is not submodular. 
+}
+\begin{center}
+\input{fig-not-submodular}
+\end{center}
+\end{figure}

### 2016-12-19 src/group.tex
group

@@
-In this section we introduce the group carpool and show that it does not fit the
-submodular maximization formulation.
+We now consider a variant of the problem when, in addition to the capacity
+function $c:V \to \N$, and the weight (profit) function $w:A \to \R$, we also
+have a size function $s:A \to \N$, and the constraint $\din[M] \leq c(v)$
+is replaced with the constraint $\sum_{(u,v)}s(u,v) \leq c(v)$.
+The motivation for this variant of the problem is when we want to allow a group
+of people to travel together in the same car, thus $s$ is the size of the group.
+
+We start by showing that this variant of the problem does not
+fit the submodular maximization formulation anymore.
 We show, however, that the problem still has a 
@@
 
-We start by giving an example why the maximum \textsc{group carpool} problem can
-not be formalized as an unconstrained submodular maximization problem as
-before.
-Considered the instance given in Figure~\ref{fig:not submodular}
+To see why the group carpool problem can not be treated as a
+submodular maximization problem considered the instance given in
+Figure~\ref{fig:not submodular}.
 

### 2017-01-30 src/abstract.tex
Merge Dror

--- 2016-11-18 src/abstract.tex
@@
-The \textsc{\CARPOOL{}} problem is a star packing problem in directed graphs.
-Formally, given a directed graph $G = (V, A)$,
-a capacity function $ c: V \rightarrow \N $,
-and a weight function $w : A \rightarrow \R $,
-a feasible \emph{carpool matching} is a triple 
-$(P, D, M)$, where $P$ (passengers) and $D$ (drivers) form a partition of $V$, 
-and $M$ is a subset of $A \cap (P \times D)$,
-under the constraints that for every vertex $d \in D$, 
-$\din(d) \leq c(d)$, 
-and for every vertex $p \in P$, $\dout(p) \leq 1$.
-In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
-total weight of $M$.
+The \carpool problem is a star packing problem in directed graphs.
+Formally, given a directed graph $G = (V, A)$, a capacity function $c:
+V \rightarrow \N$, and a weight function $w : A \rightarrow \R $, a
+feasible \emph{carpool matching} is a subset of arcs, $M \subseteq A$,
+such that every $v \in V$ satisfies:%
+\begin{inparaenum}[(i)]
+\item $\din[M](v) \cdot \dout[M](v) = 0$,
+\item $\din[M](v) \leq c(v)$, and 
+\item $\dout[M](v) \leq 1$.
+\end{inparaenum}
+A vertex $v$ for which $\dout[M](v) = 1$ is a \emph{passenger}, and a
+vertex for which $\dout[M](v) = 0$ is a driver who has $\din[M](v)$
+passengers.  In the \carpool problem the goal is to find a matching
+$M$ of maximum total weight.
 
-The problem arises when designing an online carpool service, 
-such as Zimride~\cite{zimride}, 
-that tries to connect between passengers and drivers based on (arbitrary) similarity function.
-The problem is known to be NP-hard, 
-even for uniform weights and without capacity constraints.
+The problem arises when designing an online carpool service, such as
+Zimride~\cite{zimride}, which tries to connect between passengers and
+drivers based on (arbitrary) similarity function.  The problem is
+known to be NP-hard, even for uniform weights and infinite capacities.
+%without capacity constraints.
 
-we show that the problem can be formulated as
-unconstarints submodular maximization problem, 
-thus it has a 2-approximation algorithm.
-For the unweighted variant of the problem when the maximum possible capacity, $C$, is
-fixed, we give a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm
-for the any $\varepsilon > 0$.
+We show that the problem can be formulated as an unconstrained
+submodular maximization problem, thus it admits a
+$\frac{1}{2}$-approximation algorithm.  For the unweighted variant of
+the problem when the maximum possible capacity, $C$, is fixed, we give
+a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm for the
+any $\varepsilon > 0$.
+
+We also show that the
+problem remains APX-hard even if $C \leq 3$.
+
+We also consider an extension, called \gcp, in which each vertex
+represents a group of passengers.  Group sizes are non-uniform, and we
+consider the case where a group size may change as a function of the
+driver.  Formally, each arc $(u,v) \in A$ has a size $s(u,v) \in \N$,
+and the constraint $\din[M](v) \leq c(v)$ is replaced with
+$\sum_{u:(u,v) \in M} s(u,v) \leq c(v)$.  We show that \gcp cannot be
+formulated as an unconstrained submodular maximization problem.
+Nevertheless, we give a $(\frac{1}{2} - \varepsilon)$-approximation
+algorithm for this variant, and argue that the local search algorithm
+can be generalized to this variant of the problem when $C$ is fixed.

### 2017-01-30 src/group.tex
Merge Dror

@@
-We now consider a variant of the problem when, in addition to the capacity
-function $c:V \to \N$, and the weight (profit) function $w:A \to \R$, we also
-have a size function $s:A \to \N$, and the constraint $\din[M] \leq c(v)$
-is replaced with the constraint $\sum_{(u,v)}s(u,v) \leq c(v)$.
-The motivation for this variant of the problem is when we want to allow a group
-of people to travel together in the same car, thus $s$ is the size of the group.
+We now consider a variant of the problem when, in addition to the
+capacity function $c:V \to \N$, and the weight (profit) function
+$w:A \to \R$, we also have a size function $s:A \to \N$, and the
+constraint $\din[M] \leq c(v)$ is replaced with the constraint
+$\sum_{(u,v)}s(u,v) \leq c(v)$.  The motivation for this variant of
+the problem is when we want to allow a group of people to travel
+together in the same car, thus $s$ is the size of the group.  We start
+by showing that this variant of the problem does not fit the
+submodular maximization formulation anymore. We show, however, that
+the problem still has a $(2 +\eps)$-approximation algorithm.  Finally,
+we argue that the local search algorithm can be trivially generalized
+to handle the new variant of the problem while keeping the same
+approximation guarantees.
 
-We start by showing that this variant of the problem does not
-fit the submodular maximization formulation anymore.
-We show, however, that the problem still has a 
-$\frac{1}{2} - \varepsilon$-approximation algorithm.
-Finally, we argue that the local search algorithm can be trivially generalized
-to handle the new variant of the problem while keeping the same approximation
-guarantees.
+%%%%%
 
-To see why the group carpool problem can not be treated as a
-submodular maximization problem considered the instance given in
-Figure~\ref{fig:not submodular}.
+\subsection{Submodular Maximization}
+
+To see why the group carpool problem can
+not be treated as a submodular maximization problem considered the
+instance given in Figure~\ref{fig:not submodular}.
 
 \begin{figure}
-\caption{
-\label{fig:not submodular}
-Consider the following instance where node capacity are written inside nodes, 
-arcs are labeled with their size and all weights are equal to 1.
-It is easy to see that if $f(S)$ is the optimal solution where $S$ is the set of
-drivers, then $f(A) + f(B) = 2 \leq 3 = f(A \cup B) + f(A \cap B)$,
-thus, $f$ is not submodular. 
-}
 \begin{center}
@@
 \end{center}
+\caption{Consider the following instance where node capacity are
+written inside nodes, arcs are labeled with their size and all weights
+are equal to 1.  It is easy to see that if $f(S)$ is the optimal
+solution where $S$ is the set of drivers, then $f(A) + f(B) = 2 \leq 3
+= f(A \cup B) + f(A \cap B)$, thus, $f$ is not submodular.}
+\label{fig:not submodular}
 \end{figure}
+
+%%%%%
+
+\subsection{A $(2+\eps)$-approximation Algorithm}
+
+\todo[inline]{write a theorem and a proof}
+
+We now argue that this algorithm can be generalized to solve the group carpool
+matching problem.
+The main concern when trying to adopt the algorithm to the group carpool
+matching is how to determine if a vertex can be improved.
+Observe that Remark~\ref{rem:improve} does not hold anymore.
+If the maximum possible capacity is bounded, one can test for improvement of
+$v$ by considering all the subsets of edges intersecting $v$. 
+When the capacity is unbounded, however, it is easy to see that efficient
+way to test improvement implies a solution to the Knapsack problem.
+Indeed, if this is the case, one can test for improvement by using a known FPTAS
+for Knapsack, this is in the cost of additional $\varepsilon$ reduction in the
+approximation ratio of the algorithm.
+
+%%%%%
+
+\subsection{A $(\frac{2\cmax}{\cmax+1} + \eps)$-approximation Algorithm}
+
+\todo[inline]{complete}
+
+We now argue that the local sear

### 2017-01-30 src/hardness.tex
Merge Dror

--- 2016-12-05 src/hardness.tex
@@
-Formally, the (unweighted) minimum dominating set problem is defined as
-$\min_{D}(|D|)$,
-where $D$ is any feasible dominating set.
-It is also easy to see that the (unweighted, undirected, uncapacitated) 
-maximum carpool matching problem can be defined as $max_{D}(|V \setminus D|)$, 
-where $D$ is any feasible dominating set.
-The \textsc{Dominating Set-B} is the problem of finding minimum dominating set on 
-graphs with degree bounded by $B$,
-and it was shown to be APX-hard (for $B \geq 3$) by 
-Papadimitriou et al.~\cite{papadimitriou1988optimization}.
+??????
 
-Let $G$ be a b-bounded degree graph,
-let $D^*(G)$ be a minimum dominating set in $G$,
-and let $C^*(G)$ be a maximum carpool matching in $G$, 
-then the following lemmas hold:
+As we mentioned in the introduction, the maximum spanning star forest
+can not be approximated within a factor of $\frac{31}{32} + \epsilon$
+for any $\epsilon > 0$, unless P$=$NP.  The proof, however, does not
+hold for the case when the maximum capacity is constant.  In this
+subsection we show that the problem remains APX-hard even in this
+case.
 
-\begin{lemma}
-$|C^*| = |V| - |D^*|$
-\end{lemma}
+??????
 
+Formally, the (unweighted) \textsc{Minimum Dominating Set} problem is
+defined as follows.  The input is an undirected graph $G = (V,E)$, and
+a feasible solution, or a \emph{dominating set}, is a subset
+$D \subseteq V$ that dominates $V$ namely such that
+$D \cup \bigcup_{v \in D} N(v) = V$, where $N(v)$ is the neighborhood
+of $v$.  The goal is to find a minimum cardinality dominating set.
+%
+\textsc{Minimum Dominating Set-$b$} is the special case of
+\textsc{Minimum Dominating Set} in which
+the maximum degree of a vertex in the input graph $G$ is bounded by
+$b$.  The problem was shown to be APX-hard, for $b \geq 3$, by
+Papadimitriou and Yannakakis~\cite{PapYan88}.
+
+We now consider the unweighted and undirected special case of
+the \carpool problem.  In this case, the input consists of an
+undirected graph $G$ and a capacity function $c$, and the goal is to
+find a carpool matching $M$ that maximizes $\abs{P_M}$.
+
+Given an undirected graph $G$, let $D^*$ be a minimum cardinality
+dominating set, and let $M^*$ be an optimal carpool matching with
+respect to $G$ and the capacity function: $c(v) = \deg(v)$, for every
+$v \in V$.
+
+\begin{observation}
+$\abs{P_{M^*}} + \abs{D^*} = \abs{V}$ 
+\end{observation}
 \begin{proof}
-The proof follows immediately from the definitions of the two problems. 
+Given a carpool matching $M$, observe that $D_M \cup Z_M$ is a
+dominating set.  In the other direction, a dominating set $D$ induces
+a carpool matching of size $\abs{V \setminus D}$.
 \end{proof}
 
-\begin{lemma}
-\label{lm:optc_leq_boptd}
-$|C^*| \leq b \cdot |D^*|$
-\end{lemma}
-
-\begin{proof}
-The proof follows directly from the observation that $|D^*| \geq \frac{|V|}{b}$.
-\end{proof}
-
-Let $C(G)$ be any feasible carpool matching on $G$, then the following lemma holds:
-
-\begin{lemma}
-\label{lm:erreq}
-$|C^*| - |C| = (|V| - |C|) - |D^*|$
-\end{lemma}
-
-\begin{proof}
-$$
-|C^*| - |C| 				= 
-|V| - |D^*| - |C| 	= 
-(|V| - |C|) - |D^*|
-$$
-\end{proof}
-
-Let $D(G)$ be any feasible dominating set in $G$, 
-we argue that $f(G) = G$, and $g(C(G)) = V \setminus C(G)$ 
-define a linear reduction (L-reduction) from the \textsc{Dominating Set-B} problem to the 
-\textsc{\CARPOOL{}} problem.
-\begin{proof}
-By lemma~\ref{lm:optc_leq_boptd} we get that $C^*(f(G)) = C^*(G) \leq b \cdot D^*(G)$,
-and by lemma~\ref{lm:erreq} we get that 
-\begin{equation}
-\begin{split}
-|C^*(f(G))| - |C(G)|		& = |C^*(G)| - |C(G)| 			\\
-							& = (|V| - |C(G)|) - |D^*(G)|	\\
-							& = |g(C(G))| - |D^*(G)|
-\end{split}
-\end{equation}
-\end{proof}
+We use this duality to obtain a hardness result for \carpool.
 
 \begin{theorem}
-The \textsc{\CARPOOL{}} problem is APX-hard.
+The \carpool problem is APX-hard, even for undirected and unweighted
+instances with maximum capacity bounded by $b$, for $b \geq 3$.
 \end{theorem}
+\begin{proof}
+We prove the theorem by presenting an $L$-reduction from
+\textsc{Minimum Dominating Set-$b$}.
+(For details on $L$-reductions the reader is referred to~\cite{??}.)
 
-\begin{proof}
-The proof follows directly from the above linear reduction and the fact that 
-\textsc{Dominating Set-B} is APX-hard. 
+We define a function $f$ from \textsc{Minimum Dominating Set-$b$}
+instances to \carpool instances as follows: $f(G) = (G,c)$, where
+$c(v) = \deg(v)$, for every $v \in V$.  Next, we define a function $g$
+that given a carpool matching computes a dominating set as follows:
+$g(M) = V \setminus P_{M}$.  Both $f$ and $g$ can be computed in
+polynomial time.
+
+Let $D^*$ be an optimal dominating set with respect to $G$, and let
+$M^*$ be an optimal carpool matching with respect to $G$ and $c$.
+Since $|D^*| \geq \frac{|V|}{b+1}$, it follows that 
+\[
+\abs{P_{M^*}} \leq b \abs{D^*}
+~,
+\]
+In addition, if $M$ is a carpool matching, we have that
+\[
+\abs{D_M \cup Z_M} - \abs{D*}
+= (\abs{V} - \abs{P_M}) - \abs{D^*}
+= \abs{P_{M^*}} - \abs{P_M}
+~.
+\]
+Hence, there is an $L$-reduction from \textsc{Minimum Dominating
+Set-$b$} to unweighted and undirected \carpool with bounded capacity
+$b$.
 \end{proof}

### 2017-01-30 src/intro.tex
Merge Dror

--- 2016-11-20 src/intro.tex
@@
-Carpooling, is the sharing of car journeys so that more than one person travels
-in a car.
-Knapen et al.~\cite{knapen2013estimating} describe an automatic service
-to match commuting trips.
-Users of the service register their personal profile and a set of periodically
-recurring trips, 
-and the service advises registered candidates on how to combine their commuting
-trips by carpooling.
-The service acts in two phases.
+Carpooling is the sharing of car journeys so that more than one
+person travels in a car.  Knapen et al.~\cite{knapen2013estimating}
+describe an automatic service to match commuting trips.  Users of the
+service register their personal profile and a set of periodically
+recurring trips, and the service advises registered candidates on how
+to combine their commuting trips by carpooling.  The service acts in
+two phases.
 
@@
 
-The second phase can be modeled in terms of graph theory.
-Given a directed graph $G = (V, A)$.
-Each vertex $v \in V$ corresponds to a user of the service and an arc
-$(u, v)$ exists if the user corresponding to vertex $u$ is willing to
-commute with the user corresponding to vertex $v$.
-A capacity function $ c: V \rightarrow \N $ is defined
-according to the number of passengers each user can drive if she was
-selected as a driver.
-A weight function $w : A \rightarrow \R $ defines the amount of
-satisfaction $w(u, v)$,
-that user $u$ gains when riding with user $v$.
+The second phase can be modeled in terms of graph theory.  Given a
+directed graph $G = (V, A)$, each vertex $v \in V$ corresponds to a
+user of the service and an arc $(u, v)$ exists if the user
+corresponding to vertex $u$ is willing to commute with the user
+corresponding to vertex $v$.  A capacity function $ c:
+V \rightarrow \N $ is defined according to the number of passengers
+each user can drive if she was selected as a driver.  A weight
+function $w : A \rightarrow \R $ defines the amount of satisfaction
+$w(u, v)$ that user $u$ gains when riding with user $v$.
+%
+%Let $(G,c,w)$ be a carpool instance.
+If $(u,v) \in A$ implies that $(v,u) \in A$ and $w(u,v) = w(v,u)$, we
+call the instance \emph{undirected}.  If $w(v,u) = 1$, for every
+$(v,u) \in A$, then we call the instance
+\emph{unweighted}.  If $c(v) = \infty$, for every $v$, then we
+call the instance \emph{uncapacitated}.
 
-A feasible \emph{carpool matching} (matching) is a triple 
-$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
-and $M$ is a subset of $A \cap (P \times D)$,
-under the constraints that for every driver $d \in D$, 
-$\din(d) \leq c(d)$, 
-and for every passenger $p \in P$, ${\dout(p) \leq 1}$.
-In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
-total weight of $M$.
-In other words, the \textsc{\CARPOOL{}} problem is about finding a set of 
-(directed toward the center) vertex disjoint stars 
-that maximizes the total weights on the arcs.
-Figure~\ref{fig:carpool} is an example of the \textsc{\CARPOOL{}} problem.
+Given a directed graph $G$ and a subset $M \subseteq A$, define
+$\din[M](v) \eqdf \abs{\set{u :(u,v) \in M}}$ and
+$\dout[M](v) \eqdf \abs{\set{u :(v,u) \in M}}$.
+%
+A feasible \emph{carpool matching} is a subset of arcs, $M \subseteq
+A$, such that every $v \in V$ satisfies:%
+\begin{inparaenum}[(i)]
+\item $\din[M](v) \cdot \dout[M](v) = 0$,
+\item $\din[M](v) \leq c(v)$, and 
+\item $\dout[M](v) \leq 1$.
+\end{inparaenum}
+A vertex $v$ for which $\dout[M](v) = 1$ is a \emph{passenger}, and a
+vertex for which $\dout[M](v) = 0$ is a driver who has $\din[M](v)$
+passengers.  In the \carpool problem the goal is to find a matching
+$M$ of maximum total weight, namely to minimize
+$w(M) \eqdf \sum_{(v,u) \in M} w(v,u)$.  In other words, the \carpool
+problem is about finding a set of (directed toward the center) vertex
+disjoint stars that maximizes the total weight of the arcs.
+Figure~\ref{fig:carpool} is an example of the \carpool problem.
 
@@
 
-Hartman et al.~\cite{hartman2013optimal} proved that the
-\emph{\CARPOOL{}} problem considered in this paper is NP-hard,
-and that the problem remains NP-hard even for a binary weight function when
-the capacity function $c(v) \leq 2$ for every vertex in $V$.
-It is also worth mentioning, that in the undirected, uncapacitated, unweighted
-variant of the problem, the set of drivers in an optimal solution
-form a minimum dominating set.
-When the set of drivers is known in advanced, however, the problem becomes
-tractable and can be solved using a reduction to a flow network problem.
+In this paper we also consider an extension of \carpool, called \gcp,
+in which each vertex represents a group of passengers.  Group sizes
+are non-uniform, and we consider the case where a group size may
+change as a function of the driver.  Formally, each arc $(u,v) \in A$
+is associated with a size $s(u,v) \in \N$, and the constraint
+$\din[M](v) \leq c(v)$ is replaced with the constraint
+$\sum_{u:(u,v) \in M} s(u,v) \leq c(v)$.
+%
+Notice that \textsc{Knapsack} is the special case, where only arcs
+directed at a single vertex have non-zero weights.
 
-Agatz et al.~\cite{agatz2012optimization} outlined the optimization challenges
-that arise when developing technology to support ride-sharing and survey the
-related operations research models in the academic literature.  
-Hartman et al.~\cite{hartman2014theory} designed several heuristic algorithms
-for the \CARPOOL{} problem and compared 
-their performance on real data.
-Other heuristic algorithms were developed as well~\cite{knapen2014exploiting}.
-Arkin et al.~\cite{arkin2004approximations}, considered other variants of
-capacitated star packing where a capacity vector is given as part of the input and 
-capacities need to be assigned to vertices.
+%%%%%
 
-Nguyen et al.~\cite{nguyen2008approximating} considered the \textsc{spanning star forest} problem
-(the undirected, uncapacitated, unweighted variant of the problem).
-They proved the following results:
-\begin{enumerate*}
-\item
-there is a polynomial-time approximation scheme for planner graphs;
-\item 
-there is a polynomial-time $\frac{3}{5}$-approximation algorithm for graphs;
-\item 
-there is a polynomial-time $\frac{1}{2}$-approximation algorithm for weighted graphs.
-\end{enumerate*}
-They also showed how to apply the spanning star forest model to aligning multiple
-genomic sequences over a tandem duplication region.
-Chen et al.~\cite{chen2007improved} improved the approximation ratio to 0.71,
-and also showed that the problem can not be approximated to within a factor of
-$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ under the assumption 
-that $\text{P} \neq \text{NP}$.
-It is not clear, however, if any of the technique used to address the
+\subparagraph{Related work.}
+%
+Hartman et al.~\cite{hartman2013optimal} proved that the \carpool
+problem considered in this paper is NP-hard, and that the problem
+remains NP-hard even for a binary weight function when the capacity
+function $c(v) \leq 2$ for every vertex in $V$.  It is also worth
+mentioning, that in the undirected, uncapacitated, unweighted variant
+of the problem, the set of drivers in an optimal solution form a
+minimum dominating set (see Section~\ref{sec:hardness}).  When the set
+of drivers is known in advanced, however, the problem becomes
+tractable and can be solved using a reduction to a flow network
+problem.
+
+Agatz et al.~\cite{agatz2012optimization} outlined the optimization
+challenges that arise when developing technology to support
+ride-sharing and survey the related operations research models in the
+academic literature.  Hartman et al.~\cite{hartman2014theory} designed
+several heuristic algorithms for the \carpool problem and compared
+their performance on real data.  Other heuristic algorithms were
+developed as well~\cite{knapen2014exploiting}.  Arkin et
+al.~\cite{arkin2004approximations} considered other variants of
+capacitated star packing where a capacity vector is given as part of
+the input and capacities need to be assigned to vertices.
+
+Nguyen et al.~\cite{nguyen2008approximating} considered
+the \textsc{spanning star forest} problem (the undirected,
+uncapacitated, unweighted variant of the problem).  They proved the
+following results:
+\begin{inparaenum}[(i)]
+\item there is a polynomial-time approximation scheme for planner graphs;
+\item there is a polynomial-time $\frac{3}{5}$-approximation algorithm for graphs;
+\item there is a polynomial-time $\frac{1}{2}$-approximation algorithm for weighted graphs.
+\end{inparaenum}
+They also showed how to apply the spanning star forest model to
+aligning multiple genomic sequences over a tandem duplication region.
+Chen et al.~\cite{chen2007improved} improved the approximation ratio
+to 0.71, and also showed that the problem can not be approximated to
+within a factor of $\frac{31}{32} + \epsilon$ for any $\epsilon > 0$
+under the assumption that $\text{P} \neq \text{NP}$.  It is not clear,
+however, if any of the technique used to address the
 \textsc{spanning star forest} problem can be generalized to approximate the
@@
 
-In section~\ref{sec:sub} we show that the problem can be formulated as
-unconstarints submodular maximization problem, thus it has a 2-approximation
-algorithm.
-In section~\ref{sec:local} we consider the unweighted variant of the problem.
-We show that when the maximum possible capacity, $C$, is fixed, there is a 
-$(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm for the any $\varepsilon > 0$.
+Kutiel~\cite{Kutiel16}
+
+\todo[inline]{add a paragraph about the paper from arXiv}
+
+\todo[inline]{Mention Goerge's paper with Amotz (ESA)}
+
+%%%%%
+
+\subparagraph{Our contribution.}
+%
+In Section~\ref{sec:sub} we show that the problem can be formulated as
+unconstrained submodular maximization problem, thus it has a
+randomized $2$-approximation algorithm due to~\cite{BFNS15}.  We also
+provide a deterministic $(2+\eps)$-approximation algorithm, for any
+$\eps>0$, which is based on local search.
+
+In Section~\ref{sec:local} we consider the unweighted variant of the
+problem.  We provide a $(\frac{2\cmax}{\cmax+1} + \eps)$-approximation
+algorithm, for any $\eps>0$, where $\cmax$ is the maximum capacity.
+We also show that \carpool is APX-hard even if $\cmax \leq 3$.
+%
+In Section~\ref{sec:group} we consider \gcp.  We first show that \gcp
+cannot be formulated as an unonstrained submodular maximization
+problem as \carpool.  We show, however, that this problem still admits
+a $(2 + \eps)$-approximation algorithm, and argue that the local
+search algorithm generalizes to \gcp as well.

### 2017-01-30 src/local.tex
Merge Dror

@@
-The local search algorithm maintains a feasible matching throughout its execution
-and operates in 
-iterative manner where in each iteration it tries to find a better solution by
-replacing a subset of the edges in the current solution with 
-another (larger) subset of edges not in the solution.
-The local search algorithm halts when no improvement can be done.
-The algorithm is described in Algorithm~\ref{alg:local}.
+In this section we present a $(\frac{2c_{\max}}{c_{\max} + 1}
++ \eps)$-approximation algoithm for unweighted \carpool whose running
+time is polynomial if $c_{\max} = O(1)$.
+
+Let $k$ be an integer to be determined later.  The local search
+algorithm maintains a feasible matching throughout its execution and
+operates in iterative manner where in each iteration it tries to find
+a better solution by replacing a subset of at most $k$ edges in the
+current solution with another (larger) subset of edges not in the
+solution.  The local search algorithm halts when no improvement can be
+done.  The algorithm is described in Algorithm~\ref{alg:local}.
 
@@
  	$done \leftarrow{}$ \True							\\
- 	\For{$M' \in M : |M'| \leq k$}{
- 		\For{$A' \in A \setminus M : |A'| = |M'| + 1$}{
+ 	\ForAll{$M' \subseteq M : |M'| \leq k$}{
+ 		\ForAll{$A' \subseteq A \setminus M : |A'| = |M'| + 1$}{
 			\If{$M \setminus M' \cup A'$ is feasible}{
@@
 
-\caption{
+\caption{Local Search}
 \label{alg:local}
-Local Search}
 \end{algorithm}
 
+\todo[inline]{fix running time paragraph}
+
 We claim that the local search algorithm halts in polynomial time.
-Observed that in every iteration the algorithm either improves the value of the solution
-by one or otherwise it terminates. 
-Thus, after a maximum of $n$ iterations the algorithm stops.
-In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
-both these operations can be done in polynomial time - $O(n^{Ck + 1})$.
+Observed that in every iteration the algorithm either improves the
+value of the solution by one or otherwise it terminates.  Thus, after
+a maximum of $n$ iterations the algorithm stops.  In every iteration
+we examine all the subsets of edges of a fixed size and test for
+feasibility, both these operations can be done in polynomial time.
 
-To analyze the approximation ratio achieved by the local search algorithm consider an 
-arbitrary but fixed optimal matching $M^*$.
-Given the solution outputted by the local search algorithm, 
-$M$, 
-we build the \emph{star graph} of the two solutions
-in which each node represents a star from the optimal solution 
-and edges exits between two nodes if
-there is a star in $S(M)$ that intersect the two
-corresponding stars of the optimal solution, 
-formally $G^{M^*}_M = (S, E)$ where $\{v_i : S^*_i \in S(M^*) \}$ 
-and 
-$E = \{(v_i, v_j) : 
-\exists S \in M,
-S \cap S^*_i \neq \emptyset \land S \cap S^*_j \neq \emptyset,
-\}$.
+Observe that a vertex $v \in D_M \cup Z_M$ is the center of
+a \emph{directed star} whose leaves are the passengers in the set
+$P_M(v) = \set{u : (u,v) \in M}$.  ($P_M(v) = \emptyset$, for $v \in
+Z_M$.)
+%
+Given a carpool matching $M$, we define $\calS(M)$ to be the set of
+stars that are induced by $M$.  Denote by $V(S)$ the set of vertices
+of a star, i.e., if $v$ is the center $S$, then $V(S) = \{v\} \cup
+P_M(v)$.  Also, for $\calT \subseteq \calS(M)$, define
+$V(\calT) \eqdf \bigcup_{S \in \calT} V(S)$.  Also, let $A(S)$ be the
+edges of $S$, and define $A(\calT) \eqdf \bigcup_{S \in \calT} A(S)$.
+
+To analyze the approximation ratio achieved by the local search
+algorithm consider an arbitrary but fixed optimal matching $M^*$.
+Given the solution outputted by the local search algorithm, $M$, we
+build the \emph{star graph} of the two solutions in which each node
+represents a star from the optimal solution, namely from $\calS(M^*)$,
+and an edge exists between two nodes if there is a star in $\calS(M)$
+that intersects the two corresponding stars of the optimal solution.
+%
+Formally $H = (\calS(M^*), E)$ where
+\[
+E = \set{(S^*_i, S^*_j) : \exists S \in \calS(M), 
+         V(S) \cap V(S^*_i) \neq \emptyset \land
+         V(S) \cap V(S^*_j) \neq \emptyset}
+~.
+\]
 Figure~\ref{fig:conflict} depicts a star graph.
 
-\begin{figure}[ht]
+\begin{figure}[t]
 \centering
@@
 \caption[]{
-\label{fig:conflict}
 \subref{subfloat:input} 
@@
 }
+\label{fig:conflict}
 \end{figure}
-
-For a group of vertices, $U$, denote by $w^*(U)$ the sum of the degrees 
-induced by the underlying graph of the optimal solution on this set, i.e.
-$\sum_{u \in U} \dinout[M^*](u)$, 
-and let $w(S)$ be the sum of the degrees 
-induced by the underlying graph of the local search solution on this set, i.e.
-$\sum_{u \in U} \dinout(u)$.
 
@@
 \label{lemma:r}
-If $k \geq \text{TODO}$ then in any connected induced graph of $G^{M^*}_M$, 
-$G'= G^{M^*}_M[U]$, 
-$
-\frac{w(U)}{w^*(U)} 
-\geq \frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
-$.
+Let $\calT \subseteq \calS(M^*)$ that induces a connect subgraph of
+$H$.  If $\abs{A(\calT)} \leq k$, then
+\[
+\frac{\deg_M(V(\calT))}{\deg_{M^*}(V(\calT))} 
+\geq \half + \inv{2\cmax} - \inv{2\cmax\abs{\calT}}
+~.
+\]
+\end{lemma}
+\begin{proof}
+Consider the solution $M'$ obtained from the $M$ by removing all the
+edges from $M$ that intersect $V(\calT)$ and adding all the edges from
+$M^*$ that intersect $V(\calT)$.  Observe that if an edge $(u,v)$ in
+$M^*$ intersects $V(\calT)$, then $\set{u,v} \in V(\calT)$ by the
+definition of the graph $H$.  Hence, $M'$ is feasible carpool
+matching.
+
+Since $\calT$ induces a connected subgraph of $H$, the removal of
+edges in $M$ that intersect $V(\calT)$ decreased $\abs{M}$ by at most
+$\deg_M(V(\calT)) - \abs{\calT} + 1$.
+%
+On the other hand, the increase in size is exactly
+ $\half \deg_{M^*}(V(\calT)) \leq \cmax \abs{\calT}$.
+%
+Since $\abs{A(\calT)} \leq k$, we know that this difference can not be
+positive, or else, the local search algorithm would not have been
+terminated.  Thus 
+\(
+\half \deg_{M^*}(V(\calT)) \leq \deg_M(V(\calT)) - \abs{\calT} + 1
+\),
+and so
+\[
+\frac{\deg_M(V(\calT))}{\deg_{M^*}(V(\calT))}
+\geq \half + \frac{\abs{\calT} - 1}{\deg_{M^*}(V(\calT))}
+\geq \half + \frac{\abs{\calT} - 1}{2\cmax \abs{\calT}}
+~,
+\]
+as required.
+\end{proof}
+
+\begin{lemma}
+If $k \geq 24\cmax$, then $\abs{M} \geq (\frac{\cmax+1}{2\cmax}
+- \frac{2}{k}) \cdot \abs{M^*}$.
+\end{lemma}
+\begin{proof}
+Consider a maximal (with respect to set inclusion) connected component
+of $H$ induced by the vertices in $\calT \subseteq \calS(M^*)$.
+%
+If $\abs{M \cap A(\calT)} \leq k$, then it must be that $\abs{M \cap
+A(\calT)} = \abs{M^* \cap A(\calT)}$, since otherwise $M \cap
+A(\calT)$ could be improved.
+
+It remains to consider a maximal component $\calT$ such that If
+$\abs{M \cap A(\calT)} > k$.  Observe that since the number of edges
+in a $S \in \calS(M^*)$ is at most $\cmax$, it must be that
+$\abs{V(\calT)} > \frac{k}{\cmax}$.
+%
+Given such a component $\calT$, we partition its vertex set into
+several sets, each of size at least $\frac{k}{4\cmax}$.  We do this as
+follows.  First construct any spanning tree of $\calT$ (say, by
+running DFS).  It is well known that a tree of $t$ vertices can be
+split into two subtrees each with at most $\floor{2t/3}+2$ vertices
+(see, e.g., \cite{???}).  Moreover, if $t \geq 24$, each such subtree
+contains at most $\frac{3}{4}t$.  Hence, we can decompose $\calT$
+recursively into vertex sets whose sizes is between $\frac{k}{\cmax}$
+and $\frac{k}{4\cmax}$, assuming that $\frac{k}{\cmax} \geq 24$.
+%
+Each such vertex set $\calX$ is connected and contains at most
+$\frac{k}{\cmax}$ stars.  Hence $\abs{A(\calX)} \leq k$.  Due to
+Lemma~\ref{lemma:r} and since $\abs{V(\calX)} \geq \frac{k}{4\cmax}$,
+we have that
+\[
+\frac{\deg_M(V(\calX))}{\deg_{M^*}(V(\calX))} 
+\geq \half + \inv{2\cmax} - \frac{2}{k}
+~.
+\]
+Since $\deg_{M^*}(V(\calT)) = \sum_{\calX} \deg_{M^*}(V(\calX))$ and
+$\deg_M(V(\calT)) = \sum_{\calX} \deg_M(V(\calX))$, it follows that
+\[
+\frac{\deg_M(V(\calT))}{\deg_{M^*}(V(\calT))}
+\geq \half + \inv{2\cmax} - \frac{2}{k}
+~,
+\]
+and thus $\abs{M \cap A(\calT)} \geq (\frac{\cmax + 1}{2\cmax}
+- \frac{2}{k}) \abs{M^* \cap A(\calT)}$.
+\end{proof}
+
+\begin{corollary}
+\label{cor:local}
+There exists a $(\frac{2\cmax}{\cmax+1} +\eps)$-approximation
+algorithm for \carpool, for every $\eps>0$.
+\end{corollary}
+
+\iffalse %%%%% Rmeoved
+
+\begin{lemma}
+\label{lemma:dec}
+Given a parameter $k$, a bounded degree connected graph $G$, with a
+maximum degree $d$ can be decomposed into connected components of size
+at least $k$, and at most $d(k-1) + 1$.
 \end{lemma}
@@
 \begin{proof}
-Consider the solution obtained from the $M$ by removing all the edges from $M$
-that intersect the induced subgraph, and adding all the edges from $M^*$ that
-intersect the induced subgraph.
-It is easy to verify that this is a feasible solution.
-We now bound from below the difference in the value of the solution.
-The value decrease due to the removal of the edges by at most $w(U) - |U| + 1$,
-and increase by exactly $\frac{w^*(U)}{2} \leq C |U|$.
-We know that this difference can not be positive, or else, the local search
-algorithm would not have been terminated.
-Thus 
-$\frac{w^*(U)}{2} \leq w(U) - |U| + 1$ 
-and so
-$
-\frac{w(U)}{w^*(U)} 
-\geq 
-\frac{1}{2} + \frac{|U|}{w^*(U))} - \frac{1}{w^*(U))}  
-\geq
-\frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
-$
-\end{proof}
-
-\begin{lemma}
-\label{lemma:dec}
-Given a parameter $k$, a bounded degree connected graph $G$, with a maximum
-degree $d$ can be decomposed into connected components of size at least $k$, and at most
-$d(k-1) + 1$.
-\end{lemma}
-
-\begin{proof}
-We give a constructive proof.
-Start constructing a connected component by adding adjacent vertices
-one by one to the component and removing them from the graph.
-If at some point, removing a vertex disconnect the graph, add all the small
-components (of size less than $k$) to the constructed component and decompose
-the large components (of size at least $k$) recursively.
-Note that removing a vertex can break the graph to at most $d - 1$ additional
-components.
+We give a constructive proof.  Start constructing a connected
+component by adding adjacent vertices one by one to the component and
+removing them from the graph.  If at some point, removing a vertex
+disconnect the graph, add all the small components (of size less than
+$k$) to the constructed component and decompose the large components
+(of size at least $k$) recursively.  Note that removing a vertex can
+break the graph to at most $d - 1$ additional components.
 \end{proof}
@@
 \label{theorem:local search}
-The local search is ($\frac{1}{2} + \frac{1}{2c} - \varepsilon$)-approximation
-algorithm.
+The local search is ($\frac{1}{2} + \frac{1}{2c}
+- \varepsilon$)-approximation algorithm.
 \end{theorem}
@@
 \begin{proof}
-Combine lemma~\ref{lemma:dec}, and lemma~\ref{lemma:r}, 
-and observe that the maximum degree in $G^{M^*}_M$ is $(C + 1)^C$ to
-get the desire result.
+Combine lemma~\ref{lemma:dec}, and lemma~\ref{lemma:r}, and observe
+that the maximum degree in $G^{M^*}_M$ is $(C + 1)^C$ to get the
+desire result.
 \end{proof}
 
-We now show that Theorem~\ref{theorem:local search} is tight.
-Consider the example in Figure~\ref{fig:local search tight},
-the example is for the special case when $k=11$ and $C=2$ but this example can
-be generalized in a straightforward manner.
-One can verify that as the graph in the example growth, 
-the ratio between the optimal solution and the local search solution approaches
-$\frac{3}{4}$.
+\fi %%%%% End removed
+
+\todo[inline]{Add a proper theorem}
+
+We now show that Corollary~\ref{cor:local} is tight.  Consider the
+example in Figure~\ref{fig:local search tight}, the example is for the
+special case when $k=11$ and $C=2$ but this example can be generalized
+in a straightforward manner.  One can verify that as the graph in the
+example growth, the ratio between the optimal solution and the local
+search solution approaches $\frac{3}{4}$.
+
 \begin{figure}
 \begin{center}
-\caption{
+\input{fig-local-tight}
+\caption{A tight example for Theorem~\ref{theorem:local search}. 
+The optimal solution is given by the red solid arcs while the local
+search solution is given by the green, dashed arcs.  The solution can
+be improved by the local search algorithm only if it removes all the
+edges.}
 \label{fig:local search tight}
-A tight example for Theorem~\ref{theorem:local search}. 
-The optimal solution is given by the red solid arcs while the local search
-solution is given by the green, dashed arcs.
-The solution can be improved by the local search algorithm only if it removes
-all the edges. 
-}
-\input{fig-local-tight}
 \end{center}

### 2017-01-30 src/local_search.tex
Merge Dror

In this subsection we give a local search $(2+\eps)$-approximation
algorithm for \carpool.

We need a few definitions before presenting our algorithm.
%
Let $M$ be a feasible carpool matching.  The weight $w_M(v)$ of a
vertex $v$ with respect to $M$ is the sum of the weights of the arcs
in $M$ that are incident on $v$, namely
\[
w_M(v) \eqdf \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u)
~.
\]
For a subset of vertices $U \subseteq V$ we define
$w_M(U) \eqdf \sum_{v \in U} w_M(v)$.

We now argue that, with respect to any carpool matching $M$, the total
weight of all the vertices is equal to twice the weight of the matching.

\begin{observation}
\label{lm:val-twice}
$\sum_{v \in V} w_M(v) = 2 \sum_{e \in M} w(e)$.
\end{observation}
\begin{proof}
\(
\sum_{v \in V} w_M(v)
= \sum_{v \in V} \sum_{(u, v) \in M} w(u, v) +
    \sum_{v \in V} \sum_{(v, u) \in M} w(v, u) 
= 2 \sum_{e \in M} w(e)
\).
\end{proof}

Denote by $\delta(u,v)$ the difference between the weight of the arc
and the value of its source vertex, that is:
\[
\delta_M(u, v) \eqdf w(u, v) - w_M(u)
~.
\]
For a subset $S \subseteq A$ of arcs define
$\delta(S) \eqdf \sum_{(u,v) \in S} \delta(u,v)$.

A subset $S_v$ of arcs entering a vertex $v$, whose size is not
greater than the capacity of $v$, is called an \emph{improvement} to
vertex $v$ if $\delta(S_v)$ is greater than the value of $v$.  More
formally,

\begin{definition}
A subset $S_v \subseteq A \cap (V \times \{v\})$ is
an \emph{improvement} with respect to a carpool matching $M$, if the
following conditions hold:%
\begin{inparaenum}[(i)]
\item $\abs{S_v} \leq c(v)$, and
\item $\delta_M(S_v) > w_M(v)$.
\end{inparaenum}
Furthermore, if there exists an improvement for a vertex $v$, we say
that vertex $v$ can be \emph{improved}.
\end{definition}

Given an arc $(u,v)$, let $\inc(u,v)$ be the set of arcs that incident
$(u, v)$, namely
\[
\inc(u,v) = (N^-(u) \times \{u\}) \cup (\{v\} \times N^+(v))
~.
\]
If $S$ is a set of arcs, then $\inc(S) \eqdf \bigcup_{(u,v) \in
S} \inc(u,v)$.

Figure~\ref{fig:defs} depicts all the above definitions.

\begin{figure}
\centering
\input{fig-val-delta}
\caption{In this example $M$ is the set of the blue, dashed arcs.
In this case $w_M(2) = 7$, $w_M(3) = 2$, and $w_M(6) = 0$.  Also,
$\delta_M(2, 3) = 1$ and $\delta_M(6, 3) = 2$.  The set $\set{(2,3),
(6,3)}$ is an \emph{improvement} to vertex 3 and $\inc(2,3)
= \set{(1,2),(4,2),(3,5),(6,3)}$.}
\label{fig:defs}
\end{figure}

We are now ready to describe our local search algorithm
(Algorithm~\ref{alg:grd}).  The algorithm starts with an empty
carpool matching $M$, and in every iteration it looks for a vertex
that can be improved.  If there exists such a vertex, then the
algorithm removes the arcs that are incident on it from $M$, and adds
the arcs that improve the vertex.  The algorithm terminates when no
vertex can be improved.  Figure~\ref{fig:improvement} depicts an
improvement step.

\begin{algorithm}
\caption{Local Search}
\label{alg:ls}
$M \gets \emptyset$ \\
\Repeat{$\text{done}$}{
	$\text{done} \leftarrow \textsc{True}$ \\
	\For{$v \in V$}{
		\If{$\exists$~improvment~$S_v$}{
			$M \leftarrow M \setminus \inc(S_v) \cup S_v$	\\
			$\text{done} \leftarrow \textsc{False}$ \\
		}
	}
}
\end{algorithm}

\begin{figure}
\centering
\input{fig-improvement}
\caption[]{
\label{fig:improvement}
\subref{sub:can improved}
A matching that can be improved
\subref{sub:improved}
The matching after improving vertex 3
}
\end{figure}

We proceed to bound the approximation ratio of the algorithm, assuming
termination.

For a vertex $v$ and a set $S$ of edges entering $v$, let $N^-_S(v)
= \set{u : (u,v) \in S}$ be the set in-neighbors corresponding to $S$.

\begin{lemma}
\label{lm:no improve}
Let $M$ be a matching computed by the local search algorithm.  Let $v$
be a vertex with no improvement, and let $S \subseteq N^-(v)$, such
that $\abs{S} \leq c(v)$, then $w(S) \leq w_M(v) + w_M(N^-_S(v))$.
\end{lemma}
\begin{proof}
If no improvement exists, then
\[
w(S) - w_M(N^-_S(v))
=    \sum_{(u,v) \in S} (w(u,v) - w_M(u))
=    \delta_M(S) 
\leq w_M(v)
~.
\]
\end{proof}

To bound the approximation ratio of the algorithm, we use a charging
scheme argument.

\begin{lemma}
If Algorithm~\ref{alg:ls} terminates, then the computed solution is a
$2$-approximation.
\end{lemma}
\begin{proof}
Let $M$ be the matching produced by the algorithm, and let $M^*$ be an
optimal matching.  We load every vertex $v$ with an amount of money
equal to $w_M(v)$, and then we show that this is enough to pay for
every arc in the optimal matching.  Due to
Observation~\ref{lm:val-twice} the total amount of money that we use
is exactly twice the weight of $M$.

Consider a driver $v \in D_{M^*}$, and let $S = (V \times \{v\}) \cap
M^*$.  By lemma~\ref{lm:no improve} we know that $w(S) \leq w_M(v) +
w_M(N^-_S(v))$, thus we can pay for $S$, using the money on $v$ and on
$N^-_S(v)$.  Clearly, these vertices will not be charged again.
\end{proof}

We show that our analysis is tight using in Figure~\ref{fig:grd
worst}.

\todo[inline]{fix figure: directed graph}

\begin{figure}
\centering
\input{fig-2-tight}
\caption[]{
\label{fig:grd worst}
GRD algorithm, worst case example: \\
Consider a path with $2n + 1$ arcs,
and alternating arc weights (2 and 1),
if the GRD algorithm selects all the 1 weighted arcs,
then no further improvement can be done and the value of the matching is $n + 1$,
while the optimal matching has value of $2n$.
}
\end{figure}

It remains to consider the running time of the algorithm.

\begin{theorem}
\label{thm:ls}
Algorithm~\ref{alg:ls} is a $2$-approximation algorithm for \carpool,
if edge weights are integral and polynomially bounded.
\end{theorem}
\begin{proof}
First, observe that determining if a vertex $v$ can be improved can be
done efficiently by considering the incoming arcs to $v$ in a
non-increasing order of their $\delta$s, and only ones with positive
values.  A vertex $v$ can be improved, then, if the $\delta$s of the
first $c(v)$ (or less) arcs sum up to more than $w_M(v)$.
%
It follows that the running time of an iteration of the for-loop is
polynomial.  Since the edge weights are integral and polynomially
bounded, the weight of an optimal carpool matching is polynomially
bounded.  The algorithm runs in polynomial time, because in each
iteration the algorithm improves the weight of the matching by at
least one or otherwise it terminates.
\end{proof}

It remains to consider the general case, where weight are not
polynomially bounded.  In this case one can use scaling and rounding
to ensure a polynomial running time in the cost of a $(1+\eps)$ factor
in the approximation ratio.

\begin{theorem}
There exists a $(2+\eps)$-approximation algorithm for \carpool, for
every $\eps > 0$.
\end{theorem}
\begin{proof}
Let $\eps' = \eps/4$.
%
Define the weight function $w'(e)
= \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{\eps'}}$.
%
Let $M^*$ and $M'$ be an optimal carpool matchings with respect to $w$
and $w'$, resp.  We have that
\[
w'(M^*)
=    \sum_{e \in M^*} \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{\eps'}}
>    \sum_{e \in M^*} \paren{ \frac{w(e)}{w_{\max}} \cdot \frac{m}{\eps'} } - m
=    \frac{m}{\eps' w_{\max}} \cdot w(M^*) - m
~.
\]
Since $w(M^*) \geq w_{\max}$, we have that 
\[
w'(M^*)
>    \frac{m}{\eps' w_{\max}} \cdot (w(M^*) - \eps' w_{\max})
\geq \frac{m}{\eps' w_{\max}} \cdot (1-\eps') w(M^*)
~.
\]
By Theorem~\ref{thm:ls}, our local search algorithm computes a
$2$-approximate carpool matching $M$ on $(G, c, w')$, and this
matching satisfies $w'(M) \geq w'(M')/2$.  Furthermore, since
$w'(M') \geq w'(M^*)$, it follows that $w'(M) \geq w'(M^*)/2$.
Therefore
\[
w(M)
\geq \frac{\eps' w_{\max}}{m} w'(M) 
\geq \frac{1}{2} \frac{\eps' w_{\max}}{m} w'(M^*)
>    \frac{1-\eps'}{2} w(M^*)
\geq \frac{w(M^*)}{2+\eps}
~.
\]
\end{proof}

\todo[inline]{what happen if we apply the rule on both directions ?}

### 2017-01-30 src/main.tex
Merge Dror

@@
-\documentclass[draft]{article}
+%\documentclass[11pt,draft]{article}
+%\documentclass[a4paper,11pt]{article}
+\documentclass[a4paper,UKenglish]{lipics-v2016}
 
-\input{in/libs}
+\usepackage{microtype}%if unwanted, comment out or use option "draft"
+
+\usepackage{amsmath,amssymb,mathtools,amsthm}
+\usepackage[linesnumbered, ruled]{algorithm2e}
+\usepackage{xspace}
+\usepackage{subfig}
+\usepackage{paralist}
+%\usepackage{hyperref}
+%\hypersetup{final}
+%\usepackage[inline]{enumitem}
+
+% DEBUG
+%\usepackage{fullpage}
+\usepackage{todonotes}
+%\usepackage{lineno}
+%\linenumbers
+
+% EXTRA
+%\usepackage{authblk}
+
 \input{in/def}
@@
 
-\input{in/title}
-\input{in/authors}
+\renewcommand{\floatpagefraction}{0.7}
+
+\sloppy
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{Improved Approximation Algorithms for the
+Maximum Carpool Matching Problem}
+
+\titlerunning{Improved Approximation Algorithms for Maximum Carpool Matching}
+
+\author[1]{Gilad Kutiel}
+\author[2]{Dror Rawitz%
+\thanks{Supported in part by the Israel Science Foundation (grant no.~497/14).}}
+
+\affil[1]{Department of Computer Science, Technion, Haifa,
+  Israel. \\ \texttt{gkutiel@cs.technion.ac.il}}
+\affil[2]{Faculty of Engineering, Bar Ilan University, Ramat Gan,
+  Israel. \\ \texttt{dror.rawitz@biu.ac.il}}
+
+\authorrunning{G. Kutiel and D. Rawitz}
+
+\Copyright{G. Kutiel and D. Rawitz}
+
+\subjclass{F.2.2 Nonnumerical Algorithms and Problems}
+
+\keywords{approximation algorithms, local search}
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Acces}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
+
 \maketitle
@@
 
-\bibliographystyle{plain}
+\subparagraph*{Acknowledgements.}
+
+We thank David Adjiashvili and Reuven Bar-Yehuda for helpful
+discussions.
+
+%\bibliographystyle{plain}
+\bibliographystyle{plainurl}% the recommended bibstyle
 \bibliography{main}
-% \resizebox{.9\textwidth}{!}{\input{tmp}}
 

### 2017-01-30 src/preliminaries.tex
Merge Dror

In this section

We use standard graph theoretic notation.

$N^-$ and $N^+$.

Define $\deg$

Define $\deg_M(v) \eqdf \din[M](v) + \dout[M](v)$
%
For a subset $U \subseteq V$ of vertices define
$\deg_M(U) \eqdf \sum_{v \in U} \deg_M(u)$.

We define $c_{\max} \eqdf \max_{v \in V} c(v)$.

and $w_{\max} \eqdf \max_{(v,u) \in E} w(v)$.

Given a subset $A' \subseteq A$, we define
$w(A') \eqdf \sum_{(v,u) \in A'} w(v,u)$.

Given a directed graph $G = (V,A)$ and a feasible carpool matching
$M \subseteq A$, we define a partition of $V$ as follows:
\begin{align*}
P_M & \eqdf \set{v : \dout[M](v) = 1} \\
D_M & \eqdf \set{v : \din[M](v) \geq 1} \\
Z_M & \eqdf \set{v : \dout[M](v) = \din[M](c) = 0}
~.
\end{align*}
where $P_M$ is the set of \emph{passengers}, $D_M$ is the set of
\emph{drivers}, and $Z_M$ is the set of \emph{singletons}.

In Figure~\ref{fig: }

### 2017-01-30 src/sub.tex
Merge Dror

--- 2016-11-20 src/sub.tex
@@
-In this section we show that the problem can be formulated as unconstrained
-submodular maximization problem, and thus, it has a 2-approximation algorithm.
+In this section we show that the \carpool problem can be formulated as
+unconstrained submodular maximization problem, and thus it has a
+randomized $2$-approximation algorithm based on~\cite{BFNS15}.
+
+Given a \carpool instance $(G = (V,A), c, w)$, consider a subset
+$S \subseteq V$.  Let $M(S)$ be the maximum weight carpool matching
+that satisfies $D_{M(S)} \subseteq S \subseteq V \setminus P_{M(S)}$,
+namely $M(S)$ is the best carpool matching whose drivers belong to $S$
+and whose passengers belong to $V \setminus S$.  In other words,
+$M(S)$ is the maximum weight carpool matching that is contained in
+$A \cap (V \setminus S) \times S$.
+%
+Given $S$, the carpool matching $M(S)$ can be computed in polynomial
+time using maximum flow as shown in~\cite{??}.
+
+Consider the function $\barw: 2^V \to \R$, where $\barw(S) \eqdf
+w(M(S))$.  In the next lemma we prove that $\bar{w}$ is
+a \emph{submodular set function}.  Recall that a function $f$ is
+submdular if $f(S) + f(T) \geq f(S \cup T) + f(S \cap T)$ for every
+two sets $S$ and $T$ in the domain of $f$.
+
+\begin{lemma}
+$\barw$ is submodular.
+\end{lemma}
+\begin{proof}
+Consider any two subsets $S, T \subseteq V$.  We show that $\barw(S)
++ \barw(T) \geq \barw(S \cup T) + \barw(S \cap T)$.
+%
+Let $M(S \cup T)$ and $M(S \cap T)$ be the optimal carpool matchings
+with respect to $S \cup T$ and $S \cap T$, respectively.
+%
+To prove the lemma we construct two feasible carpool matchings $M_S$
+and $M_T$ such that $M_S \subseteq (V \setminus S) \times S$,
+$M_T \subseteq (V \setminus T) \times T$, and $M_S \cup M_T = M(S \cup
+T) \cup M(S \cap T)$.
+
+First, add all the edges in $M(S \cup T)$ entering $S \setminus T$ to
+$M_S$.  Similarly, add all the edges in $M(S \cup T)$ entering
+$T \setminus S$ to $M_T$.  Observe that $\din[M_S](v) = \din[M(S \cup
+T)](v) \leq c(v)$, for every $v \in S \setminus T$ and that
+$\din[M_T](v) = \din[M(S \cup T)](v) \leq c(v)$, for every $v \in
+T \setminus S$.
+
+Next, add the edges in $M(S \cap T)$ leaving $T \setminus S$ to $S$
+and add the edges in $M(S \cap T)$ leaving $S \setminus T$ to $T$.
+%
+It remains to distribute the edges leaving $V \setminus (S \cup T)$
+and entering $S \cap T$ in both $M(S \cup T)$ and $M(S \cap T)$.  Note
+that there may exist edges $(v,u)$, where $v \not\in S \cup T$, and
+$u \in S \cap T$ such that $(v,u) \in M(S \cup T)$ and $M(S \cap T)$.
+We refer to this edges as \emph{duplicate} edges.
+%
+We add all edges leaving $V \setminus (S \cup T)$ and entering $S \cap
+T$ in $M(S \cap T)$ to $M_S$.  Notice that this is possible, since
+after this addition we have that $\din[M_S](v) \leq \din[M(S \cap
+T)](v) \leq c(v)$, for every vertex $v \in S \cap T$.
+%
+Then we add all duplicate edges in $M(S \cup T)$ to $M_T$.
+%
+The remaining edges are distributed between $M_S$ and $M_T$ without
+violating capacities.  This can be done, since $\din[M(S \cup T)](v)
++ \din[M(S \cap T)](v) \leq 2c(v)$, for every $v \in S \cap T$.
+
+The lemma follows, since $\barw(S) \geq w(M_S)$ and $\barw(T) \geq
+w(M_T)$.
+\end{proof}
+
+Buchbinder et al.~\cite{BFNS15} presented a general randomized
+$2$-approximation algorithm for unconstrained submodular maximization.
+
+\begin{theorem}
+There exists a randomized polynomial time $2$-approximation algorithm
+for \carpool.
+\end{theorem}

### 2017-01-31 src/abstract.tex
Abstract

@@
 feasible \emph{carpool matching} is a subset of arcs, $M \subseteq A$,
-such that every $v \in V$ satisfies:%
+such that every $v \in V$ satisfies:
 \begin{inparaenum}[(i)]
@@
 
-We show that the problem can be formulated as an unconstrained
+The \gcp, is an extension of the \carpool where each vertex represents a
+(unsplittable) group of passengers.
+Each group might have a different size.  
+Formally, each vertex $u \in V$ has a size $s(u) \in \N$,
+and the constraint $\din(v) \leq c(v)$ is replaced with
+$\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
+
+We show that the \carpool can be formulated as an unconstrained
 submodular maximization problem, thus it admits a
-$\frac{1}{2}$-approximation algorithm.  For the unweighted variant of
-the problem when the maximum possible capacity, $C$, is fixed, we give
-a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm for the
-any $\varepsilon > 0$.
-
-We also show that the
-problem remains APX-hard even if $C \leq 3$.
-
-We also consider an extension, called \gcp, in which each vertex
-represents a group of passengers.  Group sizes are non-uniform, and we
-consider the case where a group size may change as a function of the
-driver.  Formally, each arc $(u,v) \in A$ has a size $s(u,v) \in \N$,
-and the constraint $\din[M](v) \leq c(v)$ is replaced with
-$\sum_{u:(u,v) \in M} s(u,v) \leq c(v)$.  We show that \gcp cannot be
-formulated as an unconstrained submodular maximization problem.
-Nevertheless, we give a $(\frac{1}{2} - \varepsilon)$-approximation
-algorithm for this variant, and argue that the local search algorithm
-can be generalized to this variant of the problem when $C$ is fixed.
+$\frac{1}{2}$-approximation algorithm.
+We show that the same formulation does not hold for the \gcp,
+nevertheless, we present a $\frac{1}{2} - \varepsilon$-approximation algorithm
+for the \gcp as well.
+For the unweighted variant of
+the problems when the maximum possible capacity, $C$, is fixed, we give
+a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm.
+We also show that the problem remains APX-hard even if $C \leq 3$.

### 2017-01-31 src/fig-carpool.tex
fix subcaption, no warnings

--- 2016-12-05 src/merge.tex
@@
-\documentclass[draft]{article}
-
-\usepackage{amsmath,amssymb,amsthm,mathtools}
-\usepackage[linesnumbered, ruled]{algorithm2e}
-\usepackage[]{subfig}
-\usepackage{paralist}
-\usepackage{hyperref}
-\hypersetup{final}
-\usepackage[inline]{enumitem}
-
-% DEBUG
-\usepackage{fullpage}
-\usepackage{todonotes}
-\usepackage{lineno}
-\linenumbers
-
-% EXTRA
-\usepackage{authblk}
-\def\CARPOOL{maximum carpool matching}
-
-\newcommand{\din}[1][M]{deg^{#1}_{in}}
-\newcommand{\dout}[1][M]{deg^{#1}_{out}}
-\newcommand{\dinout}[1][M]{deg^{#1}}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\def\R{\mathbb{R}}
-\def\N{\mathbb{N}}
-
-\newtheorem{observation}{Observation}
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{remark}{Remark}
-\usepackage{tikz}
-\usetikzlibrary{
-	arrows,
-	arrows.meta,
-	calc,
-	graphs,
-	patterns,
-	positioning,
-	shapes,
-	decorations.pathmorphing,
-}
-
-%DEFAULT STYLE
-\tikzset{default style/.style={
-	>=Stealth, 
-	on grid, 
-	auto, 
-	thick,
-}}
-
-% NODE
-\tikzset{default node/.style={
-	draw, 
-	circle,
-	inner sep=0mm,
-	minimum size=5mm,
-	very thick,
-	font=\small,
-	black!70,
-}}
-
-% LABELS
-\tikzset{label/.style={
-	draw=none,
-	sloped,
-}}
-
-\tikzset{label above/.style={
-	label,
-	midway,
-	above=-1mm,
-}}
-
-\tikzset{label below/.style={
-	label,
-	midway,
-	below=-1mm,
-}}
-
-\title{Improved Approximation Algorithms for the Maximum Carpool Matching
-Problme}
-
-\date{}
-\author[1]{Reuven Bar-Yehuda	\thanks{\texttt{reuven@cs.technion.ac.il}}}
-\author[1]{Gilad Kutiel			\thanks{\texttt{gkutiel@cs.technion.ac.il}}}
-\author[2]{Dror Rawitz			\thanks{\texttt{dror.rawitz@biu.ac.il}}}
-
-\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
-\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-The \textsc{\CARPOOL{}} problem is a star packing problem in directed graphs.
-Formally, given a directed graph $G = (V, A)$,
-a capacity function $ c: V \rightarrow \N $,
-and a weight function $w : A \rightarrow \R $,
-a feasible \emph{carpool matching} is a triple 
-$(P, D, M)$, where $P$ (passengers) and $D$ (drivers) form a partition of $V$, 
-and $M$ is a subset of $A \cap (P \times D)$,
-under the constraints that for every vertex $d \in D$, 
-$\din(d) \leq c(d)$, 
-and for every vertex $p \in P$, $\dout(p) \leq 1$.
-In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
-total weight of $M$.
-
-The problem arises when designing an online carpool service, 
-such as Zimride~\cite{zimride}, 
-that tries to connect between passengers and drivers based on (arbitrary) similarity function.
-The problem is known to be NP-hard, 
-even for uniform weights and without capacity constraints.
-
-we show that the problem can be formulated as
-unconstarints submodular maximization problem, 
-thus it has a $\frac{1}{2}$-approximation algorithm.
-For the unweighted variant of the problem when the maximum possible capacity, $C$, is
-fixed, we give a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm
-for the any $\varepsilon > 0$.
-\end{abstract}
-
-\section{Introduction}
-Carpooling, is the sharing of car journeys so that more than one person travels
-in a car.
-Knapen et al.~\cite{knapen2013estimating} describe an automatic service
-to match commuting trips.
-Users of the service register their personal profile and a set of periodically
-recurring trips, 
-and the service advises registered candidates on how to combine their commuting
-trips by carpooling.
-The service acts in two phases.
-
-In the first phase, the service estimates the probability that a person $a$
-traveling in person's $b$ car will be satisfied by the trip.
-This is done based on personal information and feedback from users on past
-rides.
-The second phase is about finding a carpool matching
-that maximizes the global (total expected) satisfaction.
-
-The second phase can be modeled in terms of graph theory.
-Given a directed graph $G = (V, A)$.
-Each vertex $v \in V$ corresponds to a user of the service and an arc
-$(u, v)$ exists if the user corresponding to vertex $u$ is willing to
-commute with the user corresponding to vertex $v$.
-A capacity function $ c: V \rightarrow \N $ is defined
-according to the number of passengers each user can drive if she was
-selected as a driver.
-A weight function $w : A \rightarrow \R $ defines the amount of
-satisfaction $w(u, v)$,
-that user $u$ gains when riding with user $v$.
-
-A feasible \emph{carpool matching} (matching) is a triple 
-$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
-and $M$ is a subset of $A \cap (P \times D)$,
-under the constraints that for every driver $d \in D$, 
-$\din(d) \leq c(d)$, 
-and for every passenger $p \in P$, ${\dout(p) \leq 1}$.
-In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
-total weight of $M$.
-In other words, the \textsc{\CARPOOL{}} problem is about finding a set of 
-(directed toward the center) vertex disjoint stars 
-that maximizes the total weights on the arcs.
-Figure~\ref{fig:carpool} is an example of the \textsc{\CARPOOL{}} problem.
-
-\begin{figure}
-\centering
 \newcommand{\edge}[3]{
@@
 }
-\subfloat[]{
-\label{subfloat:input}
+
+\begin{subfigure}{.4\linewidth}
+\caption{\label{carpool:input}}
 \begin{tikzpicture}[every node/.style={default node}, ->, very thick]
@@
 
-\end{tikzpicture}}
-\hfill\subfloat[]{
-\label{subfloat:output}
+\end{tikzpicture}
+\end{subfigure}
+%
+\hfill
+%
+\begin{subfigure}{.4\linewidth}
+\caption{\label{carpool:output}}
 \begin{tikzpicture}[every node/.style={default node}, ->, very thick]
@@
 
-\end{tikzpicture}}
-\caption[]{
-\label{fig:carpool}
-A carpool matching example: 
-\subref{subfloat:input} 
-a directed graph with capacities on the vertices and weights on the arcs. 
-\subref{subfloat:output}
-a feasible matching with total weight of 26.
-$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
-}
-\end{figure}
-
-Hartman et al.~\cite{hartman2013optimal} proved that the
-\emph{\CARPOOL{}} problem considered in this paper is NP-hard,
-and that the problem remains NP-hard even for a binary weight function when
-the capacity function $c(v) \leq 2$ for every vertex in $V$.
-It is also worth mentioning, that in the undirected, uncapacitated, unweighted
-variant of the problem, the set of drivers in an optimal solution
-form a minimum dominating set.
-When the set of drivers is known in advanced, however, the problem becomes
-tractable and can be solved using a reduction to a flow network problem.
-
-Agatz et al.~\cite{agatz2012optimization} outlined the optimization challenges
-that arise when developing technology to support ride-sharing and survey the
-related operations research models in the academic literature.  
-Hartman et al.~\cite{hartman2014theory} designed several heuristic algorithms
-for the \CARPOOL{} problem and compared 
-their performance on real data.
-Other heuristic algorithms were developed as well~\cite{knapen2014exploiting}.
-Arkin et al.~\cite{arkin2004approximations}, considered other variants of
-capacitated star packing where a capacity vector is given as part of the input and 
-capacities need to be assigned to vertices.
-
-Nguyen et al.~\cite{nguyen2008approximating} considered the \textsc{spanning star forest} problem
-(the undirected, uncapacitated, unweighted variant of the problem).
-They proved the following results:
-\begin{enumerate*}
-\item
-there is a polynomial-time approximation scheme for planner graphs;
-\item 
-there is a polynomial-time $\frac{3}{5}$-approximation algorithm for graphs;
-\item 
-there is a polynomial-time $\frac{1}{2}$-approximation algorithm for weighted graphs.
-\end{enumerate*}
-They also showed how to apply the spanning star forest model to aligning multiple
-genomic sequences over a tandem duplication region.
-Chen et al.~\cite{chen2007improved} improved the approximation ratio to 0.71,
-and also showed that the problem can not be approximated to within a factor of
-$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ under the assumption 
-that $\text{P} \neq \text{NP}$.
-It is not clear, however, if any of the technique used to address the
-\textsc{spanning star forest} problem can be generalized to approximate the
-directed capacitated variant.
-
-In section~\ref{sec:sub} we show that the problem can be formulated as
-unconstarints submodular maximization problem, thus it has a 2-approximation
-algorithm.
-In section~\ref{sec:local} we consider the unweighted variant of the problem.
-We show that when the maximum possible capacity, $C$, is fixed, there is a 
-$(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm for the any $\varepsilon > 0$.
-
-\section{Submodularity}
-\label{sec:sub}
-In this section we show that the problem can be formulated as unconstrained
-submodular maximization problem, and thus, it has a 2-approximation algorithm.
-
-Consider the function $w : 2^V \to \R$ where $w(D)$ is the value of the optimal
-carpool matching when the set of drivers is $D$.
-As we mention in the introduction, $w$ can be computed efficiently.
-
-\begin{theorem}
-$w$ is submodular.
-\end{theorem}
-
-\begin{proof}
-Consider two subsets $A,B \subseteq V$, 
-we need to show that $w(A) + w(B) \geq w(A \cup B) + w(A \cap B)$.
-Let $E_{A \setminus B} = (V \setminus A) \times (A \setminus B)$, 
-$E_{B \setminus A} = (V \setminus A) \times (B \setminus A)$,
-and $E_{B \cap A} = (V \setminus (A \cap B)) \times (B \cap A)$.
-
-Let $M_{A \cup B}$ and $M_{A \cap B}$ be the set of edges in an optimal
-matching when the set of drivers are $A \cup B$ and $A \cap B$ respectively.
-We argue that we can construct two (feasible) matchings $M_A$ and $M_B$ using
-the sets of drivers $A$ and $B$ respectively and 
-$w(M_A) + w(M_B) = w(M_{A \cup B}) + w(M_{A \cap B})$.
-First, take all the edges from $M_{A \cup B} \cap E_{A \setminus B}$ and 
-add them to $M_A$, 
-add $M_{A \cup B} \cap E_{B \setminus A}$ to $M_B$.
-Clearly this can be done.
-Now, split the edges from $M_{A \cap B} \cup (M_{A \cup B} \cap E_{A \cap B})$
-between $M_A$ and $M_B$ in a way that does not violate the capacity constraints.
-One can verify that this can be done.
-\end{proof}
-
-\section{Constant Max Capacity}
-In this section we study the carpool problem when the maximum possible capacity
-is constant.
-We show that this variant of the problem is APX-hard as well.
-We also describe and analyze a local search algorithm for the unweighted
-variant of the problem, 
-and show that the algorithm achieves a 
-$\frac{C + 1}{2C} - \varepsilon$ approximation ratio for any $\varepsilon > 0$.
-Throughout this section we consider $C$ to be fixed, and $k$ to be a fixed parameter.
-
-	\subsection{Hardness}
-	\label{sec:hardness}
-As we mentioned in the introduction, the maximum spanning star forest can not 
-be approximated within a factor of 
-$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ unless P = NP.
-The proof, however, does not hold for the case when the maximum capacity is
-constant. 
-In this subsection we show that the problem remains APX-hard even in this case.
-
-Formally, the (unweighted)
-minimum dominating set problem is defined as $\min_{D}(|D|)$,
-where $D$ is any feasible dominating set.
-It is also easy to see that the (unweighted, undirected, uncapacitated) 
-maximum carpool matching problem can be defined as $max_{D}(|V \setminus D|)$, 
-where $D$ is any feasible dominating set.
-The \textsc{Dominating Set-B} is the problem of finding minimum dominating set on 
-graphs with degree bounded by $B$,
-and it was shown to be APX-hard (for $B \geq 3$) by 
-Papadimitriou et al.~\cite{papadimitriou1988optimization}.
-
-Let $G$ be a b-bounded degree graph,
-let $D^*(G)$ be a minimum dominating set in $G$,
-and let $C^*(G)$ be a maximum carpool matching in $G$, 
-then the following lemmas hold:
-
-\begin{lemma}
-$|C^*| = |V| - |D^*|$
-\end{lemma}
-
-\begin{proof}
-The proof follows immediately from the definitions of the two problems. 
-\end{proof}
-
-\begin{lemma}
-\label{lm:optc_leq_boptd}
-$|C^*| \leq b \cdot |D^*|$
-\end{lemma}
-
-\begin{proof}
-The proof follows directly from the observation that $|D^*| \geq \frac{|V|}{b}$.
-\end{proof}
-
-Let $C(G)$ be any feasible carpool matching on $G$, then the following lemma holds:
-
-\begin{lemma}
-\label{lm:erreq}
-$|C^*| - |C| = (|V| - |C|) - |D^*|$
-\end{lemma}
-
-\begin{proof}
-$$
-|C^*| - |C| 				= 
-|V| - |D^*| - |C| 	= 
-(|V| - |C|) - |D^*|
-$$
-\end{proof}
-
-Let $D(G)$ be any feasible dominating set in $G$, 
-we argue that $f(G) = G$, and $g(C(G)) = V \setminus C(G)$ 
-define a linear reduction (L-reduction) from the \textsc{Dominating Set-B} problem to the 
-\textsc{\CARPOOL{}} problem.
-\begin{proof}
-By lemma~\ref{lm:optc_leq_boptd} we get that $C^*(f(G)) = C^*(G) \leq b \cdot D^*(G)$,
-and by lemma~\ref{lm:erreq} we get that 
-\begin{equation}
-\begin{split}
-|C^*(f(G))| - |C(G)|		& = |C^*(G)| - |C(G)| 			\\
-							& = (|V| - |C(G)|) - |D^*(G)|	\\
-							& = |g(C(G))| - |D^*(G)|
-\end{split}
-\end{equation}
-\end{proof}
-
-\begin{theorem}
-The \textsc{\CARPOOL{}} problem is APX-hard.
-\end{theorem}
-
-\begin{proof}
-The proof follows directly from the above linear reduction and the fact that 
-\textsc{Dominating Set-B} is APX-hard. 
-\end{proof}
-
-	\subsection{Local Search}
-	\label{sec:local}
-The local search algorithm maintains a feasible matching throughout its execution
-and operates in 
-iterative manner where in each iteration it tries to find a better solution by
-replacing a subset of the edges in the current solution with 
-another (larger) subset of edges not in the solution.
-The local search algorithm halts when no improvement can be done.
-The algorithm is described in Algorithm~\ref{alg:local}.
-
-\begin{algorithm}
-\SetKw{True}{true}
-\SetKw{False}{false}
-\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
-\KwOut{$M$}
-$M \leftarrow \emptyset$								\\
-\Repeat{done}{
-\label{line:outerloop}
- 	$done \leftarrow{}$ \True							\\
- 	\For{$M' \in M : |M'| \leq k$}{
- 		\For{$A' \in A \setminus M : |A'| = |M'| + 1$}{
-			\If{$M \setminus M' \cup A'$ is feasible}{
-				$M \leftarrow{} M \setminus M' \cup A'$	\\
-				$done \leftarrow{}$ \False				\\
-			}
-		}
- 	}
-}
-\Return{$M$}
-
-\caption{
-\label{alg:local}
-Local Search}
-\end{algorithm}
-
-We claim that the local search algorithm halts in polynomial time.
-Observed that in every iteration the algorithm either improves the value of the solution
-by one or otherwise it terminates. 
-Thus, after a maximum of $n$ iterations the algorithm stops.
-In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
-both these operations can be done in polynomial time - $O(n^{Ck + 1})$.
-
-To analyze the approximation ratio achieved by the local search algorithm consider an 
-arbitrary but fixed optimal matching $M^*$.
-Given the solution outputted by the local search algorithm, 
-$M$, 
-we build the \emph{star graph} of the two solutions
-in which each node represents a star from the optimal solution 
-and edges exits between two nodes if
-there is a star in $S(M)$ that intersect the two
-corresponding stars of the optimal solution, 
-formally $G^{M^*}_M = (S, E)$ where $\{v_i : S^*_i \in S(M^*) \}$ 
-and 
-$E = \{(v_i, v_j) : 
-\exists S \in M,
-S \cap S^*_i \neq \emptyset \land S \cap S^*_j \neq \emptyset,
-\}$.
-Figure~\ref{fig:conflict} depicts a star graph.
-
-\begin{figure}[ht]
-\centering
-\subfloat[]{
-\label{subfloat:graph}
-\newcommand{\edge}[2]{
-	\draw (#1) -- (#2);
-}
-
-\begin{tikzpicture}[every node/.style={default node}, ->, very thick]
-
-\node(1) at(0,0) {a};
-\node(2) at(0,1.5) {b};
-\node(3) at(1.5,0) {c};
-
-\node(4) at(4,0) {d};
-\node(5) at(4,1.5) {e};
-\node(6) at(2.5,0) {f};
-
-\node(7) at(0,-1.5) {h};
-\node(8) at(0,-3) {i};
-\node(9) at(1.5,-1.5) {j};
-
-\node(10) at(4,-1.5) {k};
-\node(11) at(4,-3) {l};
-
-\begin{scope}[dashed, red]
-\edge{2}{1}
-\edge{3}{1}
-
-\edge{5}{4}
-\edge{6}{4}
-
-\edge{8}{7}
-\edge{9}{7}
-
-\edge{11}{10}
-\end{scope}
-
-\begin{scope}[green]
-\edge{2}{5}
-
-\edge{7}{1}
-\edge{3}{9}
-\end{scope}
-
 \end{tikzpicture}
-}
-\subfloat[]{
-\label{subfloat:conflict}
-\newcommand{\edge}[2]{
-	\draw (#1) -- (#2);
-}
-
-\begin{tikzpicture}[every node/.style={default node, red}, -, very thick, green]
-
-\node(1) at(0,1.5) {3};
-\node(2) at(4,1.5) {1};
-\node(3) at(0,-3) {2};
-\node(4) at(4,-3) {0};
-
-\edge{1}{2}
-\edge{1}{3}
-
-\end{tikzpicture}
-}
-\caption[]{
-\label{fig:conflict}
-\subref{subfloat:input} 
-An optimal matching depicted by the dashed red edges,
-and another solution depicted by the solid green edges.  
-\subref{subfloat:output}
-The conflict graph, the upper left vertex corresponds 
-to the star that contains the vertices a,b,c.
-The numbers inside the vertices corresponds to $d_i$.   
-}
-\end{figure}
-
-For a group of vertices, $U$, denote by $w^*(U)$ the sum of the degrees 
-induced by the underlying graph of the optimal solution on this set, i.e.
-$\sum_{u \in U} \dinout[M^*](u)$, 
-and let $w(S)$ be the sum of the degrees 
-induced by the underlying graph of the local search solution on this set, i.e.
-$\sum_{u \in U} \dinout(u)$.
-
-\begin{lemma}
-\label{lemma:r}
-If $k \geq \text{TODO}$ then in any connected induced graph of $G^{M^*}_M$, 
-$G'= G^{M^*}_M[U]$, 
-$
-\frac{w(U)}{w^*(U)} 
-\geq \frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
-$.
-\end{lemma}
-
-\begin{proof}
-Consider the solution obtained from the $M$ by removing all the edges from $M$
-that intersect the induced subgraph, and adding all the edges from $M^*$ that
-intersect the induced subgraph.
-It is easy to verify that this is a feasible solution.
-We now bound from below the difference in the value of the solution.
-The value decrease due to the removal of the edges by at most $w(U) - |U| + 1$,
-and increase by exactly $\frac{w^*(U)}{2} \leq C |U|$.
-We know that this difference can not be positive, or else, the local search
-algorithm would not have been terminated.
-Thus 
-$\frac{w^*(U)}{2} \leq w(U) - |U| + 1$ 
-and so
-$
-\frac{w(U)}{w^*(U)} 
-\geq 
-\frac{1}{2} + \frac{|U|}{w^*(U))} - \frac{1}{w^*(U))}  
-\geq
-\frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
-$
-\end{proof}
-
-\begin{lemma}
-\label{lemma:dec}
-Given a parameter $k$, a bounded degree connected graph $G$, with a maximum
-degree $d$ can be decomposed into connected components of size at least $k$, and at most
-$d(k-1) + 1$.
-\end{lemma}
-
-\begin{proof}
-We give a constructive proof.
-Start constructing a connected component by adding adjacent vertices
-one by one to the component and removing them from the graph.
-If at some point, removing a vertex disconnect the graph, add all the small
-components (of size less than $k$) to the constructed component and decompose
-the large components (of size at least $k$) recursively.
-Note that removing a vertex can break the graph to at most $d - 1$ additional
-components.
-\end{proof}
-
-\begin{theorem}
-The local search is ($\frac{1}{2} + \frac{1}{2c} - \varepsilon$)-approximation
-algorithm.
-\end{theorem}
-
-\begin{proof}
-Combine lemma~\ref{lemma:dec}, and lemma~\ref{lemma:r}, 
-and observe that the maximum degree in $G^{M^*}_M$ is $(C + 1)^C$ to
-get the desire result.
-\end{proof}
-
-\todo{show that the analysis is tight}
-
-\section{Group Carpool}
-\label{sec:group}
-In this section we introduce the group carpool and show that it does not fit the
-submodular maximization formulation while the local search algorithm handle it
-without any modification.
-
-\subsection{2-approximation}
-In this subsection we give a 2-approximation algorithm for general capacities.
-First, let us introduce a $(\frac{1}{2} - \varepsilon)$-approximation algorithm
-for the original problem.
-We then show how to generalize the algorithm to work also for the group carpool
-matching.
-
-\tikzset{m/.style={
-	blue, 
-	dashed,	
-}}
-
-Let $M$ be a feasible carpool matching,
-the \emph{value} of a vertex $v$, denoted $val(v)$, 
-is the sum of the weights of the arcs in $M$ that incident $v$. 
-That is: 
-%
-\begin{definition}[$val$]
-$val_M(v) = \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u)$
-\end{definition}
-%
-If $V$ is a set of vertices, then $val_M(V) \triangleq \sum_{v \in V} val_M(v)$.
-%
-Denote by $\delta(e)$ the difference between the weight of the arc and the value
-of its source vertex,
-that is:
-%
-\begin{definition}[$\delta$]
-$\delta_M(u, v) = w(u, v) - val_M(u)$
-\end{definition}
-%
-If $S$ is a set of arcs, then $\delta(S) \triangleq \sum_{e \in S}\delta(v)$.
-
-An \emph{improvement} to vertex $v$ 
-is a set of arcs entering $v$ of size not greater than the capacity of $v$, 
-for which the sum of the $\delta$s is greater than the value of $v$,
-formally:
-
-\begin{definition}[improvement]
-$S_v \subseteq V \times \{v\} \cap A$ is an \emph{improvement} (w.r.t $M$)
-if the following conditions hold:
-\begin{itemize}
-\item
-$|S_v| \leq c(v)$
-\item
-$\delta_M(S_v) > val_M(v)$
-\end{itemize}  
-\end{definition}
-%
-If, for vertex $v$, an improvement exists, we say that vertex $v$ can be \emph{improved}.
-%
-Given an arc $(u,v)$, 
-let $inc(u,v)$ be the set of arcs that incident $(u, v)$,
-formally:
-%
-\begin{definition}[inc]
-$inc(u,v) = (V \times \{u, v\} \cup \{u, v\} \times V) \cap A$
-\end{definition}
-%
-If $S$ is a set of arcs, then $inc(S) \triangleq \bigcup_{e \in S} inc(e)$.
-%
-The \emph{passengers} of $v$ (w.r.t some set of arcs) are all the vertices that have
-outgoing arc to $v$, formally: 
-%
-\begin{definition}[passengers]
-$\text{pass}_M(v) = \{u : (u, v) \in M\}$
-\end{definition}
-%
-Figure~\ref{fig:defs} depicts all the above definitions.
-
-\begin{figure}
-\centering
-\begin{tikzpicture}[every node/.style={default node}]
-
-\node(1) at(0,0) {1};
-\node(2) at(2,0) {2};
-\node(3) at(4,0) {3};
-
-\node(4) at(.4,1.6) {4};
-\node(5) at(2.4,1.6) {5};
-\node(6) at(6, 0) {6};
-
-\draw[m] (1) -- (2) node[label above]{$5$};
-\draw[m] (4) -- (2) node[label above]{$2$};
-\draw[m] (3) -- (5) node[label above]{$2$};
-\draw[] (6) -- (3) node[label above]{$2$};
-
-\draw (2) -- (3) node[label above]{$8$};
-
-\end{tikzpicture}
-\caption[]{
-\label{fig:defs}
-In this example, $M$ is the set of the blue, dashed arcs, then:
-$val_M(2) = 7$,
-$val_M(3) = 2$,
-$val_M(6) = 0$,
-$\delta_M(2, 3) = 1$,
-$\delta_M(6, 3) = 2$,
-the set $\{(2,3), (6,3)\}$ is an \emph{improvement} to vertex 3,
-$inc(2,3) = \{(1,2),(4,2),(3,5),(6,3)\}$,
-$\text{pass}_M(2) = \{1, 4\}$.
-}
-\end{figure}
-
-We are now ready to describe our algorithm.
-The algorithm starts with an empty matching,
-in every iteration it seeks for a vertex that can be improved,
-it then improve the matching by adding
-the arcs that improve the vertex, 
-just after removing the arcs that incident them.
-The algorithm halts when no vertex can be improved.
-Figure~\ref{fig:improvement} depicts an improvement step,
-and the full algorithm is listed in Algorithm~\ref{alg:grd}.
-
-\begin{figure}
-\centering
-\subfloat[]{
-\label{sub:can improved}
-\begin{tikzpicture}[every node/.style={default node}]
-\node(1) at(0,0) {1};
-\node(2) at(2,0) {2};
-\node(3) at(4,0) {3};
-
-\node(4) at(.4,1.6) {4};
-\node(5) at(2.4,1.6) {5};
-\node(6) at(2.4, -1.6) {6};
-
-\draw[m] (1) -- (2) node[label above]{$5$};
-\draw[m] (4) -- (2) node[label above]{$2$};
-\draw[m] (3) -- (5) node[label above]{$2$};
-\draw[] (6) -- (3) node[label above]{$2$};
-
-\draw (2) -- (3) node[label above]{$8$};
-
-\end{tikzpicture}
-}\hspace{1cm}\subfloat[]{
-\label{sub:improved}
-\begin{tikzpicture}[every node/.style={default node}]
-\node(1) at(0,0) {1};
-\node(2) at(2,0) {2};
-\node(3) at(4,0) {3};
-
-\node(4) at(.4,1.6) {4};
-\node(5) at(2.4,1.6) {5};
-\node(6) at(2.4, -1.6) {6};
-
-\draw[] (1) -- (2) node[label above]{$5$};
-\draw[] (4) -- (2) node[label above]{$2$};
-\draw[] (3) -- (5) node[label above]{$2$};
-\draw[m] (6) -- (3) node[label above]{$2$};
-
-\draw[m] (2) -- (3) node[label above]{$8$};
-
-\end{tikzpicture}
-}
-\caption[]{
-\label{fig:improvement}
-\subref{sub:can improved}
-A matching that can be improved
-\subref{sub:improved}
-The matching after improving vertex 3
-}
-\end{figure}
-
-\begin{algorithm}
-\caption{
-\label{alg:grd}
-GRD
-}
-$M \leftarrow \emptyset$									\\
-\While{done}{
-	done $\leftarrow$ True									\\
-	\For{$v \in V$}{
-		\If{$\exists$~improvment~$S_v$}{
-			$M \leftarrow M \setminus inc(S_v) \cup S_v$	\\
-			done $\leftarrow$ False							\\
-		}
-	}
-}
-\end{algorithm}
-
-\begin{remark}
-\label{rem:improve}
-Determining if a vertex $v$ can be improved can be done efficiently
-by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
-and only ones with positive value.
-Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
-sum up to more than $val_M(v)$.
-\end{remark}
-
-\begin{remark}
-It is easy to see, if the weights on the edges are integral and polynomial
-bounded the algorithm runs in polynomial time, this is because in each iteration the
-algorithm improves the value of the matching by at least one or otherwise it
-terminates.
-\end{remark}
-
-\begin{remark}
-When the weights are not integral nor polynomial bounded one can use scaling and
-rounding first to ensure polynomial runtime in the cost of $\varepsilon$ in the
-approximation ratio.
-\end{remark}
-
-We now argue that, with respect to any matching, 
-the total value of all the vertices equals twice the value of the matching, 
-formally: 
-\begin{lemma}
-\label{lm:val-twice}
-$\sum_{v \in V} val_M(v) = 2 \sum_{e \in M} w(e)$
-\end{lemma}
-
-\begin{proof}
-\begin{equation}
-\begin{split}
-\sum_{v \in V} val_M(v)	& = 
-\sum_{v \in V} \left( \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u) \right)	\\
-						& = \sum_{v \in V}\sum_{(u, v) \in M} w(u, v) + 
-							\sum_{v \in V}\sum_{(v, u) \in M} w(v, u)					\\
-						& = 2 \sum_{e \in M} w(e)
-\end{split}
-\end{equation}
-\end{proof}
-
-Let $M$ be a matching, and let $v$ be a vertex with no improvement,
-let $S \subseteq V \times \{v\} \cap A$ of size not greater than $c(v)$,
-then the following lemma holds:
-
-\begin{lemma}
-\label{lm:no improve}
-$w(S) \leq val_M(v) + val_M(\text{pass}_S(v))$
-\end{lemma}
-
-\begin{proof}
-If no improvement exists then
-$$
-w(S) - val_M(\text{pass}_S(v))=
-\sum_{(u,v) \in S}(w(u,v) - val_M(u)) =
-\delta_M(S) 
-\leq val_M(v)
-$$
-\end{proof}
-
-To bound the approximation ratio of the GRD algorithm, 
-we use a charging scheme argument.
-Given the matching produced by the algorithm, 
-we load every vertex with amount of money equal to its value,
-we then show that this is enough to pay for every arc in an optimal matching.
-
-\begin{theorem}
-Algorithm~\ref{alg:grd} is $\frac{1}{2}$-approximation.
-\end{theorem}
-
-\begin{proof}
-Let $M$ be the matching produced by algorithm~\ref{alg:grd}, 
-and let $M^*$ be an optimal matching.
-Load every vertex with $val_M(v)$ money, 
-by lemma~\ref{lm:val-twice} this is exactly twice the value of $M$.
-Consider a driver $v$ in $M^*$, and let $S = V \times \{v\} \cap M^*$.
-By lemma~\ref{lm:no improve} we know that $w(S) \leq val_M(v) + val_M(\text{pass}_S(v))$,
-thus we can pay for $S$, using the money on $v$ and $\text{pass}_S(v)$.
-Clearly, these vertices will not be charged again.
-\end{proof}
-
-We now argue that this algorithm can be generalized to solve the group carpool
-matching problem.
-The main concern when trying to adopt the algorithm to the group carpool
-matching is how to determine if a vertex can be improved.
-Observe that Remark~\ref{rem:improve} does not hold anymore.
-If the maximum possible capacity is bounded, one can test for improvement of
-$v$ by considering all the subsets of edges intersecting $v$. 
-When the capacity is unbounded, however, it is easy to see that efficient
-way to test improvement implies a solution to the Knapsack problem.
-Indeed, if this is the case, one can test for improvement by using a known FPTAS
-for Knapsack, this is in the cost of additional $\varepsilon$ reduction in the
-approximation ratio of the algorithm.
-
-To conclude this section we show that our analysis is tight, 
-as depicts in Figure~\ref{fig:grd worst}.
-\todo[inline]{what happen if we apply the rule on both directions ?}
-\begin{figure}
-\centering
-\begin{tikzpicture}[every node/.style={default node}]
-
-\def\sep{1.5}
-
-\foreach \n in {0,...,5}{
-	\pgfmathsetmacro{\x}{\n * \sep}
-	\node(\n) at(\x,0){};
-}
-
-\foreach \n/\m in {0/1,2/3,4/5}{
-	\draw[m] (\n) -- (\m) node[label above]{1};
-}
-
-\foreach \n/\m in {1/2,3/4}{
-	\draw[] (\n) -- (\m) node[label above]{2};
-}
-
-\pgfmathsetmacro{\x}{6 * \sep}
-\node[draw=none] at(\x, 0){$\cdots$};
-
-\foreach \n in {7,...,8}{
-	\pgfmathsetmacro{\x}{\n * \sep}
-	\node(\n) at(\x,0){};
-}
-
-\draw[m] (7) -- (8) node[label above]{1};
-
-\end{tikzpicture}
-\caption[]{
-\label{fig:grd worst}
-GRD algorithm, worst case example: \\
-Consider a path with $2n + 1$ arcs,
-and alternating arc weights (2 and 1),
-if the GRD algorithm selects all the 1 weighted arcs,
-then no further improvement can be done and the value of the matching is $n + 1$,
-while the optimal matching has value of $2n$.
-}
-\end{figure}
-
-\bibliographystyle{plain}
-\bibliography{main}
-
-\end{document}
+\end{subfigure}

### 2017-01-31 src/in/title.tex
fix subcaption, no warnings

@@
-\title{Improved Approximation Algorithms for the Maximum Carpool Matching
-Problme}
+\title{Improved Approximation Algorithms for the
+Maximum Carpool Matching Problem}
 
-\date{}
+\titlerunning{Improved Approximation Algorithms for Maximum Carpool Matching}
+
+\author[1]{Gilad Kutiel}
+\author[2]{Dror Rawitz%
+\thanks{Supported in part by the Israel Science Foundation (grant no.~497/14).}}
+
+\affil[1]{Department of Computer Science, Technion, Haifa,
+  Israel. \\ \texttt{gkutiel@cs.technion.ac.il}}
+\affil[2]{Faculty of Engineering, Bar Ilan University, Ramat Gan,
+  Israel. \\ \texttt{dror.rawitz@biu.ac.il}}
+
+\authorrunning{G. Kutiel and D. Rawitz}
+
+\Copyright{G. Kutiel and D. Rawitz}
+
+\subjclass{F.2.2 Nonnumerical Algorithms and Problems}
+
+\keywords{approximation algorithms, local search}

### 2017-01-31 src/intro.tex
fix subcaption, no warnings

@@
 A feasible \emph{carpool matching} is a subset of arcs, $M \subseteq
-A$, such that every $v \in V$ satisfies:%
+A$, such that every $v \in V$ satisfies:
 \begin{inparaenum}[(i)]
@@
 passengers.  In the \carpool problem the goal is to find a matching
-$M$ of maximum total weight, namely to minimize
+$M$ of maximum total weight, namely to maximize
 $w(M) \eqdf \sum_{(v,u) \in M} w(v,u)$.  In other words, the \carpool
@@
 A carpool matching example: 
-\subref{subfloat:input} 
+\subref{carpool:input}
 a directed graph with capacities on the vertices and weights on the arcs. 
-\subref{subfloat:output}
+\subref{carpool:output}
 a feasible matching with total weight of 26.
@@
 In this paper we also consider an extension of \carpool, called \gcp,
-in which each vertex represents a group of passengers.  Group sizes
-are non-uniform, and we consider the case where a group size may
-change as a function of the driver.  Formally, each arc $(u,v) \in A$
-is associated with a size $s(u,v) \in \N$, and the constraint
-$\din[M](v) \leq c(v)$ is replaced with the constraint
-$\sum_{u:(u,v) \in M} s(u,v) \leq c(v)$.
+in which each vertex represents a group of passengers, and  
+each group might have a different size. 
+Formally, each vertex $u \in V$ has a size $s(u) \in \N$, 
+and the constraint $\din[M](v) \leq c(v)$ is replaced with the constraint
+$\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
 %
-Notice that \textsc{Knapsack} is the special case, where only arcs
-directed at a single vertex have non-zero weights.
+Notice that \textsc{Knapsack} is the special case, where only
+arcs directed at a single vertex have non-zero (integral) weights.
 
@@
 Hartman et al.~\cite{hartman2013optimal} proved that the \carpool
-problem considered in this paper is NP-hard, and that the problem
+problem is NP-hard, and that the problem
 remains NP-hard even for a binary weight function when the capacity
@@
 
-Kutiel~\cite{Kutiel16}
+Kutiel~\cite{kutiel2016} presented a $\frac{1}{3}$-approximation
+algorithm for the problem and $\frac{1}{2}$-approximation algorithm for the
+unweighted variant of the problem.
 
-\todo[inline]{add a paragraph about the paper from arXiv}
+Bar-Noy et al.~\cite{bar2015improved} considered the problem of partition a
+graph into disjoint paths of length 2.
+This problem is a special case of the undirected carpool matching
+where all capacities are exactly 2.
+They show a $.5833$, and $\frac{3}{4}$-approximation algorithms for the weighted
+and unweighted variants of the problem respectively.
 
-\todo[inline]{Mention Goerge's paper with Amotz (ESA)}
+For the general set packing problem, the best known approximation algorithm is
+due to Chandra et al.~\cite{chandra2001greedy} and it admits a 
+$\frac{2(k +1)}{3}$ approximation ratio where $k$ is the size of the sets.
 
@@
 %
-In Section~\ref{sec:sub} we show that the problem can be formulated as
+In Section~\ref{sec:sub} we show that the \carpool can be formulated as
 unconstrained submodular maximization problem, thus it has a
-randomized $2$-approximation algorithm due to~\cite{BFNS15}.  We also
-provide a deterministic $(2+\eps)$-approximation algorithm, for any
-$\eps>0$, which is based on local search.
+$\frac{1}{2}$-approximation algorithm due to~\cite{BFNS15}.
 
@@
 %
-In Section~\ref{sec:group} we consider \gcp.  We first show that \gcp
-cannot be formulated as an unonstrained submodular maximization
-problem as \carpool.  We show, however, that this problem still admits
-a $(2 + \eps)$-approximation algorithm, and argue that the local
+In Section~\ref{sec:group} we consider \gcp.  
+We first show that the unconstrained submodular maximization formulation for
+the \carpool does not follow for the \gcp.
+We show, however, that this problem still admits
+a $(\frac{1}{2} -\varepsilon)$-approximation algorithm, and argue that the local
 search algorithm generalizes to \gcp as well.

### 2017-01-31 src/main.tex
fix subcaption, no warnings

@@
 \usepackage{xspace}
-\usepackage{subfig}
+\usepackage{subcaption}
 \usepackage{paralist}
-%\usepackage{hyperref}
-%\hypersetup{final}
-%\usepackage[inline]{enumitem}
 
 % DEBUG
-%\usepackage{fullpage}
 \usepackage{todonotes}
-%\usepackage{lineno}
-%\linenumbers
-
-% EXTRA
-%\usepackage{authblk}
 
@@
 
-\title{Improved Approximation Algorithms for the
-Maximum Carpool Matching Problem}
-
-\titlerunning{Improved Approximation Algorithms for Maximum Carpool Matching}
-
-\author[1]{Gilad Kutiel}
-\author[2]{Dror Rawitz%
-\thanks{Supported in part by the Israel Science Foundation (grant no.~497/14).}}
-
-\affil[1]{Department of Computer Science, Technion, Haifa,
-  Israel. \\ \texttt{gkutiel@cs.technion.ac.il}}
-\affil[2]{Faculty of Engineering, Bar Ilan University, Ramat Gan,
-  Israel. \\ \texttt{dror.rawitz@biu.ac.il}}
-
-\authorrunning{G. Kutiel and D. Rawitz}
-
-\Copyright{G. Kutiel and D. Rawitz}
-
-\subjclass{F.2.2 Nonnumerical Algorithms and Problems}
-
-\keywords{approximation algorithms, local search}
-
+\input{in/title}
 %Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\bibliographystyle{plain}
-\bibliographystyle{plainurl}% the recommended bibstyle
+\bibliographystyle{plainurl}
 \bibliography{main}

### 2017-01-31 src/group.tex
done my pass

@@
 capacity function $c:V \to \N$, and the weight (profit) function
-$w:A \to \R$, we also have a size function $s:A \to \N$, and the
+$w:A \to \R$, we also have a size function $s:V \to \N$, and the
 constraint $\din[M] \leq c(v)$ is replaced with the constraint
-$\sum_{(u,v)}s(u,v) \leq c(v)$.  The motivation for this variant of
+$\sum_{(u,v)}s(u) \leq c(v)$.  The motivation for this variant of
 the problem is when we want to allow a group of people to travel
@@
 
-To see why the group carpool problem can
-not be treated as a submodular maximization problem considered the
-instance given in Figure~\ref{fig:not submodular}.
+Consider the submodular maximization formulation given in Section~\ref{sec:sub}.
+Figure~\ref{fig:not submodular} shows that the function $w : 2^V \to \R$ is not
+submodular anymore.
 
@@
 
-\subsection{A $(2+\eps)$-approximation Algorithm}
+\subsection{A $(\frac{1}{2} - \varepsilon)$-approximation Algorithm}
 

### 2017-01-31 src/local.tex
done my pass

@@
 \begin{figure}[t]
-\centering
-\subfloat[]{
-\label{subfloat:graph}
+%
+\begin{subfigure}{.4\linewidth}
+\caption{\label{subfloat:graph}}
 \input{fig-sub-graph}
-}
-\subfloat[]{
-\label{subfloat:conflict}
+\end{subfigure}
+%
+\hfill
+%
+\begin{subfigure}{.4\linewidth}
+\caption{\label{subfloat:conflict}}
 \input{fig-sub-conflict}
-}
+\end{subfigure}
+%
 \caption[]{
-\subref{subfloat:input} 
+\subref{subfloat:graph} 
 An optimal matching depicted by the dashed red edges,
 and another solution depicted by the solid green edges.  
-\subref{subfloat:output}
+\subref{subfloat:conflict}
 The conflict graph, the upper left vertex corresponds 

### 2017-01-31 src/local_search.tex
done my pass

@@
 Denote by $\delta(u,v)$ the difference between the weight of the arc
-and the value of its source vertex, that is:
+and the weight of its source vertex, that is:
 \[
@@
 S} \inc(u,v)$.
-
+%
 Figure~\ref{fig:defs} depicts all the above definitions.
@@
 \caption{In this example $M$ is the set of the blue, dashed arcs.
-In this case $w_M(2) = 7$, $w_M(3) = 2$, and $w_M(6) = 0$.  Also,
+In this case $w_M(2) = 7$, $w_M(5) = 2$, and $w_M(6) = 0$.  Also,
 $\delta_M(2, 3) = 1$ and $\delta_M(6, 3) = 2$.  The set $\set{(2,3),
@@
 \begin{algorithm}
-\caption{Local Search}
-\label{alg:ls}
+\caption{
+\label{alg:grd}
+Local Search
+}
 $M \gets \emptyset$ \\
@@
 \begin{lemma}
-If Algorithm~\ref{alg:ls} terminates, then the computed solution is a
+If Algorithm~\ref{alg:grd} terminates, then the computed solution is a
 $2$-approximation.
@@
 
-\todo[inline]{fix figure: directed graph}
-
 \begin{figure}
@@
 \label{thm:ls}
-Algorithm~\ref{alg:ls} is a $2$-approximation algorithm for \carpool,
+Algorithm~\ref{alg:grd} is a $2$-approximation algorithm for \carpool,
 if edge weights are integral and polynomially bounded.
@@
 \end{proof}
-
-\todo[inline]{what happen if we apply the rule on both directions ?}

### 2017-01-31 src/sub.tex
done my pass

@@
 unconstrained submodular maximization problem, and thus it has a
-randomized $2$-approximation algorithm based on~\cite{BFNS15}.
+randomized $\frac{1}{2}$-approximation algorithm based on~\cite{BFNS15}.
 
@@
 and whose passengers belong to $V \setminus S$.  In other words,
-$M(S)$ is the maximum weight carpool matching that is contained in
+$M(S)$ is the maximum weight carpool matching that is a subset of
 $A \cap (V \setminus S) \times S$.
@@
 Given $S$, the carpool matching $M(S)$ can be computed in polynomial
-time using maximum flow as shown in~\cite{??}.
+time using maximum flow as shown in~\cite{kutiel2016}.
 
@@
 \begin{theorem}
-There exists a randomized polynomial time $2$-approximation algorithm
-for \carpool.
+There exists a polynomial time $2$-approximation algorithm for \carpool.
 \end{theorem}

### 2017-02-05 src/abstract.tex
fix

@@
 For the unweighted variant of
-the problems when the maximum possible capacity, $C$, is fixed, we give
-a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm.
-We also show that the problem remains APX-hard even if $C \leq 3$.
+the problems when the maximum possible capacity, $\cmax$, is fixed, we give
+a $(\frac{\cmax + 1}{2\cmax} - \varepsilon)$-approximation algorithm.
+We also show that the problem remains APX-hard even if $\cmax \leq 3$.

### 2017-02-05 src/intro.tex
fix

@@
 \subref{carpool:output}
-a feasible matching with total weight of 26.
-$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
+a feasible matching with total weight of 23.
+$P_M$ is the set of blue vertices, and $D_M$ is the set of red, dashed
+vertices, and $Z_M$ contains only the dotted, black vertex.
 }
@@
 due to Chandra et al.~\cite{chandra2001greedy} and it admits a 
-$\frac{2(k +1)}{3}$ approximation ratio where $k$ is the size of the sets.
+$\frac{3}{2(k +1)}$ approximation ratio where $k$ is the size of the sets.
 
@@
 In Section~\ref{sec:local} we consider the unweighted variant of the
-problem.  We provide a $(\frac{2\cmax}{\cmax+1} + \eps)$-approximation
+problem.  We provide a $(\frac{\cmax+1}{2\cmax} + \eps)$-approximation
 algorithm, for any $\eps>0$, where $\cmax$ is the maximum capacity.

### 2017-02-05 src/sub.tex
fix

@@
 Given $S$, the carpool matching $M(S)$ can be computed in polynomial
-time using maximum flow as shown in~\cite{kutiel2016}.
+time using a maximum b-matching in the bipartite graph 
+$B = (S \cup V \setminus S, A \cap (V \setminus S) \times S)$ or can be reduced
+to a max-cost flow problem as shown in~\cite{kutiel2016}.
 
@@
 a \emph{submodular set function}.  Recall that a function $f$ is
-submdular if $f(S) + f(T) \geq f(S \cup T) + f(S \cap T)$ for every
+submodular if $f(S) + f(T) \geq f(S \cup T) + f(S \cap T)$ for every
 two sets $S$ and $T$ in the domain of $f$.
@@
 \end{theorem}
+
+\begin{figure}
+\centering
+\input{fig-submodular}
+\caption[]{
+\label{fig:defs}
+In this example, $M$ is the set of the blue, dashed arcs, then:
+$val_M(2) = 7$,
+$val_M(3) = 2$,
+$val_M(6) = 0$,
+$\delta_M(2, 3) = 1$,
+$\delta_M(6, 3) = 2$,
+the set $\{(2,3), (6,3)\}$ is an \emph{improvement} to vertex 3,
+$inc(2,3) = \{(1,2),(4,2),(3,5),(6,3)\}$,
+$\text{pass}_M(2) = \{1, 4\}$.
+}
+\end{figure}

### 2017-02-06 src/sub.tex
fix

@@
 
-Buchbinder et al.~\cite{BFNS15} presented a general randomized
-$2$-approximation algorithm for unconstrained submodular maximization.
+Buchbinder et al.~\cite{BFNS15,buchbinder2016deterministic} presented a
+general randomized $2$-approximation algorithm for unconstrained submodular maximization.
 
@@
 \label{fig:defs}
-In this example, $M$ is the set of the blue, dashed arcs, then:
-$val_M(2) = 7$,
-$val_M(3) = 2$,
-$val_M(6) = 0$,
-$\delta_M(2, 3) = 1$,
-$\delta_M(6, 3) = 2$,
-the set $\{(2,3), (6,3)\}$ is an \emph{improvement} to vertex 3,
-$inc(2,3) = \{(1,2),(4,2),(3,5),(6,3)\}$,
-$\text{pass}_M(2) = \{1, 4\}$.
-}
+We show that the arcs from \subref{sub:cup} and \subref{sub:cap} can be
+redistributed over \subref{sub:s} and \subref{sub:s} \todo{write explanation}}
 \end{figure}

### 2017-02-09 src/intro.tex
merge dror

@@
-Carpooling is the sharing of car journeys so that more than one
-person travels in a car.  Knapen et al.~\cite{knapen2013estimating}
-describe an automatic service to match commuting trips.  Users of the
-service register their personal profile and a set of periodically
-recurring trips, and the service advises registered candidates on how
-to combine their commuting trips by carpooling.  The service acts in
-two phases.
+As traveling costs become higher and parking becomes sparse is it only
+natural to share rides or to \emph{carpool}.  Originally, carpooling
+was an arrangement among a group of people by which they take turns
+driving the other to and from a designated location.  However, taking
+turns is not essential, instead passengers can share the cost of the
+ride with the driver.  Carpooling has social advantages other than
+reducing the costs: it reduces fuel consumption and road congestion
+and frees parking space.  
+%
+While in the past carpooling was usually a fixed arrangement between
+friends or neighbors, the emergence of social networks has made
+carpooling more dynamic and wide scale.  These days applications like
+Zimride~\cite{zimride}, BlaBlaCar~\cite{blablacar},
+Moovit~\cite{moovit} and even Waze~\cite{waze} are matching passengers
+to drivers.
 
-In the first phase, the service estimates the probability that a person $a$
-traveling in person's $b$ car will be satisfied by the trip.
-This is done based on personal information and feedback from users on past
+The matching process of passengers to drivers entails more than
+matching the route.  Passenger satisfaction also need to be taken into
+account.
+%
+Given several riding options (including taking their own car),
+passengers have preferences.  For example, a passenger may prefer to
+ride with a co-worker or a friend.  A passenger may have an opinion on
+a driver that she rode with in the past.  She may prefer a non-smoker,
+someone who shares her taste in music, or someone who is recommended
+by others.
+%
+Preferences may also be computed using past information.  Knapen et
+al.~\cite{knapen2013estimating} described an automatic service to
+match commuting trips.  Users of the service register their personal
+profile and a set of periodically recurring trips, and the service
+advises registered candidates on how to combine their commuting trips
+by carpooling.  The service estimates the probability that a person
+$a$ traveling in person's $b$ car will be satisfied by the trip.  This
+is done based on personal information and feedback from users on past
 rides.
-The second phase is about finding a carpool matching
-that maximizes the global (total expected) satisfaction.
 
-The second phase can be modeled in terms of graph theory.  Given a
-directed graph $G = (V, A)$, each vertex $v \in V$ corresponds to a
-user of the service and an arc $(u, v)$ exists if the user
-corresponding to vertex $u$ is willing to commute with the user
-corresponding to vertex $v$.  A capacity function $ c:
-V \rightarrow \N $ is defined according to the number of passengers
-each user can drive if she was selected as a driver.  A weight
-function $w : A \rightarrow \R $ defines the amount of satisfaction
-$w(u, v)$ that user $u$ gains when riding with user $v$.
+In this paper we assume that potential passenger satisfactions are
+given as input and the goal is to compute an assignment of passengers
+to driver so as to maximize the global satisfaction.
 %
-%Let $(G,c,w)$ be a carpool instance.
+More formally, we are given a directed graph $G = (V, A)$, where each
+vertex $v \in V$ corresponds to a user of the service, and an arc $(u,
+v)$ exists if the user corresponding to vertex $u$ is willing to
+commute with the user corresponding to vertex $v$.  We are given a
+capacity function $c: V \rightarrow \N$ which bound the number of
+passengers each user can drive if she was selected as a driver.  A
+non-negative weight function $w : A \rightarrow \R^*+$ is used to model
+the amount of satisfaction $w(u,v)$ that user $u$ gains when riding
+with user $v$.
+%
 If $(u,v) \in A$ implies that $(v,u) \in A$ and $w(u,v) = w(v,u)$, we
@@
 A feasible \emph{carpool matching} is a subset of arcs, $M \subseteq
-A$, such that every $v \in V$ satisfies:
+A$, such that every $v \in V$ satisfies:%
 \begin{inparaenum}[(i)]
@@
 \end{inparaenum}
-A vertex $v$ for which $\dout[M](v) = 1$ is a \emph{passenger}, and a
-vertex for which $\dout[M](v) = 0$ is a driver who has $\din[M](v)$
-passengers.  In the \carpool problem the goal is to find a matching
-$M$ of maximum total weight, namely to maximize
-$w(M) \eqdf \sum_{(v,u) \in M} w(v,u)$.  In other words, the \carpool
-problem is about finding a set of (directed toward the center) vertex
-disjoint stars that maximizes the total weight of the arcs.
+A feasible carpool matching $M$ partition of $V$ as follows:
+\begin{align*}
+P_M & \eqdf \set{v : \dout[M](v) = 1} \\
+D_M & \eqdf \set{v : \din[M](v) \geq 1} \\
+Z_M & \eqdf \set{v : \dout[M](v) = \din[M](c) = 0}
+~.
+\end{align*}
+where $P_M$ is the set of \emph{passengers}, $D_M$ is the set of
+\emph{active drivers}, and $Z_M$ is the set of \emph{solo drivers}.
+%
+In the \carpool problem the goal is to find a matching $M$ of maximum
+total weight, namely to maximize $w(M) \eqdf \sum_{(v,u) \in M}
+w(v,u)$.  In other words, the \carpool problem is about finding a set
+of (directed toward the center) vertex disjoint stars that maximizes
+the total weight of the arcs.  
+%
 Figure~\ref{fig:carpool} is an example of the \carpool problem.
+%
+Note that in the unweighted case the goal is to find a carpool
+matching $M$ that maximizes $\abs{P_M}$.
+%
+Moreover, observe that if $G$ is undirected, $D_M \cup Z_M$ is
+a \emph{dominating set}.  Hence, in this case, an optimal carpool
+matching induces an optimal dominating set and vice versa.
+Since \textsc{Minimum Dominating Set} is NP-hard, if follows
+that \carpool is NP-hard even if the instance is undirected,
+unweigthed, and uncapacitated.
 
@@
 \label{fig:carpool}
-A carpool matching example: 
-\subref{carpool:input}
-a directed graph with capacities on the vertices and weights on the arcs. 
-\subref{carpool:output}
-a feasible matching with total weight of 23.
-$P_M$ is the set of blue vertices, and $D_M$ is the set of red, dashed
-vertices, and $Z_M$ contains only the dotted, black vertex.
-}
+A \carpool example: (\subref{carpool:input}) an instance containing a
+directed graph with capacities on the vertices and weights on the
+arcs.  (\subref{carpool:output}) a feasible matching with total weight
+of 23.  $P_M$ is the set of blue vertices, and $D_M$ is the set of
+red, dashed vertices, and $Z_M$ contains only the dotted, black
+vertex.  }
 \end{figure}
@@
 In this paper we also consider an extension of \carpool, called \gcp,
-in which each vertex represents a group of passengers, and  
-each group might have a different size. 
-Formally, each vertex $u \in V$ has a size $s(u) \in \N$, 
-and the constraint $\din[M](v) \leq c(v)$ is replaced with the constraint
-$\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
+in which each vertex represents a group of passengers, and each group
+might have a different size.  Such a group may be a family or two
+friends traveling together.  Formally, each vertex $u \in V$ has a
+size $s(u) \in \N$, and the constraint $\din[M](v) \leq c(v)$ is
+replaced with the constraint $\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
 %
-Notice that \textsc{Knapsack} is the special case, where only
-arcs directed at a single vertex have non-zero (integral) weights.
+Notice that \textsc{Knapsack} is the special case where only arcs
+directed at a single vertex have non-zero (integral) weights.
 
@@
 %
-Hartman et al.~\cite{hartman2013optimal} proved that the \carpool
-problem is NP-hard, and that the problem
-remains NP-hard even for a binary weight function when the capacity
-function $c(v) \leq 2$ for every vertex in $V$.  It is also worth
-mentioning, that in the undirected, uncapacitated, unweighted variant
-of the problem, the set of drivers in an optimal solution form a
-minimum dominating set (see Section~\ref{sec:hardness}).  When the set
-of drivers is known in advanced, however, the problem becomes
-tractable and can be solved using a reduction to a flow network
-problem.
-
 Agatz et al.~\cite{agatz2012optimization} outlined the optimization
@@
 ride-sharing and survey the related operations research models in the
-academic literature.  Hartman et al.~\cite{hartman2014theory} designed
+academic literature.
+%
+Hartman et al.~\cite{hartman2014theory} designed
 several heuristic algorithms for the \carpool problem and compared
 their performance on real data.  Other heuristic algorithms were
-developed as well~\cite{knapen2014exploiting}.  Arkin et
-al.~\cite{arkin2004approximations} considered other variants of
-capacitated star packing where a capacity vector is given as part of
-the input and capacities need to be assigned to vertices.
+developed as well~\cite{knapen2014exploiting}.
+%
+Hartman~\cite{hartman2013optimal} proved that the \carpool problem is
+NP-hard even in the case where the weight function is binary and
+$c(v) \leq 2$ for every $v \in V$.  In addition, Hartman presented a
+natural integer linear programs and showed that if the set of drivers
+is known, then an optimal assignment of passengers to drivers can be
+found in polynomial time using a reduction to \textsc{Network Flow}
+(see also Kutiel~\cite{kutiel2016}.)
 
 Nguyen et al.~\cite{nguyen2008approximating} considered
-the \textsc{spanning star forest} problem (the undirected,
-uncapacitated, unweighted variant of the problem).  They proved the
-following results:
-\begin{inparaenum}[(i)]
-\item there is a polynomial-time approximation scheme for planner graphs;
-\item there is a polynomial-time $\frac{3}{5}$-approximation algorithm for graphs;
-\item there is a polynomial-time $\frac{1}{2}$-approximation algorithm for weighted graphs.
-\end{inparaenum}
-They also showed how to apply the spanning star forest model to
-aligning multiple genomic sequences over a tandem duplication region.
-Chen et al.~\cite{chen2007improved} improved the approximation ratio
-to 0.71, and also showed that the problem can not be approximated to
-within a factor of $\frac{31}{32} + \epsilon$ for any $\epsilon > 0$
-under the assumption that $\text{P} \neq \text{NP}$.  It is not clear,
-however, if any of the technique used to address the
-\textsc{spanning star forest} problem can be generalized to approximate the
-directed capacitated variant.
+the \textsc{Spanning Star Forest} problem.  A \emph{star forest} is a
+graph consisting of node-disjoint star graphs.  In
+the \textsc{Spanning Star Forest} problem, we are given an undirected
+graph $G$, and the goal is to find a spanning subgraph which is a star
+forest that maximizes the weight of edges that are covered by the star
+forest.  Notice that this problem is equivalent to \carpool on
+undirected and uncapacitated instances.
+%
+Nguyen et al.~\cite{nguyen2008approximating} provided a PTAS for
+unweighted planner graphs and a polynomial-time
+$\frac{3}{5}$-approximation algorithm for unweighted graphs.  They
+gave an exact optimization algorithm for weighted trees, and used it
+on a minimum spanning tree of the input graph to obtain a
+$\frac{1}{2}$-approximation algorithm for weighted graphs.  They also
+shows that it is NP-hard to approximate problem \textsc{Spanning Star
+Forest} within a ratio of $\frac{259}{260}+\eps$, for any $\eps>0$.
+%
+%They also showed how to apply the spanning star forest model to
+%aligning multiple genomic sequences over a tandem duplication region.
+%
+Chen et al.~\cite{CENRRS13} improved the approximation ratios from
+$\frac{3}{5}$ and $\inv{2}$ to $0.71$ and $0.64$, resp.  They also
+showed that the problem can not be approximated to within a factor of
+$\frac{31}{32} + \eps$, for any $\eps > 0$ assuming that
+$\text{P} \neq \text{NP}$.
+%
+Chakrabarty and Goel~\cite{ChakrabartyGoel10} improved the lower bound
+to $\frac{10}{11} + \eps$.
+
+Athanassopoulos et al.~\cite{ACKK09} improve the ratio for the
+unweighted case to $\frac{193}{240} \approx 0.804$.
+%
+They consider a natural family of \emph{local search} algorithms
+for \textsc{Spanning Star Forest}.  Such an algorithm starts with the
+solution where all node are star centers.  Then, it repeatedly tries
+to turn $t \leq k$ from leaves to centers and $t+1$ centers to leaves.
+A change is made if it results in a feasible solution, namely if each
+leave is adjacent to at least one center.  The algorithm terminates
+when such changes are no longer possible.  Athanassopoulos et
+al.~\cite{ACKK09} showed that such algorithms do not provide better
+than $(\inv{2} + \frac{1}{2(k+2)})$-approximate spanning star forests.
+
+Bar-Noy et al.~\cite{bar2015improved} considered the
+\textsc{Minimum $2$-Path Partition} problem.
+In this problem the input is a complete graph on $3k$ vertices with
+non-negative edge weights, and the goal is to partition the graph into
+disjoint paths of length 2.  This problem is the special case of the
+undirected carpool matching where $c(v) = 2$, for every $v \in V$.
+They presented two approximation algorithms, one for the weighted case
+whose is ratio is $0.5833$, and another for the unweighted case whose
+ratio is $\frac{3}{4}$.
+
+Another related problem is \textsc{$k$-Set Packing}.  In this problem
+one is given a collection of weighted sets, each containing as most
+$k$ elements, and the goal is to find a maximum weight subcollection
+of disjoint sets.  Chandra and Halld\'orsson~\cite{chandra2001greedy}
+presented a $\frac{3}{2(k+1)}$-approximation algorithm for this
+problem.
+
+Consider a subset of
+nodes $U$ of size at most $k$.  Observe that each subset of nodes has
+an optimal internal assignment of passenger to drivers.  Let the
+weight of this assignment be the profit of $U$, denote $p(U)$.  If $k
+= O(1)$, then $p(U)$ can be computed for every $U$ of size at most $k$
+in polynomial time.  The outcome is a \textsc{Set Packing} instance.
+
+Arkin et al.~\cite{arkin2004approximations} considered other variants
+of capacitated star packing where a capacity vector is given as part
+of the input and capacities need to be assigned to vertices.
 
@@
 
-Bar-Noy et al.~\cite{bar2015improved} considered the problem of partition a
-graph into disjoint paths of length 2.
-This problem is a special case of the undirected carpool matching
-where all capacities are exactly 2.
-They show a $.5833$, and $\frac{3}{4}$-approximation algorithms for the weighted
-and unweighted variants of the problem respectively.
-
-For the general set packing problem, the best known approximation algorithm is
-due to Chandra et al.~\cite{chandra2001greedy} and it admits a 
-$\frac{3}{2(k +1)}$ approximation ratio where $k$ is the size of the sets.
-
 %%%%%
@@
 %
-In Section~\ref{sec:sub} we show that the \carpool can be formulated as
-unconstrained submodular maximization problem, thus it has a
-$\frac{1}{2}$-approximation algorithm due to~\cite{BFNS15}.
+In Section~\ref{sec:sub} we show that the \carpool can be formulated
+as unconstrained submodular maximization problem, thus it has a
+$\frac{1}{2}$-approximation algorithm due
+to~\cite{BFNS15,buchbinder2016deterministic}.
 
 In Section~\ref{sec:local} we consider the unweighted variant of the
-problem.  We provide a $(\frac{\cmax+1}{2\cmax} + \eps)$-approximation
-algorithm, for any $\eps>0$, where $\cmax$ is the maximum capacity.
-We also show that \carpool is APX-hard even if $\cmax \leq 3$.
+problem.  We provide a $(\frac{\cmax+1}{2\cmax} - \eps)$-approximation
+algorithm, for any $\eps>0$, where $\cmax \eqdf \max_{v \in V} c(v)$
+is the maximum capacity.  We also show that \carpool is APX-hard even
+if $\cmax \leq 3$.
 %

### 2017-02-09 src/preliminaries.tex
fix
merge dror

@@
-In this section
-
-We use standard graph theoretic notation.
-
-$N^-$ and $N^+$.
+$\nin[]$ and $\nout[]$.
 
@@
 $w(A') \eqdf \sum_{(v,u) \in A'} w(v,u)$.
-
-Given a directed graph $G = (V,A)$ and a feasible carpool matching
-$M \subseteq A$, we define a partition of $V$ as follows:
-\begin{align*}
-P_M & \eqdf \set{v : \dout[M](v) = 1} \\
-D_M & \eqdf \set{v : \din[M](v) \geq 1} \\
-Z_M & \eqdf \set{v : \dout[M](v) = \din[M](c) = 0}
-~.
-\end{align*}
-where $P_M$ is the set of \emph{passengers}, $D_M$ is the set of
-\emph{drivers}, and $Z_M$ is the set of \emph{singletons}.
-
-In Figure~\ref{fig: }

### 2017-02-09 src/sub.tex
rm todos

@@
 We show that the arcs from \subref{sub:cup} and \subref{sub:cap} can be
-redistributed over \subref{sub:s} and \subref{sub:s} \todo{write explanation}}
+redistributed over \subref{sub:s} and \subref{sub:s} 
+%\todo{write explanation}
+}
 \end{figure}

### 2017-02-09 src/group-apx.tex
fix outline

--- 2016-12-05 src/merge.tex
@@
-\documentclass[draft]{article}
-
-\usepackage{amsmath,amssymb,amsthm,mathtools}
-\usepackage[linesnumbered, ruled]{algorithm2e}
-\usepackage[]{subfig}
-\usepackage{paralist}
-\usepackage{hyperref}
-\hypersetup{final}
-\usepackage[inline]{enumitem}
-
-% DEBUG
-\usepackage{fullpage}
-\usepackage{todonotes}
-\usepackage{lineno}
-\linenumbers
-
-% EXTRA
-\usepackage{authblk}
-\def\CARPOOL{maximum carpool matching}
-
-\newcommand{\din}[1][M]{deg^{#1}_{in}}
-\newcommand{\dout}[1][M]{deg^{#1}_{out}}
-\newcommand{\dinout}[1][M]{deg^{#1}}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\def\R{\mathbb{R}}
-\def\N{\mathbb{N}}
-
-\newtheorem{observation}{Observation}
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{remark}{Remark}
-\usepackage{tikz}
-\usetikzlibrary{
-	arrows,
-	arrows.meta,
-	calc,
-	graphs,
-	patterns,
-	positioning,
-	shapes,
-	decorations.pathmorphing,
-}
-
-%DEFAULT STYLE
-\tikzset{default style/.style={
-	>=Stealth, 
-	on grid, 
-	auto, 
-	thick,
-}}
-
-% NODE
-\tikzset{default node/.style={
-	draw, 
-	circle,
-	inner sep=0mm,
-	minimum size=5mm,
-	very thick,
-	font=\small,
-	black!70,
-}}
-
-% LABELS
-\tikzset{label/.style={
-	draw=none,
-	sloped,
-}}
-
-\tikzset{label above/.style={
-	label,
-	midway,
-	above=-1mm,
-}}
-
-\tikzset{label below/.style={
-	label,
-	midway,
-	below=-1mm,
-}}
-
-\title{Improved Approximation Algorithms for the Maximum Carpool Matching
-Problme}
-
-\date{}
-\author[1]{Reuven Bar-Yehuda	\thanks{\texttt{reuven@cs.technion.ac.il}}}
-\author[1]{Gilad Kutiel			\thanks{\texttt{gkutiel@cs.technion.ac.il}}}
-\author[2]{Dror Rawitz			\thanks{\texttt{dror.rawitz@biu.ac.il}}}
-
-\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
-\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-The \textsc{\CARPOOL{}} problem is a star packing problem in directed graphs.
-Formally, given a directed graph $G = (V, A)$,
-a capacity function $ c: V \rightarrow \N $,
-and a weight function $w : A \rightarrow \R $,
-a feasible \emph{carpool matching} is a triple 
-$(P, D, M)$, where $P$ (passengers) and $D$ (drivers) form a partition of $V$, 
-and $M$ is a subset of $A \cap (P \times D)$,
-under the constraints that for every vertex $d \in D$, 
-$\din(d) \leq c(d)$, 
-and for every vertex $p \in P$, $\dout(p) \leq 1$.
-In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
-total weight of $M$.
-
-The problem arises when designing an online carpool service, 
-such as Zimride~\cite{zimride}, 
-that tries to connect between passengers and drivers based on (arbitrary) similarity function.
-The problem is known to be NP-hard, 
-even for uniform weights and without capacity constraints.
-
-we show that the problem can be formulated as
-unconstarints submodular maximization problem, 
-thus it has a $\frac{1}{2}$-approximation algorithm.
-For the unweighted variant of the problem when the maximum possible capacity, $C$, is
-fixed, we give a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm
-for the any $\varepsilon > 0$.
-\end{abstract}
-
-\section{Introduction}
-Carpooling, is the sharing of car journeys so that more than one person travels
-in a car.
-Knapen et al.~\cite{knapen2013estimating} describe an automatic service
-to match commuting trips.
-Users of the service register their personal profile and a set of periodically
-recurring trips, 
-and the service advises registered candidates on how to combine their commuting
-trips by carpooling.
-The service acts in two phases.
-
-In the first phase, the service estimates the probability that a person $a$
-traveling in person's $b$ car will be satisfied by the trip.
-This is done based on personal information and feedback from users on past
-rides.
-The second phase is about finding a carpool matching
-that maximizes the global (total expected) satisfaction.
-
-The second phase can be modeled in terms of graph theory.
-Given a directed graph $G = (V, A)$.
-Each vertex $v \in V$ corresponds to a user of the service and an arc
-$(u, v)$ exists if the user corresponding to vertex $u$ is willing to
-commute with the user corresponding to vertex $v$.
-A capacity function $ c: V \rightarrow \N $ is defined
-according to the number of passengers each user can drive if she was
-selected as a driver.
-A weight function $w : A \rightarrow \R $ defines the amount of
-satisfaction $w(u, v)$,
-that user $u$ gains when riding with user $v$.
-
-A feasible \emph{carpool matching} (matching) is a triple 
-$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
-and $M$ is a subset of $A \cap (P \times D)$,
-under the constraints that for every driver $d \in D$, 
-$\din(d) \leq c(d)$, 
-and for every passenger $p \in P$, ${\dout(p) \leq 1}$.
-In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
-total weight of $M$.
-In other words, the \textsc{\CARPOOL{}} problem is about finding a set of 
-(directed toward the center) vertex disjoint stars 
-that maximizes the total weights on the arcs.
-Figure~\ref{fig:carpool} is an example of the \textsc{\CARPOOL{}} problem.
-
-\begin{figure}
-\centering
-\newcommand{\edge}[3]{
-	\draw (#1) -- (#2) node[label above] {#3};
-}
-\subfloat[]{
-\label{subfloat:input}
-\begin{tikzpicture}[every node/.style={default node}, ->, very thick]
-
-\node(1) at(-1,3) {2};
-\node(2) at(.5,.5) {3};
-\node(3) at(-1,0) {1};
-\node(4) at(-1,1) {3};
-\node(5) at(-2,2) {0};
-\node(6) at(-2,-1) {4};
-\node(7) at(-3,0) {3};
-\node(8) at(.5,-1) {2};
-\node(9) at(0,2) {1};
-\node(10) at(2,1) {4};
-
-\edge{1}{4}{3}
-\edge{2}{4}{4}
-\edge{3}{4}{5}
-
-\edge{5}{7}{2}
-\edge{6}{7}{4}
-
-\edge{8}{10}{6}
-\edge{9}{10}{2}
-
-\edge{1}{5}{4}
-\edge{4}{5}{4}
-
-\edge{2}{3}{2}
-\edge{6}{3}{2}
-\edge{7}{3}{2}
-
-\edge{8}{2}{1}
-\edge{10}{2}{1}
-
-\edge{3}{8}{3}
-\edge{8}{3}{3}
-
-\edge{1}{9}{1}
-\edge{4}{9}{1}
-
-\end{tikzpicture}}
-\hfill\subfloat[]{
-\label{subfloat:output}
-\begin{tikzpicture}[every node/.style={default node}, ->, very thick]
-
-\begin{scope}[every node/.style={default node, draw=blue}]
-\node(5) at(-2,2) {0};
-\node(6) at(-2,-1) {4};
-
-\node(2) at(.5,.5) {3};
-\node(3) at(-1,0) {1};
-\node(1) at(-1,3) {2};
-
-\node(8) at(.5,-1) {2};
-\node(9) at(0,2) {1};
-\end{scope}
-
-\begin{scope}[every node/.style={default node, draw=red, dashed}]
-\node(7) at(-3,0) {3};
-
-\node(4) at(-1,1) {3};
-
-\node(10) at(2,1) {4};
-\end{scope}
-
-\edge{1}{4}{3}
-\edge{2}{4}{4}
-\edge{3}{4}{5}
-
-\edge{5}{7}{2}
-\edge{6}{7}{4}
-
-\edge{8}{10}{6}
-\edge{9}{10}{2}
-
-\end{tikzpicture}}
-\caption[]{
-\label{fig:carpool}
-A carpool matching example: 
-\subref{subfloat:input} 
-a directed graph with capacities on the vertices and weights on the arcs. 
-\subref{subfloat:output}
-a feasible matching with total weight of 26.
-$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
-}
-\end{figure}
-
-Hartman et al.~\cite{hartman2013optimal} proved that the
-\emph{\CARPOOL{}} problem considered in this paper is NP-hard,
-and that the problem remains NP-hard even for a binary weight function when
-the capacity function $c(v) \leq 2$ for every vertex in $V$.
-It is also worth mentioning, that in the undirected, uncapacitated, unweighted
-variant of the problem, the set of drivers in an optimal solution
-form a minimum dominating set.
-When the set of drivers is known in advanced, however, the problem becomes
-tractable and can be solved using a reduction to a flow network problem.
-
-Agatz et al.~\cite{agatz2012optimization} outlined the optimization challenges
-that arise when developing technology to support ride-sharing and survey the
-related operations research models in the academic literature.  
-Hartman et al.~\cite{hartman2014theory} designed several heuristic algorithms
-for the \CARPOOL{} problem and compared 
-their performance on real data.
-Other heuristic algorithms were developed as well~\cite{knapen2014exploiting}.
-Arkin et al.~\cite{arkin2004approximations}, considered other variants of
-capacitated star packing where a capacity vector is given as part of the input and 
-capacities need to be assigned to vertices.
-
-Nguyen et al.~\cite{nguyen2008approximating} considered the \textsc{spanning star forest} problem
-(the undirected, uncapacitated, unweighted variant of the problem).
-They proved the following results:
-\begin{enumerate*}
-\item
-there is a polynomial-time approximation scheme for planner graphs;
-\item 
-there is a polynomial-time $\frac{3}{5}$-approximation algorithm for graphs;
-\item 
-there is a polynomial-time $\frac{1}{2}$-approximation algorithm for weighted graphs.
-\end{enumerate*}
-They also showed how to apply the spanning star forest model to aligning multiple
-genomic sequences over a tandem duplication region.
-Chen et al.~\cite{chen2007improved} improved the approximation ratio to 0.71,
-and also showed that the problem can not be approximated to within a factor of
-$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ under the assumption 
-that $\text{P} \neq \text{NP}$.
-It is not clear, however, if any of the technique used to address the
-\textsc{spanning star forest} problem can be generalized to approximate the
-directed capacitated variant.
-
-In section~\ref{sec:sub} we show that the problem can be formulated as
-unconstarints submodular maximization problem, thus it has a 2-approximation
-algorithm.
-In section~\ref{sec:local} we consider the unweighted variant of the problem.
-We show that when the maximum possible capacity, $C$, is fixed, there is a 
-$(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm for the any $\varepsilon > 0$.
-
-\section{Submodularity}
-\label{sec:sub}
-In this section we show that the problem can be formulated as unconstrained
-submodular maximization problem, and thus, it has a 2-approximation algorithm.
-
-Consider the function $w : 2^V \to \R$ where $w(D)$ is the value of the optimal
-carpool matching when the set of drivers is $D$.
-As we mention in the introduction, $w$ can be computed efficiently.
-
-\begin{theorem}
-$w$ is submodular.
-\end{theorem}
-
-\begin{proof}
-Consider two subsets $A,B \subseteq V$, 
-we need to show that $w(A) + w(B) \geq w(A \cup B) + w(A \cap B)$.
-Let $E_{A \setminus B} = (V \setminus A) \times (A \setminus B)$, 
-$E_{B \setminus A} = (V \setminus A) \times (B \setminus A)$,
-and $E_{B \cap A} = (V \setminus (A \cap B)) \times (B \cap A)$.
-
-Let $M_{A \cup B}$ and $M_{A \cap B}$ be the set of edges in an optimal
-matching when the set of drivers are $A \cup B$ and $A \cap B$ respectively.
-We argue that we can construct two (feasible) matchings $M_A$ and $M_B$ using
-the sets of drivers $A$ and $B$ respectively and 
-$w(M_A) + w(M_B) = w(M_{A \cup B}) + w(M_{A \cap B})$.
-First, take all the edges from $M_{A \cup B} \cap E_{A \setminus B}$ and 
-add them to $M_A$, 
-add $M_{A \cup B} \cap E_{B \setminus A}$ to $M_B$.
-Clearly this can be done.
-Now, split the edges from $M_{A \cap B} \cup (M_{A \cup B} \cap E_{A \cap B})$
-between $M_A$ and $M_B$ in a way that does not violate the capacity constraints.
-One can verify that this can be done.
-\end{proof}
-
-\section{Constant Max Capacity}
-In this section we study the carpool problem when the maximum possible capacity
-is constant.
-We show that this variant of the problem is APX-hard as well.
-We also describe and analyze a local search algorithm for the unweighted
-variant of the problem, 
-and show that the algorithm achieves a 
-$\frac{C + 1}{2C} - \varepsilon$ approximation ratio for any $\varepsilon > 0$.
-Throughout this section we consider $C$ to be fixed, and $k$ to be a fixed parameter.
-
-	\subsection{Hardness}
-	\label{sec:hardness}
-As we mentioned in the introduction, the maximum spanning star forest can not 
-be approximated within a factor of 
-$\frac{31}{32} + \epsilon$ for any $\epsilon > 0$ unless P = NP.
-The proof, however, does not hold for the case when the maximum capacity is
-constant. 
-In this subsection we show that the problem remains APX-hard even in this case.
-
-Formally, the (unweighted)
-minimum dominating set problem is defined as $\min_{D}(|D|)$,
-where $D$ is any feasible dominating set.
-It is also easy to see that the (unweighted, undirected, uncapacitated) 
-maximum carpool matching problem can be defined as $max_{D}(|V \setminus D|)$, 
-where $D$ is any feasible dominating set.
-The \textsc{Dominating Set-B} is the problem of finding minimum dominating set on 
-graphs with degree bounded by $B$,
-and it was shown to be APX-hard (for $B \geq 3$) by 
-Papadimitriou et al.~\cite{papadimitriou1988optimization}.
-
-Let $G$ be a b-bounded degree graph,
-let $D^*(G)$ be a minimum dominating set in $G$,
-and let $C^*(G)$ be a maximum carpool matching in $G$, 
-then the following lemmas hold:
-
-\begin{lemma}
-$|C^*| = |V| - |D^*|$
-\end{lemma}
-
-\begin{proof}
-The proof follows immediately from the definitions of the two problems. 
-\end{proof}
-
-\begin{lemma}
-\label{lm:optc_leq_boptd}
-$|C^*| \leq b \cdot |D^*|$
-\end{lemma}
-
-\begin{proof}
-The proof follows directly from the observation that $|D^*| \geq \frac{|V|}{b}$.
-\end{proof}
-
-Let $C(G)$ be any feasible carpool matching on $G$, then the following lemma holds:
-
-\begin{lemma}
-\label{lm:erreq}
-$|C^*| - |C| = (|V| - |C|) - |D^*|$
-\end{lemma}
-
-\begin{proof}
-$$
-|C^*| - |C| 				= 
-|V| - |D^*| - |C| 	= 
-(|V| - |C|) - |D^*|
-$$
-\end{proof}
-
-Let $D(G)$ be any feasible dominating set in $G$, 
-we argue that $f(G) = G$, and $g(C(G)) = V \setminus C(G)$ 
-define a linear reduction (L-reduction) from the \textsc{Dominating Set-B} problem to the 
-\textsc{\CARPOOL{}} problem.
-\begin{proof}
-By lemma~\ref{lm:optc_leq_boptd} we get that $C^*(f(G)) = C^*(G) \leq b \cdot D^*(G)$,
-and by lemma~\ref{lm:erreq} we get that 
-\begin{equation}
-\begin{split}
-|C^*(f(G))| - |C(G)|		& = |C^*(G)| - |C(G)| 			\\
-							& = (|V| - |C(G)|) - |D^*(G)|	\\
-							& = |g(C(G))| - |D^*(G)|
-\end{split}
-\end{equation}
-\end{proof}
-
-\begin{theorem}
-The \textsc{\CARPOOL{}} problem is APX-hard.
-\end{theorem}
-
-\begin{proof}
-The proof follows directly from the above linear reduction and the fact that 
-\textsc{Dominating Set-B} is APX-hard. 
-\end{proof}
-
-	\subsection{Local Search}
-	\label{sec:local}
-The local search algorithm maintains a feasible matching throughout its execution
-and operates in 
-iterative manner where in each iteration it tries to find a better solution by
-replacing a subset of the edges in the current solution with 
-another (larger) subset of edges not in the solution.
-The local search algorithm halts when no improvement can be done.
-The algorithm is described in Algorithm~\ref{alg:local}.
-
-\begin{algorithm}
-\SetKw{True}{true}
-\SetKw{False}{false}
-\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
-\KwOut{$M$}
-$M \leftarrow \emptyset$								\\
-\Repeat{done}{
-\label{line:outerloop}
- 	$done \leftarrow{}$ \True							\\
- 	\For{$M' \in M : |M'| \leq k$}{
- 		\For{$A' \in A \setminus M : |A'| = |M'| + 1$}{
-			\If{$M \setminus M' \cup A'$ is feasible}{
-				$M \leftarrow{} M \setminus M' \cup A'$	\\
-				$done \leftarrow{}$ \False				\\
-			}
-		}
- 	}
-}
-\Return{$M$}
-
-\caption{
-\label{alg:local}
-Local Search}
-\end{algorithm}
-
-We claim that the local search algorithm halts in polynomial time.
-Observed that in every iteration the algorithm either improves the value of the solution
-by one or otherwise it terminates. 
-Thus, after a maximum of $n$ iterations the algorithm stops.
-In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
-both these operations can be done in polynomial time - $O(n^{Ck + 1})$.
-
-To analyze the approximation ratio achieved by the local search algorithm consider an 
-arbitrary but fixed optimal matching $M^*$.
-Given the solution outputted by the local search algorithm, 
-$M$, 
-we build the \emph{star graph} of the two solutions
-in which each node represents a star from the optimal solution 
-and edges exits between two nodes if
-there is a star in $S(M)$ that intersect the two
-corresponding stars of the optimal solution, 
-formally $G^{M^*}_M = (S, E)$ where $\{v_i : S^*_i \in S(M^*) \}$ 
-and 
-$E = \{(v_i, v_j) : 
-\exists S \in M,
-S \cap S^*_i \neq \emptyset \land S \cap S^*_j \neq \emptyset,
-\}$.
-Figure~\ref{fig:conflict} depicts a star graph.
-
-\begin{figure}[ht]
-\centering
-\subfloat[]{
-\label{subfloat:graph}
-\newcommand{\edge}[2]{
-	\draw (#1) -- (#2);
-}
-
-\begin{tikzpicture}[every node/.style={default node}, ->, very thick]
-
-\node(1) at(0,0) {a};
-\node(2) at(0,1.5) {b};
-\node(3) at(1.5,0) {c};
-
-\node(4) at(4,0) {d};
-\node(5) at(4,1.5) {e};
-\node(6) at(2.5,0) {f};
-
-\node(7) at(0,-1.5) {h};
-\node(8) at(0,-3) {i};
-\node(9) at(1.5,-1.5) {j};
-
-\node(10) at(4,-1.5) {k};
-\node(11) at(4,-3) {l};
-
-\begin{scope}[dashed, red]
-\edge{2}{1}
-\edge{3}{1}
-
-\edge{5}{4}
-\edge{6}{4}
-
-\edge{8}{7}
-\edge{9}{7}
-
-\edge{11}{10}
-\end{scope}
-
-\begin{scope}[green]
-\edge{2}{5}
-
-\edge{7}{1}
-\edge{3}{9}
-\end{scope}
-
-\end{tikzpicture}
-}
-\subfloat[]{
-\label{subfloat:conflict}
-\newcommand{\edge}[2]{
-	\draw (#1) -- (#2);
-}
-
-\begin{tikzpicture}[every node/.style={default node, red}, -, very thick, green]
-
-\node(1) at(0,1.5) {3};
-\node(2) at(4,1.5) {1};
-\node(3) at(0,-3) {2};
-\node(4) at(4,-3) {0};
-
-\edge{1}{2}
-\edge{1}{3}
-
-\end{tikzpicture}
-}
-\caption[]{
-\label{fig:conflict}
-\subref{subfloat:input} 
-An optimal matching depicted by the dashed red edges,
-and another solution depicted by the solid green edges.  
-\subref{subfloat:output}
-The conflict graph, the upper left vertex corresponds 
-to the star that contains the vertices a,b,c.
-The numbers inside the vertices corresponds to $d_i$.   
-}
-\end{figure}
-
-For a group of vertices, $U$, denote by $w^*(U)$ the sum of the degrees 
-induced by the underlying graph of the optimal solution on this set, i.e.
-$\sum_{u \in U} \dinout[M^*](u)$, 
-and let $w(S)$ be the sum of the degrees 
-induced by the underlying graph of the local search solution on this set, i.e.
-$\sum_{u \in U} \dinout(u)$.
-
-\begin{lemma}
-\label{lemma:r}
-If $k \geq \text{TODO}$ then in any connected induced graph of $G^{M^*}_M$, 
-$G'= G^{M^*}_M[U]$, 
-$
-\frac{w(U)}{w^*(U)} 
-\geq \frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
-$.
-\end{lemma}
-
-\begin{proof}
-Consider the solution obtained from the $M$ by removing all the edges from $M$
-that intersect the induced subgraph, and adding all the edges from $M^*$ that
-intersect the induced subgraph.
-It is easy to verify that this is a feasible solution.
-We now bound from below the difference in the value of the solution.
-The value decrease due to the removal of the edges by at most $w(U) - |U| + 1$,
-and increase by exactly $\frac{w^*(U)}{2} \leq C |U|$.
-We know that this difference can not be positive, or else, the local search
-algorithm would not have been terminated.
-Thus 
-$\frac{w^*(U)}{2} \leq w(U) - |U| + 1$ 
-and so
-$
-\frac{w(U)}{w^*(U)} 
-\geq 
-\frac{1}{2} + \frac{|U|}{w^*(U))} - \frac{1}{w^*(U))}  
-\geq
-\frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
-$
-\end{proof}
-
-\begin{lemma}
-\label{lemma:dec}
-Given a parameter $k$, a bounded degree connected graph $G$, with a maximum
-degree $d$ can be decomposed into connected components of size at least $k$, and at most
-$d(k-1) + 1$.
-\end{lemma}
-
-\begin{proof}
-We give a constructive proof.
-Start constructing a connected component by adding adjacent vertices
-one by one to the component and removing them from the graph.
-If at some point, removing a vertex disconnect the graph, add all the small
-components (of size less than $k$) to the constructed component and decompose
-the large components (of size at least $k$) recursively.
-Note that removing a vertex can break the graph to at most $d - 1$ additional
-components.
-\end{proof}
-
-\begin{theorem}
-The local search is ($\frac{1}{2} + \frac{1}{2c} - \varepsilon$)-approximation
-algorithm.
-\end{theorem}
-
-\begin{proof}
-Combine lemma~\ref{lemma:dec}, and lemma~\ref{lemma:r}, 
-and observe that the maximum degree in $G^{M^*}_M$ is $(C + 1)^C$ to
-get the desire result.
-\end{proof}
-
-\todo{show that the analysis is tight}
-
-\section{Group Carpool}
-\label{sec:group}
-In this section we introduce the group carpool and show that it does not fit the
-submodular maximization formulation while the local search algorithm handle it
-without any modification.
-
-\subsection{2-approximation}
-In this subsection we give a 2-approximation algorithm for general capacities.
-First, let us introduce a $(\frac{1}{2} - \varepsilon)$-approximation algorithm
-for the original problem.
-We then show how to generalize the algorithm to work also for the group carpool
-matching.
-
-\tikzset{m/.style={
-	blue, 
-	dashed,	
-}}
-
-Let $M$ be a feasible carpool matching,
-the \emph{value} of a vertex $v$, denoted $val(v)$, 
-is the sum of the weights of the arcs in $M$ that incident $v$. 
-That is: 
-%
-\begin{definition}[$val$]
-$val_M(v) = \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u)$
-\end{definition}
-%
-If $V$ is a set of vertices, then $val_M(V) \triangleq \sum_{v \in V} val_M(v)$.
-%
-Denote by $\delta(e)$ the difference between the weight of the arc and the value
-of its source vertex,
-that is:
-%
-\begin{definition}[$\delta$]
-$\delta_M(u, v) = w(u, v) - val_M(u)$
-\end{definition}
-%
-If $S$ is a set of arcs, then $\delta(S) \triangleq \sum_{e \in S}\delta(v)$.
-
-An \emph{improvement} to vertex $v$ 
-is a set of arcs entering $v$ of size not greater than the capacity of $v$, 
-for which the sum of the $\delta$s is greater than the value of $v$,
-formally:
-
-\begin{definition}[improvement]
-$S_v \subseteq V \times \{v\} \cap A$ is an \emph{improvement} (w.r.t $M$)
-if the following conditions hold:
-\begin{itemize}
-\item
-$|S_v| \leq c(v)$
-\item
-$\delta_M(S_v) > val_M(v)$
-\end{itemize}  
-\end{definition}
-%
-If, for vertex $v$, an improvement exists, we say that vertex $v$ can be \emph{improved}.
-%
-Given an arc $(u,v)$, 
-let $inc(u,v)$ be the set of arcs that incident $(u, v)$,
-formally:
-%
-\begin{definition}[inc]
-$inc(u,v) = (V \times \{u, v\} \cup \{u, v\} \times V) \cap A$
-\end{definition}
-%
-If $S$ is a set of arcs, then $inc(S) \triangleq \bigcup_{e \in S} inc(e)$.
-%
-The \emph{passengers} of $v$ (w.r.t some set of arcs) are all the vertices that have
-outgoing arc to $v$, formally: 
-%
-\begin{definition}[passengers]
-$\text{pass}_M(v) = \{u : (u, v) \in M\}$
-\end{definition}
-%
-Figure~\ref{fig:defs} depicts all the above definitions.
-
-\begin{figure}
-\centering
-\begin{tikzpicture}[every node/.style={default node}]
-
-\node(1) at(0,0) {1};
-\node(2) at(2,0) {2};
-\node(3) at(4,0) {3};
-
-\node(4) at(.4,1.6) {4};
-\node(5) at(2.4,1.6) {5};
-\node(6) at(6, 0) {6};
-
-\draw[m] (1) -- (2) node[label above]{$5$};
-\draw[m] (4) -- (2) node[label above]{$2$};
-\draw[m] (3) -- (5) node[label above]{$2$};
-\draw[] (6) -- (3) node[label above]{$2$};
-
-\draw (2) -- (3) node[label above]{$8$};
-
-\end{tikzpicture}
-\caption[]{
-\label{fig:defs}
-In this example, $M$ is the set of the blue, dashed arcs, then:
-$val_M(2) = 7$,
-$val_M(3) = 2$,
-$val_M(6) = 0$,
-$\delta_M(2, 3) = 1$,
-$\delta_M(6, 3) = 2$,
-the set $\{(2,3), (6,3)\}$ is an \emph{improvement} to vertex 3,
-$inc(2,3) = \{(1,2),(4,2),(3,5),(6,3)\}$,
-$\text{pass}_M(2) = \{1, 4\}$.
-}
-\end{figure}
-
-We are now ready to describe our algorithm.
-The algorithm starts with an empty matching,
-in every iteration it seeks for a vertex that can be improved,
-it then improve the matching by adding
-the arcs that improve the vertex, 
-just after removing the arcs that incident them.
-The algorithm halts when no vertex can be improved.
-Figure~\ref{fig:improvement} depicts an improvement step,
-and the full algorithm is listed in Algorithm~\ref{alg:grd}.
-
-\begin{figure}
-\centering
-\subfloat[]{
-\label{sub:can improved}
-\begin{tikzpicture}[every node/.style={default node}]
-\node(1) at(0,0) {1};
-\node(2) at(2,0) {2};
-\node(3) at(4,0) {3};
-
-\node(4) at(.4,1.6) {4};
-\node(5) at(2.4,1.6) {5};
-\node(6) at(2.4, -1.6) {6};
-
-\draw[m] (1) -- (2) node[label above]{$5$};
-\draw[m] (4) -- (2) node[label above]{$2$};
-\draw[m] (3) -- (5) node[label above]{$2$};
-\draw[] (6) -- (3) node[label above]{$2$};
-
-\draw (2) -- (3) node[label above]{$8$};
-
-\end{tikzpicture}
-}\hspace{1cm}\subfloat[]{
-\label{sub:improved}
-\begin{tikzpicture}[every node/.style={default node}]
-\node(1) at(0,0) {1};
-\node(2) at(2,0) {2};
-\node(3) at(4,0) {3};
-
-\node(4) at(.4,1.6) {4};
-\node(5) at(2.4,1.6) {5};
-\node(6) at(2.4, -1.6) {6};
-
-\draw[] (1) -- (2) node[label above]{$5$};
-\draw[] (4) -- (2) node[label above]{$2$};
-\draw[] (3) -- (5) node[label above]{$2$};
-\draw[m] (6) -- (3) node[label above]{$2$};
-
-\draw[m] (2) -- (3) node[label above]{$8$};
-
-\end{tikzpicture}
-}
-\caption[]{
-\label{fig:improvement}
-\subref{sub:can improved}
-A matching that can be improved
-\subref{sub:improved}
-The matching after improving vertex 3
-}
-\end{figure}
-
-\begin{algorithm}
-\caption{
-\label{alg:grd}
-GRD
-}
-$M \leftarrow \emptyset$									\\
-\While{done}{
-	done $\leftarrow$ True									\\
-	\For{$v \in V$}{
-		\If{$\exists$~improvment~$S_v$}{
-			$M \leftarrow M \setminus inc(S_v) \cup S_v$	\\
-			done $\leftarrow$ False							\\
-		}
-	}
-}
-\end{algorithm}
-
-\begin{remark}
-\label{rem:improve}
-Determining if a vertex $v$ can be improved can be done efficiently
-by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
-and only ones with positive value.
-Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
-sum up to more than $val_M(v)$.
-\end{remark}
-
-\begin{remark}
-It is easy to see, if the weights on the edges are integral and polynomial
-bounded the algorithm runs in polynomial time, this is because in each iteration the
-algorithm improves the value of the matching by at least one or otherwise it
-terminates.
-\end{remark}
-
-\begin{remark}
-When the weights are not integral nor polynomial bounded one can use scaling and
-rounding first to ensure polynomial runtime in the cost of $\varepsilon$ in the
-approximation ratio.
-\end{remark}
-
-We now argue that, with respect to any matching, 
-the total value of all the vertices equals twice the value of the matching, 
-formally: 
-\begin{lemma}
-\label{lm:val-twice}
-$\sum_{v \in V} val_M(v) = 2 \sum_{e \in M} w(e)$
-\end{lemma}
-
-\begin{proof}
-\begin{equation}
-\begin{split}
-\sum_{v \in V} val_M(v)	& = 
-\sum_{v \in V} \left( \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u) \right)	\\
-						& = \sum_{v \in V}\sum_{(u, v) \in M} w(u, v) + 
-							\sum_{v \in V}\sum_{(v, u) \in M} w(v, u)					\\
-						& = 2 \sum_{e \in M} w(e)
-\end{split}
-\end{equation}
-\end{proof}
-
-Let $M$ be a matching, and let $v$ be a vertex with no improvement,
-let $S \subseteq V \times \{v\} \cap A$ of size not greater than $c(v)$,
-then the following lemma holds:
-
-\begin{lemma}
-\label{lm:no improve}
-$w(S) \leq val_M(v) + val_M(\text{pass}_S(v))$
-\end{lemma}
-
-\begin{proof}
-If no improvement exists then
-$$
-w(S) - val_M(\text{pass}_S(v))=
-\sum_{(u,v) \in S}(w(u,v) - val_M(u)) =
-\delta_M(S) 
-\leq val_M(v)
-$$
-\end{proof}
-
-To bound the approximation ratio of the GRD algorithm, 
-we use a charging scheme argument.
-Given the matching produced by the algorithm, 
-we load every vertex with amount of money equal to its value,
-we then show that this is enough to pay for every arc in an optimal matching.
-
-\begin{theorem}
-Algorithm~\ref{alg:grd} is $\frac{1}{2}$-approximation.
-\end{theorem}
-
-\begin{proof}
-Let $M$ be the matching produced by algorithm~\ref{alg:grd}, 
-and let $M^*$ be an optimal matching.
-Load every vertex with $val_M(v)$ money, 
-by lemma~\ref{lm:val-twice} this is exactly twice the value of $M$.
-Consider a driver $v$ in $M^*$, and let $S = V \times \{v\} \cap M^*$.
-By lemma~\ref{lm:no improve} we know that $w(S) \leq val_M(v) + val_M(\text{pass}_S(v))$,
-thus we can pay for $S$, using the money on $v$ and $\text{pass}_S(v)$.
-Clearly, these vertices will not be charged again.
-\end{proof}
-
 We now argue that this algorithm can be generalized to solve the group carpool
@@
 approximation ratio of the algorithm.
-
-To conclude this section we show that our analysis is tight, 
-as depicts in Figure~\ref{fig:grd worst}.
-\todo[inline]{what happen if we apply the rule on both directions ?}
-\begin{figure}
-\centering
-\begin{tikzpicture}[every node/.style={default node}]
-
-\def\sep{1.5}
-
-\foreach \n in {0,...,5}{
-	\pgfmathsetmacro{\x}{\n * \sep}
-	\node(\n) at(\x,0){};
-}
-
-\foreach \n/\m in {0/1,2/3,4/5}{
-	\draw[m] (\n) -- (\m) node[label above]{1};
-}
-
-\foreach \n/\m in {1/2,3/4}{
-	\draw[] (\n) -- (\m) node[label above]{2};
-}
-
-\pgfmathsetmacro{\x}{6 * \sep}
-\node[draw=none] at(\x, 0){$\cdots$};
-
-\foreach \n in {7,...,8}{
-	\pgfmathsetmacro{\x}{\n * \sep}
-	\node(\n) at(\x,0){};
-}
-
-\draw[m] (7) -- (8) node[label above]{1};
-
-\end{tikzpicture}
-\caption[]{
-\label{fig:grd worst}
-GRD algorithm, worst case example: \\
-Consider a path with $2n + 1$ arcs,
-and alternating arc weights (2 and 1),
-if the GRD algorithm selects all the 1 weighted arcs,
-then no further improvement can be done and the value of the matching is $n + 1$,
-while the optimal matching has value of $2n$.
-}
-\end{figure}
-
-\bibliographystyle{plain}
-\bibliography{main}
-
-\end{document}

### 2017-02-09 src/group-sub.tex
fix outline

--- 2017-01-31 src/group.tex
@@
-We now consider a variant of the problem when, in addition to the
-capacity function $c:V \to \N$, and the weight (profit) function
-$w:A \to \R$, we also have a size function $s:V \to \N$, and the
-constraint $\din[M] \leq c(v)$ is replaced with the constraint
-$\sum_{(u,v)}s(u) \leq c(v)$.  The motivation for this variant of
-the problem is when we want to allow a group of people to travel
-together in the same car, thus $s$ is the size of the group.  We start
-by showing that this variant of the problem does not fit the
-submodular maximization formulation anymore. We show, however, that
-the problem still has a $(2 +\eps)$-approximation algorithm.  Finally,
-we argue that the local search algorithm can be trivially generalized
-to handle the new variant of the problem while keeping the same
-approximation guarantees.
-
-%%%%%
-
-\subsection{Submodular Maximization}
-
 Consider the submodular maximization formulation given in Section~\ref{sec:sub}.
@@
 \end{figure}
-
-%%%%%
-
-\subsection{A $(\frac{1}{2} - \varepsilon)$-approximation Algorithm}
-
-\todo[inline]{write a theorem and a proof}
-
-We now argue that this algorithm can be generalized to solve the group carpool
-matching problem.
-The main concern when trying to adopt the algorithm to the group carpool
-matching is how to determine if a vertex can be improved.
-Observe that Remark~\ref{rem:improve} does not hold anymore.
-If the maximum possible capacity is bounded, one can test for improvement of
-$v$ by considering all the subsets of edges intersecting $v$. 
-When the capacity is unbounded, however, it is easy to see that efficient
-way to test improvement implies a solution to the Knapsack problem.
-Indeed, if this is the case, one can test for improvement by using a known FPTAS
-for Knapsack, this is in the cost of additional $\varepsilon$ reduction in the
-approximation ratio of the algorithm.
-
-%%%%%
-
-\subsection{A $(\frac{2\cmax}{\cmax+1} + \eps)$-approximation Algorithm}
-
-\todo[inline]{complete}
-
-We now argue that the local sear

### 2017-02-09 src/group.tex
rm todos
fix outline

--- 2016-12-19 src/group.tex
@@
-We now consider a variant of the problem when, in addition to the capacity
-function $c:V \to \N$, and the weight (profit) function $w:A \to \R$, we also
-have a size function $s:A \to \N$, and the constraint $\din[M] \leq c(v)$
-is replaced with the constraint $\sum_{(u,v)}s(u,v) \leq c(v)$.
-The motivation for this variant of the problem is when we want to allow a group
-of people to travel together in the same car, thus $s$ is the size of the group.
-
-We start by showing that this variant of the problem does not
-fit the submodular maximization formulation anymore.
-We show, however, that the problem still has a 
-$\frac{1}{2} - \varepsilon$-approximation algorithm.
-Finally, we argue that the local search algorithm can be trivially generalized
-to handle the new variant of the problem while keeping the same approximation
-guarantees.
-
-To see why the group carpool problem can not be treated as a
-submodular maximization problem considered the instance given in
-Figure~\ref{fig:not submodular}.
-
-\begin{figure}
-\caption{
-\label{fig:not submodular}
-Consider the following instance where node capacity are written inside nodes, 
-arcs are labeled with their size and all weights are equal to 1.
-It is easy to see that if $f(S)$ is the optimal solution where $S$ is the set of
-drivers, then $f(A) + f(B) = 2 \leq 3 = f(A \cup B) + f(A \cap B)$,
-thus, $f$ is not submodular. 
-}
-\begin{center}
-\input{fig-not-submodular}
-\end{center}
-\end{figure}
+We now consider a variant of the problem when, in addition to the
+capacity function $c:V \to \N$, and the weight (profit) function
+$w:A \to \R$, we also have a size function $s:V \to \N$, and the
+constraint $\din[M] \leq c(v)$ is replaced with the constraint
+$\sum_{(u,v)}s(u) \leq c(v)$.  The motivation for this variant of
+the problem is when we want to allow a group of people to travel
+together in the same car, thus $s$ is the size of the group.  We start
+by showing that this variant of the problem does not fit the
+submodular maximization formulation anymore. We show, however, that
+the problem still has a $(2 +\eps)$-approximation algorithm.  Finally,
+we argue that the local search algorithm can be trivially generalized
+to handle the new variant of the problem while keeping the same
+approximation guarantees.

### 2017-02-10 src/abstract.tex
merge dror

--- 2017-01-31 src/abstract.tex
@@
 Formally, given a directed graph $G = (V, A)$, a capacity function $c:
-V \rightarrow \N$, and a weight function $w : A \rightarrow \R $, a
+V \rightarrow \N$, and a weight function $w: A \rightarrow \R^+$, a
 feasible \emph{carpool matching} is a subset of arcs, $M \subseteq A$,
-such that every $v \in V$ satisfies:
+such that every $v \in V$ satisfies:%
 \begin{inparaenum}[(i)]
@@
 A vertex $v$ for which $\dout[M](v) = 1$ is a \emph{passenger}, and a
-vertex for which $\dout[M](v) = 0$ is a driver who has $\din[M](v)$
-passengers.  In the \carpool problem the goal is to find a matching
-$M$ of maximum total weight.
-
+vertex for which $\dout[M](v) = 0$ is a \emph{driver} who has
+$\din[M](v)$ passengers.  In the \carpool problem the goal is to find
+a matching $M$ of maximum total weight.
+%
 The problem arises when designing an online carpool service, such as
 Zimride~\cite{zimride}, which tries to connect between passengers and
-drivers based on (arbitrary) similarity function.  The problem is
-known to be NP-hard, even for uniform weights and infinite capacities.
-%without capacity constraints.
+drivers based on a similarity function.  The problem is known to be
+NP-hard, even for uniform weights and infinite capacities.
+%
+The \gcp problem, is an extension of the \carpool where each vertex
+represents an unsplittable group of passengers.  Formally, each vertex
+$u \in V$ has a size $s(u) \in \N$, and the constraint $\din(v) \leq
+c(v)$ is replaced with $\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
 
-The \gcp, is an extension of the \carpool where each vertex represents a
-(unsplittable) group of passengers.
-Each group might have a different size.  
-Formally, each vertex $u \in V$ has a size $s(u) \in \N$,
-and the constraint $\din(v) \leq c(v)$ is replaced with
-$\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
-
-We show that the \carpool can be formulated as an unconstrained
-submodular maximization problem, thus it admits a
-$\frac{1}{2}$-approximation algorithm.
-We show that the same formulation does not hold for the \gcp,
-nevertheless, we present a $\frac{1}{2} - \varepsilon$-approximation algorithm
-for the \gcp as well.
-For the unweighted variant of
-the problems when the maximum possible capacity, $C$, is fixed, we give
-a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm.
-We also show that the problem remains APX-hard even if $C \leq 3$.
+We show that \carpool can be formulated as an unconstrained submodular
+maximization problem, thus it admits a $\frac{1}{2}$-approximation
+algorithm.  We show that the same formulation does not work for \gcp,
+nevertheless, we present a $(\frac{1}{2} - \eps)$-approximation
+algorithm for \gcp.
+%
+For the unweighted variant of both problems when the maximum possible
+capacity, $\cmax \eqdf \max_{v \in V} c(v)$, is bounded by a constant,
+we provide a $(\half + \inv{2\cmax} - \eps)$-approximation algorithm.
+We also show that the problem remains APX-hard, even if $\cmax \leq
+3$.

### 2017-02-10 src/appendix.tex
merge dror

\section{Omitted Proof}

\begin{proof}[Proof of Theorem~\ref{thm:improve}]
Define the weight function $w'(e)
= \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}$, where
$w_{\max} \eqdf \max_{e \in A} w(v)$.
%
Let $M^*$ and $M'$ be an optimal carpool matchings with respect to $w$
and $w'$, resp.  We have that
\[
w'(M^*)
=    \sum_{e \in M^*} \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}
>    \sum_{e \in M^*} \paren{ \frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps} } - m
=    \frac{m}{2\eps w_{\max}} \cdot w(M^*) - m
~.
\]
Since $w(M^*) \geq w_{\max}$, we have that 
\[
w'(M^*)
>    \frac{m}{2\eps w_{\max}} \cdot (w(M^*) - 2\eps w_{\max})
\geq \frac{m}{2\eps w_{\max}} \cdot (1 - 2\eps) w(M^*)
~.
\]
By Theorem~\ref{thm:improve-bounded}, our local improvement algorithm computes a
$\half$-approximate carpool matching $M$ on $(G, c, w')$, and this
matching satisfies $w'(M) \geq w'(M')/2$.  Furthermore, since
$w'(M') \geq w'(M^*)$, it follows that $w'(M) \geq w'(M^*)/2$.
Therefore
\[
w(M)
\geq \frac{2\eps w_{\max}}{m} w'(M) 
\geq \frac{1}{2} \frac{2\eps w_{\max}}{m} w'(M^*)
>    \frac{1-2\eps}{2} w(M^*)
~,
\]
as required.
\end{proof}

### 2017-02-10 src/group-apx.tex
merge dror

@@
-We now argue that this algorithm can be generalized to solve the group carpool
-matching problem.
-The main concern when trying to adopt the algorithm to the group carpool
-matching is how to determine if a vertex can be improved.
-Observe that Remark~\ref{rem:improve} does not hold anymore.
-If the maximum possible capacity is bounded, one can test for improvement of
-$v$ by considering all the subsets of edges intersecting $v$. 
-When the capacity is unbounded, however, it is easy to see that efficient
-way to test improvement implies a solution to the Knapsack problem.
-Indeed, if this is the case, one can test for improvement by using a known FPTAS
-for Knapsack, this is in the cost of additional $\varepsilon$ reduction in the
-approximation ratio of the algorithm.
+We now argue that the local improvement algorithm from
+Section~\ref{sec:improve} can be generalized to solve \gcp.
+%
+The main concern when trying to adopt the algorithm to \gcp is how to
+determine if a vertex can be improved.
+%
+With \carpool, if weights are polynomially-bounded, it was enough to
+consider in the incoming arcs to a vertex $v$ in a non-increasing
+order of $\delta_M$ (See proof of Theorem~\ref{thm:improve-bounded}).
+This does not work anymore, since \gcp we have sizes.  In fact, given
+$v$, finding the best star with respect to $\delta_M$ is
+a \textsc{Knapsack} instance where the size of the knapsack is $c(v)$.
+%
+If weights are polynomially-bounded, then $\delta_M(e)$ is bounded for
+every arc $e \in A$, and therefore this instance of \textsc{Knapsack}
+can be solved in polynomial time using dynamic programming.
+
+\begin{theorem}
+Algorithm~\ref{alg:grd} is a $\half$-approximation algorithm for \gcp,
+if edge weights are integral and polynomially bounded.
+\end{theorem}
+
+Using stadard scaling and rounding we obtain the following result.
+
+\begin{theorem}
+There exists a $(\half-\eps)$-approximation algorithm for \gcp,
+for every $\eps \in (0,\half)$.
+\end{theorem}

### 2017-02-10 src/group-sub.tex
merge dror

@@
-Consider the submodular maximization formulation given in Section~\ref{sec:sub}.
-Figure~\ref{fig:not submodular} shows that the function $w : 2^V \to \R$ is not
-submodular anymore.
+Consider the submodular maximization formulation given in
+Section~\ref{sec:sub}, namely $\barw: 2^V \to \R$, where
+$\barw(S) \eqdf w(M(S))$ and $M(S)$ is the maximum weight carpool
+matching that satisfies $D_{M(S)} \subseteq S \subseteq V \setminus
+P_{M(S)}$.
+%
+Figure~\ref{fig:not submodular} contains an instance that shows that
+the function $\barw$ is not submodular anymore.
 
@@
 written inside nodes, arcs are labeled with their size and all weights
-are equal to 1.  It is easy to see that if $f(S)$ is the optimal
-solution where $S$ is the set of drivers, then $f(A) + f(B) = 2 \leq 3
-= f(A \cup B) + f(A \cap B)$, thus, $f$ is not submodular.}
+are equal to 1.  We have that $f(A) + f(B) = 2 < 3 = f(A \cup B) +
+f(A \cap B)$.}
 \label{fig:not submodular}

### 2017-02-10 src/group.tex
merge dror

@@
-We now consider a variant of the problem when, in addition to the
-capacity function $c:V \to \N$, and the weight (profit) function
-$w:A \to \R$, we also have a size function $s:V \to \N$, and the
-constraint $\din[M] \leq c(v)$ is replaced with the constraint
-$\sum_{(u,v)}s(u) \leq c(v)$.  The motivation for this variant of
-the problem is when we want to allow a group of people to travel
-together in the same car, thus $s$ is the size of the group.  We start
-by showing that this variant of the problem does not fit the
+We now consider \gcp which a variant of \carpool in which in addition
+to the capacity function $c:V \to \N$, and the weight function
+$w:A \to \R^+$, we also have a size function $s:V \to \N$, and the
+constraint $\din[M](v) \leq c(v)$ is replaced with the constraint
+$\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
+%
+%The motivation for this variant of the problem is when we want to
+%allow a group of people to travel together in the same car, thus $s$
+%is the size of the group.
+%
+We start by showing that this variant of the problem does not fit the
 submodular maximization formulation anymore.  We show, however, that
-the problem still has a $(2 +\eps)$-approximation algorithm.  Finally,
-we argue that the local search algorithm can be trivially generalized
-to handle the new variant of the problem while keeping the same
-approximation guarantees.
+the problem still has a $(\half -\eps)$-approximation algorithm by
+extending the local improvement algorithm from
+Section~\ref{sec:improve}.
+%
+Finally, we show that the local search algorithm from
+Section~\ref{sec:local} can be generalized to handle \gcp while
+keeping the same approximation guarantees.

### 2017-02-10 src/improve.tex
merge dror

--- 2017-01-31 src/local_search.tex
@@
-In this subsection we give a local search $(2+\eps)$-approximation
-algorithm for \carpool.
+In this subsection we give a local improvement
+$(\half-\eps)$-approximation algorithm for \carpool.  This algorithm
+repeatedly checks whether the current carpool matching $M$ can be
+improved by means of a star centered at a vertex $v$.  The profit from
+this star is the total weight of the arcs in the star, and the cost is
+the total weight of lost arcs (e.g., arcs from passengers to drivers
+that became passengers of $v$).  If the profit is larger than the
+cost, then an improvement step is performed.  The algorithm terminates
+when such a step is not possible.
+%
+We remind the reader that this algorithm will be extended to \gcp in
+Section~\ref{sec:group}.
 
 We need a few definitions before presenting our algorithm.
+%
+Given a directed graphs $G = (V,A)$, define $\nin[] \eqdf \set{u :
+(u,v) \in A}$ and $\nout[] \eqdf \set{u : (v,u) \in A}$.
 %
@@
 \[
-w_M(v) \eqdf \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u)
+\textstyle
+w_M(v)
+\eqdf w(M \cap \nin[]) + w(M \cap \nout[])
+=     \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u)
 ~.
@@
 \label{lm:val-twice}
-$\sum_{v \in V} w_M(v) = 2 \sum_{e \in M} w(e)$.
+$w_M(V) = 2 w(M)$.
+%\sum_{v \in V} w_M(v) = 2 \sum_{e \in M} w(e)$.
 \end{observation}
@@
 
-Given an arc $(u,v)$, let $\inc(u,v)$ be the set of arcs that incident
-$(u, v)$, namely
-\[
-\inc(u,v) = (N^-(u) \times \{u\}) \cup (\{v\} \times N^+(v))
-~.
-\]
+Given an arc $(u,v) \in A$, let $\inc(u,v)$ be the set of arcs that
+incident $(u, v)$, namely define
+\(
+\inc(u,v) \eqdf (\nin[](u) \times \{u\}) \cup (\{v\} \times \nout[](v))
+%~.
+\).
 If $S$ is a set of arcs, then $\inc(S) \eqdf \bigcup_{(u,v) \in
@@
 
-We are now ready to describe our local search algorithm
-(Algorithm~\ref{alg:grd}).  The algorithm starts with an empty
-carpool matching $M$, and in every iteration it looks for a vertex
-that can be improved.  If there exists such a vertex, then the
-algorithm removes the arcs that are incident on it from $M$, and adds
-the arcs that improve the vertex.  The algorithm terminates when no
-vertex can be improved.  Figure~\ref{fig:improvement} depicts an
-improvement step.
+We are now ready to describe our local improvement algorithm
+(Algorithm~\ref{alg:grd}).  The algorithm starts with an empty carpool
+matching $M$, and in every iteration it looks for a vertex that can be
+improved.  If there exists such a vertex $v$, then the algorithm
+removes the arcs that are incident on it from $M$, and adds the arcs
+in $S_v$.  The algorithm terminates when no vertex can be improved.
+Figure~\ref{fig:improvement} depicts an improvement step.
 
 \begin{algorithm}
-\caption{
+\caption{Local Improvement}
 \label{alg:grd}
-Local Search
-}
 $M \gets \emptyset$ \\
@@
 	\For{$v \in V$}{
-		\If{$\exists$~improvment~$S_v$}{
+		\If{there exists an improvement $S_v$}{
 			$M \leftarrow M \setminus \inc(S_v) \cup S_v$	\\
@@
 
-For a vertex $v$ and a set $S$ of edges entering $v$, let $N^-_S(v)
+For a vertex $v$ and a set $S$ of edges entering $v$, let $\nin[S](v)
 = \set{u : (u,v) \in S}$ be the set in-neighbors corresponding to $S$.
@@
 \label{lm:no improve}
-Let $M$ be a matching computed by the local search algorithm.  Let $v$
-be a vertex with no improvement, and let $S \subseteq N^-(v)$, such
-that $\abs{S} \leq c(v)$, then $w(S) \leq w_M(v) + w_M(N^-_S(v))$.
+Let $M$ be a matching computed by the local improvement algorithm.
+Let $v$ be a vertex with no improvement, and let
+$S \subseteq \nin(v)$, such that $\abs{S} \leq c(v)$, then $w(S) \leq
+w_M(v) + w_M(\nin[S](v))$.
 \end{lemma}
 \begin{proof}
-If no improvement exists, then
-\[
-w(S) - w_M(N^-_S(v))
+If no improvement exists, then we have that \\
+\(
+w(S) - w_M(\nin[S](v))
 =    \sum_{(u,v) \in S} (w(u,v) - w_M(u))
@@
 ~.
-\]
+\)
 \end{proof}
@@
 If Algorithm~\ref{alg:grd} terminates, then the computed solution is a
-$2$-approximation.
+$\half$-approximation.
 \end{lemma}
@@
 M^*$.  By lemma~\ref{lm:no improve} we know that $w(S) \leq w_M(v) +
-w_M(N^-_S(v))$, thus we can pay for $S$, using the money on $v$ and on
-$N^-_S(v)$.  Clearly, these vertices will not be charged again.
+w_M(\nin[S](v))$, thus we can pay for $S$, using the money on $v$ and
+on $N^-_S(v)$.  Clearly, these vertices will not be charged again.
 \end{proof}
@@
 \input{fig-2-tight}
-\caption[]{
+\caption[]{%
+Consider a path with $2n + 1$ arcs, and alternating arc weights (2 and
+1), if the local improvement algorithm selects all arcs of weight 1,
+then no further improvement can be done and the value of the matching
+is $n + 1$, while the optimal matching has value of $2n$.}
 \label{fig:grd worst}
-GRD algorithm, worst case example: \\
-Consider a path with $2n + 1$ arcs,
-and alternating arc weights (2 and 1),
-if the GRD algorithm selects all the 1 weighted arcs,
-then no further improvement can be done and the value of the matching is $n + 1$,
-while the optimal matching has value of $2n$.
-}
 \end{figure}
@@
 \begin{theorem}
-\label{thm:ls}
-Algorithm~\ref{alg:grd} is a $2$-approximation algorithm for \carpool,
-if edge weights are integral and polynomially bounded.
+\label{thm:improve-bounded}
+Algorithm~\ref{alg:grd} is a $\half$-approximation algorithm
+for \carpool, if edge weights are integral and polynomially bounded.
 \end{theorem}
@@
 done efficiently by considering the incoming arcs to $v$ in a
-non-increasing order of their $\delta$s, and only ones with positive
+non-increasing order of their $\delta_M$s, and only ones with positive
 values.  A vertex $v$ can be improved, then, if the $\delta$s of the
@@
 
-It remains to consider the general case, where weight are not
-polynomially bounded.  In this case one can use scaling and rounding
-to ensure a polynomial running time in the cost of a $(1+\eps)$ factor
-in the approximation ratio.
+It remains to consider the case, where weight are not polynomially
+bounded.  In this case one can use scaling and rounding to ensure a
+polynomial running time in the cost of a $(1+\eps)$ factor in the
+approximation ratio.
+%
+The proof of the next theorem is given in the appendix.
 
 \begin{theorem}
-There exists a $(2+\eps)$-approximation algorithm for \carpool, for
-every $\eps > 0$.
+\label{thm:improve}
+There exists a $(\half-\eps)$-approximation algorithm for \carpool,
+for every $\eps \in (0,\half)$.
 \end{theorem}
-\begin{proof}
-Let $\eps' = \eps/4$.
-%
-Define the weight function $w'(e)
-= \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{\eps'}}$.
-%
-Let $M^*$ and $M'$ be an optimal carpool matchings with respect to $w$
-and $w'$, resp.  We have that
-\[
-w'(M^*)
-=    \sum_{e \in M^*} \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{\eps'}}
->    \sum_{e \in M^*} \paren{ \frac{w(e)}{w_{\max}} \cdot \frac{m}{\eps'} } - m
-=    \frac{m}{\eps' w_{\max}} \cdot w(M^*) - m
-~.
-\]
-Since $w(M^*) \geq w_{\max}$, we have that 
-\[
-w'(M^*)
->    \frac{m}{\eps' w_{\max}} \cdot (w(M^*) - \eps' w_{\max})
-\geq \frac{m}{\eps' w_{\max}} \cdot (1-\eps') w(M^*)
-~.
-\]
-By Theorem~\ref{thm:ls}, our local search algorithm computes a
-$2$-approximate carpool matching $M$ on $(G, c, w')$, and this
-matching satisfies $w'(M) \geq w'(M')/2$.  Furthermore, since
-$w'(M') \geq w'(M^*)$, it follows that $w'(M) \geq w'(M^*)/2$.
-Therefore
-\[
-w(M)
-\geq \frac{\eps' w_{\max}}{m} w'(M) 
-\geq \frac{1}{2} \frac{\eps' w_{\max}}{m} w'(M^*)
->    \frac{1-\eps'}{2} w(M^*)
-\geq \frac{w(M^*)}{2+\eps}
-~.
-\]
-\end{proof}

### 2017-02-10 src/intro.tex
merge dror

@@
 
-In this paper we assume that potential passenger satisfactions are
-given as input and the goal is to compute an assignment of passengers
-to driver so as to maximize the global satisfaction.
+%In this paper
+We assume that potential passenger satisfactions are given as input
+and the goal is to compute an assignment of passengers to driver so as
+to maximize the global satisfaction.
 %
@@
 passengers each user can drive if she was selected as a driver.  A
-non-negative weight function $w : A \rightarrow \R^*+$ is used to model
+non-negative weight function $w : A \rightarrow \R^+$ is used to model
 the amount of satisfaction $w(u,v)$ that user $u$ gains when riding
@@
 \end{inparaenum}
-A feasible carpool matching $M$ partition of $V$ as follows:
+A feasible carpool matching $M$ partitions of $V$ as follows:
 \begin{align*}
@@
 %
-Figure~\ref{fig:carpool} is an example of the \carpool problem.
+Figure~\ref{fig:carpool} contains an example of a \carpool instance.
 %
@@
 (see also Kutiel~\cite{kutiel2016}.)
+%
+Kutiel~\cite{kutiel2016} presented a $\frac{1}{3}$-approximation
+algorithm for \carpool and a $\half$-approximation algorithm for the
+unweighted variant of \carpool.
 
@@
 
+Arkin et al.~\cite{arkin2004approximations} considered
+the \textsc{Maximum Capacitated Star Packing} problem.  In this
+problem the input consists of a complete undirected graph with
+non-negative edge weights and a capacity vector $c
+= \set{c_1,\ldots,c_p}$, where $\sum_{i=1}^p c_i = \abs{V} - p$.  The
+goal is to find a set of vertex-disjoint stars in $G$ of size
+$c_1,\ldots,c_p$ of maximum total weight.  Arkin et
+al.~\cite{arkin2004approximations} provided a local search algorithm
+whose approximation ratio is $\inv{3}$, and a matching-based
+$\half$-approximation algorithm for the case where edge weights
+satisfy the triangle inequality.
+
 Bar-Noy et al.~\cite{bar2015improved} considered the
@@
 
-Another related problem is \textsc{$k$-Set Packing}.  In this problem
-one is given a collection of weighted sets, each containing as most
-$k$ elements, and the goal is to find a maximum weight subcollection
-of disjoint sets.  Chandra and Halld\'orsson~\cite{chandra2001greedy}
+Another related problem is \textsc{$k$-Set Packing}, where one is
+given a collection of weighted sets, each containing as most $k$
+elements, and the goal is to find a maximum weight subcollection of
+disjoint sets.  Chandra and Halld\'orsson~\cite{chandra2001greedy}
 presented a $\frac{3}{2(k+1)}$-approximation algorithm for this
 problem.
-
-Consider a subset of
-nodes $U$ of size at most $k$.  Observe that each subset of nodes has
-an optimal internal assignment of passenger to drivers.  Let the
-weight of this assignment be the profit of $U$, denote $p(U)$.  If $k
-= O(1)$, then $p(U)$ can be computed for every $U$ of size at most $k$
-in polynomial time.  The outcome is a \textsc{Set Packing} instance.
-
-Arkin et al.~\cite{arkin2004approximations} considered other variants
-of capacitated star packing where a capacity vector is given as part
-of the input and capacities need to be assigned to vertices.
-
-Kutiel~\cite{kutiel2016} presented a $\frac{1}{3}$-approximation
-algorithm for the problem and $\frac{1}{2}$-approximation algorithm for the
-unweighted variant of the problem.
+%
+\carpool can be seen a special case of \textsc{$k$-Set Packing}
+with $k = \cmax + 1$.  Consider a subset of nodes $U$ of size at most
+$k$.  Observe that each subset of nodes has an optimal internal
+assignment of passenger to drivers.  Let the weight of this assignment
+be the profit of $U$, denote $p(U)$.  If $k = O(1)$, $p(U)$ can be
+computed for every $U$ of size at most $k$ in polynomial time.  The
+outcome is a \textsc{$k$-Set Packing} instance.  This leads to a
+$\frac{3}{2(\cmax+2)}$-approximation algorithm for the case where
+$\cmax = O(1)$.
 
@@
 %
-In Section~\ref{sec:sub} we show that the \carpool can be formulated
-as unconstrained submodular maximization problem, thus it has a
-$\frac{1}{2}$-approximation algorithm due
-to~\cite{BFNS15,buchbinder2016deterministic}.
+Sections~\ref{sec:approx} contains approximation algorithms
+for \carpool.  First, in Section~\ref{sec:sub} we show that
+the \carpool can be formulated as unconstrained submodular
+maximization problem, thus it has a $\frac{1}{2}$-approximation
+algorithm due to~\cite{BFNS15,buchbinder2016deterministic}.
+%
+We show a local improvement algorithm for \carpool%
+\footnote{We use the term \emph{local improvement} to differentiate
+this algorithm from the local search algorithm that is given in
+Section~\ref{sec:local}.}.
+%
+This algorithm repeatedly checks whether the current carpool matching
+can be improved by means of a star centered at a vertex, and it
+terminates when such a step is not possible.
+%
+The approximation ratio of this algorithm is $\half$ if weights are
+polynomially bounded, and its ratio is $\half-\eps$ in general.
 
+Section~\ref{sec:cmax} we consider \carpool with bounded maximum
+capacity.   Define $\cmax \eqdf \max_{v \in V} c(v)$.
+%
+In Section~\ref{sec:hardness} we show that \carpool is APX-hard even
+for undirected and unweighted instances with $\cmax \leq b$, for any
+$b \geq 3$.
+%
 In Section~\ref{sec:local} we consider the unweighted variant of the
-problem.  We provide a $(\frac{\cmax+1}{2\cmax} - \eps)$-approximation
-algorithm, for any $\eps>0$, where $\cmax \eqdf \max_{v \in V} c(v)$
-is the maximum capacity.  We also show that \carpool is APX-hard even
-if $\cmax \leq 3$.
-%
-In Section~\ref{sec:group} we consider \gcp.  
-We first show that the unconstrained submodular maximization formulation for
-the \carpool does not follow for the \gcp.
-We show, however, that this problem still admits
-a $(\frac{1}{2} -\varepsilon)$-approximation algorithm, and argue that the local
-search algorithm generalizes to \gcp as well.
+problem.  We provide a local search algorithm whose approximation
+ratio is $\half + \inv{2\cmax} - \eps$, for any $\eps>0$.
+
+\dror{Compare to [7]!}
+
+Finally, Section~\ref{sec:group} discusses \gcp.  We first show that
+the unconstrained submodular maximization formulation for the \carpool
+does not work for \gcp.  We show, however, that this problem still
+admits a $(\frac{1}{2} -\varepsilon)$-approximation algorithm by
+extending the local improvement algorithm.  In addition, we show that
+the local search algorithm generalizes to \gcp with the same
+approximation ratio.

### 2017-02-10 src/local.tex
fix
rm todos
merge dror

@@
-In this section we present a $(\frac{2c_{\max}}{c_{\max} + 1}
-+ \eps)$-approximation algoithm for unweighted \carpool whose running
+In this section we present a $(\half + \inv{2c_{\max}}
+- \eps)$-approximation algoithm for unweighted \carpool whose running
 time is polynomial if $c_{\max} = O(1)$.
@@
 
-\todo[inline]{fix running time paragraph}
+%\todo[inline]{fix running time paragraph}
 
@@
 
+Define $\deg_M(v) \eqdf \din[M](v) + \dout[M](v)$.  For a subset
+$U \subseteq V$ of vertices define $\deg_M(U) \eqdf \sum_{v \in
+U} \deg_M(u)$.
+
 \begin{lemma}
@@
 
+\dror{fix proof of next lemma}
+
 \begin{lemma}
@@
 split into two subtrees each with at most $\floor{2t/3}+2$ vertices
-(see, e.g., \cite{???}).  Moreover, if $t \geq 24$, each such subtree
+% (see, e.g., \cite{???}).  
+Moreover, if $t \geq 24$, each such subtree
 contains at most $\frac{3}{4}t$.  Hence, we can decompose $\calT$
@@
 \label{cor:local}
-There exists a $(\frac{2\cmax}{\cmax+1} +\eps)$-approximation
-algorithm for \carpool, for every $\eps>0$.
+There exists a $(\half + \inv{2\cmax} - \eps)$-approximation algorithm
+for \carpool, for every $\eps>0$.
 \end{corollary}
@@
 
-\todo[inline]{Add a proper theorem}
+\dror{make sure that example is aligned with the conditions of the
+previous lemma}
 
@@
 example in Figure~\ref{fig:local search tight}, the example is for the
-special case when $k=11$ and $C=2$ but this example can be generalized
-in a straightforward manner.  One can verify that as the graph in the
-example growth, the ratio between the optimal solution and the local
-search solution approaches $\frac{3}{4}$.
+special case when $k = 11$ and $\cmax = 2$ but this example can be
+generalized in a straightforward manner.  One can verify that as the
+graph in the example growth, the ratio between the optimal solution
+and the local search solution approaches $\frac{3}{4}$.
 
@@
 \input{fig-local-tight}
-\caption{A tight example for Theorem~\ref{theorem:local search}. 
+\caption{A tight example for Corollary~\ref{cor:local}. 
 The optimal solution is given by the red solid arcs while the local
@@
 \end{figure}
+
+\dror{Mention [7]}

### 2017-02-10 src/sub.tex
no errors
merge dror

@@
 unconstrained submodular maximization problem, and thus it has a
-randomized $\frac{1}{2}$-approximation algorithm based on~\cite{BFNS15}.
+$\frac{1}{2}$-approximation algorithm based on Buchbinder et
+al.~\cite{BFNS15,buchbinder2016deterministic}.
 
@@
 Given $S$, the carpool matching $M(S)$ can be computed in polynomial
-time using a maximum b-matching in the bipartite graph 
-$B = (S \cup V \setminus S, A \cap (V \setminus S) \times S)$ or can be reduced
-to a max-cost flow problem as shown in~\cite{kutiel2016}.
+time by computing a maximum $b$-matching in the bipartite graph $B =
+(S \cup V \setminus S, A \cap (V \setminus S) \times S)$ which can be
+done using an algorithm for \textsc{Minimum Cost Flow} as shown
+in~\cite{kutiel2016}.
 
 Consider the function $\barw: 2^V \to \R$, where $\barw(S) \eqdf
-w(M(S))$.  In the next lemma we prove that $\bar{w}$ is
-a \emph{submodular set function}.  Recall that a function $f$ is
-submodular if $f(S) + f(T) \geq f(S \cup T) + f(S \cap T)$ for every
-two sets $S$ and $T$ in the domain of $f$.
+w(M(S)) = \sum_{e \in M(S)} w(e)$.  Observe that $\barw(\emptyset)
+= \barw(V) = 0$, and that $\barw$ is not monotone.
+%
+In the next lemma we prove that $\bar{w}$ is a \emph{submodular set
+function}.  Recall that a function $f$ is submodular if $f(S) +
+f(T) \geq f(S \cup T) + f(S \cap T)$ for every two sets $S$ and $T$ in
+the domain of $f$.
 
@@
 
-Buchbinder et al.~\cite{BFNS15,buchbinder2016deterministic} presented a
-general randomized $2$-approximation algorithm for unconstrained submodular maximization.
+Buchbinder et al.~\cite{BFNS15,buchbinder2016deterministic} presented
+a general randomized $\half$-approximation algorithm for unconstrained
+submodular maximization.
 
 \begin{theorem}
-There exists a polynomial time $2$-approximation algorithm for \carpool.
+There exists a polynomial time $\half$-approximation algorithm
+for \carpool.
 \end{theorem}
@@
 \caption[]{
-\label{fig:defs}
 We show that the arcs from \subref{sub:cup} and \subref{sub:cap} can be

### 2017-02-12 src/group-apx.tex
pass

@@
 With \carpool, if weights are polynomially-bounded, it was enough to
-consider in the incoming arcs to a vertex $v$ in a non-increasing
+consider the incoming arcs to a vertex $v$ in a non-increasing
 order of $\delta_M$ (See proof of Theorem~\ref{thm:improve-bounded}).
-This does not work anymore, since \gcp we have sizes.  In fact, given
+This does not work anymore, since in the \gcp we have sizes.  In fact, given
 $v$, finding the best star with respect to $\delta_M$ is

### 2017-02-12 src/intro.tex
pass

@@
-As traveling costs become higher and parking becomes sparse is it only
+As traveling costs become higher and parking becomes sparse it is only
 natural to share rides or to \emph{carpool}.  Originally, carpooling
@@
 \end{inparaenum}
-A feasible carpool matching $M$ partitions of $V$ as follows:
+A feasible carpool matching $M$ partitions $V$ as follows:
 \begin{align*}
@@
 matching induces an optimal dominating set and vice versa.
-Since \textsc{Minimum Dominating Set} is NP-hard, if follows
+Since \textsc{Minimum Dominating Set} is NP-hard, it follows
 that \carpool is NP-hard even if the instance is undirected,
@@
 gave an exact optimization algorithm for weighted trees, and used it
-on a minimum spanning tree of the input graph to obtain a
+on a maximum spanning tree of the input graph to obtain a
 $\frac{1}{2}$-approximation algorithm for weighted graphs.  They also
@@
 %
-Chen et al.~\cite{CENRRS13} improved the approximation ratios from
-$\frac{3}{5}$ and $\inv{2}$ to $0.71$ and $0.64$, resp.  They also
-showed that the problem can not be approximated to within a factor of
+Chen et al.~\cite{CENRRS13} improved the approximation ratio for unweighted
+graphs from $\frac{3}{5}$ to $0.71$ and and gave a $0.64$-approximation
+algorithm for node weighted graphs.
+They also showed that the problem can not be approximated to within a factor of
 $\frac{31}{32} + \eps$, for any $\eps > 0$ assuming that
@@
 when such changes are no longer possible.  Athanassopoulos et
-al.~\cite{ACKK09} showed that such algorithms do not provide better
-than $(\inv{2} + \frac{1}{2(k+2)})$-approximate spanning star forests.
+al.~\cite{ACKK09} showed that for any $k$ and $\varepsilon$ there exists an
+instance $G$ and a local optima $M$ such that 
+$\frac{|M|}{|OPT|} \leq \inv(2) + \varepsilon$, where $|OPT|$ is the number of
+edges in an optimal spanning star forest \footnote{Note that this lower bound
+does not contradict our result regarding approximation ratio of our local
+search algorithm where the maximum possible capacity is constant.}.
 
@@
 
-Another related problem is \textsc{$k$-Set Packing}, where one is
+Another related problem is the \textsc{$k$-Set Packing}, where one is
 given a collection of weighted sets, each containing as most $k$
@@
 %
-\carpool can be seen a special case of \textsc{$k$-Set Packing}
+\carpool can be seen as a special case of \textsc{$k$-Set Packing}
 with $k = \cmax + 1$.  Consider a subset of nodes $U$ of size at most
@@
 %
-Sections~\ref{sec:approx} contains approximation algorithms
+In Sections~\ref{sec:approx} contains approximation algorithms
 for \carpool.  First, in Section~\ref{sec:sub} we show that
@@
 
-Finally, Section~\ref{sec:group} discusses \gcp.  We first show that
+Finally, Section~\ref{sec:group} discusses the \gcp.  We first show that
 the unconstrained submodular maximization formulation for the \carpool

### 2017-02-12 src/sub.tex
pass

@@
 Buchbinder et al.~\cite{BFNS15,buchbinder2016deterministic} presented
-a general randomized $\half$-approximation algorithm for unconstrained
-submodular maximization.
+a general $\half$-approximation algorithm for unconstrained
+submodular maximization, thus we have the following theorem.
 

### 2017-02-13 src/intro.tex
merge dror

@@
 \begin{align*}
-P_M & \eqdf \set{v : \dout[M](v) = 1} \\
-D_M & \eqdf \set{v : \din[M](v) \geq 1} \\
+P_M & \eqdf \set{v : \dout[M](v) = 1} &
+D_M & \eqdf \set{v : \din[M](v) \geq 1} &
 Z_M & \eqdf \set{v : \dout[M](v) = \din[M](c) = 0}
-~.
+%~.
 \end{align*}
@@
 forest.  Notice that this problem is equivalent to \carpool on
-undirected and uncapacitated instances.
+undirected and uncapacitated instances.  We also note that if all
+weights leaving a node are the same, then the instance is referred to
+as node-weighted.
 %
@@
 $\frac{1}{2}$-approximation algorithm for weighted graphs.  They also
-shows that it is NP-hard to approximate problem \textsc{Spanning Star
-Forest} within a ratio of $\frac{259}{260}+\eps$, for any $\eps>0$.
+shows that it is NP-hard to approximate unweighted \textsc{Spanning
+Star Forest} within a ratio of $\frac{259}{260}+\eps$, for any
+$\eps>0$.
 %
@@
 %
-Chen et al.~\cite{CENRRS13} improved the approximation ratio for unweighted
-graphs from $\frac{3}{5}$ to $0.71$ and and gave a $0.64$-approximation
-algorithm for node weighted graphs.
-They also showed that the problem can not be approximated to within a factor of
-$\frac{31}{32} + \eps$, for any $\eps > 0$ assuming that
+Chen et al.~\cite{CENRRS13} improved the approximation ratio for
+unweighted graphs from $\frac{3}{5}$ to $0.71$ and gave a
+$0.64$-approximation algorithm for node weighted graphs.  They also
+showed that the edge- and node-weighted problem cannot be approximated
+to within a factor of $\frac{19}{20} + \eps$, and $\frac{31}{32}
++ \eps$, resp., for any $\eps > 0$, assuming that
 $\text{P} \neq \text{NP}$.
 %
-Chakrabarty and Goel~\cite{ChakrabartyGoel10} improved the lower bound
-to $\frac{10}{11} + \eps$.
+Chakrabarty and Goel~\cite{ChakrabartyGoel10} improved the lower bounds
+to $\frac{10}{11} + \eps$ and $\frac{13}{14}$.
 
@@
 leave is adjacent to at least one center.  The algorithm terminates
-when such changes are no longer possible.  Athanassopoulos et
-al.~\cite{ACKK09} showed that for any $k$ and $\varepsilon$ there exists an
-instance $G$ and a local optima $M$ such that 
-$\frac{|M|}{|OPT|} \leq \inv(2) + \varepsilon$, where $|OPT|$ is the number of
-edges in an optimal spanning star forest \footnote{Note that this lower bound
-does not contradict our result regarding approximation ratio of our local
-search algorithm where the maximum possible capacity is constant.}.
+when such changes are no longer possible.
+%
+Athanassopoulos et al.~\cite{ACKK09} showed that, for any $k$ and
+$\eps \in (0,\inv{2(k+2)}]$, there exists an instance $G$ and a local
+optima whose size is smaller than $(\half + \eps) \textsc{opt}$,
+where \textsc{opt} is the size of the optimal spanning star forest.
+We note that the construction of the above result requires that the
+maximum degree of $G$ is at least $2(k+2)$.  Hence, in graphs with
+maximum degree $\Delta$, the above ratio becomes $\half
++ \inv{\Delta}$.
 
@@
 problem.  We provide a local search algorithm whose approximation
-ratio is $\half + \inv{2\cmax} - \eps$, for any $\eps>0$.
-
-\dror{Compare to [7]!}
+ratio is $\half + \inv{2\cmax} - \eps$, for any $\eps>0$.  Given a
+parameter $K$, our algorithm starts with the empty carpool matching.
+Then, it repeatedly tries to find a better matching by replacing
+$t \leq k$ arc in the current solution by $t+1$ arcs that are not in
+the solution.
+%
+We show that our analysis is tight.  We also note that our algorithm
+is a special case of the local search family that was defined
+in~\cite{ACKK09} with a parameter of $2k$.  On undirected and
+uncapaciated instances we have that $\cmax = \Delta$, where $\Delta$
+is the maximum degree, hence the approximation ratio of our algorithm
+is $\half + \inv{2\Delta} - \eps$ which is tight with respect
+to~\cite{ACKK09}.
 

### 2017-02-13 src/local.tex
pass
merge dror

@@
 of a star, i.e., if $v$ is the center $S$, then $V(S) = \{v\} \cup
-P_M(v)$.  Also, for $\calT \subseteq \calS(M)$, define
-$V(\calT) \eqdf \bigcup_{S \in \calT} V(S)$.  Also, let $A(S)$ be the
-edges of $S$, and define $A(\calT) \eqdf \bigcup_{S \in \calT} A(S)$.
+P_M(v)$.  Also, let $A(S)$ be the arcs of $S$.  For
+$\calT \subseteq \calS(M)$, define
+$V(\calT) \eqdf \bigcup_{S \in \calT} V(S)$ and
+$A(\calT) \eqdf \bigcup_{S \in \calT} A(S)$.
 
@@
 
+\begin{lemma}
+The maximum degree of $H$ is $\cmax(\cmax+1)$.
+\end{lemma}
+\begin{proof}
+Each star in $\calS(M^*)$ consists of at most $\cmax+1$ vertices and
+each such vertex can belong to a star in $\calS(M)$ containing
+additional $\cmax$ vertices, each of which is located in a different
+star in $\calS(M^*)$.
+\end{proof}
+
 Define $\deg_M(v) \eqdf \din[M](v) + \dout[M](v)$.  For a subset
@@
 \label{lemma:r}
-Let $\calT \subseteq \calS(M^*)$ that induces a connect subgraph of
+Let $\calT \subseteq \calS(M^*)$ that induces a connected subgraph of
 $H$.  If $\abs{A(\calT)} \leq k$, then
@@
 \geq \half + \frac{\abs{\calT} - 1}{2\cmax \abs{\calT}}
+=    \half + \inv{2\cmax} - \inv{2\cmax \abs{\calT}}
 ~,
@@
 
-\dror{fix proof of next lemma}
+\begin{lemma}
+\label{lemma:dec}
+Let $G = (V,E)$ be an undirected connected graph with maximum degree
+$\Delta$, and let $\ell < \abs{V}/\Delta$.  Then $G$ can be decomposed
+into connected components of size at least $\ell$, and at most
+$\Delta \ell$.
+\end{lemma}
+\begin{proof}
+Let $T$ be any spanning tree of $G$ and let $r$ be an arbitrary root.
+Starting with $r$, repeatedly choose a child whose subtree is strictly
+larger than $\frac{\Delta-1}{\Delta} \abs{V}$, until this is not
+possible.  Hence, we have reached a vertex $v$ whose subtree contains
+more than $\frac{\Delta-1}{\Delta} \abs{V}$ vertices, but the subtrees
+of its children contain at most $\frac{\Delta-1}{\Delta} \abs{V}$
+vertices.
+%
+If $v = r$, then $v$ has a child $u$ with at least $\inv{\Delta}
+(\abs{V}-1) \geq \ell$ vertices.  Otherwise, there exists a child $u$
+of $v$ whose subtree is of size at least
+$\inv{\Delta} \abs{V} \geq \ell$.  Disconnect $u$ and the vertices in
+its subtree from the graph.
+%
+In both cases $u$'s subtree contains at most
+$\frac{\Delta-1}{\Delta} \abs{V}$ vertices, and thus at least
+$\inv{\Delta} \abs{V} \geq \ell$ vertices remain in the graph.  Hence
+we obtain two connected subgraphs of size at least $\ell$.
+%
+We repeat this procedure recursively on any component of size
+strictly larger $\Delta\ell$.
+\end{proof}
+
+\iffalse %%%%% Removed
 
 \begin{lemma}
-If $k \geq 24\cmax$, then $\abs{M} \geq (\frac{\cmax+1}{2\cmax}
-- \frac{2}{k}) \cdot \abs{M^*}$.
-\end{lemma}
-\begin{proof}
-Consider a maximal (with respect to set inclusion) connected component
-of $H$ induced by the vertices in $\calT \subseteq \calS(M^*)$.
-%
-If $\abs{M \cap A(\calT)} \leq k$, then it must be that $\abs{M \cap
-A(\calT)} = \abs{M^* \cap A(\calT)}$, since otherwise $M \cap
-A(\calT)$ could be improved.
-
-It remains to consider a maximal component $\calT$ such that If
-$\abs{M \cap A(\calT)} > k$.  Observe that since the number of edges
-in a $S \in \calS(M^*)$ is at most $\cmax$, it must be that
-$\abs{V(\calT)} > \frac{k}{\cmax}$.
-%
-Given such a component $\calT$, we partition its vertex set into
-several sets, each of size at least $\frac{k}{4\cmax}$.  We do this as
-follows.  First construct any spanning tree of $\calT$ (say, by
-running DFS).  It is well known that a tree of $t$ vertices can be
-split into two subtrees each with at most $\floor{2t/3}+2$ vertices
-% (see, e.g., \cite{???}).  
-Moreover, if $t \geq 24$, each such subtree
-contains at most $\frac{3}{4}t$.  Hence, we can decompose $\calT$
-recursively into vertex sets whose sizes is between $\frac{k}{\cmax}$
-and $\frac{k}{4\cmax}$, assuming that $\frac{k}{\cmax} \geq 24$.
-%
-Each such vertex set $\calX$ is connected and contains at most
-$\frac{k}{\cmax}$ stars.  Hence $\abs{A(\calX)} \leq k$.  Due to
-Lemma~\ref{lemma:r} and since $\abs{V(\calX)} \geq \frac{k}{4\cmax}$,
-we have that
-\[
-\frac{\deg_M(V(\calX))}{\deg_{M^*}(V(\calX))} 
-\geq \half + \inv{2\cmax} - \frac{2}{k}
-~.
-\]
-Since $\deg_{M^*}(V(\calT)) = \sum_{\calX} \deg_{M^*}(V(\calX))$ and
-$\deg_M(V(\calT)) = \sum_{\calX} \deg_M(V(\calX))$, it follows that
-\[
-\frac{\deg_M(V(\calT))}{\deg_{M^*}(V(\calT))}
-\geq \half + \inv{2\cmax} - \frac{2}{k}
-~,
-\]
-and thus $\abs{M \cap A(\calT)} \geq (\frac{\cmax + 1}{2\cmax}
-- \frac{2}{k}) \abs{M^* \cap A(\calT)}$.
-\end{proof}
-
-\begin{corollary}
-\label{cor:local}
-There exists a $(\half + \inv{2\cmax} - \eps)$-approximation algorithm
-for \carpool, for every $\eps>0$.
-\end{corollary}
-
-\iffalse %%%%% Rmeoved
-
-\begin{lemma}
-\label{lemma:dec}
-Given a parameter $k$, a bounded degree connected graph $G$, with a
-maximum degree $d$ can be decomposed into connected components of size
-at least $k$, and at most $d(k-1) + 1$.
+%\label{lemma:dec}
+Given a parameter $k$, a connected graph $G$ with a maximum degree $d$
+can be decomposed into connected components of size at least $k$, and
+at most $d(k-1) + 1$.
 \end{lemma}
@@
 
-\begin{theorem}
-\label{theorem:local search}
-The local search is ($\frac{1}{2} + \frac{1}{2c}
-- \varepsilon$)-approximation algorithm.
-\end{theorem}
+\fi %%%%% End removed
 
+\begin{lemma}
+If $k \geq \cmax$, then $\abs{M} \geq (\half + \inv{2\cmax}
+- \frac{\cmax(\cmax+1)}{2k}) \cdot \abs{M^*}$.
+\end{lemma}
 \begin{proof}
-Combine lemma~\ref{lemma:dec}, and lemma~\ref{lemma:r}, and observe
-that the maximum degree in $G^{M^*}_M$ is $(C + 1)^C$ to get the
-desire result.
+Consider a maximal (with respect to set inclusion) connected component
+of $H$ induced by the vertices in $\calT \subseteq \calS(M^*)$.
+%
+If $\abs{M \cap A(\calT)} \leq k$, then it must be that $\abs{M \cap
+A(\calT)} = \abs{M^* \cap A(\calT)}$, since otherwise $M \cap
+A(\calT)$ could be improved.
+
+It remains to consider a maximal component $\calT$ such that If
+$\abs{M \cap A(\calT)} > k$.  Observe that since the number of edges
+in $S \in \calS(M^*)$ is at most $\cmax$, it must be that
+$\abs{V(\calT)} > \frac{k}{\cmax}$.
+%
+Due to Lemma~\ref{lemma:dec} (with $\ell = \frac{k}{\cmax}$) we can
+partition $\calT$ into connected components each of which contains
+between $\frac{k}{\cmax^2(\cmax+1)}$ and $\frac{k}{\cmax}$ vertices.
+%
+Since each such vertex set $\calX$ is connected and contains at most
+$\frac{k}{\cmax}$ stars, it follows that $\abs{A(\calX)} \leq k$.
+%
+Due to Lemma~\ref{lemma:r} we have that
+\[
+\frac{\deg_M(V(\calX))}{\deg_{M^*}(V(\calX))} 
+\geq \half + \inv{2\cmax} - \frac{\cmax(\cmax+1)}{2k}
+~.
+\]
+Since $\deg_{M^*}(V(\calT)) = \sum_{\calX} \deg_{M^*}(V(\calX))$ and
+$\deg_M(V(\calT)) = \sum_{\calX} \deg_M(V(\calX))$, it follows that
+\[
+\frac{\deg_M(V(\calT))}{\deg_{M^*}(V(\calT))}
+\geq \half + \inv{2\cmax} - \frac{\cmax(\cmax+1)}{2k}
+~,
+\]
+and thus
+\[
+\abs{M \cap A(\calT)}
+\geq \paren{ \half + \inv{2\cmax} -
+             \frac{\cmax(\cmax+1)}{2k}} \abs{M^* \cap A(\calT)}
+~,
+\]
+and the lemma follows.
 \end{proof}
 
-\fi %%%%% End removed
+By setting $k = \ceil{\cmax(\cmax+1)/2\eps}$, we get the following
+result.
 
-\dror{make sure that example is aligned with the conditions of the
-previous lemma}
+\begin{corollary}
+\label{cor:local}
+There exists a $(\half + \inv{2\cmax} - \eps)$-approximation algorithm
+for \carpool, for every $\eps>0$.
+\end{corollary}
 
@@
 \end{figure}
-
-\dror{Mention [7]}

### 2017-02-13 src/appendix.tex
fix figs

@@
 \section{Omitted Proof}
-
 \begin{proof}[Proof of Theorem~\ref{thm:improve}]
@@
 \end{proof}
+
+\section{Tight Analysis}
+We now show that Corollary~\ref{cor:local} is tight.  Consider the
+example in Figure~\ref{fig:local search tight}, the example is for the
+special case when $k = 11$ and $\cmax = 2$ but this example can be
+generalized in a straightforward manner.  One can verify that as the
+graph in the example growth, the ratio between the optimal solution
+and the local search solution approaches $\frac{3}{4}$.
+
+\begin{figure}
+\begin{center}
+\scalebox{.85}{\input{fig-local-tight}}
+\caption{A tight example for Corollary~\ref{cor:local}. 
+The optimal solution is given by the red solid arcs while the local
+search solution is given by the green, dashed arcs.  The solution can
+be improved by the local search algorithm only if it removes all the
+edges.}
+\label{fig:local search tight}
+\end{center}
+\end{figure}

### 2017-02-13 src/in/tikz.tex
Merge Dror
fix
fix figs

@@
 \usetikzlibrary{
-	arrows,
 	arrows.meta,
@@
 
+% NODE
+\tikzset{default node/.style={draw,circle,inner sep=0mm,minimum size=5mm,very thick,font=\small,black!70,}}
+
+% LABELS
+\tikzset{label/.style={draw=none,sloped,}}
+\tikzset{label above/.style={label,midway,above=-1mm,}}
+\tikzset{label below/.style={label,midway,below=-1mm,}}
+\tikzset{outline/.style={loosely dashed, ultra thin, lightgray}}
+\tikzset{m/.style={blue, dashed}}
+
 %DEFAULT STYLE
-\tikzset{default style/.style={
-	>=Stealth, 
+\tikzset{
+	>=Triangle[], 
 	on grid, 
@@
 	thick,
-}}
-
-% NODE
-\tikzset{default node/.style={
-	draw, 
-	circle,
-	inner sep=0mm,
-	minimum size=5mm,
-	very thick,
-	font=\small,
-	black!70,
-}}
-
-% LABELS
-\tikzset{label/.style={
-	draw=none,
-	sloped,
-}}
-
-\tikzset{label above/.style={
-	label,
-	midway,
-	above=-1mm,
-}}
-
-\tikzset{label below/.style={
-	label,
-	midway,
-	below=-1mm,
-}}
+}

### 2017-02-13 src/local.tex
fix figs

@@
 Formally $H = (\calS(M^*), E)$ where
-\[
-E = \set{(S^*_i, S^*_j) : \exists S \in \calS(M), 
+$
+{E = \set{(S^*_i, S^*_j) : \exists S \in \calS(M), 
          V(S) \cap V(S^*_i) \neq \emptyset \land
-         V(S) \cap V(S^*_j) \neq \emptyset}
-~.
-\]
+         V(S) \cap V(S^*_j) \neq \emptyset}}
+$.
 Figure~\ref{fig:conflict} depicts a star graph.
@@
 %
-\begin{subfigure}{.4\linewidth}
+\begin{subfigure}[t]{.4\linewidth}
 \caption{\label{subfloat:graph}}
@@
 %
-\begin{subfigure}{.4\linewidth}
+\begin{subfigure}[t]{.4\linewidth}
 \caption{\label{subfloat:conflict}}
@@
 and another solution depicted by the solid green edges.
+The optimal stars are outlined.  
 \subref{subfloat:conflict}
-The conflict graph, the upper left vertex corresponds 
-to the star that contains the vertices a,b,c.
+The star graph, each vertex corresponded to a star in the original graph. 
+The upper left vertex corresponds to the star that contains the vertices a,b,c.
 The numbers inside the vertices corresponds to $d_i$.   
@@
 
-We now show that Corollary~\ref{cor:local} is tight.  Consider the
-example in Figure~\ref{fig:local search tight}, the example is for the
-special case when $k = 11$ and $\cmax = 2$ but this example can be
-generalized in a straightforward manner.  One can verify that as the
-graph in the example growth, the ratio between the optimal solution
-and the local search solution approaches $\frac{3}{4}$.
-
-\begin{figure}
-\begin{center}
-\input{fig-local-tight}
-\caption{A tight example for Corollary~\ref{cor:local}. 
-The optimal solution is given by the red solid arcs while the local
-search solution is given by the green, dashed arcs.  The solution can
-be improved by the local search algorithm only if it removes all the
-edges.}
-\label{fig:local search tight}
-\end{center}
-\end{figure}
+In the appendix we show that our analysis is tight.

### 2017-02-14 src/local.tex
local

@@
 
-%\todo[inline]{fix running time paragraph}
-
 We claim that the local search algorithm halts in polynomial time.
@@
 a \emph{directed star} whose leaves are the passengers in the set
-$P_M(v) = \set{u : (u,v) \in M}$.  ($P_M(v) = \emptyset$, for $v \in
-Z_M$.)
+$P_M(v) = \set{u : (u,v) \in M}$
+($P_M(v) = \emptyset$, for $v \in Z_M$).
 %
@@
 stars that are induced by $M$.  Denote by $V(S)$ the set of vertices
-of a star, i.e., if $v$ is the center $S$, then $V(S) = \{v\} \cup
+of a star, i.e., if $v$ is the center of $S$, then $V(S) = \{v\} \cup
 P_M(v)$.  Also, let $A(S)$ be the arcs of $S$.  For
@@
 \begin{proof}
-Consider the solution $M'$ obtained from the $M$ by removing all the
+Consider the solution $M'$ obtained from $M$ by removing all the
 edges from $M$ that intersect $V(\calT)$ and adding all the edges from
@@
 Let $G = (V,E)$ be an undirected connected graph with maximum degree
-$\Delta$, and let $\ell < \abs{V}/\Delta$.  Then $G$ can be decomposed
-into connected components of size at least $\ell$, and at most
-$\Delta \ell$.
+$\Delta$, and let $\ell < \abs{V}$.  
+Then $G$ can be decomposed into connected components of size at least $\ell$,
+and at most $\Delta \ell$.
 \end{lemma}
+
 \begin{proof}
+We give a constructive proof.
+If $\ell \leq |V| \leq \Delta \ell$ we are done.
+%
+Otherwise, remove (in any desired way) up to $\ell$ connected vertices $C =
+\{v_1,\ldots,v_m\}$ from $G$ until $G$ is disconnected.
+If $m = \ell$ then let $C_1 = \{v_1,\ldots,v_\ell\}$ and recursively decompose
+$G - C$.
+If, on the other hand, the above process disconnects $G$ then consider the
+connected components $\{C_1, \ldots, C_t\}$ of $G - C$.
+Join all the small components and $C$, i.e. $C \cup \bigcup_{i : |C_i| < \ell}$
+and decompose the other components recursively, 
+noting that $|C \cup \bigcup_{i : |C_i| < \ell}| \leq \Delta \ell$.
+If all the components are large, i.e. $\forall i |C_i| \geq \ell$ then join $C$
+to an arbitrary component and decompose the resulting components recursively.
+
+\iffalse
 Let $T$ be any spanning tree of $G$ and let $r$ be an arbitrary root.
@@
 strictly larger $\Delta\ell$.
+\fi
 \end{proof}

### 2017-02-15 src/abstract.tex
merge dror

@@
 algorithm.  We show that the same formulation does not work for \gcp,
-nevertheless, we present a $(\frac{1}{2} - \eps)$-approximation
-algorithm for \gcp.
+nevertheless, we present a local search $(\frac{1}{2}
+- \eps)$-approximation algorithm for \gcp.
 %
 For the unweighted variant of both problems when the maximum possible
-capacity, $\cmax \eqdf \max_{v \in V} c(v)$, is bounded by a constant,
-we provide a $(\half + \inv{2\cmax} - \eps)$-approximation algorithm.
-We also show that the problem remains APX-hard, even if $\cmax \leq
-3$.
+capacity, $\cmax$, is bounded by a constant, we provide a local search
+$(\half + \inv{2\cmax} - \eps)$-approximation algorithm.  We also show
+that the problem APX-hard, even if $\cmax \leq 3$.

### 2017-02-15 src/appendix.tex
merge dror

@@
-\section{Omitted Proof}
+\section{Omitted Proofs}
+\label{sec:omitted}
+
 \begin{proof}[Proof of Theorem~\ref{thm:improve}]
@@
 
+\medskip
+
+\begin{proof}[Proof of Lemma~\ref{lemma:dec}]
+We give a constructive proof.
+%
+First, if $\ell \leq |V| \leq \Delta \ell$, then we are done.
+%
+Otherwise, we partition the graph recursively as follows.  Let $U
+= \emptyset$.  As long as $\abs{U} < \ell$, choose an arbitrary vertex
+$u$ such that $U \cup \set{u}$ is connected and add $u$ to $U$.
+%
+If the graph $G[V \setminus U]$, which is induced by $V \setminus U$,
+is connected, then choose the next vertex.
+%
+However, if $G[V \setminus U]$ becomes disconnected, then consider the
+maximal connected components of $G[V \setminus U]$.  Add the vertices
+of any maximal component that contains less than $\ell$ vertices to
+$U$.  Observe that afterwards $\abs{U} < \ell + (\Delta-1) \ell
+= \Delta \ell$.
+%
+If $\abs{U} \geq \ell$, then recursively partition any component of
+$G[V \setminus U]$ that contains more than $\ell$ vertices.
+%
+If $\abs{U} < \ell$, then there must exist at least one maximal
+component $C$ of $G[V \setminus U]$ that contains more than $\ell$
+vertices.  In this case recursively partition any maximal component of
+$G[V \setminus (U \cup C)]$ that contains more than $\ell$ vertices.
+Also, continue to augment $U$ in the graph $G[U \cup C]$.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+
+\section{Figures}
+\label{sec:figures}
+
+\begin{figure}[h]
+\centering
+\input{fig-submodular}
+\caption[]{%
+We show that the arcs from \subref{sub:cup} and \subref{sub:cap} can be
+redistributed over \subref{sub:s} and \subref{sub:s} 
+%\todo{write explanation}
+}
+\label{fig:sub}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+
 \section{Tight Analysis}
+\label{sec:tight}
+
 We now show that Corollary~\ref{cor:local} is tight.  Consider the
@@
 
-\begin{figure}
+\begin{figure}[h]
 \begin{center}

### 2017-02-15 src/group-apx.tex
merge dror

@@
-We now argue that the local improvement algorithm from
+We now argue that Algorithm~\textbf{StarImprove} from
 Section~\ref{sec:improve} can be generalized to solve \gcp.
@@
 \begin{theorem}
-Algorithm~\ref{alg:grd} is a $\half$-approximation algorithm for \gcp,
-if edge weights are integral and polynomially bounded.
+Algorithm~\textbf{StarImprove} is a $\half$-approximation algorithm
+for \gcp, if edge weights are integral and polynomially bounded.
 \end{theorem}

### 2017-02-15 src/hardness.tex
done my pass
fix
merge dror

@@
-??????
-
-As we mentioned in the introduction, the maximum spanning star forest
-can not be approximated within a factor of $\frac{31}{32} + \epsilon$
-for any $\epsilon > 0$, unless P$=$NP.  The proof, however, does not
-hold for the case when the maximum capacity is constant.  In this
-subsection we show that the problem remains APX-hard even in this
+As we mentioned earlier, \textsc{Spanning Star Forest} has a lower
+bound of $\frac{10}{11} + \eps$ for any $\eps > 0$, unless
+P$=$NP~\cite{ChakrabartyGoel10}, and this bound applies to \carpool.
+The result, however, does not hold for the case where $\cmax = O(1)$.
+In this section we show that the problem remains APX-hard even in this
 case.
-
-??????
 
@@
 \textsc{Minimum Dominating Set-$b$}.
-(For details on $L$-reductions the reader is referred to~\cite{??}.)
+(For details on $L$-reductions the reader is referred to~\cite{PapYan88}.)
 
@@
 Since $|D^*| \geq \frac{|V|}{b+1}$, it follows that 
-\[
+\(
 \abs{P_{M^*}} \leq b \abs{D^*}
-~,
-\]
+%~,
+\),
 In addition, if $M$ is a carpool matching, we have that
-\[
-\abs{D_M \cup Z_M} - \abs{D*}
+\(
+\abs{D_M \cup Z_M} - \abs{D^*}
 = (\abs{V} - \abs{P_M}) - \abs{D^*}
 = \abs{P_{M^*}} - \abs{P_M}
-~.
-\]
+%~.
+\).
 Hence, there is an $L$-reduction from \textsc{Minimum Dominating

### 2017-02-15 src/improve.tex
merge dror

@@
-In this subsection we give a local improvement
-$(\half-\eps)$-approximation algorithm for \carpool.  This algorithm
-repeatedly checks whether the current carpool matching $M$ can be
-improved by means of a star centered at a vertex $v$.  The profit from
-this star is the total weight of the arcs in the star, and the cost is
-the total weight of lost arcs (e.g., arcs from passengers to drivers
-that became passengers of $v$).  If the profit is larger than the
-cost, then an improvement step is performed.  The algorithm terminates
-when such a step is not possible.
+In this subsection we give a local search $(\half-\eps)$-approximation
+algorithm for \carpool.  This algorithm repeatedly checks whether the
+current carpool matching $M$ can be improved by means of a star
+centered at a vertex $v$.  The profit from this star is the total
+weight of the arcs in the star, and the cost is the total weight of
+lost arcs (e.g., arcs from passengers to drivers that became
+passengers of $v$).  If the profit is larger than the cost, then an
+improvement step is performed.  The algorithm terminates when such a
+step is not possible.
 %
@@
 \[
-\textstyle
+%\textstyle
 w_M(v)
@@
 \(
+\displaystyle
 \sum_{v \in V} w_M(v)
@@
 A subset $S_v \subseteq A \cap (V \times \{v\})$ is
-an \emph{improvement} with respect to a carpool matching $M$, if the
-following conditions hold:%
+an \emph{improvement} with respect to a carpool matching $M$, if%
+%the following conditions hold:%
 \begin{inparaenum}[(i)]
@@
 
-We are now ready to describe our local improvement algorithm
-(Algorithm~\ref{alg:grd}).  The algorithm starts with an empty carpool
-matching $M$, and in every iteration it looks for a vertex that can be
-improved.  If there exists such a vertex $v$, then the algorithm
-removes the arcs that are incident on it from $M$, and adds the arcs
-in $S_v$.  The algorithm terminates when no vertex can be improved.
-Figure~\ref{fig:improvement} depicts an improvement step.
+We are now ready to describe our local search algorithm, which is
+called \textbf{StarImprove} (Algorithm~\ref{alg:grd}).  It starts with
+an empty carpool matching $M$, and in every iteration it looks for a
+vertex that can be improved.  If there exists such a vertex $v$, then
+the algorithm removes the arcs that are incident on it from $M$, and
+adds the arcs in $S_v$.  The algorithm terminates when no vertex can
+be improved.  Figure~\ref{fig:improvement} depicts an improvement
+step.
 
 \begin{algorithm}
-\caption{Local Improvement}
+\caption{\textbf{StarImprove}$(G,c)$}
 \label{alg:grd}
+\begin{small}
 $M \gets \emptyset$ \\
@@
 }
+\end{small}
 \end{algorithm}
@@
 \label{lm:no improve}
-Let $M$ be a matching computed by the local improvement algorithm.
-Let $v$ be a vertex with no improvement, and let
-$S \subseteq \nin(v)$, such that $\abs{S} \leq c(v)$, then $w(S) \leq
-w_M(v) + w_M(\nin[S](v))$.
+Let $M$ be a matching computed by \textbf{StarImprove}.  Let $v$ be a
+vertex with no improvement, and let $S \subseteq \nin(v)$, such that
+$\abs{S} \leq c(v)$, then $w(S) \leq w_M(v) + w_M(\nin[S](v))$.
 \end{lemma}
@@
 \begin{lemma}
-If Algorithm~\ref{alg:grd} terminates, then the computed solution is a
-$\half$-approximation.
+If \textbf{StarImprove} terminates, then the computed solution is
+$\half$-approximate.
 \end{lemma}
@@
 Consider a path with $2n + 1$ arcs, and alternating arc weights (2 and
-1), if the local improvement algorithm selects all arcs of weight 1,
-then no further improvement can be done and the value of the matching
-is $n + 1$, while the optimal matching has value of $2n$.}
+1), if \textbf{StarImprove} selects all arcs of weight 1, then no
+further improvement can be done and the value of the matching is $n +
+1$, while the optimal matching has value of $2n$.}
 \label{fig:grd worst}
@@
 \label{thm:improve-bounded}
-Algorithm~\ref{alg:grd} is a $\half$-approximation algorithm
+Algorithm~\textbf{StarImprove} is a $\half$-approximation algorithm
 for \carpool, if edge weights are integral and polynomially bounded.
@@
 It remains to consider the case, where weight are not polynomially
-bounded.  In this case one can use scaling and rounding to ensure a
-polynomial running time in the cost of a $(1+\eps)$ factor in the
-approximation ratio.
-%
-The proof of the next theorem is given in the appendix.
+bounded.  In Appendix~\ref{sec:omitted} we prove that one can use
+standard scaling and rounding to ensure a polynomial running time in
+the cost of a $(1+\eps)$ factor in the approximation ratio.
 

### 2017-02-15 src/in/title.tex
refactor
merge dror

@@
-\title{Improved Approximation Algorithms for the
-Maximum Carpool Matching Problem}
+\title{%Improved Approximation
+Local Search Algorithms for the Maximum Carpool Matching Problem}
 
-\titlerunning{Improved Approximation Algorithms for Maximum Carpool Matching}
+\titlerunning{%Improved
+Local Search Approximation Algorithms for Maximum Carpool Matching}
 
@@
 \keywords{approximation algorithms, local search}
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\EventEditors{John Q. Open and Joan R. Acces}
+%\EventNoEds{2}
+%\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+%\EventShortTitle{CVIT 2016}
+%\EventAcronym{CVIT}
+\EventYear{2017}
+%\EventDate{December 24--27, 2016}
+%\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{1} %42
+\ArticleNo{1} %23
+% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-15 src/intro.tex
merge dror

@@
 \label{fig:carpool}
-A \carpool example: (\subref{carpool:input}) an instance containing a
-directed graph with capacities on the vertices and weights on the
-arcs.  (\subref{carpool:output}) a feasible matching with total weight
-of 23.  $P_M$ is the set of blue vertices, and $D_M$ is the set of
-red, dashed vertices, and $Z_M$ contains only the dotted, black
-vertex.  }
+A \carpool example.
+%(\subref{carpool:input}) an instance containing a
+%directed graph with capacities on the vertices and weights on the
+%arcs.  (\subref{carpool:output}) a feasible matching with total weight
+%of 23.  $P_M$ is the set of blue vertices, and $D_M$ is the set of
+%red, dashed vertices, and $Z_M$ contains only the dotted, black
+%vertex.
+}
 \end{figure}
 
-In this paper we also consider an extension of \carpool, called \gcp,
+%In this paper
+%
+We also consider an extension of \carpool, called \gcp,
 in which each vertex represents a group of passengers, and each group
@@
 %
-In Sections~\ref{sec:approx} contains approximation algorithms
+Sections~\ref{sec:approx} contains approximation algorithms
 for \carpool.  First, in Section~\ref{sec:sub} we show that
@@
 %
-We show a local improvement algorithm for \carpool%
-\footnote{We use the term \emph{local improvement} to differentiate
-this algorithm from the local search algorithm that is given in
-Section~\ref{sec:local}.}.
-%
-This algorithm repeatedly checks whether the current carpool matching
-can be improved by means of a star centered at a vertex, and it
-terminates when such a step is not possible.
+We present a local search algorithm for \carpool which repeatedly
+checks whether the current carpool matching can be improved by means
+of a star centered at a vertex, and it terminates when such a step is
+not possible.
 %
@@
 In Section~\ref{sec:local} we consider the unweighted variant of the
-problem.  We provide a local search algorithm whose approximation
-ratio is $\half + \inv{2\cmax} - \eps$, for any $\eps>0$.  Given a
-parameter $K$, our algorithm starts with the empty carpool matching.
-Then, it repeatedly tries to find a better matching by replacing
-$t \leq k$ arc in the current solution by $t+1$ arcs that are not in
-the solution.
+problem.  We provide another local search algorithm whose
+approximation ratio is $\half + \inv{2\cmax} - \eps$, for any
+$\eps>0$.  Given a parameter $k$, our algorithm starts with the empty
+carpool matching.  Then, it repeatedly tries to find a better matching
+by replacing $t \leq k$ arc in the current solution by $t+1$ arcs that
+are not in the solution.
 %
@@
 
-Finally, Section~\ref{sec:group} discusses the \gcp.  We first show that
-the unconstrained submodular maximization formulation for the \carpool
-does not work for \gcp.  We show, however, that this problem still
-admits a $(\frac{1}{2} -\varepsilon)$-approximation algorithm by
-extending the local improvement algorithm.  In addition, we show that
-the local search algorithm generalizes to \gcp with the same
-approximation ratio.
+Finally, Section~\ref{sec:group} discusses the \gcp.  We first show
+that the unconstrained submodular maximization formulation for
+the \carpool does not work for \gcp.  We show, however, that this
+problem still admits a $(\frac{1}{2} -\varepsilon)$-approximation
+algorithm by extending our first the local search algorithm.  In
+addition, we show that the second local search algorithm generalizes
+to unweighted \gcp with the same approximation ratio.

### 2017-02-15 src/local.tex
merge dror

@@
-In this section we present a $(\half + \inv{2c_{\max}}
+In this section we present a local search $(\half + \inv{2c_{\max}}
 - \eps)$-approximation algoithm for unweighted \carpool whose running
@@
 
-Let $k$ be an integer to be determined later.  The local search
-algorithm maintains a feasible matching throughout its execution and
-operates in iterative manner where in each iteration it tries to find
-a better solution by replacing a subset of at most $k$ edges in the
-current solution with another (larger) subset of edges not in the
-solution.  The local search algorithm halts when no improvement can be
-done.  The algorithm is described in Algorithm~\ref{alg:local}.
+Let $k$ be a constant integer to be determined later.
+Algorithm~\textbf{EdgeSwap} (Algorithm~\ref{alg:local}) maintains a
+feasible matching $M$ throughout its execution and operates in
+iterative manner where in each iteration it tries to find a better
+solution by replacing a subset of at most $k$ edges in the current
+solution with another (larger) subset of edges not in the solution.
+The algorithm halts when no improvement can be done.
 
 \begin{algorithm}
+\caption{\textbf{EdgeSwap}$(G,c,k)$}
+\label{alg:local}
+\begin{small}
 \SetKw{True}{true}
 \SetKw{False}{false}
-\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
-\KwOut{$M$}
+%\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
+%\KwOut{$M$}
 $M \leftarrow \emptyset$								\\
@@
 \Return{$M$}
-
-\caption{Local Search}
-\label{alg:local}
+\end{small}
 \end{algorithm}
 
-We claim that the local search algorithm halts in polynomial time.
-Observed that in every iteration the algorithm either improves the
-value of the solution by one or otherwise it terminates.  Thus, after
-a maximum of $n$ iterations the algorithm stops.  In every iteration
-we examine all the subsets of edges of a fixed size and test for
-feasibility, both these operations can be done in polynomial time.
+Algorithm~\textbf{EdgeSwap} terminates in polynomial time, since in
+every non-final iteration it improves the value of the solution by
+one.  Thus, after at most $n$ iterations the algorithm terminates.  In
+every iteration the algorithm examines all subsets of edges of a fixed
+size and tests for feasibility, both these operations can be done in
+polynomial time.
 
@@
 
-To analyze the approximation ratio achieved by the local search
-algorithm consider an arbitrary but fixed optimal matching $M^*$.
-Given the solution outputted by the local search algorithm, $M$, we
-build the \emph{star graph} of the two solutions in which each node
-represents a star from the optimal solution, namely from $\calS(M^*)$,
-and an edge exists between two nodes if there is a star in $\calS(M)$
-that intersects the two corresponding stars of the optimal solution.
+It remains to analyze the approximation ratio of \textbf{EdgeSwap}.
+Consider an optimal matching $M^*$, and $M$ be the matching computed
+by \textbf{EdgeSwap}.  Given both matchings we build the \emph{star
+graph} of the two solutions in which each node represents a star from
+the optimal solution, namely from $\calS(M^*)$, and an edge exists
+between two nodes if there is a star in $\calS(M)$ that intersects the
+two corresponding stars of the optimal solution.
 %
@@
 \begin{proof}
-Each star in $\calS(M^*)$ consists of at most $\cmax+1$ vertices and
-each such vertex can belong to a star in $\calS(M)$ containing
-additional $\cmax$ vertices, each of which is located in a different
-star in $\calS(M^*)$.
+Each star in $\calS(M^*)$ contains at most $\cmax+1$ vertices and each
+such vertex can belong to a star in $\calS(M)$ containing additional
+$\cmax$ vertices, each of which is located in a different star in
+$\calS(M^*)$.
 \end{proof}
+
+In what follows we compare $\abs{M}$ and $\abs{M^*}$ in maximal
+connected components of the star graph $H$.  Intuitively, we show that
+$M$ is optimal on small maximal components, and that the approximation
+ratio on medium (non-necessarily) components can be bounded due to the
+termination condition of \textbf{EdgeSwap}.  Large maximal components
+will be partitioned into medium components.
+
+We first show that large connected graphs (or maximal connected
+components) can be partitioned in to medium size components.  The
+proof is given in Appnedix~\ref{sec:omitted}.
+
+\begin{lemma}
+\label{lemma:dec}
+An undirected connected graph $G = (V,E)$ with maximum degree
+$\Delta$, can be decomposed into connected components of size at least
+$\ell$ and at most $\Delta \ell$, if $\ell \leq \abs{V}$.
+\end{lemma}
+
+\iffalse %%%%%% Removed
+
+\begin{proof}
+Let $T$ be any spanning tree of $G$ and let $r$ be an arbitrary root.
+Starting with $r$, repeatedly choose a child whose subtree is strictly
+larger than $\frac{\Delta-1}{\Delta} \abs{V}$, until this is not
+possible.  Hence, we have reached a vertex $v$ whose subtree contains
+more than $\frac{\Delta-1}{\Delta} \abs{V}$ vertices, but the subtrees
+of its children contain at most $\frac{\Delta-1}{\Delta} \abs{V}$
+vertices.
+%
+If $v = r$, then $v$ has a child $u$ with at least $\inv{\Delta}
+(\abs{V}-1) \geq \ell$ vertices.  Otherwise, there exists a child $u$
+of $v$ whose subtree is of size at least
+$\inv{\Delta} \abs{V} \geq \ell$.  Disconnect $u$ and the vertices in
+its subtree from the graph.
+%
+In both cases $u$'s subtree contains at most
+$\frac{\Delta-1}{\Delta} \abs{V}$ vertices, and thus at least
+$\inv{\Delta} \abs{V} \geq \ell$ vertices remain in the graph.  Hence
+we obtain two connected subgraphs of size at least $\ell$.
+%
+We repeat this procedure recursively on any component of size
+strictly larger $\Delta\ell$.
+\end{proof}
+
+\fi %%%%%% End removed
 
@@
 U} \deg_M(u)$.
+%
+Observe that $\abs{M} = \half \deg_M(V)$.
+
+In the next lemma we bound the degree ratio in a component that
+contains stars with at most $k$ arcs.
 
@@
 Since $\abs{A(\calT)} \leq k$, we know that this difference can not be
-positive, or else, the local search algorithm would not have been
-terminated.  Thus 
+positive, or else, \textsc{EdgeSwap} would not have terminated.  Thus
 \(
@@
 as required.
-\end{proof}
-
-\begin{lemma}
-\label{lemma:dec}
-Let $G = (V,E)$ be an undirected connected graph with maximum degree
-$\Delta$, and let $\ell < \abs{V}$.  
-Then $G$ can be decomposed into connected components of size at least $\ell$,
-and at most $\Delta \ell$.
-\end{lemma}
-
-\begin{proof}
-We give a constructive proof.
-If $\ell \leq |V| \leq \Delta \ell$ we are done.
-%
-Otherwise, remove (in any desired way) up to $\ell$ connected vertices $C =
-\{v_1,\ldots,v_m\}$ from $G$ until $G$ is disconnected.
-If $m = \ell$ then let $C_1 = \{v_1,\ldots,v_\ell\}$ and recursively decompose
-$G - C$.
-If, on the other hand, the above process disconnects $G$ then consider the
-connected components $\{C_1, \ldots, C_t\}$ of $G - C$.
-Join all the small components and $C$, i.e. $C \cup \bigcup_{i : |C_i| < \ell}$
-and decompose the other components recursively, 
-noting that $|C \cup \bigcup_{i : |C_i| < \ell}| \leq \Delta \ell$.
-If all the components are large, i.e. $\forall i |C_i| \geq \ell$ then join $C$
-to an arbitrary component and decompose the resulting components recursively.
-
-\iffalse
-Let $T$ be any spanning tree of $G$ and let $r$ be an arbitrary root.
-Starting with $r$, repeatedly choose a child whose subtree is strictly
-larger than $\frac{\Delta-1}{\Delta} \abs{V}$, until this is not
-possible.  Hence, we have reached a vertex $v$ whose subtree contains
-more than $\frac{\Delta-1}{\Delta} \abs{V}$ vertices, but the subtrees
-of its children contain at most $\frac{\Delta-1}{\Delta} \abs{V}$
-vertices.
-%
-If $v = r$, then $v$ has a child $u$ with at least $\inv{\Delta}
-(\abs{V}-1) \geq \ell$ vertices.  Otherwise, there exists a child $u$
-of $v$ whose subtree is of size at least
-$\inv{\Delta} \abs{V} \geq \ell$.  Disconnect $u$ and the vertices in
-its subtree from the graph.
-%
-In both cases $u$'s subtree contains at most
-$\frac{\Delta-1}{\Delta} \abs{V}$ vertices, and thus at least
-$\inv{\Delta} \abs{V} \geq \ell$ vertices remain in the graph.  Hence
-we obtain two connected subgraphs of size at least $\ell$.
-%
-We repeat this procedure recursively on any component of size
-strictly larger $\Delta\ell$.
-\fi
 \end{proof}
@@
 
+It remains to bound the approximation ratio of \textbf{EdgeSwap}.
+
 \begin{lemma}
@@
 It remains to consider a maximal component $\calT$ such that If
-$\abs{M \cap A(\calT)} > k$.  Observe that since the number of edges
-in $S \in \calS(M^*)$ is at most $\cmax$, it must be that
-$\abs{V(\calT)} > \frac{k}{\cmax}$.
+$\abs{M \cap A(\calT)} > k$.  Since the number of edges in
+$S \in \calS(M^*)$ is at most $\cmax$, it must be that $\abs{V(\calT)}
+> \frac{k}{\cmax}$.
 %
-Due to Lemma~\ref{lemma:dec} (with $\ell = \frac{k}{\cmax}$) we can
-partition $\calT$ into connected components each of which contains
-between $\frac{k}{\cmax^2(\cmax+1)}$ and $\frac{k}{\cmax}$ vertices.
+Due to Lemma~\ref{lemma:dec} (with $\ell
+= \frac{k}{\cmax^2(\cmax+1)}$) we can partition $\calT$ into connected
+components each of which contains between $\frac{k}{\cmax^2(\cmax+1)}$
+and $\frac{k}{\cmax}$ vertices.
 %
@@
 and thus
-\[
+\(
 \abs{M \cap A(\calT)}
@@
              \frac{\cmax(\cmax+1)}{2k}} \abs{M^* \cap A(\calT)}
-~,
-\]
-and the lemma follows.
+%~,
+\).
+%and the lemma follows.
 \end{proof}
@@
 There exists a $(\half + \inv{2\cmax} - \eps)$-approximation algorithm
-for \carpool, for every $\eps>0$.
+for unweighted \carpool, for every $\eps>0$.
 \end{corollary}
 
-In the appendix we show that our analysis is tight.
+In the Appendix~\ref{sec:tight} we show that our analysis is tight.

### 2017-02-15 src/appendix.tex
fix some refs

@@
 \section{Figures}
-\label{sec:figures}
+%\label{sec:figures}
 
@@
 \caption[]{%
-We show that the arcs from \subref{sub:cup} and \subref{sub:cap} can be
-redistributed over \subref{sub:s} and \subref{sub:s} 
-%\todo{write explanation}
+Given the two solutions on the left, 
+\subref{sub:cup} and \subref{sub:cap}, we
+can construct the two solutions on the right side,
+\subref{sub:s} and \subref{sub:t}, with equal total weight.
+The edges of type 
+\inlineedge{e1}, 
+\inlineedge{e2}, 
+\inlineedge{e3}, 
+\inlineedge{e5}, 
+\inlineedge{e6}
+from the left side are ``naturally'' distributed over the two solutions on the
+right side and the edges of type \inlineedge{e4} can be distrebuted between the
+two solutions without violating the capacity constraints.
 }

### 2017-02-15 src/local.tex
fix some refs

@@
 \Repeat{done}{
-\label{line:outerloop}
  	$done \leftarrow{}$ \True							\\
@@
 \begin{figure}[t]
+\centering
 %
-\begin{subfigure}[t]{.4\linewidth}
-\caption{\label{subfloat:graph}}
+\begin{subfigure}[t]{.45\linewidth}
+\centering
+\caption{
+An optimal matching depicted by the dashed red edges,
+and another solution depicted by the solid green edges.
+The optimal stars are outlined.  
+}
 \input{fig-sub-graph}
@@
 %
-\begin{subfigure}[t]{.4\linewidth}
-\caption{\label{subfloat:conflict}}
-\input{fig-sub-conflict}
-\end{subfigure}
-%
-\caption[]{
-\subref{subfloat:graph} 
-An optimal matching depicted by the dashed red edges,
-and another solution depicted by the solid green edges.
-The optimal stars are outlined.  
-\subref{subfloat:conflict}
+\begin{subfigure}[t]{.53\linewidth}
+\centering
+\caption{
 The star graph, each vertex corresponded to a star in the original graph. 
@@
 }
+\input{fig-sub-conflict}
+\end{subfigure}
+%
+\caption{A \emph{Star Graph}}
 \label{fig:conflict}

### 2017-02-15 src/intro.tex
intro

@@
 They presented two approximation algorithms, one for the weighted case
-whose is ratio is $0.5833$, and another for the unweighted case whose
+whose ratio is $0.5833$, and another for the unweighted case whose
 ratio is $\frac{3}{4}$.
@@
 Another related problem is the \textsc{$k$-Set Packing}, where one is
-given a collection of weighted sets, each containing as most $k$
+given a collection of weighted sets, each containing at most $k$
 elements, and the goal is to find a maximum weight subcollection of
@@
 
-Section~\ref{sec:cmax} we consider \carpool with bounded maximum
+In Section~\ref{sec:cmax} we consider \carpool with bounded maximum
 capacity.   Define $\cmax \eqdf \max_{v \in V} c(v)$.
@@
 problem still admits a $(\frac{1}{2} -\varepsilon)$-approximation
-algorithm by extending our first the local search algorithm.  In
+algorithm by extending our first local search algorithm.  In
 addition, we show that the second local search algorithm generalizes

### 2017-02-15 src/appendix.tex
merge dror

@@
+%\newpage
+%\bigskip
+
+\section{Figure}
+%\label{sec:figures}
+
+\begin{figure}[h]
+\centering
+\input{fig-submodular}
+\caption[]{%
+Given the two solutions on the left, 
+\subref{sub:cup} and \subref{sub:cap}, we
+can construct the two solutions on the right side,
+\subref{sub:s} and \subref{sub:t}, with equal total weight.
+The edges of type 
+\inlineedge{e1}, 
+\inlineedge{e2}, 
+\inlineedge{e3}, 
+\inlineedge{e5}, 
+\inlineedge{e6}
+from the left side are ``naturally'' distributed over the two solutions on the
+right side and the edges of type \inlineedge{e4} can be distributed between the
+two solutions without violating the capacity constraints.
+}
+\label{fig:sub}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Omitted Proofs}
@@
 \[
+\textstyle
 w'(M^*)
@@
 \[
+\textstyle
 w(M)
@@
 
-\newpage
-
-\section{Figures}
-%\label{sec:figures}
-
-\begin{figure}[h]
-\centering
-\input{fig-submodular}
-\caption[]{%
-Given the two solutions on the left, 
-\subref{sub:cup} and \subref{sub:cap}, we
-can construct the two solutions on the right side,
-\subref{sub:s} and \subref{sub:t}, with equal total weight.
-The edges of type 
-\inlineedge{e1}, 
-\inlineedge{e2}, 
-\inlineedge{e3}, 
-\inlineedge{e5}, 
-\inlineedge{e6}
-from the left side are ``naturally'' distributed over the two solutions on the
-right side and the edges of type \inlineedge{e4} can be distrebuted between the
-two solutions without violating the capacity constraints.
-}
-\label{fig:sub}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-
 \section{Tight Analysis}

### 2017-02-15 src/group.tex
merge dror

@@
-We now consider \gcp which a variant of \carpool in which in addition
-to the capacity function $c:V \to \N$, and the weight function
-$w:A \to \R^+$, we also have a size function $s:V \to \N$, and the
-constraint $\din[M](v) \leq c(v)$ is replaced with the constraint
+We now consider \gcp which a variant of \carpool in which
+%
+%in addition to the capacity function $c:V \to \N$, and the weight
+%function $w:A \to \R^+$, we also have
+we are given a size function $s:V \to \N$, and the constraint
+$\din[M](v) \leq c(v)$ is replaced with the constraint
 $\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
@@
 %is the size of the group.
+
+We start by showing that this variant of the problem does not fit the
+submodular maximization formulation as defined for \carpool.
 %
-We start by showing that this variant of the problem does not fit the
-submodular maximization formulation anymore.  We show, however, that
-the problem still has a $(\half -\eps)$-approximation algorithm by
-extending the local improvement algorithm from
+Recall the submodular maximization formulation given in
+Section~\ref{sec:sub}, namely $\barw: 2^V \to \R$, where
+$\barw(S) \eqdf w(M(S))$ and $M(S)$ is the maximum weight carpool
+matching that satisfies $D_{M(S)} \subseteq S \subseteq V \setminus
+P_{M(S)}$.
+%
+Figure~\ref{fig:not submodular} contains an instance that shows that
+the function $\barw$ is not submodular anymore.
+
+\begin{figure}
+\begin{center}
+\input{fig-not-submodular}
+\end{center}
+\caption{An unweighted \carpool instance.  Capacities are written inside
+nodes, and arcs are labeled with their size.  We have that $f(A) +
+f(B) = 2 < 3 = f(A \cup B) + f(A \cap B)$.}
+\label{fig:not submodular}
+\end{figure}
+
+We show, however, that \gcp has a $(\half -\eps)$-approximation
+algorithm by extending the local improvement algorithm from
 Section~\ref{sec:improve}.
 %
-Finally, we show that the local search algorithm from
-Section~\ref{sec:local} can be generalized to handle \gcp while
-keeping the same approximation guarantees.
+The main concern when trying to adopt the algorithm to \gcp is how to
+determine if a vertex can be improved.
+%
+With \carpool, if weights are polynomially-bounded, it was enough to
+consider the incoming arcs to a vertex $v$ in a non-increasing
+order of $\delta_M$ (See proof of Theorem~\ref{thm:improve-bounded}).
+This does not work anymore, since in the \gcp we have sizes.  In fact, given
+$v$, finding the best star with respect to $\delta_M$ is
+a \textsc{Knapsack} instance where the size of the knapsack is $c(v)$.
+%
+If weights are polynomially-bounded, then $\delta_M(e)$ is bounded for
+every arc $e \in A$, and therefore this instance of \textsc{Knapsack}
+can be solved in polynomial time using dynamic programming.
+
+\begin{theorem}
+Algorithm~\textbf{StarImprove} is a $\half$-approximation algorithm
+for \gcp, if edge weights are integral and polynomially bounded.
+\end{theorem}
+
+Using standard scaling and rounding we obtain the following result.
+
+\begin{theorem}
+There exists a $(\half-\eps)$-approximation algorithm for \gcp,
+for every $\eps \in (0,\half)$.
+\end{theorem}
+
+Finally, we show that a variant of Algorithm~\textbf{EdgeSwap} from
+Section~\ref{sec:local} can be used to solve \gcp while keeping the
+same approximation guarantees. 
+%
+The only difference is that when checking feasibility of a set of arcs
+we do not compare the number of passengers to the capacity of a
+driver, but rather compare the total size of the passengers to the
+capacity.
+
+\begin{theorem}
+There exists a $(\half + \inv{2\cmax} - \eps)$-approximation algorithm
+for unweighted \gcp, for every $\eps>0$.
+\end{theorem}

### 2017-02-15 src/improve.tex
fix some refs
merge dror

@@
-In this subsection we give a local search $(\half-\eps)$-approximation
+In this section we give a local search $(\half-\eps)$-approximation
 algorithm for \carpool.  This algorithm repeatedly checks whether the
@@
 \[
-%\textstyle
+\textstyle
 w_M(v)
@@
 \input{fig-improvement}
-\caption[]{
+\caption[]{An improvement example.}
 \label{fig:improvement}
-\subref{sub:can improved}
-A matching that can be improved
-\subref{sub:improved}
-The matching after improving vertex 3
-}
 \end{figure}

### 2017-02-15 src/intro.tex
merge dror

@@
 The matching process of passengers to drivers entails more than
-matching the route.  Passenger satisfaction also need to be taken into
-account.
+matching the route.
 %
-Given several riding options (including taking their own car),
-passengers have preferences.  For example, a passenger may prefer to
-ride with a co-worker or a friend.  A passenger may have an opinion on
-a driver that she rode with in the past.  She may prefer a non-smoker,
-someone who shares her taste in music, or someone who is recommended
-by others.
+Passenger satisfaction also need to be taken into account.  Given
+several riding options (including taking their own car), passengers
+have preferences.  For example, a passenger may prefer to ride with a
+co-worker or a friend.  A passenger may have an opinion on a driver
+that she rode with in the past.  She may prefer a non-smoker, someone
+who shares her taste in music, or someone who is recommended by
+others.
+%
+Moreover, the matching process may take into account driver
+preferences.  For instance, we would like to minimize the extra
+distance that a driver has to take.
 %
@@
 %In this paper
-We assume that potential passenger satisfactions are given as input
-and the goal is to compute an assignment of passengers to driver so as
-to maximize the global satisfaction.
+We assume that potential passenger-driver satisfactions are given as
+input and the goal is to compute an assignment of passengers to
+drivers so as to maximize the global satisfaction.
 %
@@
 commute with the user corresponding to vertex $v$.  We are given a
-capacity function $c: V \rightarrow \N$ which bound the number of
-passengers each user can drive if she was selected as a driver.  A
+capacity function $c: V \rightarrow \N$ which bounds the number of
+passengers each user can drive if she is selected as a driver.  A
 non-negative weight function $w : A \rightarrow \R^+$ is used to model
-the amount of satisfaction $w(u,v)$ that user $u$ gains when riding
-with user $v$.
+the amount of satisfaction $w(u,v)$ of assigning $u$ to $v$.
 %
-If $(u,v) \in A$ implies that $(v,u) \in A$ and $w(u,v) = w(v,u)$, we
-call the instance \emph{undirected}.  If $w(v,u) = 1$, for every
-$(v,u) \in A$, then we call the instance
-\emph{unweighted}.  If $c(v) = \infty$, for every $v$, then we
-call the instance \emph{uncapacitated}.
+If $(u,v) \in A$ implies that $(v,u) \in A$ and $w(u,v) = w(v,u)$, the
+instance is \emph{undirected}.  If $w(v,u) = 1$, for every $(v,u) \in
+A$, then the instance is \emph{unweighted}.  If $c(v) = \infty$, for
+every $v$, then the instance in \emph{uncapacitated}.
 
@@
 %
-In Section~\ref{sec:local} we consider the unweighted variant of the
-problem.  We provide another local search algorithm whose
-approximation ratio is $\half + \inv{2\cmax} - \eps$, for any
-$\eps>0$.  Given a parameter $k$, our algorithm starts with the empty
-carpool matching.  Then, it repeatedly tries to find a better matching
-by replacing $t \leq k$ arc in the current solution by $t+1$ arcs that
-are not in the solution.
+In Section~\ref{sec:local} we provide another local search algorithm,
+whose approximation ratio is $\half + \inv{2\cmax} - \eps$, for any
+$\eps>0$, for unweighted \carpool.  Given a parameter $k$, our
+algorithm starts with the empty carpool matching.  Then, it repeatedly
+tries to find a better matching by replacing $t \leq k$ arcs in the
+current solution by $t+1$ arcs that are not in the solution.
 %
 We show that our analysis is tight.  We also note that our algorithm
-is a special case of the local search family that was defined
-in~\cite{ACKK09} with a parameter of $2k$.  On undirected and
-uncapaciated instances we have that $\cmax = \Delta$, where $\Delta$
-is the maximum degree, hence the approximation ratio of our algorithm
-is $\half + \inv{2\Delta} - \eps$ which is tight with respect
-to~\cite{ACKK09}.
+falls within the local search family defined in~\cite{ACKK09} with a
+parameter of $2k$.  On undirected and uncapaciated instances we have
+that $\cmax = \Delta$, where $\Delta$ is the maximum degree, hence the
+approximation ratio of our algorithm is $\half + \inv{2\Delta} - \eps$
+which is nearly tight with respect to~\cite{ACKK09}.
 

### 2017-02-15 src/local.tex
merge dror

@@
 \begin{figure}[t]
-\centering
+%\centering
 %
@@
 \centering
-\caption{
-An optimal matching depicted by the dashed red edges,
+\input{fig-sub-graph}
+\caption{An optimal matching depicted by the dashed red edges,
 and another solution depicted by the solid green edges.
-The optimal stars are outlined.  
-}
-\input{fig-sub-graph}
+The optimal stars are outlined.}
 \end{subfigure}
@@
 %
-\begin{subfigure}[t]{.53\linewidth}
+\begin{subfigure}[t]{.45\linewidth}
 \centering
-\caption{
-The star graph, each vertex corresponded to a star in the original graph. 
-The upper left vertex corresponds to the star that contains the vertices a,b,c.
-The numbers inside the vertices corresponds to $d_i$.   
-}
 \input{fig-sub-conflict}
+\caption{The star graph, each vertex corresponded to a star in the
+original graph.  The upper left vertex corresponds to the star that
+contains the vertices a,b,c.  The numbers inside the vertices
+corresponds to $d_i$.}
 \end{subfigure}
 %
-\caption{A \emph{Star Graph}}
+\caption{An example of a star graph.}
 \label{fig:conflict}
@@
 Due to Lemma~\ref{lemma:r} we have that
-\[
+\(
 \frac{\deg_M(V(\calX))}{\deg_{M^*}(V(\calX))} 
 \geq \half + \inv{2\cmax} - \frac{\cmax(\cmax+1)}{2k}
-~.
-\]
+%~.
+\).
 Since $\deg_{M^*}(V(\calT)) = \sum_{\calX} \deg_{M^*}(V(\calX))$ and
 $\deg_M(V(\calT)) = \sum_{\calX} \deg_M(V(\calX))$, it follows that
-\[
+\(
 \frac{\deg_M(V(\calT))}{\deg_{M^*}(V(\calT))}
 \geq \half + \inv{2\cmax} - \frac{\cmax(\cmax+1)}{2k}
-~,
-\]
+%~,
+\),
 and thus

### 2017-02-15 src/sub.tex
merge dror

@@
 In this section we show that the \carpool problem can be formulated as
-unconstrained submodular maximization problem, and thus it has a
-$\frac{1}{2}$-approximation algorithm based on Buchbinder et
+an unconstrained submodular maximization problem, and thus it has a
+$\frac{1}{2}$-approximation algorithm due to Buchbinder et
 al.~\cite{BFNS15,buchbinder2016deterministic}.
@@
 Given a \carpool instance $(G = (V,A), c, w)$, consider a subset
-$S \subseteq V$.  Let $M(S)$ be the maximum weight carpool matching
-that satisfies $D_{M(S)} \subseteq S \subseteq V \setminus P_{M(S)}$,
+$S \subseteq V$.  Let $M(S)$ be a maximum weight carpool matching
+satisfying $D_{M(S)} \subseteq S \subseteq V \setminus P_{M(S)}$,
 namely $M(S)$ is the best carpool matching whose drivers belong to $S$
@@
 T) \cup M(S \cap T)$.
+%
+The lemma follows, since $\barw(S) \geq w(M_S)$ and $\barw(T) \geq
+w(M_T)$.
 
@@
 T \setminus S$.
-
+%
 Next, add the edges in $M(S \cap T)$ leaving $T \setminus S$ to $S$
@@
 + \din[M(S \cap T)](v) \leq 2c(v)$, for every $v \in S \cap T$.
-
-The lemma follows, since $\barw(S) \geq w(M_S)$ and $\barw(T) \geq
-w(M_T)$.
+%
+Figure~\ref{fig:sub} contains a graphical representation of the above
+edge distribution.
 \end{proof}
@@
 \end{theorem}
-
-\begin{figure}
-\centering
-\input{fig-submodular}
-\caption[]{
-We show that the arcs from \subref{sub:cup} and \subref{sub:cap} can be
-redistributed over \subref{sub:s} and \subref{sub:s} 
-%\todo{write explanation}
-}
-\end{figure}

### 2017-02-15 src/appendix.tex
refactoring

@@
 \centering
-\input{fig-submodular}
+\input{fig/fig-submodular}
 \caption[]{%
@@
 \inlineedge{e3}, 
-\inlineedge{e5}, 
 \inlineedge{e6}
 from the left side are ``naturally'' distributed over the two solutions on the
-right side and the edges of type \inlineedge{e4} can be distributed between the
-two solutions without violating the capacity constraints.
+right side and the edges of type \inlineedge{e5} and \inlineedge{e4} can be
+distributed between the two solutions without violating the capacity constraints.
 }
@@
 \begin{center}
-\scalebox{.85}{\input{fig-local-tight}}
+\scalebox{.85}{\input{fig/fig-local-tight}}
 \caption{A tight example for Corollary~\ref{cor:local}. 

### 2017-02-17 src/abstract.tex
merge dror

@@
-The \carpool problem is a star packing problem in directed graphs.
-Formally, given a directed graph $G = (V, A)$, a capacity function $c:
-V \rightarrow \N$, and a weight function $w: A \rightarrow \R^+$, a
-feasible \emph{carpool matching} is a subset of arcs, $M \subseteq A$,
-such that every $v \in V$ satisfies:%
+The \carpool problem is a \emph{star packing} problem in directed
+graphs.  Formally, given a directed graph $G = (V, A)$, a capacity
+function $c: V \rightarrow \N$, and a weight function $w:
+A \rightarrow \R^+$, a \emph{carpool matching} is a subset of arcs,
+$M \subseteq A$, such that every $v \in V$ satisfies:%
 \begin{inparaenum}[(i)]
@@
 $\din[M](v)$ passengers.  In the \carpool problem the goal is to find
-a matching $M$ of maximum total weight.
+a carpool matching $M$ of maximum total weight.
 %
 The problem arises when designing an online carpool service, such as
-Zimride~\cite{zimride}, which tries to connect between passengers and
-drivers based on a similarity function.  The problem is known to be
-NP-hard, even for uniform weights and infinite capacities.
+Zimride~\cite{zimride}, which tries to connect between users based on
+a similarity function.  The problem is known to be NP-hard, even in
+the unweighted and uncapacitated case.
 %
@@
 $(\half + \inv{2\cmax} - \eps)$-approximation algorithm.  We also show
-that the problem APX-hard, even if $\cmax \leq 3$.
+that the problem APX-hard, even if the maximum degree (and $\cmax$) is
+at most $3$.

### 2017-02-17 src/intro.tex
refactoring
merge dror

@@
 
-%In this paper
-We assume that potential passenger-driver satisfactions are given as
-input and the goal is to compute an assignment of passengers to
-drivers so as to maximize the global satisfaction.
+In this paper we assume that potential passenger-driver satisfactions
+are given as input and the goal is to compute an assignment of
+passengers to drivers so as to maximize the global satisfaction.
 %
@@
 instance is \emph{undirected}.  If $w(v,u) = 1$, for every $(v,u) \in
-A$, then the instance is \emph{unweighted}.  If $c(v) = \infty$, for
+A$, then the instance is \emph{unweighted}.  If $c(v) = \deg(v)$, for
 every $v$, then the instance in \emph{uncapacitated}.
@@
 \centering
-\input{fig-carpool}
+\input{fig/fig-carpool}
 \caption[]{
@@
 %
-We also consider an extension of \carpool, called \gcp,
-in which each vertex represents a group of passengers, and each group
-might have a different size.  Such a group may be a family or two
-friends traveling together.  Formally, each vertex $u \in V$ has a
-size $s(u) \in \N$, and the constraint $\din[M](v) \leq c(v)$ is
-replaced with the constraint $\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
+We also consider an extension of \carpool, called \gcp, in which each
+vertex represents a group of passengers, and each group may have a
+different size.  Such a group may represent a family or two friends
+traveling together.  Formally, each vertex $u \in V$ has a size
+$s(u) \in \N$, and the constraint $\din[M](v) \leq c(v)$ is replaced
+with the constraint $\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
 %
@@
 %
-Hartman et al.~\cite{hartman2014theory} designed
-several heuristic algorithms for the \carpool problem and compared
-their performance on real data.  Other heuristic algorithms were
-developed as well~\cite{knapen2014exploiting}.
+Hartman et al.~\cite{hartman2014theory} designed several heuristic
+algorithms for the \carpool problem and compared their performance on
+real data.  Other heuristic algorithms were developed by Knapen et
+al.~\cite{knapen2014exploiting}.
 %
@@
 $c(v) \leq 2$ for every $v \in V$.  In addition, Hartman presented a
-natural integer linear programs and showed that if the set of drivers
+natural integer linear program and showed that if the set of drivers
 is known, then an optimal assignment of passengers to drivers can be
 found in polynomial time using a reduction to \textsc{Network Flow}
-(see also Kutiel~\cite{kutiel2016}.)
+(see also~\cite{kutiel2016}.)
 %
 Kutiel~\cite{kutiel2016} presented a $\frac{1}{3}$-approximation
-algorithm for \carpool and a $\half$-approximation algorithm for the
-unweighted variant of \carpool.
+algorithm for \carpool that is based on a \textsc{Minimum Cost Flow}
+computation and a local search $\half$-approximation algorithm for the
+unweighted variant of \carpool.  The latter starts with an empty
+matching and tries to improve the matching by turning a single
+passenger into a driver.
 
@@
 where \textsc{opt} is the size of the optimal spanning star forest.
-We note that the construction of the above result requires that the
-maximum degree of $G$ is at least $2(k+2)$.  Hence, in graphs with
-maximum degree $\Delta$, the above ratio becomes $\half
-+ \inv{\Delta}$.
+We note that, for a given $k$, the construction of the above result
+requires that the maximum degree of $G$ is at least $2(k+2)$.  Hence,
+this result does not hold in graphs with maximum degree $\Delta$.
 
@@
 %
-Sections~\ref{sec:approx} contains approximation algorithms
-for \carpool.  First, in Section~\ref{sec:sub} we show that
-the \carpool can be formulated as unconstrained submodular
-maximization problem, thus it has a $\frac{1}{2}$-approximation
-algorithm due to~\cite{BFNS15,buchbinder2016deterministic}.
+Section~\ref{sec:approx} contains approximation algorithms
+for \carpool.  First, in Section~\ref{sec:sub} we show that \carpool
+can be formulated as an unconstrained submodular maximization problem,
+thus it has a $\frac{1}{2}$-approximation algorithm due
+to~\cite{BFNS15,buchbinder2016deterministic}.
 %
@@
 In Section~\ref{sec:cmax} we consider \carpool with bounded maximum
-capacity.   Define $\cmax \eqdf \max_{v \in V} c(v)$.
+capacity.   
 %
 In Section~\ref{sec:hardness} we show that \carpool is APX-hard even
-for undirected and unweighted instances with $\cmax \leq b$, for any
+for undirected and unweighted instances with $\Delta \leq b$, for any
 $b \geq 3$.
@@
 whose approximation ratio is $\half + \inv{2\cmax} - \eps$, for any
-$\eps>0$, for unweighted \carpool.  Given a parameter $k$, our
-algorithm starts with the empty carpool matching.  Then, it repeatedly
-tries to find a better matching by replacing $t \leq k$ arcs in the
-current solution by $t+1$ arcs that are not in the solution.
+$\eps>0$, for unweighted \carpool, where $\cmax \eqdf \max_{v \in V}
+c(v)$.  Given a parameter $k$, our algorithm starts with the empty
+carpool matching.  Then, it repeatedly tries to find a better matching
+by replacing $t \leq k$ arcs in the current solution by $t+1$ arcs
+that are not in the solution.
 %
-We show that our analysis is tight.  We also note that our algorithm
-falls within the local search family defined in~\cite{ACKK09} with a
-parameter of $2k$.  On undirected and uncapaciated instances we have
-that $\cmax = \Delta$, where $\Delta$ is the maximum degree, hence the
-approximation ratio of our algorithm is $\half + \inv{2\Delta} - \eps$
-which is nearly tight with respect to~\cite{ACKK09}.
+We show that our analysis is tight.
+%
+We also note that our algorithm falls within the local search family
+defined in~\cite{ACKK09}.  However, on undirected and uncapaciated
+instances we have that $\cmax = \Delta$, and as mentioned above the
+result from~\cite{ACKK09} does not hold in bounded degree graphs.
 
-Finally, Section~\ref{sec:group} discusses the \gcp.  We first show
-that the unconstrained submodular maximization formulation for
-the \carpool does not work for \gcp.  We show, however, that this
-problem still admits a $(\frac{1}{2} -\varepsilon)$-approximation
-algorithm by extending our first local search algorithm.  In
-addition, we show that the second local search algorithm generalizes
-to unweighted \gcp with the same approximation ratio.
+Finally, Section~\ref{sec:group} discusses \gcp.  We show that the
+unconstrained submodular maximization formulation for \carpool does
+not work for \gcp.  We show, however, that this problem still admits a
+$(\frac{1}{2} -\varepsilon)$-approximation algorithm by extending our
+first local search algorithm.  In addition, we show that the second
+local search algorithm generalizes to unweighted \gcp with the same
+approximation ratio.

### 2017-02-17 src/local.tex
refactoring
merge dror

@@
 %
-\begin{subfigure}[t]{.45\linewidth}
+\begin{subfigure}[b]{.47\linewidth}
 \centering
-\input{fig-sub-graph}
-\caption{An optimal matching depicted by the dashed red edges,
-and another solution depicted by the solid green edges.
-The optimal stars are outlined.}
+\input{fig/fig-sub-graph}
+\vspace{-20pt}
+\caption{$M^*$ is depicted by the dashed red edges,
+and $M$ is depicted by the solid green edges.
+The optimal stars are outlined.
+}
 \end{subfigure}
@@
 %
-\begin{subfigure}[t]{.45\linewidth}
+\begin{subfigure}[b]{.51\linewidth}
 \centering
-\input{fig-sub-conflict}
-\caption{The star graph, each vertex corresponded to a star in the
-original graph.  The upper left vertex corresponds to the star that
-contains the vertices a,b,c.  The numbers inside the vertices
-corresponds to $d_i$.}
+\input{fig/fig-sub-conflict}
+\vspace{9pt}
+\caption{The star graph: each vertex corresponds to a star in $G$.
+The upper left vertex corresponds to the star that
+contains the vertices a,b,c.  }
 \end{subfigure}
@@
 
-In the Appendix~\ref{sec:tight} we show that our analysis is tight.
+In Appendix~\ref{sec:tight} we show that our analysis is tight.

### 2017-02-17 src/sub.tex
merge dror

@@
 time by computing a maximum $b$-matching in the bipartite graph $B =
-(S \cup V \setminus S, A \cap (V \setminus S) \times S)$ which can be
-done using an algorithm for \textsc{Minimum Cost Flow} as shown
+(V \setminus S, S, A \cap (V \setminus S) \times S)$ which can be done
+using an algorithm for \textsc{Minimum Cost Flow} as shown
 in~\cite{kutiel2016}.

### 2017-10-29 src/appendix.tex
merge dror
refactor figs ins
foo
sub figure

--- 2017-02-15 src/appendix.tex
@@
-%\newpage
-%\bigskip
+\newpage
 
@@
 %\label{sec:figures}
-
-\begin{figure}[h]
-\centering
-\input{fig-submodular}
-\caption[]{%
-Given the two solutions on the left, 
-\subref{sub:cup} and \subref{sub:cap}, we
-can construct the two solutions on the right side,
-\subref{sub:s} and \subref{sub:t}, with equal total weight.
-The edges of type 
-\inlineedge{e1}, 
-\inlineedge{e2}, 
-\inlineedge{e3}, 
-\inlineedge{e5}, 
-\inlineedge{e6}
-from the left side are ``naturally'' distributed over the two solutions on the
-right side and the edges of type \inlineedge{e4} can be distributed between the
-two solutions without violating the capacity constraints.
-}
-\label{fig:sub}
-\end{figure}
 
@@
 
-\medskip
+\newpage
 
@@
 \begin{center}
-\scalebox{.85}{\input{fig-local-tight}}
+\scalebox{.9}{
+\input{fig-local-tight}
+}
 \caption{A tight example for Corollary~\ref{cor:local}. 

### 2017-10-29 src/sub.tex
sub figure

@@
 
+\begin{figure}[h]
+\centering
+\input{fig-submodular}
+\caption[]{%
+Given the two solutions on the left, 
+\subref{sub:cup} and \subref{sub:cap}, we
+can construct the two solutions on the right side,
+\subref{sub:s} and \subref{sub:t}, with equal total weight.
+The edges of type 
+\inlineedge{e1}, 
+\inlineedge{e2}, 
+\inlineedge{e3}, 
+\inlineedge{e6}
+from the left side are ``naturally'' distributed over the two solutions on the
+right side and the edges of type \inlineedge{e5} and \inlineedge{e4} can be
+distributed between the two solutions without violating the capacity constraints.
+}
+\label{fig:sub}
+\end{figure}
+
 Buchbinder et al.~\cite{BFNS15,buchbinder2016deterministic} presented

### 2017-10-29 src/appendix.tex
thm8

@@
 \label{sec:omitted}
-
-\begin{proof}[Proof of Theorem~\ref{thm:improve}]
-Define the weight function $w'(e)
-= \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}$, where
-$w_{\max} \eqdf \max_{e \in A} w(v)$.
-%
-Let $M^*$ and $M'$ be an optimal carpool matchings with respect to $w$
-and $w'$, resp.  We have that
-\[
-w'(M^*)
-=    \sum_{e \in M^*} \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}
->    \sum_{e \in M^*} \paren{ \frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps} } - m
-=    \frac{m}{2\eps w_{\max}} \cdot w(M^*) - m
-~.
-\]
-Since $w(M^*) \geq w_{\max}$, we have that 
-\[
-\textstyle
-w'(M^*)
->    \frac{m}{2\eps w_{\max}} \cdot (w(M^*) - 2\eps w_{\max})
-\geq \frac{m}{2\eps w_{\max}} \cdot (1 - 2\eps) w(M^*)
-~.
-\]
-By Theorem~\ref{thm:improve-bounded}, our local improvement algorithm computes a
-$\half$-approximate carpool matching $M$ on $(G, c, w')$, and this
-matching satisfies $w'(M) \geq w'(M')/2$.  Furthermore, since
-$w'(M') \geq w'(M^*)$, it follows that $w'(M) \geq w'(M^*)/2$.
-Therefore
-\[
-\textstyle
-w(M)
-\geq \frac{2\eps w_{\max}}{m} w'(M) 
-\geq \frac{1}{2} \frac{2\eps w_{\max}}{m} w'(M^*)
->    \frac{1-2\eps}{2} w(M^*)
-~,
-\]
-as required.
-\end{proof}
 

### 2017-10-29 src/improve.tex
refactoring
thm8

@@
 It remains to consider the case, where weight are not polynomially
-bounded.  In Appendix~\ref{sec:omitted} we prove that one can use
+bounded. 
+We prove that one can use
 standard scaling and rounding to ensure a polynomial running time in
@@
 \end{theorem}
+
+\begin{proof}[Proof of Theorem~\ref{thm:improve}]
+Define the weight function $w'(e)
+= \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}$, where
+$w_{\max} \eqdf \max_{e \in A} w(v)$.
+%
+Let $M^*$ and $M'$ be an optimal carpool matchings with respect to $w$
+and $w'$, resp.  We have that
+\[
+w'(M^*)
+=    \sum_{e \in M^*} \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}
+>    \sum_{e \in M^*} \paren{ \frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps} } - m
+=    \frac{m}{2\eps w_{\max}} \cdot w(M^*) - m
+~.
+\]
+Since $w(M^*) \geq w_{\max}$, we have that 
+\[
+\textstyle
+w'(M^*)
+>    \frac{m}{2\eps w_{\max}} \cdot (w(M^*) - 2\eps w_{\max})
+\geq \frac{m}{2\eps w_{\max}} \cdot (1 - 2\eps) w(M^*)
+~.
+\]
+By Theorem~\ref{thm:improve-bounded}, our local improvement algorithm computes a
+$\half$-approximate carpool matching $M$ on $(G, c, w')$, and this
+matching satisfies $w'(M) \geq w'(M')/2$.  Furthermore, since
+$w'(M') \geq w'(M^*)$, it follows that $w'(M) \geq w'(M^*)/2$.
+Therefore
+\[
+\textstyle
+w(M)
+\geq \frac{2\eps w_{\max}}{m} w'(M) 
+\geq \frac{1}{2} \frac{2\eps w_{\max}}{m} w'(M^*)
+>    \frac{1-2\eps}{2} w(M^*)
+~,
+\]
+as required.
+\end{proof}

### 2017-10-29 src/appendix.tex
lemma12

@@
 \newpage
-
-\begin{proof}[Proof of Lemma~\ref{lemma:dec}]
-We give a constructive proof.
-%
-First, if $\ell \leq |V| \leq \Delta \ell$, then we are done.
-%
-Otherwise, we partition the graph recursively as follows.  Let $U
-= \emptyset$.  As long as $\abs{U} < \ell$, choose an arbitrary vertex
-$u$ such that $U \cup \set{u}$ is connected and add $u$ to $U$.
-%
-If the graph $G[V \setminus U]$, which is induced by $V \setminus U$,
-is connected, then choose the next vertex.
-%
-However, if $G[V \setminus U]$ becomes disconnected, then consider the
-maximal connected components of $G[V \setminus U]$.  Add the vertices
-of any maximal component that contains less than $\ell$ vertices to
-$U$.  Observe that afterwards $\abs{U} < \ell + (\Delta-1) \ell
-= \Delta \ell$.
-%
-If $\abs{U} \geq \ell$, then recursively partition any component of
-$G[V \setminus U]$ that contains more than $\ell$ vertices.
-%
-If $\abs{U} < \ell$, then there must exist at least one maximal
-component $C$ of $G[V \setminus U]$ that contains more than $\ell$
-vertices.  In this case recursively partition any maximal component of
-$G[V \setminus (U \cup C)]$ that contains more than $\ell$ vertices.
-Also, continue to augment $U$ in the graph $G[U \cup C]$.
-\end{proof}
 

### 2017-10-29 src/improve.tex
lemma12

@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:improve}]
+\begin{proof}
 Define the weight function $w'(e)

### 2017-10-29 src/local.tex
refactor figs ins
lemma12

@@
 \centering
-\input{fig/fig-sub-graph}
+\input{fig-sub-graph}
 \vspace{-20pt}
@@
 \centering
-\input{fig/fig-sub-conflict}
+\input{fig-sub-conflict}
 \vspace{9pt}
@@
 We first show that large connected graphs (or maximal connected
-components) can be partitioned in to medium size components.  The
-proof is given in Appnedix~\ref{sec:omitted}.
+components) can be partitioned in to medium size components.
 
@@
 \end{lemma}
+
+\begin{proof}
+We give a constructive proof.
+%
+First, if $\ell \leq |V| \leq \Delta \ell$, then we are done.
+%
+Otherwise, we partition the graph recursively as follows.  Let $U
+= \emptyset$.  As long as $\abs{U} < \ell$, choose an arbitrary vertex
+$u$ such that $U \cup \set{u}$ is connected and add $u$ to $U$.
+%
+If the graph $G[V \setminus U]$, which is induced by $V \setminus U$,
+is connected, then choose the next vertex.
+%
+However, if $G[V \setminus U]$ becomes disconnected, then consider the
+maximal connected components of $G[V \setminus U]$.  Add the vertices
+of any maximal component that contains less than $\ell$ vertices to
+$U$.  Observe that afterwards $\abs{U} < \ell + (\Delta-1) \ell
+= \Delta \ell$.
+%
+If $\abs{U} \geq \ell$, then recursively partition any component of
+$G[V \setminus U]$ that contains more than $\ell$ vertices.
+%
+If $\abs{U} < \ell$, then there must exist at least one maximal
+component $C$ of $G[V \setminus U]$ that contains more than $\ell$
+vertices.  In this case recursively partition any maximal component of
+$G[V \setminus (U \cup C)]$ that contains more than $\ell$ vertices.
+Also, continue to augment $U$ in the graph $G[U \cup C]$.
+\end{proof}
 

### 2017-10-29 src/appendix.tex
coro15

@@
 \label{sec:tight}
-
-We now show that Corollary~\ref{cor:local} is tight.  Consider the
-example in Figure~\ref{fig:local search tight}, the example is for the
-special case when $k = 11$ and $\cmax = 2$ but this example can be
-generalized in a straightforward manner.  One can verify that as the
-graph in the example growth, the ratio between the optimal solution
-and the local search solution approaches $\frac{3}{4}$.
-
-\begin{figure}[h]
-\begin{center}
-\scalebox{.9}{
-\input{fig-local-tight}
-}
-\caption{A tight example for Corollary~\ref{cor:local}. 
-The optimal solution is given by the red solid arcs while the local
-search solution is given by the green, dashed arcs.  The solution can
-be improved by the local search algorithm only if it removes all the
-edges.}
-\label{fig:local search tight}
-\end{center}
-\end{figure}

### 2017-10-29 src/local.tex
coro15

@@
 
-In Appendix~\ref{sec:tight} we show that our analysis is tight.
+We now show that Corollary~\ref{cor:local} is tight.  
+Consider the
+example in Figure~\ref{fig:local search tight}, the example is for the
+special case when $k = 11$ and $\cmax = 2$ but this example can be
+generalized in a straightforward manner.  One can verify that as the
+graph in the example growth, the ratio between the optimal solution
+and the local search solution approaches $\frac{3}{4}$.
+
+\begin{figure}[h]
+\begin{center}
+\scalebox{.9}{
+\input{fig-local-tight}
+}
+\caption{A tight example for Corollary~\ref{cor:local}. 
+The optimal solution is given by the red solid arcs while the local
+search solution is given by the green, dashed arcs.  The solution can
+be improved by the local search algorithm only if it removes all the
+edges.}
+\label{fig:local search tight}
+\end{center}
+\end{figure}

### 2017-11-02 src/carpool.tex
dror

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{microtype}

\usepackage{amsmath,amssymb,mathtools,amsthm}
%\usepackage[linesnumbered, ruled]{algorithm2e}
\usepackage[vlined,linesnumbered,ruled]{algorithm2e}
\usepackage{xspace}
\usepackage{paralist}
\usepackage{subcaption}

%\usepackage{color,soul}

%\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}

%\usepackage{refcheck}

%\renewcommand{\floatpagefraction}{0.8}

\parskip = \smallskipamount

\sloppy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% handy theorems

\newtheorem{lemma}{Lemma}
\newtheorem{observation}[lemma]{Observation}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{property}{Property}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}

%\spnewtheorem{observation}{Observation}{\bfseries}{\itshape}

%\theoremstyle{plain}
%\newtheorem{observation}[theorem]{Observation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\eqdf}{\triangleq}
\newcommand{\half}{\frac{1}{2}}
\newcommand{\inv}[1]{\frac{1}{#1}}
\newcommand{\inlineedge}[1]{
\tikz[baseline=-0.5ex, very thick, ->] \draw[#1] (0,0) -- (1,0);
}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\def\R{\mathbb{R}}
\def\N{\mathbb{N}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\din}[1][M]{d^{\text{in}}_{#1}}
\newcommand{\dout}[1][M]{d^{\text{out}}_{#1}}
\newcommand{\dinout}[1][M]{d_{#1}}

\newcommand{\nin}[1][M]{N^{\text{in}}_{#1}}
\newcommand{\nout}[1][M]{N^{\text{out}}_{#1}}
\newcommand{\ninout}[1][M]{N_{#1}}

\newcommand{\carpool}{\textsc{Maximum Carpool Matching}\xspace}
\newcommand{\gcp}{\textsc{Maximum Group Carpool Matching}\xspace}

\newcommand{\cmax}{c_{\max}}
\newcommand{\barw}{\bar{w}}
\newcommand{\eps}{\varepsilon}
\newcommand{\inc}{\Gamma}

\newcommand{\calS}{\mathcal{S}}
\newcommand{\calT}{\mathcal{T}}
\newcommand{\calX}{\mathcal{X}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{tikz}
\usetikzlibrary{
	arrows.meta,
	calc,
	graphs,
	patterns,
	positioning,
	shapes,
	decorations.pathmorphing,
	math,
}

% NODE
\tikzset{default node/.style={draw,circle,inner sep=0mm,minimum size=5mm,very thick,font=\small,black!70,}}

% LABELS
\tikzset{label/.style={draw=none,sloped,}}
\tikzset{label above/.style={label,midway,above=-1mm,}}
\tikzset{label below/.style={label,midway,below=-1mm,}}

% EDGES
\tikzset{e1/.style={cyan}}
\tikzset{e2/.style={green, loosely dash dot dot}}
\tikzset{e3/.style={blue, loosely dotted}}
\tikzset{e4/.style={loosely dashed}}
\tikzset{e5/.style={red, loosely dashed}}
\tikzset{e6/.style={orange, loosely dash dot}}

% LINES
\tikzset{m/.style={blue, dashed}}
\tikzset{outline/.style={loosely dashed, ultra thin}}

%DEFAULT STYLE
\tikzset{
	>=Triangle[], 
	on grid, 
	auto, 
	thick,
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{%
%
\textbf{Local Search Algorithms for the \\ Maximum Carpool Matching
  Problem}%
%
\thanks{A preliminary version was presented at the 25th Annual
  European Symposium on Algorithms, 2017}
%
}

\author{%
Gilad Kutiel%
\thanks{Department of Computer Science, Technion, Haifa 32000, Israel.} \\
\texttt{gkutiel@cs.technion.ac.il}
\and
Dror Rawitz%
\thanks{Faculty of Engineering, Bar Ilan University, Ramat Gan 52900, Israel.
Supported in part by the Israel Science Foundation (grant no.~497/14).} \\
\texttt{dror.rawitz@biu.ac.il}
}

\begin{titlepage}

\maketitle

\begin{abstract}
The \carpool problem is a \emph{star packing} problem in directed
graphs.  Formally, given a directed graph $G = (V, A)$, a capacity
function $c: V \rightarrow \N$, and a weight function $w:
A \rightarrow \R^+$, a \emph{carpool matching} is a subset of arcs,
$M \subseteq A$, such that every $v \in V$ satisfies:%
\begin{inparaenum}[(i)]
\item $\din[M](v) \cdot \dout[M](v) = 0$,
\item $\din[M](v) \leq c(v)$, and 
\item $\dout[M](v) \leq 1$.
\end{inparaenum}
A vertex $v$ for which $\dout[M](v) = 1$ is a \emph{passenger}, and a
vertex for which $\dout[M](v) = 0$ is a \emph{driver} who has
$\din[M](v)$ passengers.  In the \carpool problem the goal is to find
a carpool matching $M$ of maximum total weight.
%
The problem arises when designing an online carpool service, such as
Zimride~\cite{zimride}, which tries to connect between users based on
a similarity function.  The problem is known to be NP-hard, even in
the unweighted and uncapacitated case.
%
The \gcp problem, is an extension of the \carpool where each vertex
represents an unsplittable group of passengers.  Formally, each vertex
$u \in V$ has a size $s(u) \in \N$, and the constraint $\din(v) \leq
c(v)$ is replaced with $\sum_{u:(u,v) \in M} s(u) \leq c(v)$.

We show that \carpool can be formulated as an unconstrained submodular
maximization problem, thus it admits a $\frac{1}{2}$-approximation
algorithm.  We show that the same formulation does not work for \gcp,
nevertheless, we present a local search $(\frac{1}{2}
- \eps)$-approximation algorithm for \gcp.
%
For the unweighted variant of both problems when the maximum possible
capacity, $\cmax$, is bounded by a constant, we provide a local search
$(\half + \inv{2\cmax} - \eps)$-approximation algorithm.  We also
provide an APX-hardness result, even if the maximum degree and $\cmax$
are at most $3$.
\end{abstract}

%\subjclass{F.2.2 Nonnumerical Algorithms and Problems}

\medskip
\noindent
\textbf{Keywords:} approximation algorithms, local search, star
packing, submodular maximization.

\thispagestyle{empty}
\end{titlepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

As traveling costs become higher and parking becomes sparse it is only
natural to share rides or to \emph{carpool}.  Originally, carpooling
was an arrangement among a group of people by which they take turns
driving the others to and from a designated location.  However, taking
turns is not essential, instead passengers can share the cost of the
ride with the driver.  Carpooling has social advantages other than
reducing the costs: it reduces fuel consumption and road congestion
and frees parking space.  
%
While in the past carpooling was usually a fixed arrangement between
friends or neighbors, the emergence of social networks has made
carpooling more dynamic and wide scale.  These days applications like
Zimride~\cite{zimride}, BlaBlaCar~\cite{blablacar},
Moovit~\cite{moovit} and even Waze~\cite{waze} are matching passengers
to drivers.

The matching process of passengers to drivers entails more than
matching the route.
%
Passenger satisfaction also need to be taken into account.  Given
several riding options (including taking their own car), passengers
have preferences.  For example, a passenger may prefer to ride with a
co-worker or a friend.  A passenger may have an opinion on a driver
that she rode with in the past.  She may prefer a non-smoker, someone
who shares her taste in music, or someone who is recommended by
others.
%
Moreover, the matching process may take into account driver
preferences.  For instance, we would like to minimize the extra
distance that a driver has to take.
%
Preferences may also be computed using past information.  Knapen et
al.~\cite{knapen2013estimating} described an automatic service to
match commuting trips.  Users of the service register their personal
profile and a set of periodically recurring trips, and the service
advises registered candidates on how to combine their commuting trips
by carpooling.  The service estimates the probability that a person
$a$ traveling in person's $b$ car will be satisfied by the trip.  This
is done based on personal information and feedback from users on past
rides.

In this paper we assume that potential passenger-driver satisfactions
are given as input and the goal is to compute an assignment of
passengers to drivers so as to maximize the global satisfaction.
%
More formally, we are given a directed graph $G = (V, A)$, where each
vertex $v \in V$ corresponds to a user of the service, and an arc $(u,
v)$ exists if the user corresponding to vertex $u$ is willing to
commute with the user corresponding to vertex $v$.  We are given a
capacity function $c: V \rightarrow \N$ which bounds the number of
passengers each user can drive if she is selected as a driver.  A
non-negative weight function $w : A \rightarrow \R^+$ is used to model
the amount of satisfaction $w(u,v)$ of assigning $u$ to $v$.
%
If $(u,v) \in A$ implies that $(v,u) \in A$ and $w(u,v) = w(v,u)$, the
instance is \emph{undirected}.  If $w(v,u) = 1$, for every $(v,u) \in
A$, then the instance is \emph{unweighted}.  If $c(v) = \deg(v)$, for
every $v$, then the instance is \emph{uncapacitated}.

Given a directed graph $G$ and a subset $M \subseteq A$, define
\(
\din[M](v) \eqdf \abs{\set{u :(u,v) \in M}}
\)
and
\(
\dout[M](v) \eqdf \abs{\set{u :(v,u) \in M}}
%~.
\).
%
A feasible \emph{carpool matching} is a subset of arcs, $M \subseteq
A$, such that every $v \in V$ satisfies:%
\begin{inparaenum}[(i)]
\item $\din[M](v) \cdot \dout[M](v) = 0$,
\item $\din[M](v) \leq c(v)$, and 
\item $\dout[M](v) \leq 1$.
\end{inparaenum}
A feasible carpool matching $M$ partitions $V$ as follows:
\begin{align*}
P_M & \eqdf \set{v : \dout[M](v) = 1} \\
D_M & \eqdf \set{v : \din[M](v) \geq 1} \\
Z_M & \eqdf \set{v : \dout[M](v) = \din[M](c) = 0}
%~,
\end{align*}
where $P_M$ is the set of \emph{passengers}, $D_M$ is the set of
\emph{active drivers}, and $Z_M$ is the set of \emph{solo drivers}.
%
In the \carpool problem the goal is to find a matching $M$ of maximum
total weight, namely to maximize $w(M) \eqdf \sum_{(v,u) \in M}
w(v,u)$.  In other words, the \carpool problem is about finding a set
of (directed toward the center) vertex disjoint stars that maximizes
the total weight of the arcs.  
%
Figure~\ref{fig:carpool} contains an example of a \carpool instance.
%
Note that in the unweighted case the goal is to find a carpool
matching $M$ that maximizes $\abs{P_M}$.
%
Moreover, observe that if $G$ is undirected, $D_M \cup Z_M$ is
a \emph{dominating set}.  Hence, in this case, an optimal carpool
matching induces an optimal dominating set and vice versa.
Since \textsc{Minimum Dominating Set} is NP-hard, it follows
that \carpool is NP-hard even if the instance is undirected,
unweigthed, and uncapacitated.

\begin{figure}[t]
\centering
\newcommand{\edge}[3]{
	\draw (#1) -- (#2) node[label above] {#3};
}

\begin{subfigure}[t]{.45\linewidth}
\centering
\begin{tikzpicture}[every node/.style={default node}, ->, very thick]

\node(1) at(-1,3) {2};
\node(2) at(.5,.5) {3};
\node(3) at(-.9,-.3) {1};
\node(4) at(-1,1) {2};
\node(5) at(-2,2) {0};
\node(6) at(-2,-1) {4};
\node(7) at(-3,0) {3};
\node(8) at(.5,-1) {2};
\node(9) at(0,2) {1};
\node(10) at(2,1) {4};

\edge{1}{4}{3}
\edge{2}{4}{4}
\edge{3}{4}{5}

\edge{5}{7}{2}
\edge{6}{7}{4}

\edge{8}{10}{6}
\edge{9}{10}{2}

\edge{1}{5}{4}
\edge{4}{5}{4}

\edge{2}{3}{2}
\edge{6}{3}{2}
\edge{7}{3}{2}

\edge{8}{2}{1}
\edge{10}{2}{1}

\edge{3}{8}{3}
\edge{8}{3}{3}

\edge{1}{9}{1}
\edge{4}{9}{1}

\end{tikzpicture}
\caption{An instance containing a directed graph with capacities on
  the vertices and weights on the arcs. }
\end{subfigure}
%
\hfill
%
\begin{subfigure}[t]{.5\linewidth}
\centering
\begin{tikzpicture}[every node/.style={default node}, ->, very thick]

\node[dotted](1) at(-1,3) {2};

\begin{scope}[every node/.style={default node, draw=blue}]
\node(5) at(-2,2) {0};
\node(6) at(-2,-1) {4};

\node(2) at(.5,.5) {3};
\node(3) at(-.9,-.3) {1};

\node(8) at(.5,-1) {2};
\node(9) at(0,2) {1};
\end{scope}

\begin{scope}[every node/.style={default node, draw=red, dashed}]
\node(7) at(-3,0) {3};

\node(4) at(-1,1) {2};

\node(10) at(2,1) {4};
\end{scope}

\edge{2}{4}{4}
\edge{3}{4}{5}

\edge{5}{7}{2}
\edge{6}{7}{4}

\edge{8}{10}{6}
\edge{9}{10}{2}

\end{tikzpicture}
\caption{A feasible carpool matching with total weight
of 23.  $P_M$ is the set of blue vertices, and $D_M$ is the set of
red, dashed vertices, and $Z_M$ contains only the dotted, black
vertex.}
\end{subfigure}
\caption[]{
\label{fig:carpool}
A \carpool example.
%(\subref{carpool:input}) an instance containing a
%directed graph with capacities on the vertices and weights on the
%arcs.  (\subref{carpool:output}) a feasible matching with total weight
%of 23.  $P_M$ is the set of blue vertices, and $D_M$ is the set of
%red, dashed vertices, and $Z_M$ contains only the dotted, black
%vertex.
}
\end{figure}

%In this paper
%
We also consider an extension of \carpool, called \gcp, in which each
vertex represents a group of passengers, and each group may have a
different size.  Such a group may represent a family or two friends
traveling together.  Formally, each vertex $u \in V$ has a size
$s(u) \in \N$, and the constraint $\din[M](v) \leq c(v)$ is replaced
with the constraint $\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
%
Notice that \textsc{Knapsack} is the special case where only arcs
directed at a single vertex have non-zero (integral) weights.

%%%%%

\paragraph*{Related work.}
%
Agatz et al.~\cite{agatz2012optimization} outlined the optimization
challenges that arise when developing technology to support
ride-sharing and survey the related operations research models in the
academic literature.
%
Hartman et al.~\cite{hartman2014theory} designed several heuristic
algorithms for the \carpool problem and compared their performance on
real data.  Other heuristic algorithms were developed by Knapen et
al.~\cite{knapen2014exploiting}.
%
Hartman~\cite{hartman2013optimal} proved that the \carpool problem is
NP-hard even in the case where the weight function is binary and
$c(v) \leq 2$ for every $v \in V$.  In addition, Hartman presented a
natural integer linear program and showed that if the set of drivers
is known, then an optimal assignment of passengers to drivers can be
found in polynomial time using a reduction to \textsc{Network Flow}
(see also~\cite{kutiel2017}.)
%
Kutiel~\cite{kutiel2017} presented a $\frac{1}{3}$-approximation
algorithm for \carpool that is based on a \textsc{Minimum Cost Flow}
computation and a local search $\half$-approximation algorithm for the
unweighted variant of \carpool.  The latter starts with an empty
matching and tries to improve the matching by turning a single
passenger into a driver.

Nguyen et al.~\cite{nguyen2008approximating} considered the
\textsc{Spanning Star Forest} problem.  A \emph{star forest} is a
graph consisting of vertex-disjoint star graphs.  In the
\textsc{Spanning Star Forest} problem, we are given an undirected
graph $G$, and the goal is to find a spanning subgraph which is a star
forest that maximizes the weight of edges that are covered by the star
forest.  Notice that this problem is equivalent to \carpool on
undirected and uncapacitated instances.  We also note that if all
weights leaving a vertex are the same, then the instance is referred
to as vertex-weighted.
%
Nguyen et al.~\cite{nguyen2008approximating} provided a PTAS for
unweighted planner graphs and a polynomial-time
$\frac{3}{5}$-approximation algorithm for unweighted graphs.  They
gave an exact optimization algorithm for weighted trees, and used it
on a maximum spanning tree of the input graph to obtain a
$\frac{1}{2}$-approximation algorithm for weighted graphs.  They also
shows that it is NP-hard to approximate unweighted \textsc{Spanning
Star Forest} within a ratio of $\frac{259}{260}+\eps$, for any
$\eps>0$.
%
%They also showed how to apply the spanning star forest model to
%aligning multiple genomic sequences over a tandem duplication region.
%
Chen et al.~\cite{CENRRS13} improved the approximation ratio for
unweighted graphs from $\frac{3}{5}$ to $0.71$ and gave a
$0.64$-approximation algorithm for vertex weighted graphs.  They also
showed that the edge- and vertex-weighted problem cannot be
approximated to within a factor of $\frac{19}{20} + \eps$, and
$\frac{31}{32} + \eps$, resp., for any $\eps > 0$, assuming that
$\text{P} \neq \text{NP}$.
%
Chakrabarty and Goel~\cite{ChakrabartyGoel10} improved the lower bounds
to $\frac{10}{11} + \eps$ and $\frac{13}{14}$.

Athanassopoulos et al.~\cite{ACKK09} improved the ratio for the
unweighted case to $\frac{193}{240} \approx 0.804$.
%
They considered a natural family of \emph{local search} algorithms for
\textsc{Spanning Star Forest}.  Such an algorithm starts with the
solution where all vertices are star centers.  Then, it repeatedly
tries to turn $t \leq k$ from leaves to centers and $t+1$ centers to
leaves.  A change is made if it results in a feasible solution, namely
if each leave is adjacent to at least one center.  The algorithm
terminates when such changes are no longer possible.
%
Athanassopoulos et al.~\cite{ACKK09} showed that, for any $k$ and
$\eps \in (0,\inv{2(k+2)}]$, there exists an instance $G$ and a local
optima whose size is smaller than $(\half + \eps) \textsc{opt}$,
where \textsc{opt} is the size of the optimal spanning star forest.
We note that, for a given $k$, the construction of the above result
requires that the maximum degree of $G$ is at least $2(k+2)$.  Hence,
this result does not hold in graphs with maximum degree $\Delta$.

Arkin et al.~\cite{arkin2004approximations} considered
the \textsc{Maximum Capacitated Star Packing} problem.  In this
problem the input consists of a complete undirected graph with
non-negative edge weights and a capacity vector $c
= \set{c_1,\ldots,c_p}$, where $\sum_{i=1}^p c_i = \abs{V} - p$.  The
goal is to find a set of vertex-disjoint stars in $G$ of size
$c_1,\ldots,c_p$ of maximum total weight.  Arkin et
al.~\cite{arkin2004approximations} provided a local search algorithm
whose approximation ratio is $\inv{3}$, and a matching-based
$\half$-approximation algorithm for the case where edge weights
satisfy the triangle inequality.

Bar-Noy et al.~\cite{bar2015improved} considered the
\textsc{Minimum $2$-Path Partition} problem.
In this problem the input is a complete graph on $3k$ vertices with
non-negative edge weights, and the goal is to partition the graph into
disjoint paths of length 2.  This problem is the special case of the
undirected carpool matching where $c(v) = 2$, for every $v \in V$.
They presented two approximation algorithms, one for the weighted case
whose ratio is $0.5833$, and another for the unweighted case whose
ratio is $\frac{3}{4}$.

Another related problem is \textsc{$k$-Set Packing}, where one is
given a collection of weighted sets, each containing at most $k$
elements, and the goal is to find a maximum weight subcollection of
disjoint sets.  Chandra and Halld\'orsson~\cite{chandra2001greedy}
presented a $\frac{3}{2(k+1)}$-approximation algorithm for this
problem.
%
\carpool can be seen as a special case of \textsc{$k$-Set Packing}
with $k = \cmax + 1$.  Consider a subset of vertice $U$ of size at
most $k$.  Observe that each subset of vertices has an optimal
internal assignment of passenger to drivers.  Let the weight of this
assignment be the profit of $U$, denote by $p(U)$.  If $k = O(1)$,
$p(U)$ can be computed for every $U$ of size at most $k$ in polynomial
time.  The outcome is a \textsc{$k$-Set Packing} instance.  This leads
to a $\frac{3}{2(\cmax+2)}$-approximation algorithm
%for the case where
when $\cmax = O(1)$.

%%%%%

\paragraph*{Our contribution.}
%
Section~\ref{sec:approx} contains approximation algorithms
for \carpool.  First, in Section~\ref{sec:sub} we show that \carpool
can be formulated as an unconstrained submodular maximization problem,
thus it has a $\frac{1}{2}$-approximation algorithm due
to~\cite{BFNS15,buchbinder2016deterministic}.
%
We present a local search algorithm for \carpool which repeatedly
checks whether the current carpool matching can be improved by means
of a star centered at a vertex, and it terminates when such a step is
not possible.
%
The approximation ratio of this algorithm is $\half$ if weights are
polynomially bounded, and its ratio is $\half-\eps$ in general.

In Section~\ref{sec:cmax} we consider \carpool with bounded maximum
capacity.   
%
In Section~\ref{sec:hardness} we show that \carpool is APX-hard even
for undirected and unweighted instances with $\Delta \leq b$, for any
$b \geq 3$.
%
In Section~\ref{sec:local} we provide another local search algorithm,
whose approximation ratio is $\half + \inv{2\cmax} - \eps$, for any
$\eps>0$, for unweighted \carpool, where $\cmax \eqdf \max_{v \in V}
c(v)$.  Given a parameter $k$, our algorithm starts with the empty
carpool matching.  Then, it repeatedly tries to find a better matching
by replacing $t \leq k$ arcs in the current solution by $t+1$ arcs
that are not in the solution.
%
We show that our analysis is tight.
%
We also note that our algorithm falls within the local search family
defined in~\cite{ACKK09}.  However, on undirected and uncapaciated
instances we have that $\cmax = \Delta$, and as mentioned above the
result from~\cite{ACKK09} does not hold in bounded degree graphs.

Finally, Section~\ref{sec:group} discusses \gcp.  We show that the
unconstrained submodular maximization formulation for \carpool does
not work for \gcp.  We show, however, that this problem still admits a
$(\frac{1}{2} -\varepsilon)$-approximation algorithm by extending our
first local search algorithm.  In addition, we show that the second
local search algorithm generalizes to unweighted \gcp with the same
approximation ratio.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Approximation Algorithms}
\label{sec:approx}

We present two algorithms for \carpool: a $\frac{1}{2}$-approximation
algorithm that is based on formulating the problem as an unconstrained
submodular maximization problem and a local search $(\frac{1}{2} -
\varepsilon)$-approximation algorithm.  While the latter does not
improve upon the former, it will be shown (in Section~\ref{sec:group})
that it can be generalized to \gcp without decreasing the
approximation ratio.

%%%%%

\subsection{Submodular Maximization}
\label{sec:sub}

In this section we show that the \carpool problem can be formulated as
an unconstrained submodular maximization problem, and thus it has a
$\frac{1}{2}$-approximation algorithm due to Buchbinder et
al.~\cite{BFNS15,buchbinder2016deterministic}.

Given a \carpool instance $(G = (V,A), c, w)$, consider a subset
$S \subseteq V$.  Let $M(S)$ be a maximum weight carpool matching
satisfying $D_{M(S)} \subseteq S \subseteq V \setminus P_{M(S)}$,
namely $M(S)$ is the best carpool matching whose drivers belong to $S$
and whose passengers belong to $V \setminus S$.  In other words,
$M(S)$ is the maximum weight carpool matching that is a subset of
$A \cap (V \setminus S) \times S$.
%
Given $S$, the carpool matching $M(S)$ can be computed in polynomial
time by computing a maximum $b$-matching in the bipartite graph $B =
(V \setminus S, S, A \cap (V \setminus S) \times S)$ which can be done
using an algorithm for \textsc{Minimum Cost Flow} as shown
in~\cite{kutiel2017}.

Consider the function $\barw: 2^V \to \R$, where $\barw(S) \eqdf
w(M(S)) = \sum_{e \in M(S)} w(e)$.  Observe that $\barw(\emptyset)
= \barw(V) = 0$, and that $\barw$ is not monotone.
%
In the next lemma we prove that $\bar{w}$ is a \emph{submodular set
function}.  Recall that a function $f$ is submodular if $f(S) +
f(T) \geq f(S \cup T) + f(S \cap T)$ for every two sets $S$ and $T$ in
the domain of $f$.

\begin{lemma}
$\barw$ is submodular.
\end{lemma}
\begin{proof}
Consider any two subsets $S, T \subseteq V$.  We show that $\barw(S)
+ \barw(T) \geq \barw(S \cup T) + \barw(S \cap T)$.
%
Let $M(S \cup T)$ and $M(S \cap T)$ be optimal carpool matchings with
respect to $S \cup T$ and $S \cap T$.
%
To prove the lemma we construct two feasible carpool matchings $M_S$
and $M_T$ such that $M_S \subseteq (V \setminus S) \times S$,
$M_T \subseteq (V \setminus T) \times T$, and $M_S \cup M_T = M(S \cup
T) \cup M(S \cap T)$.
%
The lemma follows, since $\barw(S) \geq w(M_S)$ and $\barw(T) \geq
w(M_T)$.

First, add all the edges in $M(S \cup T)$ entering $S \setminus T$ to
$M_S$.  Similarly, add all the edges in $M(S \cup T)$ entering
$T \setminus S$ to $M_T$.  Observe that $\din[M_S](v) = \din[M(S \cup
T)](v) \leq c(v)$, for every $v \in S \setminus T$ and that
$\din[M_T](v) = \din[M(S \cup T)](v) \leq c(v)$, for every $v \in
T \setminus S$.
%
Next, add the edges in $M(S \cap T)$ leaving $T \setminus S$ to $S$
and add the edges in $M(S \cap T)$ leaving $S \setminus T$ to $T$.
%
It remains to distribute the edges leaving $V \setminus (S \cup T)$
and entering $S \cap T$ in both $M(S \cup T)$ and $M(S \cap T)$.  Note
that there may exist edges $(v,u)$, where $v \not\in S \cup T$, and
$u \in S \cap T$ such that $(v,u) \in M(S \cup T)$ and $M(S \cap T)$.
We refer to this edges as \emph{duplicate} edges.
%
We add all edges leaving $V \setminus (S \cup T)$ and entering $S \cap
T$ in $M(S \cap T)$ to $M_S$.  Notice that this is possible, since
after this addition we have that $\din[M_S](v) \leq \din[M(S \cap
T)](v) \leq c(v)$, for every vertex $v \in S \cap T$.
%
Then we add all duplicate edges in $M(S \cup T)$ to $M_T$.
%
The remaining edges are distributed between $M_S$ and $M_T$ without
violating capacities.  This can be done, since $\din[M(S \cup T)](v)
+ \din[M(S \cap T)](v) \leq 2c(v)$, for every $v \in S \cap T$.
%
Figure~\ref{fig:sub} contains a graphical representation of the above
edge distribution.
\end{proof}

\begin{figure}[t]
\centering
\def \sst {\draw[e1] (-2, -.5) -- (-.5, -.5);}
\def \tst {\draw[e2] (2, -.5) -- (.5, -.5);}

\def \os {\draw[e3] (-2, 1.5) -- (-2, .4);}
\def \cupst {\draw[e4] (-.5, 1.5) -- (-.5, .4);}
\def \capst {\draw[e5] (.5, 1.5) -- (.5, .4);}
\def \ot {\draw[e6] (2, 1.5) -- (2, .4);}

\begin{subfigure}{.48\linewidth}
\centering
\begin{tikzpicture}[very thick]

\begin{scope}[every node/.style={inner sep=.8cm}]
\node(s) at(-2,0) {$S$};
\node(st) at(0,0) {$S \cap T$};
\node(t) at(2,0) {$T$};
\end{scope}

\draw 
(s.west) to[out=90, in=172] 
(st.north) to[out=-8, in=90] 
(st.east) to[out=270, in=8]
(st.south) to[out=188, in=270]
(s.west)
;

\draw 
(t.east) to[out=90, in=8] 
(st.north) to[out=188, in=90] 
(st.west) to[out=270, in=172]
(st.south) to[out=-8, in=270]
(t.east)
;

\begin{scope}[->]
\os
\cupst
\ot
\end{scope}

\end{tikzpicture}
\caption{}
\label{sub:cup}
\end{subfigure}
%
\hfill
%
\begin{subfigure}{.48\linewidth}
\centering
\begin{tikzpicture}[very thick]

\begin{scope}[every node/.style={inner sep=.8cm}]
\node(s) at(-2,0) {$S$};
\node(st) at(0,0) {$S \cap T$};
\node(t) at(2,0) {$T$};
\end{scope}

\draw 
(s.west) to[out=90, in=172] 
(st.north) to[out=-8, in=90] 
(st.east) to[out=270, in=8]
(st.south) to[out=188, in=270]
(s.west)
;

\draw[outline] 
(st.south) to[out=-8, in=270]
(t.east) to[out=90, in=8] 
(st.north) 
;
\draw 
(st.north) to[out=188, in=90] 
(st.west) to[out=270, in=172]
(st.south)
;

\begin{scope}[->]
\os
\capst
\cupst
\tst
\end{scope}

\end{tikzpicture}
\caption{}
\label{sub:s}
\end{subfigure}
%
%
\begin{subfigure}{.48\linewidth}
\centering
\begin{tikzpicture}[very thick]

\begin{scope}[every node/.style={inner sep=.8cm}]
\node(s) at(-2,0) {$S$};
\node(st) at(0,0) {$S \cap T$};
\node(t) at(2,0) {$T$};
\end{scope}

\draw[outline] 
(st.south) to[out=188, in=270]
(s.west) to[out=90, in=172] 
(st.north)
;
\draw 
(st.north) to[out=-8, in=90] 
(st.east) to[out=270, in=8]
(st.south)
;

\draw[outline] 
(st.south) to[out=-8, in=270]
(t.east) to[out=90, in=8] 
(st.north)
;
\draw 
(st.north) to[out=188, in=90] 
(st.west) to[out=270, in=172]
(st.south)
;

\begin{scope}[->]
\sst
\capst
\tst
\end{scope}

\end{tikzpicture}
\caption{}
\label{sub:cap}
\end{subfigure}
%
\hfill
%
\begin{subfigure}{.48\linewidth}
\centering
\begin{tikzpicture}[very thick]

\begin{scope}[every node/.style={inner sep=.8cm}]
\node(s) at(-2,0) {$S$};
\node(st) at(0,0) {$S \cap T$};
\node(t) at(2,0) {$T$};
\end{scope}

\draw[outline] 
(st.south) to[out=188, in=270]
(s.west) to[out=90, in=172] 
(st.north)
;
\draw 
(st.north) to[out=-8, in=90] 
(st.east) to[out=270, in=8]
(st.south)
;

\draw 
(t.east) to[out=90, in=8] 
(st.north) to[out=188, in=90] 
(st.west) to[out=270, in=172]
(st.south) to[out=-8, in=270]
(t.east)
;

\begin{scope}[->]
\sst
\cupst
\ot
\end{scope}

\end{tikzpicture}
\caption{}
\label{sub:t}
\end{subfigure}
%
\caption[]{%
Given the two solutions on the left, 
\subref{sub:cup} and \subref{sub:cap}, we
can construct the two solutions on the right side,
\subref{sub:s} and \subref{sub:t}, with equal total weight.
The edges of type 
\inlineedge{e1}, 
\inlineedge{e2}, 
\inlineedge{e3}, 
\inlineedge{e6}
from the left side are ``naturally'' distributed over the two solutions on the
right side and the edges of type \inlineedge{e5} and \inlineedge{e4} can be
distributed between the two solutions without violating the capacity constraints.
}
\label{fig:sub}
\end{figure}

Buchbinder et al.~\cite{BFNS15,buchbinder2016deterministic} presented
a general $\half$-approximation algorithm for unconstrained
submodular maximization, thus we have the following theorem.

\begin{theorem}
There exists a polynomial time $\half$-approximation algorithm
for \carpool.
\end{theorem}

%%%%%

\subsection{A Star Improvement Algorithm}
\label{sec:improve}

In this section we give a local search $(\half-\eps)$-approximation
algorithm for \carpool.  This algorithm repeatedly checks whether the
current carpool matching $M$ can be improved by means of a star
centered at a vertex $v$.  The profit from this star is the total
weight of the arcs in the star, and the cost is the total weight of
lost arcs (e.g., arcs from passengers to drivers that became
passengers of $v$).  If the profit is larger than the cost, then an
improvement step is performed.  The algorithm terminates when such a
step is not possible.
%
We remind the reader that this algorithm will be extended to \gcp in
Section~\ref{sec:group}.

We need a few definitions before presenting our algorithm.
%
Given a directed graphs $G = (V,A)$, define $\nin[] \eqdf \set{u :
(u,v) \in A}$ and $\nout[] \eqdf \set{u : (v,u) \in A}$.
%
Let $M$ be a feasible carpool matching.  The weight $w_M(v)$ of a
vertex $v$ with respect to $M$ is the sum of the weights of the arcs
in $M$ that are incident on $v$, namely
\[
\textstyle
w_M(v)
\eqdf w(M \cap \nin[]) + w(M \cap \nout[])
=     \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u)
~.
\]
For a subset of vertices $U \subseteq V$ we define
$w_M(U) \eqdf \sum_{v \in U} w_M(v)$.

We now argue that, with respect to any carpool matching $M$, the total
weight of all the vertices is equal to twice the weight of the matching.

\begin{observation}
\label{lm:val-twice}
$w_M(V) = 2 w(M)$.
%\sum_{v \in V} w_M(v) = 2 \sum_{e \in M} w(e)$.
\end{observation}
\begin{proof}
\(
\displaystyle
\sum_{v \in V} w_M(v)
= \sum_{v \in V} \sum_{(u, v) \in M} w(u, v) +
    \sum_{v \in V} \sum_{(v, u) \in M} w(v, u) 
= 2 \sum_{e \in M} w(e)
\).
\end{proof}

Denote by $\delta(u,v)$ the difference between the weight of the arc
and the weight of its source vertex, that is:
\[
\delta_M(u, v) \eqdf w(u, v) - w_M(u)
~.
\]
For a subset $S \subseteq A$ of arcs define
$\delta(S) \eqdf \sum_{(u,v) \in S} \delta(u,v)$.

A subset $S_v$ of arcs entering a vertex $v$, whose size is not
greater than the capacity of $v$, is called an \emph{improvement} to
vertex $v$ if $\delta(S_v)$ is greater than the value of $v$.  More
formally,

\begin{definition}
A subset $S_v \subseteq A \cap (V \times \{v\})$ is
an \emph{improvement} with respect to a carpool matching $M$, if%
%the following conditions hold:%
\begin{inparaenum}[(i)]
\item $\abs{S_v} \leq c(v)$, and
\item $\delta_M(S_v) > w_M(v)$.
\end{inparaenum}
Furthermore, if there exists an improvement for a vertex $v$, we say
that vertex $v$ can be \emph{improved}.
\end{definition}

Given an arc $(u,v) \in A$, let $\inc(u,v)$ be the set of arcs that
incident $(u, v)$, namely define
\(
\inc(u,v) \eqdf (\nin[](u) \times \{u\}) \cup (\{v\} \times \nout[](v))
%~.
\).
If $S$ is a set of arcs, then $\inc(S) \eqdf \bigcup_{(u,v) \in
S} \inc(u,v)$.
%
Figure~\ref{fig:defs} depicts all the above definitions.

\begin{figure}[t]
\centering
\begin{tikzpicture}[every node/.style={default node}]

\node(1) at(0,0) {1};
\node(2) at(2,0) {2};
\node(3) at(4,0) {3};

\node(4) at(.4,1.6) {4};
\node(5) at(2.4,1.6) {5};
\node(6) at(6, 0) {6};

\draw[m,->] (1) -- (2) node[label above]{$5$};
\draw[m,->] (4) -- (2) node[label above]{$2$};
\draw[m,<-] (3) -- (5) node[label above]{$2$};
\draw[->] (6) -- (3) node[label above]{$2$};
\draw[->] (2) -- (3) node[label above]{$8$};

\end{tikzpicture}
\caption{In this example $M$ is the set of the blue, dashed arcs.
In this case $w_M(2) = 7$, $w_M(5) = 2$, and $w_M(6) = 0$.  Also,
$\delta_M(2, 3) = 1$ and $\delta_M(6, 3) = 2$.  The set $\set{(2,3),
(6,3)}$ is an \emph{improvement} to vertex 3 and $\inc(2,3)
= \set{(1,2),(4,2),(3,5),(6,3)}$.}
\label{fig:defs}
\end{figure}

We are now ready to describe our local search algorithm, which is
called \textbf{StarImprove} (Algorithm~\ref{alg:grd}).  It starts with
an empty carpool matching $M$, and in every iteration it looks for a
vertex that can be improved.  If there exists such a vertex $v$, then
the algorithm removes the arcs that are incident on it from $M$, and
adds the arcs in $S_v$.  The algorithm terminates when no vertex can
be improved.  Figure~\ref{fig:improvement} depicts an improvement
step.

\begin{algorithm}
\caption{\textbf{StarImprove}$(G,c)$}
\label{alg:grd}
%\begin{small}
$M \gets \emptyset$ \\
\Repeat{$\text{done}$}{
	$\text{done} \leftarrow \textsc{True}$ \\
	\For{$v \in V$}{
		\If{there exists an improvement $S_v$}{
			$M \leftarrow M \setminus \inc(S_v) \cup S_v$	\\
			$\text{done} \leftarrow \textsc{False}$ \\
		}
	}
}
%\end{small}
\end{algorithm}

\begin{figure}[t]
\centering
\begin{subfigure}{.4\linewidth}
\centering
\begin{tikzpicture}[every node/.style={default node}]
\node(1) at(0,0) {1};
\node(2) at(2,0) {2};
\node(3) at(4,0) {3};

\node(4) at(.4,1.6) {4};
\node(5) at(2.4,1.6) {5};
\node(6) at(2.4, -1.6) {6};

\draw[m,->] (1) -- (2) node[label above]{$5$};
\draw[m,->] (4) -- (2) node[label above]{$2$};
\draw[m,<-] (3) -- (5) node[label above]{$2$};
\draw[->] (6) -- (3) node[label above]{$2$};
\draw[->] (2) -- (3) node[label above]{$8$};

\end{tikzpicture}
\caption{A matching that can be improved.}
\end{subfigure}
%
\hfill
%
\begin{subfigure}{.5\linewidth}
\centering
\begin{tikzpicture}[every node/.style={default node}]
\node(1) at(0,0) {1};
\node(2) at(2,0) {2};
\node(3) at(4,0) {3};

\node(4) at(.4,1.6) {4};
\node(5) at(2.4,1.6) {5};
\node(6) at(2.4, -1.6) {6};

\draw[->] (1) -- (2) node[label above]{$5$};
\draw[->] (4) -- (2) node[label above]{$2$};
\draw[<-] (3) -- (5) node[label above]{$2$};
\draw[m,->] (6) -- (3) node[label above]{$2$};
\draw[m,->] (2) -- (3) node[label above]{$8$};

\end{tikzpicture}
\caption{The matching after improving vertex 3.}
\end{subfigure}
\caption[]{An improvement example.}
\label{fig:improvement}
\end{figure}

We proceed to bound the approximation ratio of the algorithm, assuming
termination.

For a vertex $v$ and a set $S$ of edges entering $v$, let $\nin[S](v)
= \set{u : (u,v) \in S}$ be the set in-neighbors corresponding to $S$.

\begin{lemma}
\label{lm:no improve}
Let $M$ be a matching computed by \textbf{StarImprove}.  Let $v$ be a
vertex with no improvement, and let $S \subseteq \nin(v)$, such that
$\abs{S} \leq c(v)$, then $w(S) \leq w_M(v) + w_M(\nin[S](v))$.
\end{lemma}
\begin{proof}
If no improvement exists, then we have that 
\[
w(S) - w_M(\nin[S](v))
=    \sum_{(u,v) \in S} (w(u,v) - w_M(u))
=    \delta_M(S) 
\leq w_M(v)
~,
\]
as required.
\end{proof}

To bound the approximation ratio of the algorithm, we use a charging
scheme argument.

\begin{lemma}
If \textbf{StarImprove} terminates, then the computed solution is
$\half$-approximate.
\end{lemma}
\begin{proof}
Let $M$ be the matching produced by the algorithm, and let $M^*$ be an
optimal matching.  We load every vertex $v$ with an amount of money
equal to $w_M(v)$, and then we show that this is enough to pay for
every arc in the optimal matching.  Due to
Observation~\ref{lm:val-twice} the total amount of money that we use
is exactly twice the weight of $M$.

Consider a driver $v \in D_{M^*}$, and let $S = (V \times \{v\}) \cap
M^*$.  By lemma~\ref{lm:no improve} we know that $w(S) \leq w_M(v) +
w_M(\nin[S](v))$, thus we can pay for $S$, using the money on $v$ and
on $N^-_S(v)$.  Clearly, these vertices will not be charged again.
\end{proof}

We show that our analysis is tight using in Figure~\ref{fig:grd
worst}.

\begin{figure}[t]
\centering
\begin{tikzpicture}[every node/.style={default node}, <->]

\def\sep{1.5}

\foreach \n in {0,...,5}{
	\pgfmathsetmacro{\x}{\n * \sep}
	\node(\n) at(\x,0){};
}

\foreach \n/\m in {0/1,2/3,4/5}{
	\draw[m] (\n) -- (\m) node[label above]{1};
}

\foreach \n/\m in {1/2,3/4}{
	\draw[] (\n) -- (\m) node[label above]{2};
}

\pgfmathsetmacro{\x}{6 * \sep}
\node[draw=none] at(\x, 0){$\cdots$};

\foreach \n in {7,...,8}{
	\pgfmathsetmacro{\x}{\n * \sep}
	\node(\n) at(\x,0){};
}

\draw[m] (7) -- (8) node[label above]{1};

\end{tikzpicture}
\caption[]{%
Consider a path with $2n + 1$ arcs, and alternating arc weights (2 and
1), if \textbf{StarImprove} selects all arcs of weight 1, then no
further improvement can be done and the value of the matching is $n +
1$, while the optimal matching has value of $2n$.}
\label{fig:grd worst}
\end{figure}

It remains to consider the running time of the algorithm.

\begin{theorem}
\label{thm:improve-bounded}
Algorithm~\textbf{StarImprove} is a $\half$-approximation algorithm
for \carpool, if edge weights are integral and polynomially bounded.
\end{theorem}
\begin{proof}
First, observe that determining if a vertex $v$ can be improved can be
done efficiently by considering the incoming arcs to $v$ in a
non-increasing order of their $\delta_M$s, and only ones with positive
values.  A vertex $v$ can be improved, then, if the $\delta$s of the
first $c(v)$ (or less) arcs sum up to more than $w_M(v)$.
%
It follows that the running time of an iteration of the for-loop is
polynomial.  Since the edge weights are integral and polynomially
bounded, the weight of an optimal carpool matching is polynomially
bounded.  The algorithm runs in polynomial time, because in each
iteration the algorithm improves the weight of the matching by at
least one or otherwise it terminates.
\end{proof}

It remains to consider the case, where weight are not polynomially
bounded.  We prove that one can use standard scaling and rounding to
ensure a polynomial running time in the cost of a slight degradation
of the approximation ratio.

\begin{theorem}
\label{thm:improve}
There exists a $(\half-\eps)$-approximation algorithm for \carpool,
for every $\eps \in (0,\half)$.
\end{theorem}
\begin{proof}%[Proof of Theorem~\ref{thm:improve}]
Define the weight function $w'(e)
= \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}$, where
$w_{\max} \eqdf \max_{e \in A} w(v)$.
%
Let $M^*$ and $M'$ be an optimal carpool matchings with respect to $w$
and $w'$, resp.  We have that
\[
w'(M^*)
=    \sum_{e \in M^*} \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}
>    \sum_{e \in M^*} \paren{ \frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps} } - m
=    \frac{m}{2\eps w_{\max}} \cdot w(M^*) - m
~.
\]
Since $w(M^*) \geq w_{\max}$, we have that 
\[
w'(M^*)
>    \frac{m}{2\eps w_{\max}} \cdot (w(M^*) - 2\eps w_{\max})
\geq \frac{m}{2\eps w_{\max}} \cdot (1 - 2\eps) w(M^*)
~.
\]
By Theorem~\ref{thm:improve-bounded}, our local improvement algorithm computes a
$\half$-approximate carpool matching $M$ on $(G, c, w')$, and this
matching satisfies $w'(M) \geq w'(M')/2$.  Furthermore, since
$w'(M') \geq w'(M^*)$, it follows that $w'(M) \geq w'(M^*)/2$.
Therefore
\[
w(M)
\geq \frac{2\eps w_{\max}}{m} w'(M) 
\geq \frac{1}{2} \frac{2\eps w_{\max}}{m} w'(M^*)
>    \frac{1-2\eps}{2} w(M^*)
~,
\]
as required.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Constant Maximum Capacity}
\label{sec:cmax}
In this section we study the \carpool problem when the maximum
capacity is constant, i.e., when $\cmax = O(1)$.  We show that this
variant of the problem is APX-hard even for unweighted and undirected
instances.  We also describe and analyze a local search algorithm for
the unweighted variant of the problem, and show that the algorithm
achieves a $\half + \inv{2\cmax} - \eps$ approximation ratio, for any
$\varepsilon > 0$.

%%%%%

\subsection{Hardness}
\label{sec:hardness}

As we mentioned earlier, \textsc{Spanning Star Forest} has a lower
bound of $\frac{10}{11} + \eps$ for any $\eps > 0$, unless
P$=$NP~\cite{ChakrabartyGoel10}, and this bound applies to \carpool.
%
The result, however, does not hold for the case where $\Delta = O(1)$
(and $\cmax = O(1)$).  In this section we show that the problem remains
APX-hard even in this case.

Formally, the (unweighted) \textsc{Minimum Dominating Set} problem is
defined as follows.  The input is an undirected graph $G = (V,E)$, and
a feasible solution, or a \emph{dominating set}, is a subset
$D \subseteq V$ that dominates $V$ namely such that
$D \cup \bigcup_{v \in D} N(v) = V$, where $N(v)$ is the neighborhood
of $v$.  The goal is to find a minimum cardinality dominating set.
%
\textsc{Minimum Dominating Set-$b$} is the special case of
\textsc{Minimum Dominating Set} in which
the maximum degree of a vertex in the input graph $G$ is bounded by
$b$.  The problem was shown to be APX-hard, for $b \geq 3$, by
Papadimitriou and Yannakakis~\cite{PapYan88}.

We now consider the unweighted and undirected special case of
the \carpool problem.  In this case, the input consists of an
undirected graph $G$ and a capacity function $c$, and the goal is to
find a carpool matching $M$ that maximizes $\abs{P_M}$.

Given an undirected graph $G$, let $D^*$ be a minimum cardinality
dominating set, and let $M^*$ be an optimal carpool matching with
respect to $G$ and the capacity function: $c(v) = \deg(v)$, for every
$v \in V$.

\begin{observation}
$\abs{P_{M^*}} + \abs{D^*} = \abs{V}$ 
\end{observation}
\begin{proof}
Given a carpool matching $M$, observe that $D_M \cup Z_M$ is a
dominating set.  In the other direction, a dominating set $D$ induces
a carpool matching of size $\abs{V \setminus D}$.
\end{proof}

We use this duality to obtain a hardness result for \carpool.

\begin{theorem}
The \carpool problem is APX-hard, even for undirected and unweighted
instances with maximum degree bounded by $b$, for $b \geq 3$.
\end{theorem}
\begin{proof}
We prove the theorem by presenting an $L$-reduction from
\textsc{Minimum Dominating Set-$b$}.
(For details on $L$-reductions the reader is referred to~\cite{PapYan88}.)
%
We define a function $f$ from \textsc{Minimum Dominating Set-$b$}
instances to \carpool instances as follows: $f(G) = (G,c)$, where
$c(v) = \deg(v)$, for every $v \in V$.  Next, we define a function $g$
that given a carpool matching computes a dominating set as follows:
$g(M) = V \setminus P_{M}$.  Both $f$ and $g$ can be computed in
polynomial time.

Let $D^*$ be an optimal dominating set with respect to $G$, and let
$M^*$ be an optimal carpool matching with respect to $G$ and $c$.
Since $|D^*| \geq \frac{|V|}{b+1}$, it follows that 
\(
\abs{P_{M^*}} \leq b \abs{D^*}
%~,
\),
In addition, if $M$ is a carpool matching, we have that
\[
\abs{D_M \cup Z_M} - \abs{D^*}
= (\abs{V} - \abs{P_M}) - \abs{D^*}
= \abs{P_{M^*}} - \abs{P_M}
~.
\]
Hence, there is an $L$-reduction from \textsc{Minimum Dominating
Set-$b$} to unweighted and undirected \carpool with bounded capacity
$b$.
\end{proof}

%%%%%

\subsection{Local Search}
\label{sec:local}

In this section we present a local search $(\half + \inv{2c_{\max}} -
\eps)$-approximation algorithm for unweighted \carpool whose running
time is polynomial if $c_{\max} = O(1)$.

Let $k$ be a constant integer to be determined later.
Algorithm~\textbf{EdgeSwap} (Algorithm~\ref{alg:local}) maintains a
feasible matching $M$ throughout its execution and operates in
iterative manner where in each iteration it tries to find a better
solution by replacing a subset of at most $k$ edges in the current
solution with another (larger) subset of edges not in the solution.
The algorithm halts when no improvement can be done.

\begin{algorithm}
\caption{\textbf{EdgeSwap}$(G,c,k)$}
\label{alg:local}
%\begin{small}
\SetKw{True}{true}
\SetKw{False}{false}
%\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
%\KwOut{$M$}
$M \leftarrow \emptyset$								\\
\Repeat{done}{
 	$done \leftarrow{}$ \True							\\
 	\ForAll{$M' \subseteq M : |M'| \leq k$}{
 		\ForAll{$A' \subseteq A \setminus M : |A'| = |M'| + 1$}{
			\If{$M \setminus M' \cup A'$ is feasible}{
				$M \leftarrow{} M \setminus M' \cup A'$	\\
				$done \leftarrow{}$ \False				\\
			}
		}
 	}
}
\Return{$M$}
%\end{small}
\end{algorithm}

Algorithm~\textbf{EdgeSwap} terminates in polynomial time, since in
every non-final iteration it improves the value of the solution by
one.  Thus, after at most $n$ iterations the algorithm terminates.  In
every iteration the algorithm examines all subsets of edges of a fixed
size and tests for feasibility, both these operations can be done in
polynomial time.

Observe that a vertex $v \in D_M \cup Z_M$ is the center of
a \emph{directed star} whose leaves are the passengers in the set
$P_M(v) = \set{u : (u,v) \in M}$
($P_M(v) = \emptyset$, for $v \in Z_M$).
%
Given a carpool matching $M$, we define $\calS(M)$ to be the set of
stars that are induced by $M$.  Denote by $V(S)$ the set of vertices
of a star, i.e., if $v$ is the center of $S$, then $V(S) = \{v\} \cup
P_M(v)$.  Also, let $A(S)$ be the arcs of $S$.  For
$\calT \subseteq \calS(M)$, define
$V(\calT) \eqdf \bigcup_{S \in \calT} V(S)$ and
$A(\calT) \eqdf \bigcup_{S \in \calT} A(S)$.

It remains to analyze the approximation ratio of \textbf{EdgeSwap}.
Consider an optimal matching $M^*$, and $M$ be the matching computed
by \textbf{EdgeSwap}.  Given both matchings we build the \emph{star
  graph} of the two solutions in which each vertex represents a star
from the optimal solution, namely from $\calS(M^*)$, and an edge
exists between two vertices if there is a star in $\calS(M)$ that
intersects the two corresponding stars of the optimal solution.
%
Formally $H = (\calS(M^*), E)$ where
\[
E = \set{(S^*_i, S^*_j) : \exists S \in \calS(M), 
         V(S) \cap V(S^*_i) \neq \emptyset \land
         V(S) \cap V(S^*_j) \neq \emptyset}
~.
\]
Figure~\ref{fig:conflict} depicts a star graph.

\begin{figure}[t]
%\centering
%
\begin{subfigure}[b]{.47\linewidth}
\centering
\newcommand{\edge}[2]{
	\draw (#1) -- (#2);
}

\begin{tikzpicture}[every node/.style={default node}, ->, very thick]

\node(1) at(0,0) {a};
\node(2) at(0,1.5) {b};
\node(3) at(1.5,0) {c};

\node(4) at(4,0) {d};
\node(5) at(4,1.5) {e};
\node(6) at(2.5,0) {f};

\node(7) at(0,-1.5) {h};
\node(8) at(-1.5,-1.5) {i};
\node(9) at(1.5,-1.5) {j};

\node(10) at(4,-1.5) {k};
\node(11) at(2.5,-1.5) {l};

\draw[outline]
(1.south) to[out=180,in=180] 
(2.north) to[out=0,in=90]
(3.east) to[out=-90,in=0]
(1.south)
;

\draw[outline]
(8.west) to[out=90,in=90,looseness=.6] 
(9.east) to[out=-90,in=-90,looseness=.6]
(8.west)
;

\draw[outline]
(6.south) to[out=180,in=180] 
(5.north) to[out=0,in=90]
(4.east) to[out=-90,in=180]
(6.south)  
;

\draw[outline]
(10.east) to[out=90,in=90] 
(11.west) to[out=-90,in=-90]
(10.east)  
;

\begin{scope}[dashed, red]
\edge{2}{1}
\edge{3}{1}

\edge{5}{4}
\edge{6}{4}

\edge{8}{7}
\edge{9}{7}

\edge{11}{10}
\end{scope}

\begin{scope}[green]
\edge{2}{5}

\edge{7}{1}
\edge{3}{9}
\end{scope}

\end{tikzpicture}
\caption{$M^*$ is depicted by the dashed red edges,
and $M$ is depicted by the solid green edges.
The optimal stars are outlined.
}
\end{subfigure}
%
\hfill
%
\begin{subfigure}[b]{.51\linewidth}
\centering
\newcommand{\edge}[2]{
	\draw (#1) -- (#2);
}

\begin{tikzpicture}[every node/.style={default node, red}, -, very thick, green]

\node(1) at(0,0) {};
\node(2) at(4,0) {};
\node(3) at(0,-1.5) {};
\node(4) at(4,-1.5) {};

\edge{1}{2}
\edge{1}{3}

\end{tikzpicture}
\vspace{15pt}
\caption{The star graph: each vertex corresponds to a star in $G$.
The upper left vertex corresponds to the star that
contains the vertices a,b,c.  }
\end{subfigure}
%
\caption{An example of a star graph.}
\label{fig:conflict}
\end{figure}

\begin{lemma}
The maximum degree of $H$ is $\cmax(\cmax+1)$.
\end{lemma}
\begin{proof}
Each star in $\calS(M^*)$ contains at most $\cmax+1$ vertices and each
such vertex can belong to a star in $\calS(M)$ containing additional
$\cmax$ vertices, each of which is located in a different star in
$\calS(M^*)$.
\end{proof}

In what follows we compare $\abs{M}$ and $\abs{M^*}$ in maximal
connected components of the star graph $H$.  Intuitively, we show that
$M$ is optimal on small maximal components, and that the approximation
ratio on medium (non-necessarily) components can be bounded due to the
termination condition of \textbf{EdgeSwap}.  Large maximal components
will be partitioned into medium components.

We first show that large connected graphs (or maximal connected
components) can be partitioned into medium size components.
%The proof is omitted for lack of space.
%The proof is given in Appnedix~\ref{sec:omitted}.

\begin{lemma}
\label{lemma:dec}
An undirected connected graph $G = (V,E)$ with maximum degree
$\Delta$, can be decomposed into connected components of size at least
$\ell$ and at most $\Delta \ell$, if $\ell \leq \abs{V}$.
\end{lemma}
\begin{proof}%[Proof of Lemma~\ref{lemma:dec}]
We give a constructive proof.
%
First, if $\ell \leq |V| \leq \Delta \ell$, then we are done.
%
Otherwise, we partition the graph recursively as follows.  Let $U
= \emptyset$.  As long as $\abs{U} < \ell$, choose an arbitrary vertex
$u$ such that $U \cup \set{u}$ is connected and add $u$ to $U$.
%
If the graph $G[V \setminus U]$, which is induced by $V \setminus U$,
is connected, then choose the next vertex.
%
However, if $G[V \setminus U]$ becomes disconnected, then consider the
maximal connected components of $G[V \setminus U]$.  Add the vertices
of any maximal component that contains less than $\ell$ vertices to
$U$.  Observe that afterwards $\abs{U} < \ell + (\Delta-1) \ell
= \Delta \ell$.
%
If $\abs{U} \geq \ell$, then recursively partition any component of
$G[V \setminus U]$ that contains more than $\ell$ vertices.
%
If $\abs{U} < \ell$, then there must exist at least one maximal
component $C$ of $G[V \setminus U]$ that contains more than $\ell$
vertices.  In this case recursively partition any maximal component of
$G[V \setminus (U \cup C)]$ that contains more than $\ell$ vertices.
Also, continue to augment $U$ in the graph $G[U \cup C]$.
\end{proof}

\iffalse %%%%%% Removed

\begin{proof}
Let $T$ be any spanning tree of $G$ and let $r$ be an arbitrary root.
Starting with $r$, repeatedly choose a child whose subtree is strictly
larger than $\frac{\Delta-1}{\Delta} \abs{V}$, until this is not
possible.  Hence, we have reached a vertex $v$ whose subtree contains
more than $\frac{\Delta-1}{\Delta} \abs{V}$ vertices, but the subtrees
of its children contain at most $\frac{\Delta-1}{\Delta} \abs{V}$
vertices.
%
If $v = r$, then $v$ has a child $u$ with at least $\inv{\Delta}
(\abs{V}-1) \geq \ell$ vertices.  Otherwise, there exists a child $u$
of $v$ whose subtree is of size at least
$\inv{\Delta} \abs{V} \geq \ell$.  Disconnect $u$ and the vertices in
its subtree from the graph.
%
In both cases $u$'s subtree contains at most
$\frac{\Delta-1}{\Delta} \abs{V}$ vertices, and thus at least
$\inv{\Delta} \abs{V} \geq \ell$ vertices remain in the graph.  Hence
we obtain two connected subgraphs of size at least $\ell$.
%
We repeat this procedure recursively on any component of size
strictly larger $\Delta\ell$.
\end{proof}

\fi %%%%%% End removed

Define $\deg_M(v) \eqdf \din[M](v) + \dout[M](v)$.  For a subset
$U \subseteq V$ of vertices define $\deg_M(U) \eqdf \sum_{v \in
U} \deg_M(u)$.
%
Observe that $\abs{M} = \half \deg_M(V)$.

In the next lemma we bound the degree ratio in a component that
contains stars with at most $k$ arcs.

\begin{lemma}
\label{lemma:r}
Let $\calT \subseteq \calS(M^*)$ that induces a connected subgraph of
$H$.  If $\abs{A(\calT)} \leq k$, then
\[
\frac{\deg_M(V(\calT))}{\deg_{M^*}(V(\calT))} 
\geq \half + \inv{2\cmax} - \inv{2\cmax\abs{\calT}}
~.
\]
\end{lemma}
\begin{proof}
Consider the solution $M'$ obtained from $M$ by removing all the
edges from $M$ that intersect $V(\calT)$ and adding all the edges from
$M^*$ that intersect $V(\calT)$.  Observe that if an edge $(u,v)$ in
$M^*$ intersects $V(\calT)$, then $\set{u,v} \in V(\calT)$ by the
definition of the graph $H$.  Hence, $M'$ is feasible carpool
matching.

Since $\calT$ induces a connected subgraph of $H$, the removal of
edges in $M$ that intersect $V(\calT)$ decreased $\abs{M}$ by at most
$\deg_M(V(\calT)) - \abs{\calT} + 1$.
%
On the other hand, the increase in size is exactly
 $\half \deg_{M^*}(V(\calT)) \leq \cmax \abs{\calT}$.
%
Since $\abs{A(\calT)} \leq k$, we know that this difference can not be
positive, or else, \textsc{EdgeSwap} would not have terminated.  Thus
\[
\half \deg_{M^*}(V(\calT)) \leq \deg_M(V(\calT)) - \abs{\calT} + 1
~,
\]
and so
\[
\frac{\deg_M(V(\calT))}{\deg_{M^*}(V(\calT))}
\geq \half + \frac{\abs{\calT} - 1}{\deg_{M^*}(V(\calT))}
\geq \half + \frac{\abs{\calT} - 1}{2\cmax \abs{\calT}}
=    \half + \inv{2\cmax} - \inv{2\cmax \abs{\calT}}
~,
\]
as required.
\end{proof}

\iffalse %%%%% Removed

\begin{lemma}
%\label{lemma:dec}
Given a parameter $k$, a connected graph $G$ with a maximum degree $d$
can be decomposed into connected components of size at least $k$, and
at most $d(k-1) + 1$.
\end{lemma}

\begin{proof}
We give a constructive proof.  Start constructing a connected
component by adding adjacent vertices one by one to the component and
removing them from the graph.  If at some point, removing a vertex
disconnect the graph, add all the small components (of size less than
$k$) to the constructed component and decompose the large components
(of size at least $k$) recursively.  Note that removing a vertex can
break the graph to at most $d - 1$ additional components.
\end{proof}

\fi %%%%% End removed

It remains to bound the approximation ratio of \textbf{EdgeSwap}.

\begin{lemma}
If $k \geq \cmax$, then $\abs{M} \geq (\half + \inv{2\cmax}
- \frac{\cmax(\cmax+1)}{2k}) \cdot \abs{M^*}$.
\end{lemma}
\begin{proof}
Consider a maximal (with respect to set inclusion) connected component
of $H$ induced by the vertices in $\calT \subseteq \calS(M^*)$.
%
If $\abs{M \cap A(\calT)} \leq k$, then it must be that $\abs{M \cap
A(\calT)} = \abs{M^* \cap A(\calT)}$, since otherwise $M \cap
A(\calT)$ could be improved.

It remains to consider a maximal component $\calT$ such that If
$\abs{M \cap A(\calT)} > k$.  Since the number of edges in
$S \in \calS(M^*)$ is at most $\cmax$, it must be that $\abs{V(\calT)}
> \frac{k}{\cmax}$.
%
Due to Lemma~\ref{lemma:dec} (with $\ell
= \frac{k}{\cmax^2(\cmax+1)}$) we can partition $\calT$ into connected
components each of which contains between $\frac{k}{\cmax^2(\cmax+1)}$
and $\frac{k}{\cmax}$ vertices.
%
Since each such vertex set $\calX$ is connected and contains at most
$\frac{k}{\cmax}$ stars, it follows that $\abs{A(\calX)} \leq k$.
%
Due to Lemma~\ref{lemma:r} we have that
\[
\frac{\deg_M(V(\calX))}{\deg_{M^*}(V(\calX))} 
\geq \half + \inv{2\cmax} - \frac{\cmax(\cmax+1)}{2k}
~.
\]
Since $\deg_{M^*}(V(\calT)) = \sum_{\calX} \deg_{M^*}(V(\calX))$ and
$\deg_M(V(\calT)) = \sum_{\calX} \deg_M(V(\calX))$, it follows that
\[
\frac{\deg_M(V(\calT))}{\deg_{M^*}(V(\calT))}
\geq \half + \inv{2\cmax} - \frac{\cmax(\cmax+1)}{2k}
~,
\]
and thus
\[
\abs{M \cap A(\calT)}
\geq \paren{ \half + \inv{2\cmax} -
             \frac{\cmax(\cmax+1)}{2k}} \abs{M^* \cap A(\calT)}
~,
\]
and the lemma follows.
\end{proof}

By setting $k = \ceil{\cmax(\cmax+1)/2\eps}$, we get the following
result.

\begin{corollary}
\label{cor:local}
There exists a $(\half + \inv{2\cmax} - \eps)$-approximation algorithm
for unweighted \carpool, for every $\eps>0$.
\end{corollary}

%In Appendix~\ref{sec:tight} we show that our analysis is tight.

We now show that Corollary~\ref{cor:local} is tight.  Consider the
example in Figure~\ref{fig:local search tight}, the example is for the
special case when $k = 11$ and $\cmax = 2$ but this example can be
generalized in a straightforward manner.  One can verify that as the
graph in the example grows, the ratio between the optimal solution
and the local search solution approaches $\frac{3}{4}$.

\begin{figure}[t]
\begin{center}
\scalebox{.9}{
\tikzset{local/.style={
green,
dashed,
}}

\tikzset{opt/.style={
red,
solid,
}}

\begin{tikzpicture}[
	every node/.style={default node, solid}, 
	<-,
	level distance=12mm,
	level/.style={sibling distance=100mm/#1},
	level 1/.style={local},
	level 2/.style={opt},
	level 3/.style={local},
	level 4/.style={opt},
	level 5/.style={local},
	level 6/.style={opt},
]

\node{}
child{ node{}
	child { node{}
		child{ node{}
			child{ node{}
				child{ node{}
					child{ node(1){}}
					child{ node(2){}}
				}
			}
			child{ node{}
				child{ node{}
					child{ node(3){}}
					child{ node(4){}}
				}
			}
		}
	}
	child { node{}
		child{ node{}
			child{ node{}
				child{ node{}
					child{ node(5){}}
					child{ node(6){}}
				}
			}
			child{ node{}
				child{ node{}
					child{ node(7){}}
					child{ node(8){}}
				}
			}
		}
	}
};

\begin{scope}[local]
\draw (1) to[bend right] (5);
\draw (2) to[bend right] (6);
\draw (3) to[bend right] (7);
\draw (4) to[bend right] (8);
\end{scope}

\end{tikzpicture}
}
\caption{A tight example for Corollary~\ref{cor:local}. 
The optimal solution is given by the red solid arcs while the local
search solution is given by the green, dashed arcs.  The solution can
be improved by the local search algorithm only if it removes all the
edges.}
\label{fig:local search tight}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Group Carpool}
\label{sec:group}

We now consider \gcp which a variant of \carpool in which
%
%in addition to the capacity function $c:V \to \N$, and the weight
%function $w:A \to \R^+$, we also have
we are given a size function $s:V \to \N$, and the constraint
$\din[M](v) \leq c(v)$ is replaced with the constraint
$\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
%
%The motivation for this variant of the problem is when we want to
%allow a group of people to travel together in the same car, thus $s$
%is the size of the group.

We start by showing that this variant of the problem does not fit the
submodular maximization formulation as defined for \carpool.
%
Recall the submodular maximization formulation given in
Section~\ref{sec:sub}, namely $\barw: 2^V \to \R$, where
$\barw(S) \eqdf w(M(S))$ and $M(S)$ is the maximum weight carpool
matching that satisfies $D_{M(S)} \subseteq S \subseteq V \setminus
P_{M(S)}$.
%
Figure~\ref{fig:not submodular} contains an instance that shows that
the function $\barw$ is not submodular anymore.

\begin{figure}[t]
\begin{center}
\begin{tikzpicture}[every node/.style={default node}, ->]

\node(1) at (-2,0){};
\node(2) at (0,0){2};
\node(3) at (2,0){};
\node(4) at (0,2){};

\draw (1) -- (2) node[label above]{1};
\draw (3) -- (2) node[label above]{1};
\draw (4) -- (2) node[label above]{2};

\draw[dotted,green] 
(1.west) to[out=90,in=90] node[label above] {A}
(2.east) to[out=-90, in=-90]
(1.west)
;

\draw[dashed,red] 
(2.west) to[out=90,in=90] node[label above] {B}
(3.east) to[out=-90, in=-90]
(2.west)
;

\end{tikzpicture}
\end{center}
\caption{An unweighted \carpool instance.  Capacities are written
  inside vertices, and arcs are labeled with their size.  We have that
  $f(A) + f(B) = 2 < 3 = f(A \cup B) + f(A \cap B)$.}
\label{fig:not submodular}
\end{figure}

We show, however, that \gcp has a $(\half -\eps)$-approximation
algorithm by extending the local improvement algorithm from
Section~\ref{sec:improve}.
%
The main concern when trying to adopt the algorithm to \gcp is how to
determine if a vertex can be improved.
%
With \carpool, if weights are polynomially-bounded, it was enough to
consider the incoming arcs to a vertex $v$ in a non-increasing
order of $\delta_M$ (See proof of Theorem~\ref{thm:improve-bounded}).
This does not work anymore, since in the \gcp we have sizes.  In fact, given
$v$, finding the best star with respect to $\delta_M$ is
a \textsc{Knapsack} instance where the size of the knapsack is $c(v)$.
%
If weights are polynomially-bounded, then $\delta_M(e)$ is bounded for
every arc $e \in A$, and therefore this instance of \textsc{Knapsack}
can be solved in polynomial time using dynamic programming.

\begin{theorem}
Algorithm~\textbf{StarImprove} is a $\half$-approximation algorithm
for \gcp, if edge weights are integral and polynomially bounded.
\end{theorem}

Using standard scaling and rounding we obtain the following result.

\begin{theorem}
There exists a $(\half-\eps)$-approximation algorithm for \gcp,
for every $\eps \in (0,\half)$.
\end{theorem}

Finally, we show that a variant of Algorithm~\textbf{EdgeSwap} from
Section~\ref{sec:local} can be used to solve \gcp while keeping the
same approximation guarantees. 
%
The only difference is that when checking feasibility of a set of arcs
we do not compare the number of passengers to the capacity of a
driver, but rather compare the total size of the passengers to the
capacity.

\begin{theorem}
There exists a $(\half + \inv{2\cmax} - \eps)$-approximation algorithm
for unweighted \gcp, for every $\eps>0$.
\end{theorem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Acknowledgements.}

We thank David Adjiashvili and Reuven Bar-Yehuda for helpful
discussions.

\bibliographystyle{abbrv}
\bibliography{carpool}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2019-12-06 response.tex
adding astrix near my name

\documentclass[11pt]{article}

\usepackage{amsmath,latexsym,amssymb} 
\usepackage{fullpage,ifthen}
\usepackage{color,soul,colordvi}
\usepackage{mdwlist,paralist}

%\renewcommand{\baselinestretch}{1.02}

%\parskip=\smallskipamount

\sloppy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\set}[1]{\left\{ #1 \right\}}

\newcommand{\eps}{\varepsilon}

\newcommand{\calC}{\mathcal{C}}
\newcommand{\sigmad}{\sigma_{\$}}

\newcommand{\ans}[1]{\begin{quotation}{\noindent \sl {#1}}\end{quotation}}

\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}
\newcommand{\ben}[1]{\sethlcolor{green}\hl{Ben: #1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{\textbf{Local Search Algorithms for the \\ Maximum Carpool Matching
  Problem} \\
  {\Large Response to Reviewers: Submission ALGO-D-00287}}

\author{Gilad Kutiel \and Dror Rawitz}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We thank the referee for the time that was spent on reviewing our
paper and for their thoughtful comments.  The paper was revised
according to these comments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\medskip

\section*{Response to Review}

\begin{enumerate}

\item \textbf{Comment}: There are multiple graphs used throughout the
  paper: a directed input graph, the related undirected graph
  obtained by ignoring edge orientations, and a graph $H$ that relates
  stars to one another. It would help the presentation if it were made
  completely clear at each stage which graph is being discussed.

\item[] \textbf{Response}: We now use calligraphic letters in the
  definition of the star graph, namely the star graph is denoted by
  $\mathcal{H} = (\mathcal{S}(M^*),\mathcal{E})$.

\item \textbf{Comment}: In the proof of Lemma 1, I do not see how the
  condition that $M_S \cup M_T = M(S \cup T) \cup M(S \cap T)$ is
  sufficient to finish the proof when $M(S \cup T)$ and $M(S \cap T)$
  are not disjoint. In that case the weights of elements in the
  intersection will be counted only once. The later proof seems to
  actually account for this.

\item[] \textbf{Response}: We now use $M(S \cup T) \uplus M(S \cap
  T)$.

\item \textbf{Comment}: In the proof of Lemma 8, what is meant by an
  edge of $M$ ”intersecting” $V(\mathcal{T})$?  Presumably you mean an
  edge of $M$ that is incident on one of the vertices of
  $V(\mathcal{T})$?

\item[] \textbf{Response}: We added a sentence about this issue in the
  beginning of the proof of Lemma~8.

\item \textbf{Comment}: It would be good to emphasize that the set of
  stars induced by $M^*$ includes also all of the single-vertex
  ``stars -- corresponding to $Z_M$.  This was not so clear to me on
  the first reading.

\item[] \textbf{Response}: This is now emphasized in the paragraph
  that defines $\mathcal{S}(M)$.

\item \textbf{Comment}: In the proof of Lemma~9, please point out the
  usage of Lemma~6, which bounds the degree of $H$, when you use Lemma~7.

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: In the proof of Lemma~9, you write ”Since each
  such vertex set is connected and contains at most
  $\frac{k}{c_{\max}}$ stars, it follows that $|A(\mathcal{X})| \leq
  k$.''  However, I do not see how the vertex set being connected is
  relevant for $|A(\mathcal{X})|$. I agree that it is used to apply
  Lemma~8 later.

\item[] \textbf{Response}: Corrected.

\item \textbf{Comment}: In the tight example (Figure~7) it is stated
  that the solution can be improved by local search only if removes
  all of the edges.  This is not true; please see the last page of
  this document for an improvement that does not remove every edge.
  Probably one needs to rearrange the edges connecting leaves
  appropriately.  The example given by Hurkens and Schrijver%
%
  \footnote{``On the size of systems of sets every $t$ of which have an
    SDR, with an application to the worst-case ratio of heuristics for
    packing problems'', SIAM J. Discrete Math., 2(1), 6872.}
%
  might be useable here instead.  In any case, please give some
  details for a general construction or at least provide details of
  how the example can be generalized.

\item[] \textbf{Response}: We removed this figure from the paper.

\item \textbf{Comment}: Details should be given for the proofs of
  Theorems~5, 6, and~7.  Since the group variant already generalizes
  the standard setting why not just present proofs for the general
  case?

\item[] \textbf{Response}: We moved the material from Section 4 to
  sections 2.1, 2.2 and 3.2, respectively.

\end{enumerate}

%%%%%

\subsection*{Minor comments}

\begin{enumerate}

\item \textbf{Comment}: Page 3: The best known approximation for
  weighted $k$-set packing is in fact $\frac{k+1}{2}$, due to Piotr Berman.%
%
\footnote{``A $d/2$ Approximation for Maximum Weight Independent Set
  in $d$-Claw Free Graphs'' in SWAT 2000}

\item[] \textbf{Response}: A reference was added, and the last
  sentence of the paragraph was corrected accordingly.

\item \textbf{Comment}: Page 5, line 56: $v$ is missing from the
  definition of $N^{\text{in}}$ and $N^{\text{out}}$.

\item[] \textbf{Response}: Corrected.

\item \textbf{Comment}: Page 6, line 33. Again, $v$ is missing from
  $N^{\text{in}}$ and $N^{\text{out}}$.

\item[] \textbf{Response}: Corrected.

\item \textbf{Comment}: Page 7, caption of Figure 3: it seems that the
  last two edges listed in $\Gamma(2,3)$ are incorrect.

\item[] \textbf{Response}: The example was correct.  We corrected the
  definition of $\Gamma(u,v)$.

\item \textbf{Comment}: Page 8, Figure 5: are the double arrows in
  this figure intentional? If so, I do not understand what is meant by
  selecting ``all arcs of length 1.''

\item[] \textbf{Response}: The figure and caption were corrected.

\item \textbf{Comment}: Page 8, line 34: $N_{\overline{S}}$ is used
  here instead of the previous notation $N^{\text{in}}_S(v)$.  Also,
  it might be worthwhile to point out at the end that the vertices
  will not be charged again \emph{because the stars are disjoint in
    $M^*$}.

\item[] \textbf{Response}: Corrected.

\item \textbf{Comment}: Page 12, line 28: $\deg_M(u)$ should be
  $\deg_M(v)$.

\item[] \textbf{Response}: Corrected.

\item \textbf{Comment}: Page 12, line 39-41: Starting with ``Observe
  that if an edge \ldots,'' I do not follow why this condition is
  helpful or necessary for $M'$ to be a valid carpool matching.

\item[] \textbf{Response}: It helps to explain the transition from
  $\deg_M(V(\mathcal{T}))$ to $|M \cap A(\mathcal{T})|$.

\item \textbf{Comment}: Page 13, line 30: at the end of the proof it
  would be good remind that the sets $A(\mathcal{T})$ considered form
  a partition of all the edges (and so also of the edges in both $M$
  and $M^*$, and summing over them completes the proof.

\item[] \textbf{Response}: Done.

\end{enumerate}

\end{document}

### 2019-12-06 carpool.tex
adding astrix near my name

--- 2017-11-02 src/carpool.tex
@@
 
-%\renewcommand{\floatpagefraction}{0.8}
+\renewcommand{\floatpagefraction}{0.8}
 
@@
 \newtheorem{property}{Property}
-\newtheorem{corollary}{Corollary}
+\newtheorem{corollary}[theorem]{Corollary}
 \newtheorem{proposition}{Proposition}
@@
 
+\newcommand{\calH}{\mathcal{H}}
+\newcommand{\calE}{\mathcal{E}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \author{%
-Gilad Kutiel%
+Gilad Kutiel\textsuperscript{*}%
 \thanks{Department of Computer Science, Technion, Haifa 32000, Israel.} \\
-\texttt{gkutiel@cs.technion.ac.il}
+\texttt{gkutiel@cs.technion.ac.il}\textsuperscript{*}
 \and
@@
 %
-\begin{subfigure}[t]{.5\linewidth}
+\begin{subfigure}[t]{.45\linewidth}
 \centering
@@
 \end{tikzpicture}
-\caption{A feasible carpool matching with total weight
-of 23.  $P_M$ is the set of blue vertices, and $D_M$ is the set of
-red, dashed vertices, and $Z_M$ contains only the dotted, black
-vertex.}
+\caption{A feasible carpool matching with total weight of 23.  $P_M$
+  is the set of blue, solid vertices, and $D_M$ is the set of red,
+  dashed vertices, and $Z_M$ contains only the dotted, black vertex.}
 \end{subfigure}
@@
 presented a $\frac{3}{2(k+1)}$-approximation algorithm for this
-problem.
+problem, and Berman~\cite{Berman00} gave a
+$\frac{2}{k+1}$-approximation algorithm.
 %
@@
 time.  The outcome is a \textsc{$k$-Set Packing} instance.  This leads
-to a $\frac{3}{2(\cmax+2)}$-approximation algorithm
-%for the case where
-when $\cmax = O(1)$.
+to a $\frac{2}{\cmax+2}$-approximation algorithm for \carpool for the
+case where $\cmax = O(1)$.
 
@@
 %
-Section~\ref{sec:approx} contains approximation algorithms
-for \carpool.  First, in Section~\ref{sec:sub} we show that \carpool
-can be formulated as an unconstrained submodular maximization problem,
+Section~\ref{sec:approx} contains approximation algorithms for
+\carpool.  First, in Section~\ref{sec:sub} we show that \carpool can
+be formulated as an unconstrained submodular maximization problem,
 thus it has a $\frac{1}{2}$-approximation algorithm due
-to~\cite{BFNS15,buchbinder2016deterministic}.
+to~\cite{BFNS15,buchbinder2016deterministic}.  On the other hand, we
+show that the unconstrained submodular maximization formulation for
+\carpool does not work for \gcp.
 %
@@
 The approximation ratio of this algorithm is $\half$ if weights are
-polynomially bounded, and its ratio is $\half-\eps$ in general.
+polynomially bounded, and its ratio is $\half-\eps$ in general.  This
+algorithm extends to \gcp with the same approximation ratio.
+%We show, however, that this problem still
+%admits a $(\frac{1}{2} -\varepsilon)$-approximation algorithm by
+%extending our first local search algorithm.
 
@@
 %
-We show that our analysis is tight.
+%We show that our analysis is tight.
 %
@@
 result from~\cite{ACKK09} does not hold in bounded degree graphs.
-
-Finally, Section~\ref{sec:group} discusses \gcp.  We show that the
-unconstrained submodular maximization formulation for \carpool does
-not work for \gcp.  We show, however, that this problem still admits a
-$(\frac{1}{2} -\varepsilon)$-approximation algorithm by extending our
-first local search algorithm.  In addition, we show that the second
-local search algorithm generalizes to unweighted \gcp with the same
-approximation ratio.
+%
+In addition, we show that our local search algorithm generalizes to
+unweighted \gcp with the same approximation ratio.
 
@@
 \varepsilon)$-approximation algorithm.  While the latter does not
-improve upon the former, it will be shown (in Section~\ref{sec:group})
+improve upon the former, it will be shown
+%(in Section~\ref{sec:group})
 that it can be generalized to \gcp without decreasing the
@@
 
-Consider the function $\barw: 2^V \to \R$, where $\barw(S) \eqdf
-w(M(S)) = \sum_{e \in M(S)} w(e)$.  Observe that $\barw(\emptyset)
-= \barw(V) = 0$, and that $\barw$ is not monotone.
+Consider the function $\barw: 2^V \to \R$, where
+\[
+\barw(S) \eqdf w(M(S)) = \sum_{e \in M(S)} w(e)
+~.
+\]
+Observe that $\barw(\emptyset) = \barw(V) = 0$, and that $\barw$ is
+not monotone.
 %
@@
 To prove the lemma we construct two feasible carpool matchings $M_S$
-and $M_T$ such that $M_S \subseteq (V \setminus S) \times S$,
-$M_T \subseteq (V \setminus T) \times T$, and $M_S \cup M_T = M(S \cup
-T) \cup M(S \cap T)$.
+and $M_T$ such that $M_S \subseteq (V \setminus S) \times S$, $M_T
+\subseteq (V \setminus T) \times T$, and $M_S \cup M_T = M(S \cup T)
+\biguplus M(S \cap T)$, where the RHS can be a multiset.
 %
@@
 and entering $S \cap T$ in both $M(S \cup T)$ and $M(S \cap T)$.  Note
-that there may exist edges $(v,u)$, where $v \not\in S \cup T$, and
-$u \in S \cap T$ such that $(v,u) \in M(S \cup T)$ and $M(S \cap T)$.
-We refer to this edges as \emph{duplicate} edges.
+that there may exist edges $(v,u)$, where $v \not\in S \cup T$, and $u
+\in S \cap T$ such that $(v,u) \in M(S \cup T)$ and $(v,u) \in M(S
+\cap T)$.  We refer to this edges as \emph{duplicate} edges.
 %
@@
 
+Now consider \gcp.  Recall that in this variant of \carpool, in
+addition to the capacity function $c:V \to \N$, and the weight
+function $w:A \to \R^+$, we are also given a size function $s:V \to
+\N$, and the constraint $\din[M](v) \leq c(v)$ is replaced with the
+constraint $\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
+%
+%The motivation for this variant of the problem is when we want to
+%allow a group of people to travel together in the same car, thus $s$
+%is the size of the group.
+%
+We show that this variant of the problem does not fit the submodular
+maximization formulation as defined for \carpool.
+%
+Recall the submodular maximization formulation given above,
+%in Section~\ref{sec:sub},
+namely $\barw: 2^V \to \R$, where $\barw(S)
+\eqdf w(M(S))$ and $M(S)$ is the maximum weight carpool matching that
+satisfies $D_{M(S)} \subseteq S \subseteq V \setminus P_{M(S)}$.
+%
+Figure~\ref{fig:not submodular} contains an instance that shows that
+the function $\barw$ is not submodular anymore.
+
+\begin{figure}[!t]
+\begin{center}
+\begin{tikzpicture}[every node/.style={default node},thick]
+
+\node(1) at (-2,0){2};
+\node(2) at (0,0){1};
+\node(3) at (2,0){3};
+\node(4) at (0,2){4};
+
+\draw[->] (1) -- (2);
+\draw[->] (3) -- (2);
+\draw[->] (4) -- (2);
+
+\draw[dotted,green] 
+(1.west) to[out=90,in=90] node[label above] {A}
+(2.east) to[out=-90, in=-90]
+(1.west)
+;
+
+\draw[dashed,red] 
+(2.west) to[out=90,in=90] node[label above] {B}
+(3.east) to[out=-90, in=-90]
+(2.west)
+;
+\end{tikzpicture}
+\end{center}
+\caption{An unweighted \carpool instance: $c(1) = 2$, $s(2) = s(3) =
+  1$, and $s(4) = 2$.  We have that $\barw(A) + \barw(B) = 2 < 3 =
+  \barw(A \cup B) + \barw(A \cap B)$.}
+\label{fig:not submodular}
+\end{figure}
+
 %%%%%
@@
 %
-We remind the reader that this algorithm will be extended to \gcp in
-Section~\ref{sec:group}.
+At the end of the section we show that this algorithm extends to \gcp.
+
+%We remind the reader that this algorithm will be extended to \gcp in
+%Section~\ref{sec:group}.
 
@@
 %
-Given a directed graphs $G = (V,A)$, define $\nin[] \eqdf \set{u :
-(u,v) \in A}$ and $\nout[] \eqdf \set{u : (v,u) \in A}$.
-%
-Let $M$ be a feasible carpool matching.  The weight $w_M(v)$ of a
-vertex $v$ with respect to $M$ is the sum of the weights of the arcs
-in $M$ that are incident on $v$, namely
+Given a directed graph $G = (V,A)$, define $\nin[](v) \eqdf \set{u :
+  (u,v) \in A}$ and $\nout[](v) \eqdf \set{u : (v,u) \in A}$.
+%
+Given a feasible carpool matching $M$, the weight $w_M(v)$ of a vertex
+$v$ with respect to $M$ is the sum of the weights of the arcs in $M$
+that are incident on $v$, namely
 \[
-\textstyle
 w_M(v)
-\eqdf w(M \cap \nin[]) + w(M \cap \nout[])
+\eqdf w(M \cap \nin[](v)) + w(M \cap \nout[](v))
 =     \sum_{(u, v) \in M} w(u, v) + \sum_{(v, u) \in M} w(v, u)
@@
 \begin{proof}
-\(
-\displaystyle
-\sum_{v \in V} w_M(v)
+%We have that 
+\(\displaystyle
+w_M(V)
+= \sum_{v \in V} w_M(v)
 = \sum_{v \in V} \sum_{(u, v) \in M} w(u, v) +
@@
 = 2 \sum_{e \in M} w(e)
+%~.    
 \).
@@
 
-Denote by $\delta(u,v)$ the difference between the weight of the arc
+Denote by $\delta_M(u,v)$ the difference between the weight of the arc
 and the weight of its source vertex, that is:
@@
 For a subset $S \subseteq A$ of arcs define
-$\delta(S) \eqdf \sum_{(u,v) \in S} \delta(u,v)$.
+$\delta_M(S) \eqdf \sum_{(u,v) \in S} \delta_M(u,v)$.
 
@@
 A subset $S_v \subseteq A \cap (V \times \{v\})$ is
-an \emph{improvement} with respect to a carpool matching $M$, if%
+an \emph{improvement} with respect to a carpool matching $M$, if
 %the following conditions hold:%
@@
 Given an arc $(u,v) \in A$, let $\inc(u,v)$ be the set of arcs that
-incident $(u, v)$, namely define
-\(
-\inc(u,v) \eqdf (\nin[](u) \times \{u\}) \cup (\{v\} \times \nout[](v))
-%~.
-\).
+are incident on $(u,v)$, namely define
+\[
+\inc(u,v)
+\eqdf (\nin[](u) \times \{u\}) \cup (\{u\} \times \nout[](u)) \cup
+      (\nin[](v) \times \{v\}) \cup (\{v\} \times \nout[](v))
+~.
+\]
 If $S$ is a set of arcs, then $\inc(S) \eqdf \bigcup_{(u,v) \in
@@
 vertex that can be improved.  If there exists such a vertex $v$, then
-the algorithm removes the arcs that are incident on it from $M$, and
-adds the arcs in $S_v$.  The algorithm terminates when no vertex can
-be improved.  Figure~\ref{fig:improvement} depicts an improvement
+the algorithm removes the arcs that are incident on $S_v$ from $M$,
+and adds the arcs in $S_v$.  The algorithm terminates when no vertex
+can be improved.  Figure~\ref{fig:improvement} depicts an improvement
 step.
@@
 \end{subfigure}
-\caption[]{An improvement example.}
+\caption{An improvement example.}
 \label{fig:improvement}
@@
 w_M(\nin[S](v))$, thus we can pay for $S$, using the money on $v$ and
-on $N^-_S(v)$.  Clearly, these vertices will not be charged again.
+on $\nin[S](v)$.  These vertices are not charged again, since the
+stars are disjoint in $M^*$.
 \end{proof}
 
-We show that our analysis is tight using in Figure~\ref{fig:grd
-worst}.
+We show that our analysis is tight using Figure~\ref{fig:grd worst}.
 
@@
 \centering
-\begin{tikzpicture}[every node/.style={default node}, <->]
+\begin{tikzpicture}[every node/.style={default node}, ->]
 
@@
 \end{tikzpicture}
-\caption[]{%
-Consider a path with $2n + 1$ arcs, and alternating arc weights (2 and
-1), if \textbf{StarImprove} selects all arcs of weight 1, then no
-further improvement can be done and the value of the matching is $n +
-1$, while the optimal matching has value of $2n$.}
+\caption{
+%
+Consider a directed path with $n$ vertices and $(n-1)$ arcs, where $n$
+is even.  The weights for the arcs are alternating between 1 and 2.
+%
+If \textbf{StarImprove} selects all arcs of weight 1, then no further
+improvement can be done and the value of the matching is $n/2$,
+while the optimal matching has value of $n-2$.}
 \label{fig:grd worst}
@@
 non-increasing order of their $\delta_M$s, and only ones with positive
-values.  A vertex $v$ can be improved, then, if the $\delta$s of the
+values.  A vertex $v$ can be improved, then, if the $\delta_M$s of the
 first $c(v)$ (or less) arcs sum up to more than $w_M(v)$.
@@
 
-It remains to consider the case, where weight are not polynomially
+%%%%%
+
+Next we show that \gcp has a $(\half -\eps)$-approximation algorithm
+by extending Algorithm~\textbf{StarImprove}.
+%the local improvement algorithm from Section~\ref{sec:improve}.
+%
+
+%
+This leads to the following result.
+
+\begin{theorem}
+Algorithm~\textbf{StarImprove} is a $\half$-approximation algorithm
+for \gcp, if edge weights are integral and polynomially bounded.
+\end{theorem}
+\begin{proof}
+The main concern when trying to adopt the algorithm to \gcp is how to
+efficiently determine whether a vertex can be improved.
+%
+With \carpool, if weights are polynomially-bounded, it was enough to
+consider the incoming arcs to a vertex $v$ in a non-increasing order
+of $\delta_M$ (see proof of Theorem~\ref{thm:improve-bounded}).  This
+does not work anymore, since in the \gcp we have sizes.  In fact,
+given $v$, finding the best star with respect to $\delta_M$ is a
+\textsc{Knapsack} instance where the size of the knapsack is $c(v)$.
+%
+If weights are polynomially-bounded, then $\delta_M(e)$ is bounded for
+every arc $e \in A$, and therefore this instance of \textsc{Knapsack}
+can be solved in polynomial time using dynamic programming.
+%
+As before, the number of improvements is polynomial, since the weight
+of an optimal solution is polynomially bounded.
+\end{proof}
+
+%%%%%
+
+It remains to consider the case, where weights are not polynomially
 bounded.  We prove that one can use standard scaling and rounding to
@@
 \label{thm:improve}
-There exists a $(\half-\eps)$-approximation algorithm for \carpool,
-for every $\eps \in (0,\half)$.
+There exists a $(\half-\eps)$-approximation algorithm for \carpool (or
+\gcp), for every $\eps \in (0,\half)$.
 \end{theorem}
@@
 %
-Let $M^*$ and $M'$ be an optimal carpool matchings with respect to $w$
+Let $M^*$ and $M'$ be an optimal carpool matching with respect to $w$
 and $w'$, resp.  We have that
@@
 \]
-By Theorem~\ref{thm:improve-bounded}, our local improvement algorithm computes a
-$\half$-approximate carpool matching $M$ on $(G, c, w')$, and this
-matching satisfies $w'(M) \geq w'(M')/2$.  Furthermore, since
+By Theorem~\ref{thm:improve-bounded}, our local improvement algorithm
+computes a $\half$-approximate carpool matching $M$ on $(G, c, w')$,
+and this matching satisfies $w'(M) \geq w'(M')/2$.  Furthermore, since
 $w'(M') \geq w'(M^*)$, it follows that $w'(M) \geq w'(M^*)/2$.
@@
 
+%Using standard scaling and rounding we obtain the following result.
+
+%\begin{theorem}
+%There exists a $(\half-\eps)$-approximation algorithm for \gcp,
+%for every $\eps \in (0,\half)$.
+%\end{theorem}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:cmax}
+
 In this section we study the \carpool problem when the maximum
@@
 instances.  We also describe and analyze a local search algorithm for
-the unweighted variant of the problem, and show that the algorithm
+the unweighted variant of the problem and show that the algorithm
 achieves a $\half + \inv{2\cmax} - \eps$ approximation ratio, for any
 $\varepsilon > 0$.
+%
+This algorithm also applies to \gcp.
 
@@
 
-Observe that a vertex $v \in D_M \cup Z_M$ is the center of
-a \emph{directed star} whose leaves are the passengers in the set
-$P_M(v) = \set{u : (u,v) \in M}$
-($P_M(v) = \emptyset$, for $v \in Z_M$).
+Observe that a vertex $v \in D_M \cup Z_M$ is the center of a
+\emph{directed star} whose leaves are the passengers in the set
+$P_M(v) = \set{u : (u,v) \in M}$.  Observe that $P_M(v) = \emptyset$,
+for $v \in Z_M$ (in this case the star is an isolated vertex).
 %
 Given a carpool matching $M$, we define $\calS(M)$ to be the set of
-stars that are induced by $M$.  Denote by $V(S)$ the set of vertices
-of a star, i.e., if $v$ is the center of $S$, then $V(S) = \{v\} \cup
-P_M(v)$.  Also, let $A(S)$ be the arcs of $S$.  For
-$\calT \subseteq \calS(M)$, define
-$V(\calT) \eqdf \bigcup_{S \in \calT} V(S)$ and
-$A(\calT) \eqdf \bigcup_{S \in \calT} A(S)$.
+stars that are induced by $M$.
+%
+Denote by $V(S)$ the set of vertices of a star, i.e., if $v$ is the
+center of $S$, then $V(S) = \{v\} \cup P_M(v)$.  
+Also, let $A(S)$ be
+the arcs of $S$.
+%
+Observe that $V(S) = \{v\}$ and $A(S) = \emptyset$, if $v \in Z_M$.
+%
+For $\calT \subseteq \calS(M)$, define $V(\calT) \eqdf \bigcup_{S \in
+  \calT} V(S)$ and $A(\calT) \eqdf \bigcup_{S \in \calT} A(S)$.
 
@@
 %
-Formally $H = (\calS(M^*), E)$ where
+Formally we defined an undirected \emph{star graph} $\calH =
+(\calS(M^*), \calE)$, where
 \[
-E = \set{(S^*_i, S^*_j) : \exists S \in \calS(M), 
+\calE = \set{(S^*_i, S^*_j) : \exists S \in \calS(M), 
              V(S) \cap V(S^*_i) \neq \emptyset \land
@@
 
-\node(1) at(0,0) {a};
-\node(2) at(0,1.5) {b};
-\node(3) at(1.5,0) {c};
-
-\node(4) at(4,0) {d};
-\node(5) at(4,1.5) {e};
-\node(6) at(2.5,0) {f};
-
-\node(7) at(0,-1.5) {h};
-\node(8) at(-1.5,-1.5) {i};
-\node(9) at(1.5,-1.5) {j};
-
-\node(10) at(4,-1.5) {k};
-\node(11) at(2.5,-1.5) {l};
+\node(1) at(0,0) {$a$};
+\node(2) at(0,1.5) {$b$};
+\node(3) at(1.5,0) {$c$};
+
+\node(4) at(4,0) {$d$};
+\node(5) at(4,1.5) {$e$};
+\node(6) at(2.5,0) {$f$};
+
+\node(7) at(0,-1.5) {$h$};
+\node(8) at(-1.5,-1.5) {$i$};
+\node(9) at(1.5,-1.5) {$j$};
+
+\node(10) at(4,-1.5) {$k$};
+\node(11) at(2.5,-1.5) {$l$};
 
@@
 \end{tikzpicture}
-\vspace{15pt}
-\caption{The star graph: each vertex corresponds to a star in $G$.
-The upper left vertex corresponds to the star that
-contains the vertices a,b,c.  }
+\vspace{25pt}
+\caption{The star graph $\calH$: each vertex corresponds to a star in
+  $G$ which is induced by $M^*$.  The upper left vertex of $\calH$
+  corresponds to the star in $G$ containing $a$, $b$, and $c$.}
 \end{subfigure}
 %
-\caption{An example of a star graph.}
+\caption{An example of a star graph $\calH$.}
 \label{fig:conflict}
@@
 \begin{lemma}
-The maximum degree of $H$ is $\cmax(\cmax+1)$.
+\label{lemma:maxdegH}
+The maximum degree of $\calH$ is $\cmax(\cmax+1)$.
 \end{lemma}
@@
 In what follows we compare $\abs{M}$ and $\abs{M^*}$ in maximal
-connected components of the star graph $H$.  Intuitively, we show that
-$M$ is optimal on small maximal components, and that the approximation
-ratio on medium (non-necessarily) components can be bounded due to the
-termination condition of \textbf{EdgeSwap}.  Large maximal components
-will be partitioned into medium components.
+connected components of the star graph $\calH$.  Intuitively, we show
+that $M$ is optimal on small maximal components, and that the
+approximation ratio on medium (non-necessarily) components can be
+bounded due to the termination condition of \textbf{EdgeSwap}.  Large
+maximal components will be partitioned into medium components.
 
@@
 
-Define $\deg_M(v) \eqdf \din[M](v) + \dout[M](v)$.  For a subset
-$U \subseteq V$ of vertices define $\deg_M(U) \eqdf \sum_{v \in
-U} \deg_M(u)$.
+Given a carpool matching $M$, define $\deg_M(v) \eqdf \din[M](v) +
+\dout[M](v)$.  For a subset $U \subseteq V$ of vertices define
+$\deg_M(U) \eqdf \sum_{v \in U} \deg_M(v)$.
 %
@@
 Let $\calT \subseteq \calS(M^*)$ that induces a connected subgraph of
-$H$.  If $\abs{A(\calT)} \leq k$, then
+$\calH$.  If $\abs{A(\calT)} \leq k$, then
 \[
@@
 \begin{proof}
-Consider the solution $M'$ obtained from $M$ by removing all the
-edges from $M$ that intersect $V(\calT)$ and adding all the edges from
-$M^*$ that intersect $V(\calT)$.  Observe that if an edge $(u,v)$ in
-$M^*$ intersects $V(\calT)$, then $\set{u,v} \in V(\calT)$ by the
-definition of the graph $H$.  Hence, $M'$ is feasible carpool
-matching.
-
-Since $\calT$ induces a connected subgraph of $H$, the removal of
+We say that a carpool matching $M$ in $G$ \emph{intersects} $V(\calT)$
+if one of the edge in $M$ is incident on one of the vertices in
+$V(\calT)$.
+%
+Consider the solution $M'$ obtained from $M$ by removing all the edges
+from $M$ that intersect $V(\calT)$ and adding all the edges from $M^*$
+that intersect $V(\calT)$.  Observe that if an edge $(u,v)$ in $M^*$
+intersects $V(\calT)$, then $\set{u,v} \in V(\calT)$ by the definition
+of the graph $\calH$.  Hence, $M'$ is a feasible carpool matching.
+
+Since $\calT$ induces a connected subgraph of $\calH$, the removal of
 edges in $M$ that intersect $V(\calT)$ decreased $\abs{M}$ by at most
@@
 %
-On the other hand, the increase in size is exactly
- $\half \deg_{M^*}(V(\calT)) \leq \cmax \abs{\calT}$.
-%
-Since $\abs{A(\calT)} \leq k$, we know that this difference can not be
-positive, or else, \textsc{EdgeSwap} would not have terminated.  Thus
+On the other hand, the increase in size is exactly $\half
+\deg_{M^*}(V(\calT)) \leq \cmax \abs{\calT}$.
+%
+Since $\abs{A(\calT)} \leq k$, we know that this difference cannot be
+positive, or else, \textbf{EdgeSwap} would not have terminated.  Thus
 \[
@@
 Consider a maximal (with respect to set inclusion) connected component
-of $H$ induced by the vertices in $\calT \subseteq \calS(M^*)$.
+of the star graph $\calH$ induced by the vertices in $\calT \subseteq
+\calS(M^*)$.
 %
@@
 
-It remains to consider a maximal component $\calT$ such that If
-$\abs{M \cap A(\calT)} > k$.  Since the number of edges in
-$S \in \calS(M^*)$ is at most $\cmax$, it must be that $\abs{V(\calT)}
-> \frac{k}{\cmax}$.
-%
-Due to Lemma~\ref{lemma:dec} (with $\ell
-= \frac{k}{\cmax^2(\cmax+1)}$) we can partition $\calT$ into connected
-components each of which contains between $\frac{k}{\cmax^2(\cmax+1)}$
-and $\frac{k}{\cmax}$ vertices.
-%
-Since each such vertex set $\calX$ is connected and contains at most
-$\frac{k}{\cmax}$ stars, it follows that $\abs{A(\calX)} \leq k$.
+It remains to consider a maximal component $\calT$ such that $\abs{M
+  \cap A(\calT)} > k$.  Since the number of edges in $S \in
+\calS(M^*)$ is at most $\cmax$, it must be that $\abs{V(\calT)} >
+\frac{k}{\cmax}$.
+%
+The maximum degree of $\calH$ is $\cmax(\cmax+1)$ by
+Lemma~\ref{lemma:maxdegH}, therefore due to Lemma~\ref{lemma:dec}
+(with $\ell = \frac{k}{\cmax^2(\cmax+1)}$) we can partition $\calT$
+into connected components each of which contains between
+$\frac{k}{\cmax^2(\cmax+1)}$ and $\frac{k}{\cmax}$ vertices.
+%
+Since each such vertex set $\calX$
+%is connected and
+contains at most $\frac{k}{\cmax}$ stars, it follows that
+$\abs{A(\calX)} \leq k$.
 %
@@
 \geq \half + \inv{2\cmax} - \frac{\cmax(\cmax+1)}{2k}
-~,
+~.
 \]
-and thus
+Since the set of maximal components in $\calH$ induces a partition of
+$M$, we have that
 \[
@@
 \]
-and the lemma follows.
+and 
+\[
+\abs{M}
+=    \sum_{\calT} \abs{M \cap A(\calT)}
+\geq \paren{ \half + \inv{2\cmax} - \frac{\cmax(\cmax+1)}{2k}}
+       \sum_{\calT} \abs{M^* \cap A(\calT)}
+=    \abs{M^*}
+~.
+\]
 \end{proof}
@@
 %In Appendix~\ref{sec:tight} we show that our analysis is tight.
+
+\iffalse %%%%% Removed
 
@@
 
+\fi %%%%% End removed
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Group Carpool}
-\label{sec:group}
-
-We now consider \gcp which a variant of \carpool in which
-%
-%in addition to the capacity function $c:V \to \N$, and the weight
-%function $w:A \to \R^+$, we also have
-we are given a size function $s:V \to \N$, and the constraint
-$\din[M](v) \leq c(v)$ is replaced with the constraint
-$\sum_{u:(u,v) \in M} s(u) \leq c(v)$.
-%
-%The motivation for this variant of the problem is when we want to
-%allow a group of people to travel together in the same car, thus $s$
-%is the size of the group.
-
-We start by showing that this variant of the problem does not fit the
-submodular maximization formulation as defined for \carpool.
-%
-Recall the submodular maximization formulation given in
-Section~\ref{sec:sub}, namely $\barw: 2^V \to \R$, where
-$\barw(S) \eqdf w(M(S))$ and $M(S)$ is the maximum weight carpool
-matching that satisfies $D_{M(S)} \subseteq S \subseteq V \setminus
-P_{M(S)}$.
-%
-Figure~\ref{fig:not submodular} contains an instance that shows that
-the function $\barw$ is not submodular anymore.
-
-\begin{figure}[t]
-\begin{center}
-\begin{tikzpicture}[every node/.style={default node}, ->]
-
-\node(1) at (-2,0){};
-\node(2) at (0,0){2};
-\node(3) at (2,0){};
-\node(4) at (0,2){};
-
-\draw (1) -- (2) node[label above]{1};
-\draw (3) -- (2) node[label above]{1};
-\draw (4) -- (2) node[label above]{2};
-
-\draw[dotted,green] 
-(1.west) to[out=90,in=90] node[label above] {A}
-(2.east) to[out=-90, in=-90]
-(1.west)
-;
-
-\draw[dashed,red] 
-(2.west) to[out=90,in=90] node[label above] {B}
-(3.east) to[out=-90, in=-90]
-(2.west)
-;
-
-\end{tikzpicture}
-\end{center}
-\caption{An unweighted \carpool instance.  Capacities are written
-  inside vertices, and arcs are labeled with their size.  We have that
-  $f(A) + f(B) = 2 < 3 = f(A \cup B) + f(A \cap B)$.}
-\label{fig:not submodular}
-\end{figure}
-
-We show, however, that \gcp has a $(\half -\eps)$-approximation
-algorithm by extending the local improvement algorithm from
-Section~\ref{sec:improve}.
-%
-The main concern when trying to adopt the algorithm to \gcp is how to
-determine if a vertex can be improved.
-%
-With \carpool, if weights are polynomially-bounded, it was enough to
-consider the incoming arcs to a vertex $v$ in a non-increasing
-order of $\delta_M$ (See proof of Theorem~\ref{thm:improve-bounded}).
-This does not work anymore, since in the \gcp we have sizes.  In fact, given
-$v$, finding the best star with respect to $\delta_M$ is
-a \textsc{Knapsack} instance where the size of the knapsack is $c(v)$.
-%
-If weights are polynomially-bounded, then $\delta_M(e)$ is bounded for
-every arc $e \in A$, and therefore this instance of \textsc{Knapsack}
-can be solved in polynomial time using dynamic programming.
-
-\begin{theorem}
-Algorithm~\textbf{StarImprove} is a $\half$-approximation algorithm
-for \gcp, if edge weights are integral and polynomially bounded.
-\end{theorem}
-
-Using standard scaling and rounding we obtain the following result.
-
-\begin{theorem}
-There exists a $(\half-\eps)$-approximation algorithm for \gcp,
-for every $\eps \in (0,\half)$.
-\end{theorem}
+%\section{Group Carpool}
+%\label{sec:group}
 
